### 2021-04-09 nsf/sections/description.tex
Add NIH template, move NSF template to new directory

\section{Project Description}

\subsection{Introduction}

Current attempts to characterize perceptual mechanism are limited in scope due to inefficiencies of a primary method used to characterize neural tuning, \emph{reverse correlation}.
Reverse correlation allows for unconstrained and unbiased estimation of latent neural representations using fairly simple stimulus-response data representations,
including psychophysical kernels that drive the top-down processes of perception (\eg face or phoneme recognition)
and even abstract psychological categories (\eg ``male'' vs ``female'' faces).
The method has broad applicability for characterizing any aspect of neurological, cognitive, or psychological function that can be modeled as a transductive process.

In reverse correlation, stimulus-response data are elicited via the presentation of richly-varying stimuli (\eg white noise).
Latent representations inherent in the system of interest can be estimated by regressing observed responses against the stimuli over many trials.
However, the number of stimulus-response samples required for accurate estimation is typically very large.
This inefficiency limits the feasibility of applying reverse correlation to only those experimental protocols that are very stable, such as \emph{in-vivo} preparations or where subject participation can be maintains over long timelines (\ie two weeks).
To circumvent this limitation, studies often (a) limit the richness of the stimuli, or (b) impose some constraints on the inferred representations,
for instance, by smoothing the raw estimates.
The constraints imposed by these approaches ultimately inhibit the full expressiveness of reverse correlation, leading to estiamtes that are biased.

We propose to develop an advanced signal processing pipeline based on \emph{compressive sensing} that will enable the research community to overcome the inefficiencies of existing reverse correlation methods.
Compressive sensing is a signal processing technique that can dramatically improve the efficiency of traditional sampling and signal estimation methods.
The technique has recently gained wide recognition in domains such as medical imaging,
where considerations of efficiency and bias reduction are critical.
Compressive sensing holds promise to similarly improve the efficiency of reverse correlation,
without the drawbacks of biasing estimates.
This will extend the range of experimental protocols that are feasible
as well as the range of perceptual mechanisms that can be estimated in correspondence with this technical improvements.
Moreover, compressive sensing can be directly substituted for conventional, regression-based estimation
with no other required changes to existing experimental protocols.

Latent representations, like many signals of interest, are compressible,
meaning that they can be represented as a linear combination of a small number of functions from an appropriately-selected basis set
(\ie $s = \Psi^T x$, for weights $s$, basis $\Psi$, and signal $x$).
A key insight of compressive sensing is that,
if one assumes that the responses stem from a process of comparing stimuli to the latent representation
(\ie $y = \Phi x$, for responses $y$ and measurement operation $\Phi$),
then it becomes possible to estimate the latent representation using only a small number of measurements
by acquiring the basis function representation directly
(\ie $y = \Phi \Psi s$) via sparse optimization approaches (to find $s$).
The responses can be continuous (\eg neural firing rates), ordinal similarity scores,
or binary (\ie yes/no).

\subsection{Proposed Study}

The objective of this work is to develop and validate a compressive sensing data processing pipeline,
culminating in an open-source software tool, that will allow for efficient and accurate reconstructions of latent representations using data obtained via the reverse correlation method.

\paragraph{Specific Aim \#1}

We will validate the proposed use of compressive sensing for relevant types of neural, cognitive, and behavioral data.
Validation will be accomplised through simulation studies, analysis of existing databases (\eg those available in \emph{Dryad}),
and through the collection of novel psychophysical data.
Outcomes will be assessed by examining estimation performance as a function of sample size,
including (a) reconstruction accuracy with few samples, (b) gains in high-sample reconstruction accuracy,
and (c) minimal sample size to achieve high-end convergent accuracy.
We will determine the optimal parameters for compressive sensing, which we expect to depend on the latent representation of interest, stimulus type, and response noise.
Considered parameters will include appropriate input/output representations, reconstruction algorithm, and basis type/sparsity.

\paragraph{Specific Aim \#2}

We will develop and distribute an open-source software implementation of the compressive sensing framework,
informed by the findings above, for use by the research community.
In order to make the platform maximally accessible, interfaces will be developed for widely-used, high-level programming languages
(including MATLAB, Python, R, and Julia) in addition to command-line executables.
Making the platform open-source provides opportunities for the community to better understand, customize, and improve the software for their own specific needs. \\ \\
\noindent
In sum, reverse correlation has the potential to uncover latent representations underlying
perception, and transform our understanding perceptual mechanisms at various levels of
investigation: neural, cognitive and psychological. However, in order for this potential to be fully
realized, the fundamental inefficiency of reverse correlation paradigms must be overcome.
Compressive sensing holds promise to overcome this limitation by dramatically improving the
efficiency of reverse correlation, enabling its extension to perceptual mechanisms that are out of
reach using current methods. The work proposed here will enable researchers to access the
promise of compressive sensing for broadening the impact of reverse correlation.

% The Project Description should provide a clear statement of the work to be undertaken and must include:
% objectives for the period of the proposed work and expected significance; relation to longer-term goals of the PI's
% project; and relation to the present state of knowledge in the field, to work in progress by the PI under other
% support and to work in progress elsewhere.

% The Project Description should outline the general plan of work, including the broad design of activities to be
% undertaken, and, where appropriate, provide a clear description of experimental methods and procedures.
% Proposers should address what they want to do, why they want to do it, how they plan to do it, how they will
% know if they succeed, and what benefits could accrue if the project is successful. The project activities may be
% based on previously established and/or innovative methods and approaches, but in either case must be well
% justified. These issues apply to both the technical aspects of the proposal and the way in which the project may
% make broader contributions.

\subsection{Broader Impacts of the Proposed Work}
The Project Description must contain, as a separate section within the narrative, a section labeled ``Broader
Impacts of the Proposed Work". This section should provide a discussion of the broader impacts of the proposed
activities. Broader impacts may be accomplished through the research itself, through the activities that are
directly related to specific research projects, or through activities that are supported by, but are complementary to 
the project. NSF values the advancement of scientific knowledge and activities that contribute to the
achievement of societally relevant outcomes. Such outcomes include, but are not limited to: full
participation of women, persons with disabilities, and underrepresented minorities in science, technology, engineering, and
mathematics (STEM); improved STEM education and educator development at any level; increased public
scientific literacy and public engagement with science and technology; improved well-being of individuals in
society; development of a diverse,globally competitive STEM workforce; increased partnerships between
academia, industry, and others; improved national security; increased economic competitiveness of the United
States; and enhanced infrastructure for research and education.

\subsection{Results from Prior NSF Support}
If any PI or co-PI identified on the project has received NSF funding (including any current
funding) in the past five years, in formation on the award(s) is required,
irrespective of whether the support was directly related to the proposal or not.
In cases where the PI or co-PI has received more than one award (excluding amendments),
they need only report on the one award most closely related to the proposal. Funding includes not just salary
support, but any funding awarded by NSF. The following information must be provided:\\

\noindent
\emph{\underline{Name of PI}}: NSF-Program (Award Number) ``Title of the Project'' (\$AMOUNT, PERIOD OF SUPPORT). 
{\bf Publications:} List of publications resulting from the NSF award. A complete bibliographic citation for each
publication must be provided either in this section or in the References Cited section of the proposal); if
none, state: ``No publications were produced under this award.'' {\bf Research Products:} evidence of research products 
and their availability, including, but not limited to: data, publications, samples, physical collections, software, 
and models, as described in any Data Management Plan.

### 2021-04-09 nih/specific_aims.tex
Add nih

% This example file for NIH submissions was originally written
% by Bruce Donald (http://www.cs.duke.edu/brd/).
% 
% You may freely use, modify and/or distribute this file.
% 
\documentclass[11pt]{nih}
%\documentclass{article}
%\documentclass[12pt]{article}%
% last revision:
\def\mydate{2005-06-09 13:58:03 brd}

%%%%%%% Two column control
\newif\ifdotwocol
\dotwocoltrue   % two col
%\dotwocolfalse   % one col
\long\def\twocol#1#2{\ifdotwocol{#1}\else{#2}\fi}
%%%%%%%

\def\mybeforeequation{\footnotesize}
%\def\mybeforeequation{\small}
%\def\mybeforeequation{}

\def\myafterequation{\renewcommand\baselinestretch{1.1}}
%\def\myafterequation{}

%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%

\def\citeusmark{$^{\textstyle \star}$}
\def\citeus#1#2{\cite{#1}}

\def\crow#1#2{#2}

%\usepackage{denselists}
%\usepackage{scaledfullpage}
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{boxedminipage}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{url}
%\usepackage{times}
%\usepackage{nih}		% PHS 398 Forms
%\usepackage{nihblank}		% For printing on Blank PHS 398 Forms
%\usepackage{confidential}

\def\Paper{grant application}
\def\paper{application}
\def\refappendix{Sec.}

\def\poster{(Poster)}

%Note from brd
\long\def\todo#1{{\bf{To do:}} #1}
%\long\def\todo#1{}
\def\ICRA{IEEE International Conference on Robotics and Automation (ICRA)}

\long\def\squeezable#1{#1}

%\def\a5{$\alpha_{_5}$

\def\a5{5}

%\def\mycaptionsize{\normalsize}
%\def\mycaptionsize{\small}
%\def\mycaptionsize{\small}
\def\mycaptionsize{\footnotesize}
\def\mycodesize{\footnotesize}
\def\myeqnsize{\small}

\def\sheading#1{{\bf #1:}\ }
\def\sheading#1{\subsubsection{#1}}
%\def\sheading#1{\bigskip {\bf #1.}}

\def\ssheading#1{\noindent {\bf #1.}\ }

\newtheorem{hypothesis}{Hypothesis}
\long\def\hyp#1{\begin{hypothesis} #1 \end{hypothesis}}

\def\cbk#1{[{\em #1}]}

\def\R{\mathbb{R}}
\def\midv{\mathop{\,|\,}}
\def\Fscr{\mathcal{F}}
\def\Gscr{\mathcal{G}}
\def\Sscr{\mathcal{S}}
\def\set#1{{\{#1\}}}
\def\edge{\!\rightarrow\!}
\def\dedge{\!\leftrightarrow\!}
\newcommand{\EOP}{\nolinebreak[1]~~~\hspace*{\fill} $\Box$\vspace*{\parskip}\vspace*{1ex}}
%my way of doing starred references
\newcommand{\mybibitem}[1]{\bibitem{#1} 
\label{mybiblabel:#1}}
\newcommand{\BC}{[}
\newcommand{\EC}{]}
\newcommand{\mycite}[1]{\ref{mybiblabel:#1}\nocite{#1}}
\newcommand{\starcite}[1]{\ref{mybiblabel:#1}\citeusmark\nocite{#1}}

\def\degree{$^\circ$}
\def\R{\mathbb{R}}
\def\Fscr{\mathcal{F}}
\def\set#1{{\{#1\}}}
\def\edge{\!\rightarrow\!}
\def\dedge{\!\leftrightarrow\!}

\long\def\gobble#1{}
\def\Jigsaw{{\sc Jigsaw}}
\def\ahelix{\ensuremath{\alpha}-helix}
\def\ahelices{\ensuremath{\alpha}-helices}
\def\ahelical{$\alpha$-helical}
\def\bstrand{\ensuremath{\beta}-strand}
\def\bstrands{\ensuremath{\beta}-strands}
\def\bsheet{\ensuremath{\beta}-sheet}
\def\bsheets{\ensuremath{\beta}-sheets}
\def\hone{{\ensuremath{^1}\rm{H}}}
\def\htwo{{$^{2}$H}}
\def\cthir{{\ensuremath{^{13}}\rm{C}}}
\def\nfif{{\ensuremath{^{15}}\rm{N}}}
\def\hn{{\rm{H}\ensuremath{^\mathrm{N}}}}
\def\hnone{{\textup{H}\ensuremath{^1_\mathrm{N}}}}
\def\ca{{\rm{C}\ensuremath{^\alpha}}}
\def\catwel{{\ensuremath{^{12}}\rm{C}\ensuremath{^\alpha}}}
\def\ha{{\rm{H}\ensuremath{^\alpha}}}
\def\cb{{\rm{C}\ensuremath{^\beta}}}
\def\hb{{\rm{H}\ensuremath{^\beta}}}
\def\hg{{\rm{H}\ensuremath{^\gamma}}}
\def\dnn{{\ensuremath{d_{\mathrm{NN}}}}}
\def\dan{{\ensuremath{d_{\alpha \mathrm{N}}}}}
\def\jconst{{\ensuremath{^{3}\mathrm{J}_{\mathrm{H}^{\mathrm{N}}\mathrm{H}^{\alpha}}}} }
\def\cbfb{{CBF-$\beta$}}

\newtheorem{defn}{Definition}
\newtheorem{claim}{Claim}

    \gobble{
    \psfrag{CO}[][]{\colorbox{white}{C}}
    \psfrag{OO}[][]{\colorbox{white}{O}}
    \psfrag{CA}[][]{\colorbox{white}{\ca}}
    \psfrag{HA}[][]{\colorbox{white}{\ha}}
    \psfrag{CB}[][]{\colorbox{white}{\cb}}
    \psfrag{HB}[][]{\colorbox{white}{\hb}}
    \psfrag{HN}[][]{\colorbox{white}{\hn}}
    \psfrag{N15}[][]{\colorbox{white}{\nfif}}
    \psfrag{dnn}[][]{\dnn}
    \psfrag{dan}[][]{\dan}
    \psfrag{phi}[][]{$\phi$}
    }

\newenvironment{closeenumerate}{\begin{list}{\arabic{enumi}.}{\topsep=0in\itemsep=0in\parsep=0in\usecounter{enumi}}}{\end{list}}
\def\CR{\hspace{0pt}}           % ``invisible'' space for line break

\newif\ifdbspacing
%\dbspacingtrue  % For double spacing
\dbspacingfalse  % For normal spacing

\ifdbspacing
 \doublespacing
 \newcommand{\capspacing}{\doublespace\mycaptionsize}
\else
 \newcommand{\capspacing}{\mycaptionsize}
\fi

\def\rulefigure{\smallskip\hrule}

% \def\codesize{\normalsize}
\def\codesize{\small}

% Can use macros \be, \ee, \en as shortcuts
%  for \begin{enumerate}, \end{enumerate}, \item
%  respectively.

\def\be{\begin{enumerate}}   % Begin Enumerate
\def\ee{\end{enumerate}}     % End Enumerate
\def\en{\item}               % ENtry (item)
\def\bi{\begin{itemize}}     % Begin Itemize
\def\ei{\end{itemize}}       % End Itemize
\def\bv{\begin{verbatim}}    % Begin Verbatim
\def\ev{\end{verbatim}}      % End Verbatim

\def\matlab{{\sc matlab} }
\def\amber{{\sc amber} }
\def\KS{{$K^*$}}
\def\KSM{{K^*}} % K-Star Math
\def\KSTM{{\tilde{K}^*}}  % K-Star Tilde Math (appx K*)
\def\KOP{{$K^{\dagger}_{o}$}}  % K-Star Optimal partial
\def\KOPM{{K^{\dagger}_{o}}}  % K-Star Optimal partial Math
\def\KP{{$K^{\dagger}$}}  % K-Star partial
\def\KPM{{K^{\dagger}}}  % K-Star partial Math
\def\KTPM{{\tilde{K}^{\dagger}}}  % K-Star Tilde partial Math
\def\KD{{$K_{_D}$}}
\def\KA{{$K_{_A}$}}
\def\qpM{{q_{_P}}}
\def\qlM{{q_{_L}}}
\def\qplM{{q_{_{PL}}}}
\def\qSplM{{q^*_{_{PL}}}}
\def\KSO{{$K^*_{o}$}} % K-Star Optimal
\def\KSOM{{K^*_{o}}}  % K-Star Optimal Math
\def\CBFB{{CBF-$\beta$}}   % Core binding factor beta
\def\argmin{\mathop{\mathrm{argmin}}}
\def\rhl#1{{\em \underline{RYAN}: *\{{#1}\}*}}
\def\set#1{{\left\{ #1 \right\}}}
\def\Escr{{\mathcal{E}}}
\def\Jscr{{\mathcal{J}}}
\def\Kscr{{\mathcal{K}}}
\def\th{{$^{{\mathrm{th}}}$}}

\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}

\def\eg{{\emph{e.g.,}}~}
\def\ie{{\emph{i.e.,}}~}

\begin{document}

\bigskip

\appendix

%\mydate

\setcounter{page}{20} % or whatever

%\noindent{\Large\bf Research Plan}

\section{Specific Aims}

Tinnitus is the superstitious perception of ringing, buzzing, or hissing in the ears, which can range from mild and transient to debilitating.
In the U.S. alone, it affects 45 million people per year, 30\% of which report their tinnitus to be moderate to severe.
The main treatment is tinnitus retraining therapy (TRT),
a type of habituation therapy that retrains a patient's nervous system by habituating it to non-fictive sounds that mimic the cognitive representation of the tinnitus sound.
TRT requires the medical practitioner to identify an estimate of the tinnitus sound and play it back for the patient.
In practice, this is inexact and inefficient.

Reverse correlation involves the presentation of richly-varying stimuli (\eg white noise) to a subject,
gathering responses of whether the subject perceives in any stimulus a percept corresponding to some abstract, cognitive category (\eg does this sound like your tinnitus?).
Stimuli are random and unbiased, relying on few prior assumptions about the form of the representation.
Regressing observed variables against the stimuli results in inferred cognitive representations.
Indeed, the number of features
recoverable using reverse correlation is effectively unlimited, and only constrained by broad
assumptions of the method (\eg linearity). Higher-dimensional characterization of perceptual
representations may help resolve many ambiguities inherent to lower-dimensional characterizations by
supplying additional information necessary to distinguish between representations from different subjects.

We have constructed a data processing pipeline using reverse correlation to infer unbiased estimates of cognitive representations of visual stimuli (\eg letters, faces) and phonological sounds (\eg /ee/).
In the proposed work, we aim to directly uncover and reconstruct estimates of cognitive representations of tinnitus percepts using reverse correlation,
improve the efficiency of reverse correlation through signal reconstruction,
and characterize cognitive representations of tinnitus for use in diagnosis and treatment.
This will result in an open-source software tool that efficiently constructs unbiased cognitive representations of tinnitus percepts
and insight into subject-to-subject and longitudinal variability in tinnitus self-experience to improve diagnosis and treatment.

\subsection{Uncover and reconstruct cognitive representations of tinnitus}
Participants will classify white noise stimuli as sounding like their tinnitus or not.
We will use reverse correlation to infer an unbiased estimate of each particpant's cognitive representation of their tinnitus percept.

\subsection{Develop efficient reconstruction algorithm for cognitive representations using compressive sensing}
We will develop an open-source compressive sensing data analysis pipeline to acquire convergent cognitive representations using fewer trials.
Our pilot data demonstrates that compressive sensing affords a 90\% decrease in number of trials for equivalent resulant latent representation.
We will also develop and distribute an open-source software
implementation the of the reverse correlation method for speech perception, including the proposed
compressive sensing framework, for use by the research community.

\subsection{Characterize and interpret cognitive representations of tinnitus}
Our compressive sensing framework will allow for rapid data acquisition from participants.
We will characterize cognitive representations of tinnitus between participants and over time.
What is the space of tinnitus cognitive representations? Are there subtypes or clusters on a lower dimensional manifold?
We will employ dimensionality reduction and clustering algorithms to represent and visualize the data,
providing direct insight into commonalities and variability of tinnitus experience in and between subjects.

\end{document}

### 2021-04-17 nih/specific_aims.tex
Revise specific aims

@@
 
+The objective of this proposal is to reveal and analyze cognitive representation of tinnitus percepts
+through a novel compressive sensing-based reverse correlation framework.
+
 Tinnitus is the superstitious perception of ringing, buzzing, or hissing in the ears, which can range from mild and transient to debilitating.
@@
 
+Our long-term goal is to efficiently uncover effective representations of tinnitus percepts to inform diagnosis and treatment
+and to explain variability in tinnitus experience.
+Our guiding hypothesis is that reverse correlation will produce individualized, unbiased, high-dimensional cognitive representations of tinnitus percepts
+and that we can optimize reverse correlation to require fewer samples using signal reconstruction techniques.
+[RATIONALE]
+We will test our central hypothesis and attain our objective via the following specific aims:
+
 \subsection{Uncover and reconstruct cognitive representations of tinnitus}

### 2021-04-21 nih2/NIHGrant.tex
Add significant changes to Significance

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% NIH Grant Proposal for the Specific Aims and Research Plan Sections
% LaTeX Template
% Version 1.1 (26/12/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Erick Tatro (erickttr@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% Adapted from:
% J. Hrabe (http://www.magalien.com/public/nih_grants_in_latex.html)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, notitlepage]{article} % Default font size and suppress title page

% \usepackage[utf8]{inputenc} % Required for inputting international characters
% \usepackage[T1]{fontenc} % Output font encoding for international characters
% A note on fonts: As of 2019, NIH allows Arial, Georgia, Helvetica, and Palatino Linotype. Georgia and Arial are commercial fonts so you will need to use XeLaTeX and have them installed on your machine to use them. Palatino & Helvetica are available as free LaTeX packages so select the one you want and comment out the other.
\usepackage{palatino} % Palatino font
\linespread{1.05} % A little extra line spread is better for the Palatino font
%\usepackage{helvet} % Helvetica font
\renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font

\usepackage{amsfonts, amsmath, amsthm, amssymb} % For math fonts, symbols and environments
\usepackage{graphicx} % Required for including images
\usepackage{booktabs} % Nice rules in tables
\usepackage{wrapfig} % Required for text to wrap around figures and tables
\usepackage[labelfont=bf]{caption} % Make figure numbering in captions bold
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry} % Page margins
\usepackage[style=numeric, sorting=nyt]{biblatex}
\pagestyle{empty} % Suppress headers and footers

\hyphenation{ionto-pho-re-tic iso-tro-pic fortran} % Specifies custom hyphenation points for words or words that shouldn't be hyphenated at all

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	SPECIFIC AIMS
%----------------------------------------------------------------------------------------

\section*{Specific Aims}

This is an example citation \cite{baraniukCompressiveSensingLecture2007}. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Praesent porttitor arcu luctus, imperdiet urna iaculis, mattis eros. Pellentesque iaculis odio vel nisl ullamcorper, nec faucibus ipsum molestie. Sed dictum nisl non aliquet porttitor. Etiam vulputate arcu dignissim, finibus sem et, viverra nisl. Aenean luctus congue massa, ut laoreet metus ornare in. Nunc fermentum nisi imperdiet lectus tincidunt vestibulum at ac elit. Nulla mattis nisl eu malesuada suscipit.

Aliquam arcu turpis, ultrices sed luctus ac, vehicula id metus. Morbi eu feugiat velit, et tempus augue. Proin ac mattis tortor. Donec tincidunt, ante rhoncus luctus semper, arcu lorem lobortis justo, nec convallis ante quam quis lectus. Aenean tincidunt sodales massa, et hendrerit tellus mattis ac. Sed non pretium nibh. Donec cursus maximus luctus. Vivamus lobortis eros et massa porta porttitor.

Fusce varius orci ac magna dapibus porttitor. In tempor leo a neque bibendum sollicitudin. Nulla pretium fermentum nisi, eget sodales magna facilisis eu. Praesent aliquet nulla ut bibendum lacinia. Donec vel mauris vulputate, commodo ligula ut, egestas orci. Suspendisse commodo odio sed hendrerit lobortis. Donec finibus eros erat, vel ornare enim mattis et. Donec finibus dolor quis dolor tempus consequat. Mauris fringilla dui id libero egestas, ut mattis neque ornare. Ut condimentum urna pharetra ipsum consequat, eu interdum elit cursus. Vivamus scelerisque tortor et nunc ultricies, id tincidunt libero pharetra. Aliquam eu imperdiet leo. Morbi a massa volutpat velit condimentum convallis et facilisis dolor.

\begin{description}
	\item[Aim 1: Really cool stuff.]{}
	\item{1.1. First sub-aim with more details}
	\item{1.2. Second sub-aim with more details.}  
\end{description}

\begin{description}
	\item[Aim 2: Really cool stuff.]{}
	\item{2.1. First sub-aim with more details.}
	\item{2.2. Second sub-aim with more details.}
\end{description}

\begin{description}
	\item[Aim 3: Really cool stuff.]{ }
	\item{3.1. First sub-aim with more details.}
	\item {3.2. Second sub-aim with more details.}
	\item{3.3. Third sub-aim with more details.}
\end{description}

In hac habitasse platea dictumst. Curabitur mattis elit sit amet justo luctus vestibulum. In hac habitasse platea dictumst. Pellentesque lobortis justo enim, a condimentum massa tempor eu. Ut quis nulla a quam pretium eleifend nec eu nisl. Nam cursus porttitor eros, sed luctus ligula convallis quis. Nam convallis, ligula in auctor euismod, ligula mauris fringilla tellus, et egestas mauris odio eget diam. Praesent sodales in ipsum eu dictum.

%----------------------------------------------------------------------------------------
%	SIGNIFICANCE
%----------------------------------------------------------------------------------------

\newpage

\section*{A. Significance}

\begin{description} % For subheadings within a section, this template uses the {description} environment, it is not obtrusively large like a \subsection; and facilitates a brief optional subtitle; and it will wrap around figures and tables; it also has a decent amount of whitespace above/below which is less than for a section heading
	\item[A.1. Instructions.]{Optional subtitle}
\end{description}

Explain the importance of the problem or critical barrier to progress in the field that the proposed project addresses.

Explain how the proposed project will improve scientific knowledge, technical capability, and/or clinical practice in one or more broad fields.

Describe how the concepts, methods, technologies, treatments, services, or preventative interventions that drive this field will be changed if the proposed aims are achieved.

\begin{description}
	\item[A.2. Subheading.]{}
\end{description}

Tinnitus, the perception of ringing, buzzing, or hissing in the ears when no external sound is present,
is a health condition estimated to affect 10-15\% of adults worldwide \cite{henryTinnitusEpidemiologicPerspective2020}.
The condition is highly heterogeneous and can range from mild and transient to debilitating and constant.
In the U.S., tinnitus affects approximately one in ten Americans, with 7.2\% of those rating their tinnitus as severe (\cite{bhattPrevalenceSeverityExposures2016}.
Tinnitus can be perceived unilaterally or bilaterally and may differ over time, even within individuals.
This heterogeneity in characterization has important implications for research
and clinical practice.
Identifying patterns in how tinnitus sounds and its relationship to hearing may aid in identifying
different forms of tinnitus and revealing their underlying mechanisms.
However, the subjective nature of characterizing tinnitus makes it difficult
to reliably define and measure \cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}.

Current methods to determine cognitive representations of tinnitus
are inefficient and introduce bias, resulting in a lack of standardization in tinnitus assessment \cite{henryTinnitusEpidemiologicPerspective2020}.
Alternate forced-choice (AFC) paradigm tasks ask the patient to determine which of two sounds
is closer to their tinnitus percept \cite{henryComparisonTwoComputerautomated2001,henryComputerautomatedTinnitusAssessment2004,henryComputerautomatedTinnitusAssessment2013,korthOneStepCloser2020}.
Recent computer and methodological advances have made the test more portable and efficient,
but the AFC paradigm still relies on assumptions about the subject's tinnitus percept.
Tinnitus percepts are too heterogeneous to be represented by pure tones or small-envelope waveforms.
Adequately sampling the psychoacoustic space of possible tinnitus percepts via an AFC task is unfeasible.
Other approaches have attempted to capture the richness of tinnitus percepts using likeness measures,
in which the subject rates whether a presented stimulus is part of their tinnitus percept or not \cite{norenaPsychoacousticCharacterizationTinnitus2002}.
While this method is able to capture more features of cognitive representations of tinnitus,
it is time-consuming and limited by the aural skills of the subject \cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}.
Both these approaches involve the subject comparing an external stimulus to their cognitive representation of the tinnitus percept,
however AFC tasks introduce biases by artificially limiting the stimulus space and likeness measures are time-consuming.

\emph{We believe that a novel reverse correlation-based approach will produce efficient and unbiased cognitive representations of tinnitus percepts}
\cite{gosselinSuperstitiousPerceptionsReveal2003}.
Reverse correlation allows for unconstrained and unbiased
characterization of latent representations directly from stimulus-response data by eliciting responses to
richly varying stimuli, such as white noise (Marmarelis \& Marmarelis, 1978; Nishimoto et al., 2006). Richstimuli, by virtue of the fact that they are inherently vague, force the top-down process to exert a clearly
measurable influence on responses. Latent representations that drive the top-down process can then be
estimated by regressing observed responses against the stimuli over many trials (Mineault et al., 2009).
Reverse correlation, as a method, is powerful enough to characterize any aspect of neurological,
cognitive or psychological function that can be modeled as a transductive process (Ringach, 2004). It has
become a primary method used to characterize the latent representations encapsulated in neural tuning
(e.g., receptive fields; Ringach, 2004), and is closely related to the widely-used “white noise approach” to
characterizing physiological (Marmarelis \& Marmarelis, 1978) and engineering (Ljung, 1999) systems.

Reverse correlation, in addition to its prominence as an important tool relative to lower-level
neural mechanisms, has been increasingly used for inferring higher-level cognitive representations,
including psychophysical kernels that drive the top-down processes of perception (Ahumada \& Lovell,
1971; Gosselin \& Schyns, 2003; Neri \& Levi, 2006; Smith et al., 2012), and even abstract psychological
categories (e.g., “male” vs. “female” faces; Brinkman et al., 2017; Mangini \& Biederman, 2004; Ponsot et
al., 2018). Recent work in vision (e.g., Gosselin \& Schyns, 2003; Liu et al., 2014) has demonstrated that
reverse correlation can effectively characterize cognitive representations underlying letter and face
recognition (Fig 2A). One speech study has also estimated steady-state representations of vowels the /a/
and /i/ using a closely-related paradigm to the one proposed here (Fig 2B; Brimijoin et al., 2013). Our
proposed use of reverse correlation in the domain of speech expands on classic efforts to understand
top-down processing in speech with the presentation of rich, vague stimuli to elicit responses from
listeners (Warren \& Warren, 1970; Vokey \& Read 1985). These studies provide clear evidence that rich
stimuli, such as white noise, are sufficient to engage the top-down process, even if they do not attempt to
characterize the latent representations.

Incomplete characterizations of cognitive representations impoverish our scientific understanding of tinnitus,
weak causal explanations for its etiology, and hinder progress towards effective treatments.
Reverse correlation shows promise to provide a more complete characterization of cognitive representations of tinnitus
and is applicable to other psychophysical domains as well.
Directly characterizing complex representations of tinnitus can enable more effective, targeted treatments,
reveal insights about subtypes of the condition, and pave the way for new tinnitus-masking assistive devices.
Fully characterizing a high-dimensional representation of tinnitus will improve causal explanations
for currently unexplained variability in tinnitus experience both between subjects and within single subjects over time.

\begin{description}
	\item[A.3. Rigor of the Prior Research]{}
\end{description}

\emph{The premise of the proposed work is that reverse correlation will deliver unbiased estimates
of cognitive representations of tinnitus. Furthermore, that compressive sensing will dramatically
increase the efficiency of experiments, resulting in convergent cognitive representations
in a fraction of the samples.}

The evidence for this premise is first based on well-established studies using reverse correlation
to derive cognitive representations of sounds and symbols.
Reverse correlation has been applied to infer cognitive representations from letters
\cite{gosselinSuperstitiousPerceptionsReveal2003}, vowel sounds \cite{brimijoinInternalRepresentationVowel2013},
and faces \cite{brinkmanVisualisingMentalRepresentations2017,smithMeasuringInternalRepresentations2012}.
More broadly, it has been applied to infer the shape of receptive fields
in linear transducers and spiking neurons \cite{ringachReverseCorrelationNeurophysiology2004}.
The reverse correlation paradigm makes minimal assumptions about the derived cognitive representation
since the subject is presented with high-dimensional random input.
A large number of stimulus-response samples are typically required for accurate
reconstruction of cognitive representations using conventional techniques. To address this inefficiency,
studies often limit the richness of stimuli, or impose strict constraints on the reconstructions, leading to
estimates that are biased or incomplete. However, recent advances in signal processing, most notably
a techniques known as compressive sensing, are leading to dramatic improvements the efficiency of
traditional sampling.

We propose to develop an advanced signal processing pipeline that will enable us to overcome
the inefficiencies of existing reverse correlation methods through the use of compressive sensing, a
recent advance in signal processing which has led to dramatic improvements the efficiency of traditional
sampling and signal estimation methods (Baraniuk, 2007). Compressive sensing has recently gained
wide recognition in domains such as medical imaging (Graff \& Sidky, 2015; Lustig et al., 2008), where
considerations of efficiency and bias reduction are critical. Compressive sensing holds promise to
similarly improve the efficiency of reverse correlation, without the drawback of biasing estimates. By
dramatically decreasing the number of trials needed for signal reconstruction, this technique will extend
the range of perceptual mechanisms that can be estimated. Moreover, compressive sensing can be
directly substituted for conventional, regression-based estimation, with no other required changes to
existing experimental protocols. Our ultimate objective is to develop and validate a compressive sensing
data processing pipeline - culminating in an open-source software tool – that will allow for efficient and
accurate reconstruction of latent representations using data obtained via the reverse correlation method.

\begin{wraptable}{l}{5.5cm} % Example table with text wrapping around it
	\caption{Example Table}
	\begin{center}
		\begin{tabular}{l l r}
			\toprule
			\multicolumn{1}{c}{City} & {N\textsuperscript{a}} & {\%Silly}\\
			\midrule
			San Diego & 289 & 41\%\\
			Seattle & 262 & 32\%\\
			Galveston & 261 & 15\%\\
			St Louis & 269 & 7\%\\
			New York & 271 & 4\%\\
			Baltimore & 231 & 2\%\\
			\emph{Total} & 1,586 & 21\%\\
			\hline 
		\end{tabular}\\
		\footnotesize\textsuperscript{a}{All participants clowns.}
	\end{center}
	\label{tab:example}
\end{wraptable}

Referencing a table using it's label: Table \ref{tab:example}. Maecenas consectetur metus at tellus finibus condimentum. Proin arcu lectus, ultrices non tincidunt et, tincidunt ut quam. Integer luctus posuere est, non maximus ante dignissim quis. Nunc a cursus erat. Curabitur suscipit nibh in tincidunt sagittis. Nam malesuada vestibulum quam id gravida. Proin ut dapibus velit. Vestibulum eget quam quis ipsum semper convallis. Duis consectetur nibh ac diam dignissim, id condimentum enim dictum. Nam aliquet ligula eu magna pellentesque, nec sagittis leo lobortis. Aenean tincidunt dignissim egestas. Morbi efficitur risus ante, id tincidunt odio pulvinar vitae. Proin ut dapibus velit. Vestibulum eget quam quis ipsum semper convallis. Duis consectetur nibh ac diam dignissim, id condimentum enim dictum.

Curabitur tempus hendrerit nulla. Donec faucibus lobortis nibh pharetra sagittis. Sed magna sem, posuere eget sem vitae, finibus consequat libero. Cras aliquet sagittis erat ut semper. Aenean vel enim ipsum. Fusce ut felis at eros sagittis bibendum mollis lobortis libero. Donec laoreet nisl vel risus lacinia elementum non nec lacus. Nullam luctus, nulla volutpat ultricies ultrices, quam massa placerat augue, ut fringilla urna lectus nec nibh. Vestibulum efficitur condimentum orci a semper. Pellentesque ut metus pretium lacus maximus semper. Sed tellus augue, consectetur rhoncus eleifend vel, imperdiet nec turpis. Nulla ligula ante, malesuada quis orci a, ultricies blandit elit.

In malesuada ullamcorper urna, sed dapibus diam sollicitudin non. Donec elit odio, accumsan ac nisl a, tempor imperdiet eros. Donec porta tortor eu risus consequat, a pharetra tortor tristique. Morbi sit amet laoreet erat. Morbi et luctus diam, quis porta ipsum. Quisque libero dolor, suscipit id facilisis eget, sodales volutpat dolor. Nullam vulputate interdum aliquam. Mauris id convallis erat, ut vehicula neque. Sed auctor nibh et elit fringilla, nec ultricies dui sollicitudin.

\begin{wrapfigure}{r}{8.5cm} % Example figure with text wrapping around it
	\includegraphics[width=8.2cm]{Figures/Fig1.jpg}
	\caption{\footnotesize Example wrapped figure. (A) Impressive microscopy image. (B) Impressive data.}
	\label{fig:example}
\end{wrapfigure}

Referencing a figure using it's label: Figure \ref{fig:example}. Proin lobortis efficitur dictum. Pellentesque vitae pharetra eros, quis dignissim magna. Sed tellus leo, semper non vestibulum vel, tincidunt eu mi. Aenean pretium ut velit sed facilisis. Ut placerat urna facilisis dolor suscipit vehicula. Ut ut auctor nunc. Nulla non massa eros. Proin rhoncus arcu odio, eu lobortis metus sollicitudin eu. Duis maximus ex dui, id bibendum diam dignissim id. Aliquam quis lorem lorem. Phasellus sagittis aliquet dolor, vulputate cursus dolor convallis vel. Suspendisse eu tellus feugiat, bibendum lectus quis, fermentum nunc. Nunc euismod condimentum magna nec bibendum. Curabitur elementum nibh eu sem cursus, eu aliquam leo rutrum. Sed bibendum augue sit amet pharetra ullamcorper. Aenean congue sit amet tortor vitae feugiat. Vestibulum vestibulum luctus metus venenatis facilisis. Suspendisse iaculis augue at vehicula ornare. Sed vel eros ut velit fermentum porttitor sed sed massa. Fusce venenatis, metus a rutrum sagittis, enim ex maximus velit, id semper nisi velit eu purus.

\begin{description}
	\item[A.3. Another subheading:]{optional subtitle.}
\end{description}

In congue risus leo, in gravida enim viverra id. Donec eros mauris, bibendum vel dui at, tempor commodo augue. In vel lobortis lacus. Nam ornare ullamcorper mauris vel molestie. Maecenas vehicula ornare turpis, vitae fringilla orci consectetur vel. Nam pulvinar justo nec neque egestas tristique. Donec ac dolor at libero congue varius sed vitae lectus. Donec et tristique nulla, sit amet scelerisque orci. Maecenas a vestibulum lectus, vitae gravida nulla. Proin eget volutpat orci. Morbi eu aliquet turpis. Vivamus molestie urna quis tempor tristique. Proin hendrerit sem nec tempor sollicitudin.

\begin{figure}[b] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
	\centering
	\includegraphics[scale = .80]{Figures/Fig2.pdf}
	\caption{\footnotesize Big Figure legend Big Figure legend Big Figure legend Big Figure legend Big Figure legend Big Figure legend Big Figure legend Big Figure legend Big Figure legend.}
	\label{fig2}
\end{figure}

Fusce eleifend porttitor arcu, id accumsan elit pharetra eget. Mauris luctus velit sit amet est sodales rhoncus. Donec cursus suscipit justo, sed tristique ipsum fermentum nec. Ut tortor ex, ullamcorper varius congue in, efficitur a tellus. Vivamus ut rutrum nisi. Phasellus sit amet enim efficitur, aliquam nulla id, lacinia mauris. Quisque viverra libero ac magna maximus efficitur. Interdum et malesuada fames ac ante ipsum primis in faucibus. Vestibulum mollis eros in tellus fermentum, vitae tristique justo finibus. Sed quis vehicula nibh. Etiam nulla justo, pellentesque id sapien at, semper aliquam arcu. Integer at commodo arcu. Quisque dapibus ut lacus eget vulputate.

Vestibulum sodales orci a nisi interdum tristique. In dictum vehicula dui, eget bibendum purus elementum eu. Pellentesque lobortis mattis mauris, non feugiat dolor vulputate a. Cras porttitor dapibus lacus at pulvinar. Praesent eu nunc et libero porttitor malesuada tempus quis massa. Aenean cursus ipsum a velit ultricies sagittis. Sed non leo ullamcorper, suscipit massa ut, pulvinar erat. Aliquam erat volutpat. Nulla non lacus vitae mi placerat tincidunt et ac diam. Aliquam tincidunt augue sem, ut vestibulum est volutpat eget. Suspendisse potenti. Integer condimentum, risus nec maximus elementum, lacus purus porta arcu, at ultrices diam nisl eget urna. Curabitur sollicitudin diam quis sollicitudin varius. Ut porta erat ornare laoreet euismod. In tincidunt purus dui, nec egestas dui convallis non. In vestibulum ipsum in dictum scelerisque.

\begin{description}
	\item[A.4. Yet another subheading.]{}
\end{description}

Aenean feugiat pellentesque venenatis. Sed faucibus tristique tortor vel ultrices. Donec consequat tellus sapien. Nam bibendum urna mauris, eget sagittis justo gravida vel. Mauris nisi lacus, malesuada sit amet neque ut, venenatis tempor orci. Curabitur feugiat sagittis molestie. Duis euismod arcu vitae quam scelerisque facilisis. Praesent volutpat eleifend tortor, in malesuada dui egestas id. Donec finibus ac risus sed pellentesque. Donec malesuada non magna nec feugiat. Mauris eget nibh nec orci congue porttitor vitae eu erat. Sed commodo ipsum ipsum, in elementum neque gravida euismod. Cras mi lacus, pulvinar ut sapien ut, rutrum sagittis dui. Donec non est a metus varius finibus. Pellentesque rutrum pellentesque ligula, vitae accumsan nulla hendrerit ut.

In mi mauris, finibus non faucibus non, imperdiet nec leo. In erat arcu, tincidunt nec aliquam et, volutpat eget nisl. Vivamus id eros scelerisque est condimentum condimentum at at ligula. Proin blandit sapien ac bibendum faucibus. Nunc sem elit, blandit in lectus vitae, lacinia hendrerit risus. Donec efficitur elementum massa, eget interdum nunc porttitor sed. Aenean porttitor gravida nibh, vel bibendum tellus. Nunc fermentum lobortis nunc. Cras aliquet odio mauris, eget lobortis metus lacinia sit amet. Maecenas id elit eu orci ornare ultricies. Sed consequat turpis id accumsan malesuada. Fusce varius imperdiet ex, vel sodales purus scelerisque id. Morbi ut tellus interdum, laoreet leo non, dignissim odio. Nunc vel quam diam. Sed eu tortor in dolor mattis rhoncus.

%----------------------------------------------------------------------------------------
%	INNOVATION
%----------------------------------------------------------------------------------------

\section*{B. Innovation}

\begin{description}
	\item[B.1. Instructions.]{}
\end{description}

Explain how the application challenges and seeks to shift current research or clinical practice paradigms.

Describe any novel theoretical concepts, approaches or methodologies, instrumentation or interventions to be developed or used, and any advantage over existing methodologies, instrumentation, or interventions.

Explain any refinements, improvements, or new applications of theoretical concepts, approaches or methodologies, instrumentation, or interventions.

%----------------------------------------------------------------------------------------
%	APPROACH
%----------------------------------------------------------------------------------------

\section*{C. Approach}

\begin{description}
	\item[C.1. Instructions.]{}
\end{description}

Describe the overall strategy, methodology, and analyses to be used to accomplish the specific aims of the project. Unless addressed separately in Item 15 (Resource Sharing Plan), include how the data will be collected, analyzed, and interpreted as well as any resource sharing plans as appropriate.

Discuss potential problems, alternative strategies, and benchmarks for success anticipated to achieve the aims.

If the project is in the early stages of development, describe any strategy to establish feasibility, and address the management of any high risk aspects of the proposed work.

Point out any procedures, situations, or materials that may be hazardous to personnel and precautions to be exercised. A full discussion on the use of Select Agents should appear in Item 11, below.

As applicable, also include the following information as part of the Research Strategy, keeping within the three sections listed above: Significance, Innovation, and Approach.

\begin{description}
	\item[C.2. Preliminary Studies for New Applications]{}
\end{description}

Preliminary Studies for New Applications: For new applications, include information on Preliminary Studies. Discuss the PD/PI's preliminary studies, data, and or experience pertinent to this application. Except for Exploratory/Developmental Grants (R21/R33), Small Research Grants (R03), and Academic Research Enhancement Award (AREA) Grants (R15), preliminary data can be an essential part of a research grant application and help to establish the likelihood of success of the proposed project. Early Stage Investigators should include preliminary data (however, for R01 applications, reviewers will be instructed to place less emphasis on the preliminary data in application from Early Stage Investigators than on the preliminary data in applications from more established investigators).

%----------------------------------------------------------------------------------------
%	PROGRESS REPORT
%----------------------------------------------------------------------------------------

\newpage

\section*{5. Progress Report Publication List (Renewal Applications Only)}

List the titles and complete references to all appropriate publications, manuscripts accepted for publication, patents, and other printed materials that have resulted from the project since it was last reviewed competitively. When citing articles that fall under the Public Access Policy, were authored or co-authored by the applicant and arose from NIH support, provide the NIH Manuscript Submission reference number (e.g., NIHMS97531) or the Pubmed Central (PMC) reference number (e.g., PMCID234567) for each article. If the PMCID is not yet available because the Journal submits articles directly to PMC on behalf of their authors, indicate "PMC Journal -- In Process." A list of these journals is posted at: http://publicaccess.nih.gov/submit\_process\_journals.htm.

Citations that are not covered by the Public Access Policy, but are publicly available in a free, online format may include URLs or PMCID numbers along with the full reference (note that copies of these publications are not accepted as appendix material, see Part I Section 5.5.15 for more information).

%----------------------------------------------------------------------------------------
%	PROTECTION OF HUMAN SUBJECTS
%----------------------------------------------------------------------------------------

\newpage

\section*{6. Protection of Human Subjects}

Refer to Part II, Supplemental Instructions for Preparing the Human Subjects Section of the Research Plan.

This section is required for applicants answering "yes" to the question "Are human subjects involved?" on the R\&R Other Project Information form. If the answer is "No" to the question but the proposed research involves human specimens and/or data from subjects applicants must provide a justification in this section for the claim that no human subjects are involved.

Do not use the protection of human subjects section to circumvent the page limits of the Research Strategy.

%----------------------------------------------------------------------------------------
%	INCLUSION OF WOMEN AND MINORITIES
%----------------------------------------------------------------------------------------

\newpage

\section*{7. Inclusion of Women and Minorities}

Refer to Part II, Supplemental Instructions for Preparing the Human Subjects Section of the Research Plan. This section is required for applicants answering "yes" to the question "Are human subjects involved?" on the R\&R Other Project Information form and the research does not fall under Exemption 4.

%----------------------------------------------------------------------------------------
%	INCLUSION OF CHILDREN
%----------------------------------------------------------------------------------------

\newpage

%\section*{8. Targeted/Planned Enrollment} - form to fill out 
\section*{9. Inclusion of Children}

Refer to Supplemental Instructions for Preparing the Human Subjects Section of the Research Plan, Sections 4.4 and 5.7. For applicants answering "Yes" to the question "Are human subjects involved" on the R\&R Other Project Information Form and the research does not fall under Section 4, this section is required.

%----------------------------------------------------------------------------------------
%	VERTEBRATE ANIMALS
%----------------------------------------------------------------------------------------

\newpage

\section*{10. Vertebrate Animals}

If Vertebrate Animals are involved in the project, address each of the five points below. This section should be a concise, complete description of the animals and proposed procedures. While additional details may be included in the Research Strategy, the responses to the five required points below must be cohesive and include sufficient detail to allow evaluation by peer reviewers and NIH staff. If all or part of the proposed research involving vertebrate animals will take place at alternate sites (such as project/performance or collaborating site(s)), identify those sites and describe the activities at those locations. Although no specific page limitation applies to this section of the application, be succinct. Failure to address the following five points will result in the application being designated as incomplete and will be grounds for the PHS to defer the application from the peer review round. Alternatively, the application’s impact/priority score may be negatively affected.

If the involvement of animals is indefinite, provide an explanation and indicate when it is anticipated that animals will be used. If an award is made, prior to the involvement of animals the grantee must submit to the NIH awarding office detailed information as required in points 1-5 above and verification of IACUC approval. If the grantee does not have an Animal Welfare Assurance then an appropriate Assurance will be required (See Part III, Section 2.2 Vertebrate Animals for more information).
The five points are as follows:

\begin{enumerate}
	\item Provide a detailed description of the proposed use of the animals in the work outlined in the Research Strategy section. Identify the species, strains, ages, sex, and numbers of animals to be used in the proposed work.
	\item Justify the use of animals, the choice of species, and the numbers to be used. If animals are in short supply, costly, or to be used in large numbers, provide an additional rationale for their selection and numbers.
	\item Provide information on the veterinary care of the animals involved.
	\item Describe the procedures for ensuring that discomfort, distress, pain, and injury will be limited to that which is unavoidable in the conduct of scientifically sound research. Describe the use of analgesic, anesthetic, and tranquilizing drugs and/or comfortable restraining devices, where appropriate, to minimize discomfort, distress, pain, and injury.
	\item Describe any method of euthanasia to be used and the reasons for its selection. State whether this method is consistent with the recommendations of the American Veterinary Medical Association (AVMA) Guidelines on Euthanasia. If not, include a scientific justification for not following the recommendations.
\end{enumerate}

Do not use the vertebrate animal section to circumvent the page limits of the Research Strategy.

%----------------------------------------------------------------------------------------
%	SELECT AGENT RESEARCH
%----------------------------------------------------------------------------------------

\newpage

\section*{11. Select Agent Research}

Select Agents are hazardous biological agents and toxins that have been identified by DHHS or USDA as having the potential to pose a severe threat to public health and safety, to animal and plant health, or to animal and plant products. CDC maintains a list of these agents. See http://www.cdc.gov/od/sap/docs/salist.pdf.

%----------------------------------------------------------------------------------------
%	MULTIPLE PD/PI LEADERSHIP PLAN
%----------------------------------------------------------------------------------------

\newpage

\section*{12. Multiple PD/PI Leadership Plan}

For applications designating multiple PD/PIs, a leadership plan must be included. A rationale for choosing a multiple PD/PI approach should be described. The governance and organizational structure of the leadership team and the research project should be described, including communication plans, process for making decisions on scientific direction, and procedures for resolving conflicts. The roles and administrative, technical, and scientific responsibilities for the project or program should be delineated for the PD/PIs and other collaborators.

If budget allocation is planned, the distribution of resources to specific components of the project or the individual PD/PIs should be delineated in the Leadership Plan. In the event of an award, the requested allocations may be reflected in a footnote on the Notice of Grant Award.

%----------------------------------------------------------------------------------------
%	CONSORTIUM/CONTRACTUAL ARRANGEMENTS
%----------------------------------------------------------------------------------------

\newpage

\section*{13. Consortium/Contractual Arrangements}

Explain the programmatic, fiscal, and administrative arrangements to be made between the applicant organization and the consortium organization(s). If consortium/contractual activities represent a significant portion of the overall project, explain why the applicant organization, rather than the ultimate performer of the activities, should be the grantee. The signature of the Authorized Organization Representative on the SF424 (R\&R) cover component (Item 17) signifies that the applicant and all proposed consortium participants understand and agree to the following statement:

\emph{The appropriate programmatic and administrative personnel of each organization involved in this grant application are aware of the agency's consortium agreement policy and are prepared to establish the necessary inter-organizational agreement(s) consistent with that policy.}

%----------------------------------------------------------------------------------------
%	RESOURCE SHARING
%----------------------------------------------------------------------------------------

\newpage

%   \section*{14. Letters of Support} - letters to attach
\section*{15. Resource Sharing}

NIH considers the sharing of unique research resources developed through NIH-sponsored research an important means to enhance the value and further the advancement of the research. When resources have been developed with NIH funds and the associated research findings published or provided to NIH, it is important that they be made readily available for research purposes to qualified individuals within the scientific community. See Part III, 1.5 Sharing Research Resources.

\begin{enumerate}
	\item{Data Sharing Plan:} Investigators seeking \$500,000 or more in direct costs (exclusive of consortium F\&A) in any year are expected to include a brief 1-paragraph description of how final research data will be shared, or explain why data-sharing is not possible. Specific Funding Opportunity Announcements may require that all applications include this information regardless of the dollar level. Applicants are encouraged to read the specific opportunity carefully and discuss their data-sharing plan with their program contact at the time they negotiate an agreement with the Institute/Center (IC) staff to accept assignment of their application. See Data-Sharing Policy or http://grants.nih.gov/grants/guide/notice- files/NOT-OD-03-032.html.
	\item{Sharing Model Organisms:} Regardless of the amount requested, all applications where the development of model organisms is anticipated are expected to include a description of a specific plan for sharing and distributing unique model organisms or state why such sharing is restricted or not possible. See Sharing Model Organisms Policy, and NIH Guide NOT-OD-04-042.
	\item{Genome Wide Association Studies (GWAS):} Applicants seeking funding for a genome-wide association study are expected to provide a plan for submission of GWAS data to the NIH-designated GWAS data repository, or an appropriate explanation why submission to the repository is not possible. GWAS is defined as any study of genetic variation across the entire genome that is designed to identify genetic associations with observable traits (such as blood pressure or weight) or the presence or absence of a disease or condition. For further information see Policy for Sharing of Data Obtained in NIH Supported or Conducted Genome-Wide Association Studies, NIH Guide NOT-OD-07-088, and http://grants.nih.gov/grants/gwas/.
\end{enumerate}

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

\newpage

\printbibliography
% \bibliography{mybib} % Use the NIHGrant.bib file for the reference list, replace with your own
% \bibliographystyle{nihunsrt} % Use the custom nihunsrt bibliography style included with the template

%----------------------------------------------------------------------------------------

\end{document}

### 2021-04-23 nih2/NIHGrant.tex
Some additions

@@
 
-% \usepackage[utf8]{inputenc} % Required for inputting international characters
-% \usepackage[T1]{fontenc} % Output font encoding for international characters
+\usepackage[utf8]{inputenc} % Required for inputting international characters
+\usepackage[T1]{fontenc} % Output font encoding for international characters
 % A note on fonts: As of 2019, NIH allows Arial, Georgia, Helvetica, and Palatino Linotype.
@@
 \linespread{1.05} % A little extra line spread is better for the Palatino font
-%\usepackage{helvet} % Helvetica font
-\renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font
+% \usepackage{helvet} % Helvetica font
+% \renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font
 
@@
 \usepackage[style=numeric, sorting=nyt]{biblatex}
+\addbibresource[]{mybib.bib}
 \pagestyle{empty} % Suppress headers and footers
@@
 
-This is an example citation \cite{baraniukCompressiveSensingLecture2007}.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Praesent porttitor arcu luctus, imperdiet urna iaculis, mattis eros.
-Pellentesque iaculis odio vel nisl ullamcorper, nec faucibus ipsum molestie.
-Sed dictum nisl non aliquet porttitor.
-Etiam vulputate arcu dignissim, finibus sem et, viverra nisl.
-Aenean luctus congue massa, ut laoreet metus ornare in.
-Nunc fermentum nisi imperdiet lectus tincidunt vestibulum at ac elit.
-Nulla mattis nisl eu malesuada suscipit.
+The \textbf{objective} of this proposal is to directly and more completely characterize the perceptual experience of tinnitus using the novel application of a primary method for uncovering latent perceptual representations: reverse correlation.
+Tinnitus is the perception of ringing, buzzing, or hissing in the ears, which can range from mild and transient to debilitating.
+In the U.S. alone, it affects 45 million people per year, 30\% of which report their tinnitus to be moderate to severe.
+A primary form of treatment habituation therapy that retrains a patient’s nervous system by habituating it to external sounds that mimic the perceptual experience of the tinnitus sound.
+Habituation therapies require accurate estimates of patients’ tinnitus experience in order to promote patient outcomes.
+There is a pressing need for new approaches to uncovering individuals’ perceptual experience of tinnitus, because current estimation methods rely on strongly reductionist assumptions concerning the nature of tinnitus sounds, and produce results that are correspondingly biased and incomplete.
+Reverse correlation holds promise in this regard, as a primary method used to characterize neural tuning that is known to allow for unconstrained and unbiased estimation of latent neural representations (e.g., neural receptive fields [17]), as well as higher-level cognitive representations, including psychophysical kernels that drive the top-down processes of perception (e.g., face or phoneme recognition)[1,5,14,18], and even abstract psychological categories (e.g., “male” vs.
+“female” faces)[4,10,16], all on the basis of fairly simple stimulus-response data [11,15].
+Despite its wide acceptance in other areas of inquiry, reverse correlation has not been brought to bear with respect to uncovering tinnitus experience.
 
-Aliquam arcu turpis, ultrices sed luctus ac, vehicula id metus.
-Morbi eu feugiat velit, et tempus augue.
-Proin ac mattis tortor.
-Donec tincidunt, ante rhoncus luctus semper, arcu lorem lobortis justo, nec convallis ante quam quis lectus.
-Aenean tincidunt sodales massa, et hendrerit tellus mattis ac.
-Sed non pretium nibh.
-Donec cursus maximus luctus.
-Vivamus lobortis eros et massa porta porttitor.
-
-Fusce varius orci ac magna dapibus porttitor.
-In tempor leo a neque bibendum sollicitudin.
-Nulla pretium fermentum nisi, eget sodales magna facilisis eu.
-Praesent aliquet nulla ut bibendum lacinia.
-Donec vel mauris vulputate, commodo ligula ut, egestas orci.
-Suspendisse commodo odio sed hendrerit lobortis.
-Donec finibus eros erat, vel ornare enim mattis et.
-Donec finibus dolor quis dolor tempus consequat.
-Mauris fringilla dui id libero egestas, ut mattis neque ornare.
-Ut condimentum urna pharetra ipsum consequat, eu interdum elit cursus.
-Vivamus scelerisque tortor et nunc ultricies, id tincidunt libero pharetra.
-Aliquam eu imperdiet leo.
-Morbi a massa volutpat velit condimentum convallis et facilisis dolor.
+Our \textbf{long-term goal} is to directly uncover and more completely characterize the perceptual experience of tinnitus using the demonstrated capabilities of the reverse correlation approach.
+Our guiding hypothesis is that reverse correlation will produce estimates of tinnitus percepts that are substantially more rich, individualized and unbiased than currently possible using existing approaches.
+The rationale is that high quality characterization of tinnitus percepts can promote detailed assessment of tinnitus, helping to explain individual variability in tinnitus experience, and ultimately informing individualized treatment through enhanced habituation therapies.
+The proposed work will simultaneously improve the efficiency of the reverse correlation method itself, further enhancing its potential for adoption in clinical settings.
+We will test our central hypothesis and attain our objective via the following specific aims:
 
 \begin{description}
-	\item[Aim 1: Really cool stuff.]{}
-	\item{1.1. First sub-aim with more details}
-	\item{1.2. Second sub-aim with more details.}  
+	\item[Aim \#1: Uncover and reconstruct cognitive representations of tinnitus]{} 
 \end{description}
 
+Participants will classify white noise stimuli as sounding like their tinnitus or not.
+We will use reverse correlation to infer an unbiased estimate of each participant's cognitive representation of their tinnitus percept.
+
 \begin{description}
-	\item[Aim 2: Really cool stuff.]{}
-	\item{2.1. First sub-aim with more details.}
-	\item{2.2. Second sub-aim with more details.}
+	\item[Aim \#2: Develop efficient reconstruction algorithm for cognitive representations using compressive sensing]{} 
 \end{description}
 
+The efficiency of this method can be optimized to require fewer samples using advanced signal processing techniques.
+We will develop an open-source compressive sensing data analysis pipeline to acquire convergent cognitive representations using fewer trials.
+Our pilot data demonstrates that compressive sensing affords a 90\% decrease in number of trials for equivalent resulant latent representation.
+We will also develop and distribute an open-source software implementation the of the reverse correlation method for speech perception,
+including the proposed compressive sensing framework, for use by the research community.
+
 \begin{description}
-	\item[Aim 3: Really cool stuff.]{ }
-	\item{3.1. First sub-aim with more details.}
-	\item {3.2. Second sub-aim with more details.}
-	\item{3.3. Third sub-aim with more details.}
+	\item[Aim \#3: Characterize and interpret cognitive representations of tinnitus]{} 
 \end{description}
 
-In hac habitasse platea dictumst.
-Curabitur mattis elit sit amet justo luctus vestibulum.
-In hac habitasse platea dictumst.
-Pellentesque lobortis justo enim, a condimentum massa tempor eu.
-Ut quis nulla a quam pretium eleifend nec eu nisl.
-Nam cursus porttitor eros, sed luctus ligula convallis quis.
-Nam convallis, ligula in auctor euismod, ligula mauris fringilla tellus, et egestas mauris odio eget diam.
-Praesent sodales in ipsum eu dictum.
+Our compressive sensing framework will allow for rapid data acquisition from participants.
+We will characterize cognitive representations of tinnitus between participants and over time.
+What is the space of tinnitus cognitive representations?
+Are there subtypes or clusters on a lower dimensional manifold?
+We will employ dimensionality reduction and clustering algorithms to represent and visualize the data,
+providing direct insight into commonalities and variability of tinnitus experience in and between subjects.
 
@@
 \section*{A. Significance}
-
-\begin{description} % For subheadings within a section, this template uses the {description} environment, it is not obtrusively large like a \subsection; and facilitates a brief optional subtitle; and it will wrap around figures and tables; it also has a decent amount of whitespace above/below which is less than for a section heading
-	\item[A.1. Instructions.]{Optional subtitle}
-\end{description}
-
-Explain the importance of the problem or critical barrier to progress in the field that the proposed project addresses.
-
-Explain how the proposed project will improve scientific knowledge, technical capability, and/or clinical practice in one or more broad fields.
-
-Describe how the concepts, methods, technologies, treatments, services, or preventative interventions that drive this field will be changed if the proposed aims are achieved.
-
-\begin{description}
-	\item[A.2. Subheading.]{}
-\end{description}
 
@@
 Alternate forced-choice (AFC) paradigm tasks ask the patient to determine which of two sounds
-is closer to their tinnitus percept \cite{henryComparisonTwoComputerautomated2001,henryComputerautomatedTinnitusAssessment2004,henryComputerautomatedTinnitusAssessment2013,korthOneStepCloser2020}.
+is closer to their tinnitus percept
+\cite{henryComparisonTwoComputerautomated2001,henryComputerautomatedTinnitusAssessment2004,henryComputerautomatedTinnitusAssessment2013,korthOneStepCloser2020}.
 Recent computer and methodological advances have made the test more portable and efficient,
@@
 however AFC tasks introduce biases by artificially limiting the stimulus space and likeness measures are time-consuming.
-
 \emph{We believe that a novel reverse correlation-based approach will produce efficient and unbiased cognitive representations of tinnitus percepts}
 \cite{gosselinSuperstitiousPerceptionsReveal2003}.
+
 Reverse correlation allows for unconstrained and unbiased
@@
 richly varying stimuli, such as white noise (Marmarelis \& Marmarelis, 1978; Nishimoto et al., 2006).
-Richstimuli, by virtue of the fact that they are inherently vague, force the top-down process to exert a clearly
+Rich stimuli, by virtue of the fact that they are inherently vague, force the top-down process to exert a clearly
 measurable influence on responses. Latent representations that drive the top-down process can then be
@@
 
-Referencing a table using it's label: Table \ref{tab:example}.
+Referencing a table using its label: Table \ref{tab:example}.
 Maecenas consectetur metus at tellus finibus condimentum.
@@
 
-Referencing a figure using it's label: Figure \ref{fig:example}.
+Referencing a figure using its label: Figure \ref{fig:example}.
 Proin lobortis efficitur dictum.
@@
 
-\begin{description}
-	\item[B.1. Instructions.]{}
-\end{description}
-
-Explain how the application challenges and seeks to shift current research or clinical practice paradigms.
-
-Describe any novel theoretical concepts, approaches or methodologies, instrumentation or interventions to be developed or used, and any advantage over existing methodologies, instrumentation, or interventions.
-
-Explain any refinements, improvements, or new applications of theoretical concepts, approaches or methodologies, instrumentation, or interventions.
+The proposed project is innovative for several reasons.
+First, we will leverage interdisciplinary collaboration between engineering (Lammert)
+and hearing science (Ben) to characterize tinnitus to inform clinical care.
+Second, we will apply reverse correlation to the tinnitus domain in a novel application,
+which promises to deliver unbiased, high-dimensional estimates of cognitive representations of tinnitus.
+Third, we will develop a signal processing pipeline to leverage compressive sensing
+to acquire accurate estimates of cognitive representations of tinnitus using significantly fewer samples.
+This pipeline will save experimenters and subjects time and will enable researchers
+to collect data from more subjects and from individual subjects over time.
+We will release our open-source software tool online with bindings to popular scientific computing languages.
 
@@
 
-\begin{description}
-	\item[C.1. Instructions.]{}
-\end{description}
-
-Describe the overall strategy, methodology, and analyses to be used to accomplish the specific aims of the project.
-Unless addressed separately in Item 15 (Resource Sharing Plan), include how the data will be collected, analyzed, and interpreted as well as any resource sharing plans as appropriate.
-
-Discuss potential problems, alternative strategies, and benchmarks for success anticipated to achieve the aims.
-
-If the project is in the early stages of development, describe any strategy to establish feasibility, and address the management of any high risk aspects of the proposed work.
-
-Point out any procedures, situations, or materials that may be hazardous to personnel and precautions to be exercised. A full discussion on the use of Select Agents should appear in Item 11, below.
-
-As applicable, also include the following information as part of the Research Strategy, keeping within the three sections listed above: Significance, Innovation, and Approach.
-
-\begin{description}
-	\item[C.2. Preliminary Studies for New Applications]{}
-\end{description}
-
-Preliminary Studies for New Applications: For new applications, include information on Preliminary Studies.
-Discuss the PD/PI's preliminary studies, data, and or experience pertinent to this application.
-Except for Exploratory/Developmental Grants (R21/R33), Small Research Grants (R03), and Academic Research Enhancement Award (AREA) Grants (R15), preliminary data can be an essential part of a research grant application and help to establish the likelihood of success of the proposed project.
-Early Stage Investigators should include preliminary data (however, for R01 applications, reviewers will be instructed to place less emphasis on the preliminary data in application from Early Stage Investigators than on the preliminary data in applications from more established investigators).
+In the proposed project, we will use reverse correlation to reveal unbiased high-dimensional
+representations of tinnitus and further characterize the condition
+using dimensionality-reduction and density-based clustering.
+In \emph{Aim \#1}, we will develop and run an experimental paradigm
+in which tinnitus patients listen to noisy stimuli and perform an alternate forced-choice task
+answering the question, ``Does this sound like your tinnitus?''
+In \emph{Aim \#2},
 

### 2021-04-24 nih2/NIHGrant.tex
Add to Approach

@@
 \hyphenation{ionto-pho-re-tic iso-tro-pic fortran} % Specifies custom hyphenation points for words or words that shouldn't be hyphenated at all
+\def\eg{{\emph{e.g.,}}~}
+\def\ie{{\emph{i.e.,}}~}
 
@@
 answering the question, ``Does this sound like your tinnitus?''
-In \emph{Aim \#2},
+Reverse correlation frees us from the methodological constraint of imposing strong \emph{a priori}
+assumptions about the tinnitus percept.
+In \emph{Aim \#2}, we will develop an open-source signal processing pipeline
+to reconstruct cognitive representations of tinnitus using compressive sensing.
+Compressive sensing holds promise to dramatically reduce the number of samples
+needed for accurate reconstruction, enabling us to run more experimental subjects for Aim \#1,
+and retest subjects to examine the stability of cognitive representations of tinnitus over time.
+\emph{Aim \#3} contextualizes reconstructed cognitive representations of tinnitus
+by visualizing underlying subtypes or clusters on a lower dimensional manifold.
+We will employ dimensionality reduction and clustering algorithms to represent and visualize the data,
+providing direct insight into commonalities and variability of tinnitus experience in and between subjects.
+
+\begin{description}
+	\item[C.1. Aim \#1]{Uncover and reconstruct cognitive representations of tinnitus} 
+\end{description}
+
+In this aim, we will identify high-dimensional cognitive representations of tinnitus using reverse correlation.
+Current methods for estimating cognitive representations of tinnitus fall broadly into two primary categories,
+each of which has limitations.
+One approach is to use forced-choice selection tasks.
+In this experimental paradigm,
+the experimenter presents participants with multiple samples of auditory stimuli that vary in well-characterized
+and often highly-constrained ways, along specific dimensions (\eg pure tone frequency, width of spectral envelope)
+that are known to be, or are hypothesized to be, relevant to tinnitus representation or masking
+\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}.
+The subject then makes a choice between stimuli.
+While new methodological advances in experiment design and technology have streamlined this approach
+\cite{korthOneStepCloser2020,henryComputerautomatedTinnitusAssessment2004,henryComputerautomatedTinnitusAssessment2013},
+it is still constrained by \emph{a priori} assumptions about the nature of tinnitus percepts.
+In contrast, likeness approaches use subjective judgment tasks,
+in which the subject rates how much (if at all) a presented stimulus is part of or masks their tinnitus percept
+\cite{norenaPsychoacousticCharacterizationTinnitus2002}.
+While likeness measures provide more complete reconstructions of tinnitus cognitive representations,
+likeness tests are time-consuming and generally not used in clinical practice
+\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}.
+
+The highly-constrained nature of stimuli used in the forced selection approach necessarily results
+in recovered representations that are correspondingly constrained and typically low-dimensional. It has
+long been known, however, that representations limited to only a few dimensions are insufficient to
+account for the full richness of tinnitus experiences
+\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}.
+Subjective judgment experiments yield more informative reconstructions but are time-consuming to employ.
+The nature of subjective judgment
+approach is such that it is best suited to uncover relations between perceptual categories, rather than
+characterizing cognitive representations directly, and thus provides limited information about how
+perceptual similarity comes about. While some of the recovered dimensions along which stimuli differ in
+these tasks correlate with frequently assumed dimensions of representation (\eg frequency and pitch to mask tinnitus percept),
+some recovered dimensions of contrast have no known characterization.
+Moreover, this approach is fundamentally limited by the precise stimuli presented to participants, and
+therefore may not systematically explore the entire space of perceptually-meaningful variables.
 

### 2021-04-26 nih2/NIHGrant.tex
Continue writing approach

@@
 
-\usepackage[utf8]{inputenc} % Required for inputting international characters
+% \usepackage[utf8]{inputenc} % Required for inputting international characters
 \usepackage[T1]{fontenc} % Output font encoding for international characters
@@
 \usepackage[style=numeric, sorting=nyt]{biblatex}
+\usepackage{color, colortbl, soul}
+\usepackage{tabularx}
+\usepackage{array}
+\usepackage{caption}
+\usepackage[colorlinks=false]{hyperref}
+
+\newcommand{\myfloatalign}{\centering} % to be used with each float for alignment
+
+\definecolor{Gray}{gray}{0.9}
 \addbibresource[]{mybib.bib}
@@
 \def\ie{{\emph{i.e.,}}~}
+\def\cf{{\emph{cf.,}}~}
 
-%----------------------------------------------------------------------------------------
+%---------------------------------------------------------------------
 
@@
 
-\begin{description}
-	\item[C.1. Aim \#1]{Uncover and reconstruct cognitive representations of tinnitus} 
-\end{description}
+% \begin{description}
+% 	\item[C.1. Aim \#1]{Uncover and reconstruct cognitive representations of tinnitus} 
+% \end{description}
+
+\subsection*{C. Aim \#1: Uncover and reconstruct cognitive representations of tinnitus}
 
 In this aim, we will identify high-dimensional cognitive representations of tinnitus using reverse correlation.
-Current methods for estimating cognitive representations of tinnitus fall broadly into two primary categories,
-each of which has limitations.
+Current methods for estimating cognitive representations of tinnitus fall broadly into three primary categories,
+each of which has limitations (\autoref{tab:approaches}).
 One approach is to use forced-choice selection tasks.
@@
 that are known to be, or are hypothesized to be, relevant to tinnitus representation or masking
-\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}.
+\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021,henryMeasurementTinnitus2016}.
 The subject then makes a choice between stimuli.
@@
 account for the full richness of tinnitus experiences
-\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}.
+\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021,henryMeasurementTinnitus2016}.
 Subjective judgment experiments yield more informative reconstructions but are time-consuming to employ.
@@
 therefore may not systematically explore the entire space of perceptually-meaningful variables.
+
+A third, more recent approach to uncovering cognitive representations is to employ neuroimaging
+(\eg fMRI) to identify neural activation patterns indicative of tinnitus.
+In investigations of functional connectivity in tinnitus patients,
+resting-state fMRI measures were found to be replicable and reliable,
+though no explicit representations have been proposed
+\cite{husainReplicabilityNeuralBehavioral2019}.
+This approach is also
+limited, in that it can only uncover representations that have a definite, localized seat in the brain.
+Cognitive representations, by contrast, are commonly understood to be constructs that need not have
+such a localized neural seat by definition, and which can best be revealed through analyzing behavior.
+
+% \begin{table}[h]
+% 	\centering
+% 	\begin{tabular}{| >{\raggedright}p{35mm} >{\raggedright\arraybackslash}p{40mm} >{\raggedright\arraybackslash}p{45mm} >{\raggedright\arraybackslash}p{50mm}|} 
+% 		\hline
+% 		Approach & Stimulus & Measurements & Output \\ [0.5ex] 
+% 		\hline
+% 		\rowcolor{Gray} Forced selection & Constructed stimuli, constrained variation & Subjective choice & Representation with \newline defined acoustic properties \\
+% 		Likeness measures & Constructed stimuli, constrained variation & Subjective ratings & Frequency spectra \\
+% 		\rowcolor{Gray} Neural monitoring & N/A & Neural signals (\eg fMRI) & Correlation maps in localized brain regions, functional connectivity maps \\
+% 		\textbf{Reverse Correlation} & Constructed stimuli, unconstrained variation & Response classification (\eg present/absent) & Representations best explaining classification behavior \\
+% 		\hline
+% 	\end{tabular}
+% 	\caption{Comparison of approaches for estimating cognitive representations.
+% 	Each approach has benefits and limitations regarding stimuli, measurements, and output.
+% 	The proposed approach, featured in the final row, is the only approach that can directly
+% 	uncover a time-frequency map of the cognitive representation that best explains tinnitus percepts.}
+% 	\label{table:1}
+% \end{table}
+
+\begin{table}[h]
+	\myfloatalign
+	\begin{tabularx}{\textwidth}{>{\raggedright}p{35mm} >{\raggedright\arraybackslash}p{40mm} >{\raggedright\arraybackslash}p{45mm} >{\raggedright\arraybackslash}p{50mm}}
+		\toprule
+		\textbf{Approach} & \textbf{Stimulus} & \textbf{Measurements} & \textbf{Output} \\ [0.5ex] 
+		\rowcolor{Gray} Forced selection & Constructed stimuli, constrained variation & Subjective choice & Representation with \newline defined acoustic properties \\
+		Likeness measures & Constructed stimuli, constrained variation & Subjective ratings & Frequency spectra \\
+		\rowcolor{Gray} Neural monitoring & N/A & Neural signals (\eg fMRI) & Correlation maps in localized brain regions, functional connectivity maps \\
+		\textbf{Reverse Correlation} & Constructed stimuli, unconstrained variation & Response classification (\eg present/absent) & Representations best explaining classification behavior \\
+		\bottomrule
+	\end{tabularx}
+	\caption[Approaches]{Comparison of approaches for estimating cognitive representations.
+	Each approach has benefits and limitations regarding stimuli, measurements, and output.
+	The proposed approach, featured in the final row, is the only approach that can directly
+	uncover a time-frequency map of the cognitive representation that best explains tinnitus percepts.}
+	\label{tab:approaches}
+\end{table}
+
+In a set of two experiments described below, we propose to implement a reverse correlation
+approach for recovering cognitive representations of speech which allows for unconstrained, direct
+characterization of latent representations from yes-no responses to randomly-generated stimuli.
+Participants will be asked to classify random auditory stimuli as containing or not containing their tinnitus percept.
+Latent representations that drive the top-down process
+can then be estimated by regressing observed responses against the stimuli over many trials \cite{mineaultImprovedClassificationImages2009}.
+
+Reverse correlation has been applied across multiple fields to reveal underlying representations by application of unconstrained, noisy input.
+Reverse correlation has been used to characterize low-level latent representations encapsulated in neural tuning
+(\eg receptive fields) \cite{ringachReverseCorrelationNeurophysiology2004}
+and has been used to successfully recover cognitive representations underlying visual perception \cite{gosselinSuperstitiousPerceptionsReveal2003,}
+Both existing experimental work (\cf Fig 2B in \cite{brimijoinInternalRepresentationVowel2013})
+and our preliminary simulation experiments (\hl{FIGURE CITATION}) suggest that this method can be successfully translated
+into the auditory domain.
+Reverse correlation allows us (1) to uncover more complex, potentially higher-dimensional representations
+than would be possible using more focused, constrained stimuli,
+(2) to recover directly the nature of the representations themselves rather than the relation
+between the tinnitus percept and a masking sound,
+and (3) to recover cognitive representations of the tinnitus percept directly rather than a neural correlate.
+In short, reverse correlation will be able to provide deeper understanding of cognitive representations of tinnitus percepts
+than is possible with conventional methods.
+
+\subsubsection*{C.1. Method}
+
+The proposed method for uncovering perceptual representations can be divided
+into a sequence of three main parts:
+(1) construction of vague, ``random'' stimuli for presentation to subjects,
+(2) experimental procedure and data collection,
+and (3) reconstruction of perceptual representations from subject responses.
+
+\begin{description}
+	\item[C.1.1. Stimuli Construction]{}
+\end{description}
+
+Stimuli will be generated randomly, in keeping with prior work in the visual domain
+\cite{gosselinSuperstitiousPerceptionsReveal2003}.
+The meaning of ``random'' with respect to the stimuli presented to subjects
+refers specifically to the shape of spectral envelope in the frequency domain.
+This shape will be determined randomly for all stimuli
+and will not be informed by prior knowledge
+or statistics over canonical examples of tinnitus.
+These random spectral envelopes will be used as the basis for building spectrograms
+that sound like tinnitus percepts.
+
+Our preliminary testing suggests that truly random envelopes
+often result in the perception of colored noise.
+Minimal additional spectral-temporal constraints may need to be imposed on stimuli
+such that participants will interpret the stimuli as intending to be tinnitus percepts.
+This is similar to the approach taken in some visual domain experiments,
+where bandlimited random stimuli, or stimuli with partial superimposed templates,
+are presented \cite{smithMeasuringInternalRepresentations2012} (\hl{CITE}).
+
+\hl{What are we doing to create the stimuli?}
+
+\begin{description}
+	\item[C.1.2. Experimental Procedure] 
+\end{description}
+
+\hl{Where are we getting our subjects?}
+
+\hl{How are we evaluating tinnitus in our subjects?}
+
+\hl{How do we phrase what we want the subjects to do?}
+
+\begin{description}
+	\item[C.1.3. Reconstructing Representations] 
+\end{description}
+
+To reconstruct cognitive representations from subject responses,
+we will generate a classification spectrogram by taking the difference
+between a spectrogram generated from the positive labels (the ``yes'' responses)
+and a spectrogram generated from the negative labels (the ``no'' responses)
+(\hl{FIGURE CITATION}).
+Such reconstructed representations are the best least-squares fit to the behavioral data
+\cite{gosselinSuperstitiousPerceptionsReveal2003}.
+We theorize that the classification spectrogram is used as a template vector
+against which stimuli were compared in a linear matching model of response generation.
+
+\subsection*{C.2. Aim \#2: Develop an efficient reconstruction algorithm for cognitive representations using compressive sensing}
+
+In this aim, we employ advanced signal processing techniques to overcome critical inefficiencies
+in reverse correlation that limit its scope and impact.
+
+Current attempts to characterize perceptual mechanisms using reverse correlation
+are limited in scope due to inefficiencies inherent to conventional methods.
+While reverse correlation allows for relatively unconstrained and unbiased
+estimation of latent representations using straightforward stimulus-response data
+\cite{marmarelisWhiteNoiseMethodSystem1978,nishimotoReceptiveFieldProperties2006},
+the number of stimulus-response samples required for accurate estimation
+is typically very large \cite{mineaultImprovedClassificationImages2009}.
+This inefficiency limits the feasibility of applying reverse correlation more broadly,
+as subject participation must be maintained over long timelines.
 

### 2021-05-07 nih2/NIHGrant.tex
Draft to Adam

@@
 \usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry} % Page margins
-\usepackage[style=numeric, sorting=nyt]{biblatex}
+\usepackage[style=numeric, sorting=nyt, sortcites=true]{biblatex}
 \usepackage{color, colortbl, soul}
@@
 Habituation therapies require accurate estimates of patients’ tinnitus experience in order to promote patient outcomes.
-There is a pressing need for new approaches to uncovering individuals’ perceptual experience of tinnitus, because current estimation methods rely on strongly reductionist assumptions concerning the nature of tinnitus sounds, and produce results that are correspondingly biased and incomplete.
-Reverse correlation holds promise in this regard, as a primary method used to characterize neural tuning that is known to allow for unconstrained and unbiased estimation of latent neural representations (e.g., neural receptive fields [17]), as well as higher-level cognitive representations, including psychophysical kernels that drive the top-down processes of perception (e.g., face or phoneme recognition)[1,5,14,18], and even abstract psychological categories (e.g., “male” vs.
-“female” faces)[4,10,16], all on the basis of fairly simple stimulus-response data [11,15].
+There is a pressing need for new approaches to uncovering individuals’ perceptual experience of tinnitus,
+because current estimation methods rely on strongly reductionist assumptions concerning the nature of tinnitus sounds, 
+and produce results that are correspondingly biased and incomplete.
+Reverse correlation holds promise in this regard,
+as a primary method used to characterize neural tuning that is known to allow for unconstrained and unbiased estimation of latent neural representations
+(\eg neural receptive fields) \cite{ringachReverseCorrelationNeurophysiology2004, nishimotoReceptiveFieldProperties2006},
+as well as higher-level cognitive representations, including psychophysical kernels that drive the top-down processes of perception 
+(\eg face or phoneme recognition) \cite{gosselinSuperstitiousPerceptionsReveal2003,smithMeasuringInternalRepresentations2012,neriReceptivePerceptiveFields2006,ahumadaStimulusFeaturesSignal1971},
+and even abstract psychological categories (\eg “male” vs. “female” faces)
+\cite{brinkmanVisualisingMentalRepresentations2017,manginiMakingIneffableExplicit2004,ponsotCrackingSocialCode2018},
+all on the basis of fairly simple stimulus-response data \cite{ljungMeasureLackFit1978,marmarelisWhiteNoiseMethodSystem1978}.
 Despite its wide acceptance in other areas of inquiry, reverse correlation has not been brought to bear with respect to uncovering tinnitus experience.
@@
 characterization of latent representations directly from stimulus-response data by eliciting responses to
-richly varying stimuli, such as white noise (Marmarelis \& Marmarelis, 1978; Nishimoto et al., 2006).
+richly varying stimuli, such as white noise \cite{marmarelisWhiteNoiseMethodSystem1978, nishimotoReceptiveFieldProperties2006}.
 Rich stimuli, by virtue of the fact that they are inherently vague, force the top-down process to exert a clearly
 measurable influence on responses. Latent representations that drive the top-down process can then be
-estimated by regressing observed responses against the stimuli over many trials (Mineault et al., 2009).
+estimated by regressing observed responses against the stimuli over many trials \cite{mineaultImprovedClassificationImages2009}.
 Reverse correlation, as a method, is powerful enough to characterize any aspect of neurological,
-cognitive or psychological function that can be modeled as a transductive process (Ringach, 2004). It has
-become a primary method used to characterize the latent representations encapsulated in neural tuning
-(e.g., receptive fields; Ringach, 2004), and is closely related to the widely-used “white noise approach” to
-characterizing physiological (Marmarelis \& Marmarelis, 1978) and engineering (Ljung, 1999) systems.
+cognitive or psychological function that can be modeled as a transductive process \cite{ringachReverseCorrelationNeurophysiology2004}.
+It has become a primary method used to characterize the latent representations encapsulated in neural tuning
+(\eg receptive fields; \cite{ringachReverseCorrelationNeurophysiology2004}), and is closely related to the widely-used ``white noise approach'' to
+characterizing physiological \cite{marmarelisWhiteNoiseMethodSystem1978} and engineering \cite{ljungMeasureLackFit1978} systems.
 
@@
 neural mechanisms, has been increasingly used for inferring higher-level cognitive representations,
-including psychophysical kernels that drive the top-down processes of perception (Ahumada \& Lovell,
-1971; Gosselin \& Schyns, 2003; Neri \& Levi, 2006; Smith et al., 2012), and even abstract psychological
-categories (e.g., “male” vs. “female” faces; Brinkman et al., 2017; Mangini \& Biederman, 2004; Ponsot et
-al., 2018). Recent work in vision (e.g., Gosselin \& Schyns, 2003; Liu et al., 2014) has demonstrated that
+including psychophysical kernels that drive the top-down processes of perception
+\cite{ahumadaStimulusFeaturesSignal1971, neriReceptivePerceptiveFields2006,gosselinSuperstitiousPerceptionsReveal2003,smithMeasuringInternalRepresentations2012}, 
+and even abstract psychological
+categories (\eg ``male'' vs. ``female'' faces; \cite{brinkmanVisualisingMentalRepresentations2017,manginiMakingIneffableExplicit2004,ponsotCrackingSocialCode2018}.
+Recent work in vision has demonstrated that
 reverse correlation can effectively characterize cognitive representations underlying letter and face
-recognition (Fig 2A). One speech study has also estimated steady-state representations of vowels the /a/
-and /i/ using a closely-related paradigm to the one proposed here (Fig 2B; Brimijoin et al., 2013). Our
+recognition \hl{(Fig 2A)} \cite{gosselinSuperstitiousPerceptionsReveal2003,liuSeeingJesusToast2014}.
+One speech study has also estimated steady-state representations of vowels the /a/
+and /i/ using a closely-related paradigm to the one proposed here (Fig 2B; \cite{brimijoinInternalRepresentationVowel2013}). Our
 proposed use of reverse correlation in the domain of speech expands on classic efforts to understand
 top-down processing in speech with the presentation of rich, vague stimuli to elicit responses from
-listeners (Warren \& Warren, 1970; Vokey \& Read 1985). These studies provide clear evidence that rich
+listeners \hl{(Warren \& Warren, 1970; Vokey \& Read 1985)}. These studies provide clear evidence that rich
 stimuli, such as white noise, are sufficient to engage the top-down process, even if they do not attempt to
@@
 
-\begin{wraptable}{l}{5.5cm} % Example table with text wrapping around it
-	\caption{Example Table}
-	\begin{center}
-		\begin{tabular}{l l r}
-			\toprule
-			\multicolumn{1}{c}{City} & {N\textsuperscript{a}} & {\%Silly}\\
-			\midrule
-			San Diego & 289 & 41\%\\
-			Seattle & 262 & 32\%\\
-			Galveston & 261 & 15\%\\
-			St Louis & 269 & 7\%\\
-			New York & 271 & 4\%\\
-			Baltimore & 231 & 2\%\\
-			\emph{Total} & 1,586 & 21\%\\
-			\hline 
-		\end{tabular}\\
-		\footnotesize\textsuperscript{a}{All participants clowns.}
-	\end{center}
-	\label{tab:example}
-\end{wraptable}
+% \begin{wraptable}{l}{5.5cm} % Example table with text wrapping around it
+% 	\caption{Example Table}
+% 	\begin{center}
+% 		\begin{tabular}{l l r}
+% 			\toprule
+% 			\multicolumn{1}{c}{City} & {N\textsuperscript{a}} & {\%Silly}\\
+% 			\midrule
+% 			San Diego & 289 & 41\%\\
+% 			Seattle & 262 & 32\%\\
+% 			Galveston & 261 & 15\%\\
+% 			St Louis & 269 & 7\%\\
+% 			New York & 271 & 4\%\\
+% 			Baltimore & 231 & 2\%\\
+% 			\emph{Total} & 1,586 & 21\%\\
+% 			\hline 
+% 		\end{tabular}\\
+% 		\footnotesize\textsuperscript{a}{All participants clowns.}
+% 	\end{center}
+% 	\label{tab:example}
+% \end{wraptable}
 
-Referencing a table using its label: Table \ref{tab:example}.
+% Referencing a table using its label: Table \ref{tab:example}.
 Maecenas consectetur metus at tellus finibus condimentum.
@@
 
-Curabitur tempus hendrerit nulla.
+% Curabitur tempus hendrerit nulla.
 Donec faucibus lobortis nibh pharetra sagittis.
@@
 
-In malesuada ullamcorper urna, sed dapibus diam sollicitudin non.
+% In malesuada ullamcorper urna, sed dapibus diam sollicitudin non.
 Donec elit odio, accumsan ac nisl a, tempor imperdiet eros.
@@
 
-\begin{wrapfigure}{r}{8.5cm} % Example figure with text wrapping around it
-	\includegraphics[width=8.2cm]{Figures/Fig1.jpg}
-	\caption{\footnotesize Example wrapped figure. (A) Impressive microscopy image. (B) Impressive data.}
-	\label{fig:example}
-\end{wrapfigure}
+% \begin{wrapfigure}{r}{8.5cm} % Example figure with text wrapping around it
+% 	\includegraphics[width=8.2cm]{Figures/Fig1.jpg}
+% 	\caption{\footnotesize Example wrapped figure. (A) Impressive microscopy image. (B) Impressive data.}
+% 	\label{fig:example}
+% \end{wrapfigure}
 
-Referencing a figure using its label: Figure \ref{fig:example}.
+% Referencing a figure using its label: Figure \ref{fig:example}.
 Proin lobortis efficitur dictum.
@@
 
-\begin{description}
-	\item[A.3. Another subheading:]{optional subtitle.}
-\end{description}
+% \begin{description}
+% 	\item[A.3. Another subheading:]{optional subtitle.}
+% \end{description}
 
-In congue risus leo, in gravida enim viverra id.
+% In congue risus leo, in gravida enim viverra id.
 Donec eros mauris, bibendum vel dui at, tempor commodo augue.
@@
 
-\begin{figure}[b] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
-	\centering
-	\includegraphics[scale = .80]{Figures/Fig2.pdf}
-	\caption{\footnotesize Big Figure legend Big Figure legend Big Figure legend Big Figure legend Big Figure legend Big Figure legend Big Figure legend Big Figure legend Big Figure legend.}
-	\label{fig2}
-\end{figure}
+% \begin{figure}[b] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
+% 	\centering
+% 	\includegraphics[scale = .80]{Figures/Fig2.pdf}
+% 	\caption{\footnotesize Big Figure legend Big Figure legend Big Figure legend Big Figure legend Big Figure legend Big Figure legend Big Figure legend Big Figure legend Big Figure legend.}
+% 	\label{fig2}
+% \end{figure}
 
-Fusce eleifend porttitor arcu, id accumsan elit pharetra eget.
+% Fusce eleifend porttitor arcu, id accumsan elit pharetra eget.
 Mauris luctus velit sit amet est sodales rhoncus.
@@
 
-Vestibulum sodales orci a nisi interdum tristique.
+% Vestibulum sodales orci a nisi interdum tristique.
 In dictum vehicula dui, eget bibendum purus elementum eu.
@@
 
-\begin{description}
-	\item[A.4. Yet another subheading.]{}
-\end{description}
+% \begin{description}
+% 	\item[A.4. Yet another subheading.]{}
+% \end{description}
 
-Aenean feugiat pellentesque venenatis.
+% Aenean feugiat pellentesque venenatis.
 Sed faucibus tristique tortor vel ultrices.
@@
 
-In mi mauris, finibus non faucibus non, imperdiet nec leo.
+% In mi mauris, finibus non faucibus non, imperdiet nec leo.
 In erat arcu, tincidunt nec aliquam et, volutpat eget nisl.
@@
 Both existing experimental work (\cf Fig 2B in \cite{brimijoinInternalRepresentationVowel2013})
-and our preliminary simulation experiments (\hl{FIGURE CITATION}) suggest that this method can be successfully translated
+and our preliminary simulation experiments (\autoref{fig:csexample}) suggest that this method can be successfully translated
 into the auditory domain.
@@
 
-\begin{description}
-	\item[C.1.1. Stimuli Construction]{}
-\end{description}
+% \begin{description}
+% 	\item[C.1.1. Stimuli Construction]{}
+% \end{description}
+
+\paragraph{Stimuli construction}
 
@@
 
-\begin{description}
-	\item[C.1.2. Experimental Procedure] 
-\end{description}
+% \begin{description}
+% 	\item[C.1.2. Experimental Procedure] 
+% \end{description}
+
+\paragraph{Experimental procedure}
 
@@
 
-\begin{description}
-	\item[C.1.3. Reconstructing Representations] 
-\end{description}
+% \begin{description}
+% 	\item[C.1.3. Reconstructing Representations] 
+% \end{description}
+
+\paragraph{Reconstructing representations}
 
@@
 and a spectrogram generated from the negative labels (the ``no'' responses)
-(\hl{FIGURE CITATION}).
+(\autoref{fig:experiment}).
 Such reconstructed representations are the best least-squares fit to the behavioral data
@@
 against which stimuli were compared in a linear matching model of response generation.
+
+\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
+	\centering
+	\includegraphics[width=0.5\textwidth]{Figures/BlankFigure.pdf}
+	\caption{Schematic overview of experiments proposed in Aim \#1.
+	Simulation results are shown, demonstrating proof-of-concept
+	for the proposed reverse correlation paradigm.}
+	\label{fig:experiment}
+\end{figure}
 
@@
 
-%----------------------------------------------------------------------------------------
-%	PROGRESS REPORT
-%----------------------------------------------------------------------------------------
+The impact of this inefficiency extends well beyond the present proposal.
+This fundamental sampling problem affects similar efforts to estimate higher-level
+cognitive representations and psychophysical kernels that drive top-down processes of perception
+\cite{ahumadaStimulusFeaturesSignal1971,neriReceptivePerceptiveFields2006,gosselinSuperstitiousPerceptionsReveal2003,smithMeasuringInternalRepresentations2012}.
+Since reverse correlation has broad applicability for characterizing any aspect
+of neurological, cognitive, or psychological function that can be modeled as a transductive process
+\cite{ringachReverseCorrelationNeurophysiology2004},
+the inefficiencies of reverse correlation impact efforts
+to characterize phenomena as \hl{[word meaning minute, fine-grained, detailed, specific]} latent neural representations (\eg neural receptive fields) \cite{ringachReverseCorrelationNeurophysiology2004}
+and as high-level  as abstract psychological categories (\eg ``male'' vs. ``female'' faces)
+\cite{brinkmanVisualisingMentalRepresentations2017,ponsotCrackingSocialCode2018,manginiMakingIneffableExplicit2004}.
+To combat this efficiency limitation, studies often 
+(\emph{a}) limit the richness of the stimuli (\eg by only allowing specific aspects of the stimulus to vary)
+\cite{gosselinBubblesTechniqueReveal2001},
+or (\emph{b}) impose some constraints on the inferred representations,
+for instance by smoothing the raw estimates \cite{gosselinSuperstitiousPerceptionsReveal2003}.
+The constraints imposed by these approaches ultimately defeat the full power of reverse correlation
+\cite{murrayTroublesBubbles2004},
+leading to estimates that are biased or incomplete.
 
-\newpage
+We propose to develop an advanced signal processing pipeline
+that will enable us to overcome the inefficiencies of existing reverse correlation methods
+through the use of \emph{compressive sensing},
+a recent advance in signal processing which has led to dramatic improvements in efficiency
+over conventional sampling and signal estimation methods
+\cite{baraniukCompressiveSensingLecture2007}.
+Compressive sensing has recently gain wide recognition in domains such as medical imaging
+\cite{graffCompressiveSensingMedical2015,lustigCompressedSensingMRI2008},
+where considerations of efficiency and bias reduction are critical.
+Compressive sensing holds promise to similarly improve the efficiency of reverse correlation
+without the drawback of biasing estimates.
+Compressive sensing will extend the range of possible cognitive and perceptual mechanisms that can be estimated
+by dramatically decreases the number of trials needed for signal reconstruction.
+Since compressive sensing can be directly substituted for conventional, regression-based estimation,
+it can be directly substituted into eixsting experimental protocols without requiring other changes.
+Our ultimate objective is to develop and validate a compressive sensing
+data processing pipeline – culminating in an open-source software tool – that will allow for
+efficient and accurate reconstruction of latent representations using data 
+obtained via the reverse correlation method.
 
-\section*{5. Progress Report Publication List (Renewal Applications Only)}
+% \subsubsection*{C.2.1. Method}
 
-List the titles and complete references to all appropriate publications, manuscripts accepted for publication, patents, and other printed materials that have resulted from the project since it was last reviewed competitively.
+% In this section, we describe compressive sensing,
+% including applicability to data collected in the reverse correlation paradigm,
+% and demonstrate its effectiveness for improving the efficiency and accuracy
+% of estimates of cognitive representations.
+
+\paragraph{Compressive sensing framework}
+
+Many natural signals, $x$, including latent representations, are compressible,
+meaning that they can be represented by a sum of a small number of functions
+from an appropriately-chosen basis set ($s = \Psi^{T}x$, for basis $\Psi$ and weights $s$).
+A key insight of compressive sensing is that response variables, $y$,
+stem from a process of comparing stimuli to latent representations
+($y = \Phi x$, for measurement $\Phi$).
+It is then possible to estimate the latent representation
+using only a small number of measurements
+by acquiring the basis function representation directly (\ie $ y = \Phi \Psi s$)
+via sparse optimization (to find $s$).
+The responses can be continuous (\eg firing rates),
+ordinal similarity scores
+\cite{zymnisCompressedSensingQuantized2010},
+or binary \cite{boufounos1BitCompressiveSensing2008,planOneBitCompressedSensing2013},
+as in the proposed experiments here.
+In practice, sparse representations can be found even when the chosen basis domain is quite general
+and incorporates no prior knowledge of the signal's characteristics
+(\eg the discrete cosine transform or wavelet transform).
+Critically, it has been shown that using random stimuli to elicit
+and subsequently observe responses
+is a highly effective way to ensure accurate reconstruction of latent representations
+within the compressive sensing framework
+\cite{candesIntroductionCompressiveSampling2008,candesRestrictedIsometryProperty2008,wojtaszczykStabilityInstanceOptimality2010}.
+In other words, the somewhat
+unusual model of sampling assumed by compressive sensing maps directly onto reverse correlation.
+
+\paragraph{Simulations and preliminary evidence}
+
+We have conducted simulation studies to begin validating compressive sensing
+for improving the efficiency of reverse correlation.
+Fpr example, using a template time-frequency representation, $x$,
+as a proxy for the latent representation of interest,
+we generate plausible yes/no subject responses, $y \in \{-1, 1\})$,
+based on the similarity between the template
+and a random stimuli (\ie $y = \mathrm{sign}(\phi x)$ for stimuli $\phi$).
+Estimation of the template is performed using
+(\emph{a}) convention regression-based reverse correlation
+(\ie $\hat{x}_c = n^{-1} X^\mathrm{T}y$) \cite{gosselinSuperstitiousPerceptionsReveal2003},
+or (\emph{b}) compressive sensing.
+
+\autoref{fig:csexample} shows example results from our preliminary simulation studies.
+In this example, we attempt to reconstruct a spectrally-rich signal.
+Four reconstructions are shown, corresponding to two sample sizes (12,500 and 100,000 samples)
+and two reconstruction methods (conventional linear regression and compressive sensing).
+The signal quality obtained using fewer samples via compressive sensing
+is effectively equivalent to that obtained using eight times more samples
+via conventional reconstruction.
+When allowed to operate on the full complement of 100,000 samples,
+compressive sensing shows +21\% improved accuracy over conventional reconstruction.
+If further simulation studies and validation on real data continue to align with these preliminary results,
+the number of trials required for accurate estimation using reverse correlation paradigms
+could be reduced to 12.5\% of the current standard.
+Such a drastic increase in time- and cost-effectiveness would substantially
+increase the method's potential for widespread use.
+
+\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
+	\centering
+	\includegraphics[width=\textwidth]{Figures/CompSensExamples.pdf}
+	\caption{Compressive sensing (CS) delivers accurate signal reconstruction from sampling
+	with a comparatively small number of samples.
+	The latent representation in \emph{A} is estimated in \emph{B-E}.
+	In \emph{B-C} conventional regression-based estimation is used
+	and in \emph{D-E} compressive sensing is used.
+	The number of samples $n$ is displayed along with the correlation coefficient $r^2$
+	between the estimated reconstruction and the original signal,
+	as a measure of reconstruction quality.}
+	\label{fig:csexample}
+\end{figure}
+
+\paragraph{Validation of compressive sensing}
+
+We will validate the proposed use of compressive sensing for relevant
+cognitive and behavioral data.
+Validation will be accomplished through simulation studies
+(\eg expanding on the simulation results discussed herein)
+and through analysis of data collected in Aim \#1.
+We will assess outcomes by examining estimation performance
+as a function of sample size,
+incuding
+(\emph{a}) reconstruction accuracy with few samples,
+(\emph{b}) gains in high-sample reconstruction accuracy, and
+(\emph{c}) minimal sample size to achieve high-end convergent accuracy.
+The basis for these assessments will be a comparison
+with the conventional, full-sample reconstruction
+as described in Aim \#1,
+since the true gold standard representation is unavailable.
+Potential improvements of compressive sensing reconstruction
+will be assessed using signal quality metrics that do not require direct comparison
+(\eg peak signal-to-noise ratio).
+This work will determine optimal parameters for compressive sensing
+in tinnitus percept reconstruction.
+We expect these parameters to depend on stimulus type, response noise,
+and the type of tinnitus experienced by the subject.
+Considered parameters will include appropriate input/output representations,
+reconstruction algorithm, and basis type/sparsity.
+
+\paragraph{Development of an open-source software tool}
+
+We will develop and distribute an open-source software tool for conducting
+auditory perceptual experiments using reverse correlation,
+including stimulus presentation, response collection,
+and representation reconstruction, characterization, and comparison
+as described in Aim \#3.
+This software package will include both standard reconstruction methods
+as well as an implementation of the compressive sensing framework,
+informed by the findings in this Aim, for use by the research community.
+We will develop interfaces for widely-used programming languages
+(including MATLAB and Python) in addition to command-line executables.
+Making the platform open-source provides opportunities for the community
+to make improvements and enables researchers to tailor these methods to their specific use-cases.
+
+Reverse correlation has the potential to uncover latent representations underlying perception, and
+transform our understanding of perceptual mechanisms at various levels of investigation: neural, cognitive
+and psychological. However, in order for this potential to be fully realized, the fundamental inefficiency of
+reverse correlation paradigms must be overcome. Compressive sensing holds promise to overcome this
+limitation by dramatically improving the efficiency of reverse correlation, enabling its extension to
+perceptual mechanisms that are out of reach using current methods. The work proposed here will enable
+researchers to access the promise of compressive sensing, broadening the impact of reverse correlation.
+
+\subsection*{C.3. Aim \#3: Characterize and interpret cognitive representations of tinnitus}
+
+\begin{enumerate}
+	\item What is the shape of the manifold of cognitive representations of tinnitus?
+	\item Is it reducible to fewer dimensions using PCA/t-SNE/UMAP?
+	\item Can clusters on the manifold/reduced representation be found?
+	What are those clusters?
+	\item Is this insight clinically useful?
+\end{enumerate}
+
+% %----------------------------------------------------------------------------------------
+% %	PROGRESS REPORT
+% %----------------------------------------------------------------------------------------
+
+% \newpage
+
+% \section*{5. Progress Report Publication List (Renewal Applications Only)}
+
+% List the titles and complete references to all appropriate publications, manuscripts accepted for publication, patents, and other printed materials that have resulted from the project since it was last reviewed competitively.
 When citing articles that fall under the Public Access Policy, were authored or co-authored by the applicant and arose from NIH support, provide the NIH Manuscript Submission reference number (e.g., NIHMS97531) or the Pubmed Central (PMC) reference number (e.g., PMCID234567) for each article.
@@
 
-Citations that are not covered by the Public Access Policy, but are publicly available in a free, online format may include URLs or PMCID numbers along with the full reference (note that copies of these publications are not accepted as appendix material, see Part I Section 5.5.15 for more information).
+% Citations that are not covered by the Public Access Policy, but are publicly available in a free, online format may include URLs or PMCID numbers along with the full reference (note that copies of these publications are not accepted as appendix material, see Part I Section 5.5.15 for more information).
 
-%----------------------------------------------------------------------------------------
-%	PROTECTION OF HUMAN SUBJECTS
-%----------------------------------------------------------------------------------------
+% %----------------------------------------------------------------------------------------
+% %	PROTECTION OF HUMAN SUBJECTS
+% %----------------------------------------------------------------------------------------
 
-\newpage
+% \newpage
 
-\section*{6. Protection of Human Subjects}
+% \section*{6. Protection of Human Subjects}
 
-Refer to Part II, Supplemental Instructions for Preparing the Human Subjects Section of the Research Plan.
+% Refer to Part II, Supplemental Instructions for Preparing the Human Subjects Section of the Research Plan.
 
-This section is required for applicants answering "yes" to the question "Are human subjects involved?" on the R\&R Other Project Information form.
+% This section is required for applicants answering "yes" to the question "Are human subjects involved?" on the R\&R Other Project Information form.
 If the answer is "No" to the question but the proposed research involves human specimens and/or data from subjects applicants must provide a justification in this section for the claim that no human subjects are involved.
 
-Do not use the protection of human subjects section to circumvent the page limits of the Research Strategy.
+% Do not use the protection of human subjects section to circumvent the page limits of the Research Strategy.
 
-%----------------------------------------------------------------------------------------
-%	INCLUSION OF WOMEN AND MINORITIES
-%----------------------------------------------------------------------------------------
+% %----------------------------------------------------------------------------------------
+% %	INCLUSION OF WOMEN AND MINORITIES
+% %----------------------------------------------------------------------------------------
 
-\newpage
+% \newpage
 
-\section*{7. Inclusion of Women and Minorities}
+% \section*{7. Inclusion of Women and Minorities}
 
-Refer to Part II, Supplemental Instructions for Preparing the Human Subjects Section of the Research Plan.
+% Refer to Part II, Supplemental Instructions for Preparing the Human Subjects Section of the Research Plan.
 This section is required for applicants answering "yes" to the question "Are human subjects involved?" on the R\&R Other Project Information form and the research does not fall under Exemption 4.
 
-%----------------------------------------------------------------------------------------
-%	INCLUSION OF CHILDREN
-%----------------------------------------------------------------------------------------
+% %----------------------------------------------------------------------------------------
+% %	INCLUSION OF CHILDREN
+% %----------------------------------------------------------------------------------------
 
-\newpage
+% \newpage
 
-%\section*{8. Targeted/Planned Enrollment} - form to fill out 
-\section*{9. Inclusion of Children}
+% %\section*{8. Targeted/Planned Enrollment} - form to fill out 
+% \section*{9. Inclusion of Children}
 
-Refer to Supplemental Instructions for Preparing the Human Subjects Section of the Research Plan, Sections 4.4 and 5.7.
+% Refer to Supplemental Instructions for Preparing the Human Subjects Section of the Research Plan, Sections 4.4 and 5.7.
 For applicants answering "Yes" to the question "Are human subjects involved" on the R\&R Other Project Information Form and the research does not fall under Section 4, this section is required.
 
-%----------------------------------------------------------------------------------------
-%	VERTEBRATE ANIMALS
-%----------------------------------------------------------------------------------------
+% %----------------------------------------------------------------------------------------
+% %	VERTEBRATE ANIMALS
+% %----------------------------------------------------------------------------------------
 
-\newpage
+% \newpage
 
-\section*{10. Vertebrate Animals}
+% \section*{10. Vertebrate Animals}
 
-If Vertebrate Animals are involved in the project, address each of the five points below.
+% If Vertebrate Animals are involved in the project, address each of the five points below.
 This section should be a concise, complete description of the animals and proposed procedures.
@@
 
-If the involvement of animals is indefinite, provide an explanation and indicate when it is anticipated that animals will be used.
+% If the involvement of animals is indefinite, provide an explanation and indicate when it is anticipated that animals will be used.
 If an award is made, prior to the involvement of animals the grantee must submit to the NIH awarding office detailed information as required in points 1-5 above and verification of IACUC approval.
 If the grantee does not have an Animal Welfare Assurance then an appropriate Assurance will be required (See Part III, Section 2.2 Vertebrate Animals for more information).
-The five points are as follows:
+% The five points are as follows:
 
-\begin{enumerate}
-	\item Provide a detailed description of the proposed use of the animals in the work outlined in the Research Strategy section.
+% \begin{enumerate}
+% 	\item Provide a detailed description of the proposed use of the animals in the work outlined in the Research Strategy section.
 Identify the species, strains, ages, sex, and numbers of animals to be used in the proposed work.
-	\item Justify the use of animals, the choice of species, and the numbers to be used.
+% 	\item Justify the use of animals, the choice of species, and the numbers to be used.
 If animals are in short supply, costly, or to be used in large numbers, provide an additional rationale for their selection and numbers.
-	\item Provide information on the veterinary care of the animals involved.
-	\item Describe the procedures for ensuring that discomfort, distress, pain, and injury will be limited to that which is unavoidable in the conduct of scientifically sound research.
+% 	\item Provide information on the veterinary care of the animals involved.
+% 	\item Describe the procedures for ensuring that discomfort, distress, pain, and injury will be limited to that which is unavoidable in the conduct of scientifically sound research.
 Describe the use of analgesic, anesthetic, and tranquilizing drugs and/or comfortable restraining devices, where appropriate, to minimize discomfort, distress, pain, and injury.
-	\item Describe any method of euthanasia to be used and the reasons for its selection.
+% 	\item Describe any method of euthanasia to be used and the reasons for its selection.
 State whether this method is consistent with the recommendations of the American Veterinary Medical Association (AVMA) Guidelines on Euthanasia.
 If not, include a scientific justification for not following the recommendations.
-\end{enumerate}
+% \end{enumerate}
 
-Do not use the vertebrate animal section to circumvent the page limits of the Research Strategy.
+% Do not use the vertebrate animal section to circumvent the page limits of the Research Strategy.
 
-%----------------------------------------------------------------------------------------
-%	SELECT AGENT RESEARCH
-%----------------------------------------------------------------------------------------
+% %----------------------------------------------------------------------------------------
+% %	SELECT AGENT RESEARCH
+% %----------------------------------------------------------------------------------------
 
-\newpage
+% \newpage
 
-\section*{11. Select Agent Research}
+% \section*{11. Select Agent Research}
 
-Select Agents are hazardous biological agents and toxins that have been identified by DHHS or USDA as having the potential to pose a severe threat to public health and safety, to animal and plant health, or to animal and plant products.
+% Select Agents are hazardous biological agents and toxins that have been identified by DHHS or USDA as having the potential to pose a severe threat to public health and safety, to animal and plant health, or to animal and plant products.
 CDC maintains a list of these agents.
@@
 
-%----------------------------------------------------------------------------------------
-%	MULTIPLE PD/PI LEADERSHIP PLAN
-%----------------------------------------------------------------------------------------
+% %----------------------------------------------------------------------------------------
+% %	MULTIPLE PD/PI LEADERSHIP PLAN
+% %----------------------------------------------------------------------------------------
 
-\newpage
+% \newpage
 
-\section*{12. Multiple PD/PI Leadership Plan}
+% \section*{12. Multiple PD/PI Leadership Plan}
 
-For applications designating multiple PD/PIs, a leadership plan must be included.
+% For applications designating multiple PD/PIs, a leadership plan must be included.
 A rationale for choosing a multiple PD/PI approach should be described.
@@
 
-If budget allocation is planned, the distribution of resources to specific components of the project or the individual PD/PIs should be delineated in the Leadership Plan.
+% If budget allocation is planned, the distribution of resources to specific components of the project or the individual PD/PIs should be delineated in the Leadership Plan.
 In the event of an award, the requested allocations may be reflected in a footnote on the Notice of Grant Award.
 
-%----------------------------------------------------------------------------------------
-%	CONSORTIUM/CONTRACTUAL ARRANGEMENTS
-%----------------------------------------------------------------------------------------
+% %----------------------------------------------------------------------------------------
+% %	CONSORTIUM/CONTRACTUAL ARRANGEMENTS
+% %----------------------------------------------------------------------------------------
 
-\newpage
+% \newpage
 
-\section*{13. Consortium/Contractual Arrangements}
+% \section*{13. Consortium/Contractual Arrangements}
 
-Explain the programmatic, fiscal, and administrative arrangements to be made between the applicant organization and the consortium organization(s).
+% Explain the programmatic, fiscal, and administrative arrangements to be made between the applicant organization and the consortium organization(s).
 If consortium/contractual activities represent a significant portion of the overall project, explain why the applicant organization, rather than the ultimate performer of the activities, should be the grantee.
@@
 
-\emph{The appropriate programmatic and administrative personnel of each organization involved in this grant application are aware of the agency's consortium agreement policy and are prepared to establish the necessary inter-organizational agreement(s) consistent with that policy.}
+% \emph{The appropriate programmatic and administrative personnel of each organization involved in this grant application are aware of the agency's consortium agreement policy and are prepared to establish the necessary inter-organizational agreement(s) consistent with that policy.}
 
-%----------------------------------------------------------------------------------------
-%	RESOURCE SHARING
-%----------------------------------------------------------------------------------------
+% %----------------------------------------------------------------------------------------
+% %	RESOURCE SHARING
+% %----------------------------------------------------------------------------------------
 
-\newpage
+% \newpage
 
-%   \section*{14. Letters of Support} - letters to attach
-\section*{15. Resource Sharing}
+% %   \section*{14. Letters of Support} - letters to attach
+% \section*{15. Resource Sharing}
 
-NIH considers the sharing of unique research resources developed through NIH-sponsored research an important means to enhance the value and further the advancement of the research.
+% NIH considers the sharing of unique research resources developed through NIH-sponsored research an important means to enhance the value and further the advancement of the research.
 When resources have been developed with NIH funds and the associated research findings published or provided to NIH, it is important that they be made readily available for research purposes to qualified individuals within the scientific community.
@@
 
-\begin{enumerate}
-	\item{Data Sharing Plan:} Investigators seeking \$500,000 or more in direct costs (exclusive of consortium F\&A) in any year are expected to include a brief 1-paragraph description of how final research data will be shared, or explain why data-sharing is not possible.
+% \begin{enumerate}
+% 	\item{Data Sharing Plan:} Investigators seeking \$500,000 or more in direct costs (exclusive of consortium F\&A) in any year are expected to include a brief 1-paragraph description of how final research data will be shared, or explain why data-sharing is not possible.
 Specific Funding Opportunity Announcements may require that all applications include this information regardless of the dollar level.
@@
 See Data-Sharing Policy or http://grants.nih.gov/grants/guide/notice- files/NOT-OD-03-032.html.
-	\item{Sharing Model Organisms:} Regardless of the amount requested, all applications where the development of model organisms is anticipated are expected to include a description of a specific plan for sharing and distributing unique model organisms or state why such sharing is restricted or not possible.
+% 	\item{Sharing Model Organisms:} Regardless of the amount requested, all applications where the development of model organisms is anticipated are expected to include a description of a specific plan for sharing and distributing unique model organisms or state why such sharing is restricted or not possible.
 See Sharing Model Organisms Policy, and NIH Guide NOT-OD-04-042.
-	\item{Genome Wide Association Studies (GWAS):} Applicants seeking funding for a genome-wide association study are expected to provide a plan for submission of GWAS data to the NIH-designated GWAS data repository, or an appropriate explanation why submission to the repository is not possible.
+% 	\item{Genome Wide Association Studies (GWAS):} Applicants seeking funding for a genome-wide association study are expected to provide a plan for submission of GWAS data to the NIH-designated GWAS data repository, or an appropriate explanation why submission to the repository is not possible.
 GWAS is defined as any study of genetic variation across the entire genome that is designed to identify genetic associations with observable traits (such as blood pressure or weight) or the presence or absence of a disease or condition.
 For further information see Policy for Sharing of Data Obtained in NIH Supported or Conducted Genome-Wide Association Studies, NIH Guide NOT-OD-07-088, and http://grants.nih.gov/grants/gwas/.
-\end{enumerate}
+% \end{enumerate}
 

### 2021-05-07 nih2/NIHGrant.tex
Draft to Adam

@@
 top-down processing in speech with the presentation of rich, vague stimuli to elicit responses from
-listeners \hl{(Warren \& Warren, 1970; Vokey \& Read 1985)}. These studies provide clear evidence that rich
+listeners \cite{warrenAuditoryIllusionsConfusions1970,vokeySubliminalMessagesDevil1985}.
+These studies provide clear evidence that rich
 stimuli, such as white noise, are sufficient to engage the top-down process, even if they do not attempt to
@@
 recent advance in signal processing which has led to dramatic improvements the efficiency of traditional
-sampling and signal estimation methods (Baraniuk, 2007). Compressive sensing has recently gained
-wide recognition in domains such as medical imaging (Graff \& Sidky, 2015; Lustig et al., 2008), where
+sampling and signal estimation methods \cite{baraniukCompressiveSensingLecture2007}. Compressive sensing has recently gained
+wide recognition in domains such as medical imaging \cite{graffCompressiveSensingMedical2015,lustigCompressedSensingMRI2008}, where
 considerations of efficiency and bias reduction are critical. Compressive sensing holds promise to
@@
 The proposed project is innovative for several reasons.
-First, we will leverage interdisciplinary collaboration between engineering (Lammert)
-and hearing science (Ben) to characterize tinnitus to inform clinical care.
+First, we will leverage interdisciplinary collaboration between engineering (Adam Lammert)
+and hearing science (Ben Parrell) to characterize tinnitus to inform clinical care.
 Second, we will apply reverse correlation to the tinnitus domain in a novel application,
@@
 are presented \cite{smithMeasuringInternalRepresentations2012} (\hl{CITE}).
-
-\hl{What are we doing to create the stimuli?}
-
-% \begin{description}
-% 	\item[C.1.2. Experimental Procedure] 
-% \end{description}
+The basic approach will be to use inverse Fourier transforms to generate 0.5-s noise stimuli
+including frequencies from 0.1 to 22 kHz.
+We will impose minimal constraints on the stimuli generation process,
+in order to selectively generate stimuli approaching the heterogeneous samples of tinnitus percepts
+provided by the American Tinnitus Association on their website.
 
@@
 
-\hl{Where are we getting our subjects?}
-
-\hl{How are we evaluating tinnitus in our subjects?}
-
-\hl{How do we phrase what we want the subjects to do?}
-
-% \begin{description}
-% 	\item[C.1.3. Reconstructing Representations] 
-% \end{description}
+Subjects will be recruited from the clinical population by \hl{our clinical collaborator}
+and will be assessed by the Tinnitus Severity Scale.
+We will not screen for unilateral or bilateral tinnitus but will only include subjects
+with primary (\ie subjective, not somatosensory) tinnitus.
+
+During the experiment, subjects will be asked to perform an computerized alternate forced-choice task,
+selecting whether the presented stimulus sounds similar to their tinnitus percept or not.
+Each signal will be presented to subjects over headphones
+at a comfortable listening level ($\approx 75$ dB SPL).
+Subjects will be asked to perform the task in hour-long blocks with a rest period in-between.
+Subjects can perform the task for one or more blocks at their choice,
+and will be compensated for their participation.
 
@@
 We theorize that the classification spectrogram is used as a template vector
-against which stimuli were compared in a linear matching model of response generation.
+against which stimuli are compared in a linear matching model of response generation.
 
@@
 the inefficiencies of reverse correlation impact efforts
-to characterize phenomena as \hl{[word meaning minute, fine-grained, detailed, specific]} latent neural representations (\eg neural receptive fields) \cite{ringachReverseCorrelationNeurophysiology2004}
+to characterize phenomena as fine-grained as latent neural representations (\eg neural receptive fields) \cite{ringachReverseCorrelationNeurophysiology2004}
 and as high-level  as abstract psychological categories (\eg ``male'' vs. ``female'' faces)
@@
 obtained via the reverse correlation method.
-
-% \subsubsection*{C.2.1. Method}
-
-% In this section, we describe compressive sensing,
-% including applicability to data collected in the reverse correlation paradigm,
-% and demonstrate its effectiveness for improving the efficiency and accuracy
-% of estimates of cognitive representations.
 
@@
 
-\begin{enumerate}
-	\item What is the shape of the manifold of cognitive representations of tinnitus?
-	\item Is it reducible to fewer dimensions using PCA/t-SNE/UMAP?
-	\item Can clusters on the manifold/reduced representation be found?
-	What are those clusters?
-	\item Is this insight clinically useful?
-\end{enumerate}
+Our approach in this goal is to characterize the properties of uncovered representations
+through computational modeling.
+In Aim \#1, we will have collected tinnitus percept data using the reverse correlation method.
+In Aim \#2, we will have reconstructed high-dimensional representations of tinnitus percepts
+using both conventional and compressive sensing methods.
+In this Aim, we will characterize the space of representations
+to investigate correspondence between data-driven subtypes and qualitative subtypes,
+evaluate the stability of tinnitus percepts over time,
+and accelerate the diagnostic process.
+
+\paragraph{Data-driven tinnitus subtypes}
+
+Surveys of tinnitus patients have identified sixteen qualitative subtypes of tinnitus
+\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021,meikleTinnitusArchiveArchive2004,stoufferCharacterizationTinnitusTinnitus1990},
+but these categories are limited by the fuzziness of linguistic categories and the musical ability of the tinnitus patients.
+One tinnitus patient we interviewed, who has a degree in music performance,
+was able to identify her tinnitus as sounding like a particular note played on the crotales,
+a niche percussion instrument.
+For most tinnitus patients who lack the depth of vocabulary to explain their tinnitus percept that precisely,
+linguistic description of tinnitus can be vague and overlapping.
+For instance, two of the aforementioned categories are ``high tension wire'' and ``transformer noise,''
+which may mean different things to different people and are difficult to disambiguate.
+Therefore, we propose to perform a quantitative analysis of the recovered high-dimensional tinnitus percepts
+to reveal data-driven latent subtypes of tinnitus.
+
+We will perform a quantitative analysis based on latent variable analysis methods.
+Latent variable methods relate observed variation (\eg in tinnitus representations)
+to latent variables that capture the observed variation (\eg major variation types across tinnitus percepts).
+We will use principle component analysis (PCA), t-stochastic neighbor embedding (t-SNE; \cite{vandermaatenBarnesHutSNE2013}),
+and uniform manifold approximation and projection (UMAP; \cite{mcinnesUMAPUniformManifold2020}).
+Applying these dimensionality-reduction algorithms to a collection of representations
+will identify major modes of variation across those representations,
+and, in the case of PCA, provide an analysis of the proportion of variance explained by each mode
+(the PCA eigenvalues).
+Clusters of data points become readily visible in the lower-dimensional manifold generated
+by these unsupervised machine learning methods, each of which represents
+a data-driven tinnitus subtype.
+We will characterize these subtypes, identifying their properties and assigning them descriptive names.
+In the case of PCA and UMAP, new data can be mapped into the lower-dimensional manifold,
+allowing representations from new subjects to be classified into these subtypes.
+
+\paragraph{Stability of tinnitus percepts over time}
+
+It is an open question in tinnitus research, whether tinnitus percepts remain stable over time
+\cite{husainReplicabilityNeuralBehavioral2019}.
+Using data from subjects who returned to perform the experiment multiple times
+over the course of several weeks,
+we will examine representations derived from each experiment instance
+to quantitatively evaluate drift in the tinnitus representation over time.
+We will assess measures of variance and spectral distance between representations
+computed during different temporally-separated experiment sessions.
+
+\paragraph{Acceleration of diagnosis through subtype identification}
+
+While we anticipate remarkable performance gains in the number of samples required for accurate representation
+through compressive sensing,
+it may be clinically useful to identify only the subtype of tinnitus
+(\ie which cluster on the lower-dimensional manifold the representation belongs to)
+to some convergent accuracy.
+If only the subtype is needed,
+we believe the number of samples required for convergent accuracy can be further reduced.
+We will devise an algorithm to perform the data-driven tinnitus subtyping ``online''
+while the subject performs the task.
+When convergent accuracy is reached, the task will automatically conclude.
+By this process, both patient and clinician time is optimized, while still providing high-fidelity quantitative medical data
+for use in diagnosis and treatment.
 

### 2021-05-18 paper/NIHGrant.tex
Rename and delete old files

--- 2021-05-07 nih2/NIHGrant.tex
@@
 
+To reconstruct cognitive representations of tinnitus from a binary classification task.
 Participants will classify white noise stimuli as sounding like their tinnitus or not.
-We will use reverse correlation to infer an unbiased estimate of each participant's cognitive representation of their tinnitus percept.
+Reverse correlation will be used to infer an unbiased estimate of each participant's
+cognitive representation of their tinnitus percept.
 
@@
 
-The efficiency of this method can be optimized to require fewer samples using advanced signal processing techniques.
-We will develop an open-source compressive sensing data analysis pipeline to acquire convergent cognitive representations using fewer trials.
-Our pilot data demonstrates that compressive sensing affords a 90\% decrease in number of trials for equivalent resulant latent representation.
-We will also develop and distribute an open-source software implementation the of the reverse correlation method for speech perception,
-including the proposed compressive sensing framework, for use by the research community.
+To enhance the efficiency of reverse correlation using compressive sensing,
+which requires significantly fewer samples to achieve convergent accuracy.
+The reverse correlation and compressive sensing framework will be released
+as an open-source software implementation for use by the research community.
+Our pilot data demonstrates that compressive sensing affords a 90\% decrease
+in the number of trials for equivalent resultant latent representation.
 
@@
 
-Our compressive sensing framework will allow for rapid data acquisition from participants.
-We will characterize cognitive representations of tinnitus between participants and over time.
-What is the space of tinnitus cognitive representations?
-Are there subtypes or clusters on a lower dimensional manifold?
-We will employ dimensionality reduction and clustering algorithms to represent and visualize the data,
-providing direct insight into commonalities and variability of tinnitus experience in and between subjects.
+To characterize cognitive representations of tinnitus between participants and over time.
+Dimensionality reduction algorithms will reveal latent similarities between
+tinnitus representations which will be subtyped using a data-driven approach.
+
+% Our compressive sensing framework will allow for rapid data acquisition from participants.
+% We will characterize cognitive representations of tinnitus between participants and over time.
+% What is the space of tinnitus cognitive representations?
+% Are there subtypes or clusters on a lower dimensional manifold?
+% We will employ dimensionality reduction and clustering algorithms to represent and visualize the data,
+% providing direct insight into commonalities and variability of tinnitus experience in and between subjects.
 
@@
 are inefficient and introduce bias, resulting in a lack of standardization in tinnitus assessment \cite{henryTinnitusEpidemiologicPerspective2020}.
-Alternate forced-choice (AFC) paradigm tasks ask the patient to determine which of two sounds
+One common method is the alternate forced-choice (AFC) paradigm task, which asks the patient to determine which of two sounds
 is closer to their tinnitus percept
@@
 Tinnitus percepts are too heterogeneous to be represented by pure tones or small-envelope waveforms.
+\autoref{fig:tinnitusexamples} displays spectrograms of example tinnitus percepts
+from the American Tinnitus Association website,
+showing the heterogeneity of tinnius percepts as well as their richness in frequency spectra and temporal characteristics.
 Adequately sampling the psychoacoustic space of possible tinnitus percepts via an AFC task is unfeasible.
@@
 \cite{gosselinSuperstitiousPerceptionsReveal2003}.
+
+\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
+	\centering
+	\includegraphics[width=0.8\textwidth]{Figures/Figures_tinnitus_6.png}
+	\caption{Examples of tinnitus spectrograms from the American Tinnitus Association website.
+	These spectrograms are heterogeneous as well as high-dimensional; the signals contain many frequency bands and vary over time.}
+	\label{fig:tinnitusexamples}
+\end{figure}
 
@@
 reverse correlation can effectively characterize cognitive representations underlying letter and face
-recognition \hl{(Fig 2A)} \cite{gosselinSuperstitiousPerceptionsReveal2003,liuSeeingJesusToast2014}.
+recognition \cite{gosselinSuperstitiousPerceptionsReveal2003,liuSeeingJesusToast2014}.
 One speech study has also estimated steady-state representations of vowels the /a/
@@
 each of which has limitations (\autoref{tab:approaches}).
+
 One approach is to use forced-choice selection tasks.
@@
 
-In a set of two experiments described below, we propose to implement a reverse correlation
+We propose to implement a reverse correlation
 approach for recovering cognitive representations of speech which allows for unconstrained, direct
@@
 Participants will be asked to classify random auditory stimuli as containing or not containing their tinnitus percept.
-Latent representations that drive the top-down process
+This is a transductive task that we model as comparing a stimulus to a latent ``cognitive template'' in a top-down process
+(\autoref{fig:template}).
+The latent representation that drives that top-down process
 can then be estimated by regressing observed responses against the stimuli over many trials \cite{mineaultImprovedClassificationImages2009}.
+We use random stimuli in order to sample the space of percepts without biasing towards any particular representation, a problem with other approaches.
+
+\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
+	\centering
+	\includegraphics[width=0.8\textwidth]{Figures/Figures_tinnitus_1.png}
+	\caption{Model of the discrimination task as a transductive process.
+	Random stimuli is filtered by the subject using low-level sensory mechanisms.
+	The perceptual discrimination task however is a top-down process that
+	compares the sensory information to a perceptual representation ``template''
+	to determine if the stimulus belongs to that perceptual representation.}
+	\label{fig:template}
+\end{figure}
 
 Reverse correlation has been applied across multiple fields to reveal underlying representations by application of unconstrained, noisy input.
-Reverse correlation has been used to characterize low-level latent representations encapsulated in neural tuning
+It has been used to characterize low-level latent representations encapsulated in neural tuning
 (\eg receptive fields) \cite{ringachReverseCorrelationNeurophysiology2004}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{Figures/BlankFigure.pdf}
+	\includegraphics[width=0.8\textwidth]{Figures/Figures_tinnitus_3.png}
 	\caption{Schematic overview of experiments proposed in Aim \#1.
@@
 stem from a process of comparing stimuli to latent representations
-($y = \Phi x$, for measurement $\Phi$).
+($y = \Phi x$, for measurement $\Phi$) (\autoref{fig:csexplanation}).
 It is then possible to estimate the latent representation
@@
 unusual model of sampling assumed by compressive sensing maps directly onto reverse correlation.
+
+\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
+	\centering
+	\includegraphics[width=0.8\textwidth]{Figures/Figures_tinnitus_5.png}
+	\caption{Comparison of reverse correlation and compressive sensing.
+	(\emph{a}) In reverse correlation, the vector of subject responses is modeled as
+	resulting from the multiplication of a latent representation vector, $x$,
+	and a stimulus matrix, $\Phi$, which can be thought of as a similarity calculation
+	between the latent representation and a vector representation of each presented stimulus.
+	(\emph{b}) An estimate of the latent representation, $\hat{x}$, is then reconstructed
+	by regressing responses against the stimuli.
+	(\emph{c}) In compressive sensing,
+	the vector of subject responses is modeled as resulting from the multiplication
+	of a sparse latent representation vector, $s$, and a compressive sensing matrix, $\Theta$.
+	The compressive sensing matrix is formed by multiplying a matrix of basis functions
+	by the stimulus matrix, $\Theta = \Phi \Psi$, which amounts to a similarity calculation
+	between the stimuli and the known basis functions.
+	(\emph{d}) An estimate of the sparse latent representation, $\hat{s}$, is then reconstructed
+	by regressing the responses against the compressive sensing sparse representations
+	and known basis functions, $\hat{x} = \Psi \hat{s}$. Note that the response vector, $y$,
+	in compressive sensing is generally assumed to contain many fewer entries than
+	in reverse correlation without sacrificing reconstruction accuracy.}
+	\label{fig:csexplanation}
+\end{figure}
 

### 2021-05-23 paper/NIHGrant.tex
Add new figures, section on VAEs/manifold

@@
 	The proposed approach, featured in the final row, is the only approach that can directly
-	uncover a time-frequency map of the cognitive representation that best explains tinnitus percepts.}
+	uncover a time-frequency map of the cognitive representation (a spectrogram) that best explains tinnitus percepts.}
 	\label{tab:approaches}
@@
 characterization of latent representations from yes-no responses to randomly-generated stimuli.
-Participants will be asked to classify random auditory stimuli as containing or not containing their tinnitus percept.
-This is a transductive task that we model as comparing a stimulus to a latent ``cognitive template'' in a top-down process
+Participants will be asked to classify auditory stimuli,
+which vary in their time-frequency content, as containing or not containing their tinnitus percept.
+This is a transductive task which we model as comparing a stimulus to a latent ``cognitive template'' in a top-down process
 (\autoref{fig:template}).
@@
 can then be estimated by regressing observed responses against the stimuli over many trials \cite{mineaultImprovedClassificationImages2009}.
-We use random stimuli in order to sample the space of percepts without biasing towards any particular representation, a problem with other approaches.
+We use random stimuli,
+\ie stimuli where the frequency magnitudes are randomly chosen, in order to sample the space of percepts without biasing towards any particular representation, a problem with other approaches.
+We will consider both time-varying and stationary stimuli, \ie where the spectral content of the stimuli changes over time and where it remains constant.
 
@@
 	Random stimuli is filtered by the subject using low-level sensory mechanisms.
-	The perceptual discrimination task however is a top-down process that
+	The perceptual discrimination task is modeled as a top-down process that
 	compares the sensory information to a perceptual representation ``template''
@@
 	\caption{Schematic overview of experiments proposed in Aim \#1.
+	Subjects are presented with random stimuli,
+	which is compared to a latent internal representation.
+	Reverse correlation is used to reconstruct the latent internal representation
+	from many trials.
 	Simulation results are shown, demonstrating proof-of-concept
@@
 Since compressive sensing can be directly substituted for conventional, regression-based estimation,
-it can be directly substituted into eixsting experimental protocols without requiring other changes.
+it can be directly substituted into existing experimental protocols without requiring other changes.
 Our ultimate objective is to develop and validate a compressive sensing
@@
 	with a comparatively small number of samples.
-	The latent representation in \emph{A} is estimated in \emph{B-E}.
-	In \emph{B-C} conventional regression-based estimation is used
-	and in \emph{D-E} compressive sensing is used.
+	The latent representation in (\emph{A}) is estimated in (\emph{B-E}).
+	In (\emph{B-C}) conventional regression-based estimation is used
+	and in (\emph{D-E}) compressive sensing is used.
 	The number of samples $n$ is displayed along with the correlation coefficient $r^2$
@@
 will identify major modes of variation across those representations,
-and, in the case of PCA, provide an analysis of the proportion of variance explained by each mode
-(the PCA eigenvalues).
+uncovering latent similarities between representations.
 Clusters of data points become readily visible in the lower-dimensional manifold generated
 by these unsupervised machine learning methods, each of which represents
-a data-driven tinnitus subtype.
+a data-driven tinnitus subtype (\autoref{fig:dimredexample}).
 We will characterize these subtypes, identifying their properties and assigning them descriptive names.
@@
 
-\paragraph{Stability of tinnitus percepts over time}
-
-It is an open question in tinnitus research, whether tinnitus percepts remain stable over time
-\cite{husainReplicabilityNeuralBehavioral2019}.
-Using data from subjects who returned to perform the experiment multiple times
-over the course of several weeks,
-we will examine representations derived from each experiment instance
-to quantitatively evaluate drift in the tinnitus representation over time.
-We will assess measures of variance and spectral distance between representations
-computed during different temporally-separated experiment sessions.
+\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
+	\centering
+	\includegraphics[width=0.8\textwidth]{Figures/umap.png}
+	\caption{Tinnitus representations with different spectral characteristics cluster in a lower dimensional manifold.
+	Tinnitus representation waveforms were generated using examples from the American Tinnitus Association website with added Gaussian noise.
+	(\emph{a}) shows the frequency spectra for representative waveforms. In (\emph{b}), the waveforms
+	are dimensonally-reduced using UMAP from 8,193 dimensions to 2.
+	The waveforms cluster in this lower dimensional, revealing latent similarities.}
+	\label{fig:dimredexample}
+\end{figure}
+
+\paragraph{Improving stimuli generation through data-driven distributions}
+
+In Aim \#1, we generate stimuli by randomly sampling Fourier coefficients from a flat distribution to generate a spectrum.
+We enforce minimal constraints on the stimuli (\eg that the frequency content is audible).
+This has the benefit of reducing bias in the reconstructed representations,
+but results in experiments that take longer to converge to a good reconstruction.
+Previous studies using reverse correlation have attempted to reduce noise in the reconstructed representation
+(and thus converge much faster) by carefully selecting stimuli biased towards a certain representation.
+For example, Smith and colleagues \cite{smithMeasuringInternalRepresentations2012}
+devised a task to uncover cognitive representations of faces using reverse correlation,
+using pictures of human faces distorted by noise as stimuli for the task.
+While this allowed the experimenters to perform fewer trials to achieve good reconstructions,
+it introduced bias of what experimenters think human faces look like (by selecting the pictures),
+defeating one of the main advantages of reverse correlation.
+
+We propose to improve stimuli generation by exploiting our data from subsequent experiments.
+Each putative reconstruction that we uncover leads to a new known data point hypothesized to lie on the manifold
+of tinnitus representations.
+We can treat this manifold much like a distribution and sample our stimuli from it,
+resulting in stimuli that sound ``less random'' and more like actual tinnitus percepts.
+This closed-loop experimental protocol means that our stimuli generation becomes more tinnitus-like
+with every reconstruction, without introducing experimenter bias \emph{a priori}.
+
+We will implement a variational autoencoder (VAE), a type of unsupervised machine learning model
+that learns a latent representation of data as well as how to generate new data
+that appears similar to data the model has been presented with before.
+A VAE consists of an encoder artificial neural network
+which constructs a latent representation
+as a zero-mean, unit-variance normal-distributed vector
+and a decoder artificial neural network
+that reconstructs the input (\autoref{fig:vae}).
+By training the VAE on reconstructed representations,
+forcing the encoder to create a latent representation
+and the decoder to reproduce the input from the latent representation,
+the model will learn the manifold of tinnitus percepts.
+By sampling the latent vector,
+we can generate new stimuli informed by the representations the model has learned.
+One limitation of VAEs is that sampling from the latent vector
+tends to produce new data points that appear noisy.
+In our experiment, this is a benefit,
+as noisy, random stimuli is crucial to reverse correlation.
+Through this generative model,
+we will create stimuli that appear closer to actual tinnitus percepts
+by learning directly from the data
+without introducing external experimenter bias.
+
+\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
+	\centering
+	\includegraphics[width=0.8\textwidth]{Figures/variational-autoencoder.png}
+	\caption{Diagram of a variational autoencoder (VAE) learning a representation of the digit ``2''.
+	VAEs assume that the data, $x$, are generated by a directed graphical model, $p_\theta(x|z)$,
+	and that the encoder is learning an approximation $q_\phi(z|x)$, where $\phi$ and $\theta$
+	denote the parameters of encoder and decoder respectively.
+	The latent representation, $z$, is interpreted as originating from a multivariate Gaussian distribution.
+	By sampling from the latent distribution, new data can be generated. Figure from \cite{IntroductionAutoencoders2020}.}
+	\label{fig:vae}
+\end{figure}
 
@@
 
+\paragraph{Stability of tinnitus percepts over time}
+
+It is an open question in tinnitus research, whether tinnitus percepts remain stable over time
+\cite{husainReplicabilityNeuralBehavioral2019}.
+Using data from subjects who returned to perform the experiment multiple times
+over the course of several weeks,
+we will examine representations derived from each experiment instance
+to quantitatively evaluate drift in the tinnitus representation over time.
+We will assess measures of variance and spectral distance between representations
+computed during different temporally-separated experiment sessions.
+
 % %----------------------------------------------------------------------------------------

### 2021-05-23 code/P.m

@@ -1,0 +1,10 @@
+function beta = P(alpha,gamma)
+
+beta = zeros(length(alpha),1);
+
+ind = abs(alpha)>gamma;
+
+beta(ind) = sign(alpha(ind)).*(abs(alpha(ind))-gamma);
+
+return
+%eof

### 2021-05-23 code/Script_tinnituscs.m

@@ -1,0 +1,327 @@
+% Inspired by 
+% o By S.Gibson, School of Physical Sciences, University of Kent. 
+% o 1st May, 2013.
+% o version 1.0
+% o NOTES: If the max number of iterations exceeds 25, error sometimes
+%   occurs in l1eq_pd function call.
+%
+% www.mathworks.com/matlabcentral/fileexchange/41792-simple-compressed-sensing-example
+
+%%%%%%%%%%%%%%%%%%%
+
+% FIDDLE WITH:
+% noisyness of subject selection process (below)
+% cs samples - parameter m (below)
+% biht parameter - sparsity (biht code) - lower (<64) is better
+% basis type (1d vs 2d) - rougly the same, preference for 2D
+
+%%%%%%%%%%%%%%%%%%%
+% Setup
+
+l = 100000;
+
+A = imread('Screeching.png');
+A = rgb2gray(A);
+A = imresize(A,1024/size(A,1)); % 0.3
+A = imresize(A,[min(size(A)) min(size(A))]); % 0.3
+A = double(A)./256;
+
+% Convert image to spectrum
+A = mean(A,2);
+A = 20.*log10(mean(A,2));
+A = flipud(A);
+A(1:5) = -4;
+
+n = length(A);
+m = 12500; % 2.5% of recommended 20k trials
+
+%%%%%%%%%%%%%%%%%%%
+% Real Basis
+
+ii = 32;
+b = dct(A);
+bm = zeros(n,1);
+[val idx] = sort(abs(b(:)),'descend');
+bm(abs(b)>val(ii)) = b(abs(b)>val(ii));
+
+AA = idct(bm);
+figure
+plot(A,'k');
+hold all
+plot(AA,'r')
+
+A = AA;
+
+%%%%%%%%%%%%%%%%%%%
+% Subject Selection Process
+
+AA = repmat(A',l,1);
+X = round(rand(l,n));
+
+% % Ideal selection
+% e = sum((X-AA).^2,2);
+% y = double(e>=prctile(e,49.5));
+% y(y==0) = -1;
+
+% Ideal Selection
+e = X*A;
+y = double(e>=prctile(e,50));
+y(y==0) = -1;
+
+% % % % Noisy selection
[…]

### 2021-05-23 code/pipeline.m

@@ -1,0 +1,181 @@
+%% End-to-end proof-of-concept for the data analysis in the proposal
+% using fake data.
+% This script assumes that we know the cognitive representations
+% of tinnitus for a number of patients,
+% and that those representations
+% are noised versions of the examples from the ATA website.
+
+data_dir = '/home/alec/data/sounds/';
+data_files = {
+    'ATA_Tinnitus_Buzzing_Tone_1sec.wav',
+    'ATA_Tinnitus_Electric_Tone_1sec.wav',
+    'ATA_Tinnitus_Roaring_Tone_1sec.wav',
+    'ATA_Tinnitus_Static_Tone_1sec.wav',
+    'ATA_Tinnitus_Tea_Kettle_Tone_1sec.wav'
+};
+data_names = {
+    'buzzing',
+    'electric',
+    'roaring',
+    'static',
+    'tea kettle'
+};
+
+plot_alpha = 0.03;
+
+%% Compute gold-standard spectra
+
+s = {};
+f = {};
+for ii = 1:length(data_files)
+    [s{ii}, f{ii}] = wav2spect([data_dir, data_files{ii}]);
+end
+s = [s{:}];
+f = [f{:}];
+
+% % plot the spectra
+% figure
+% plot(f(:, 1)/1e3, s)
+% xlabel('frequency (kHz)')
+% ylabel('magnitude')
+% title('canonical spectra')
+
+%% Generate fake data
+
+n_data_points_per_cluster = 20;
+n_data_points = n_data_points_per_cluster * length(data_files);
+noise_magnitude = 1;
+
+% replicate the canonical representations
+% x = repmat(f, 1, n_data_points);
+labels = repmat(1:length(data_files), n_data_points_per_cluster, 1)';
+y = repmat(s, 1, n_data_points_per_cluster);
+
+% convert to dB
+y = 10 * log10(y);
+
+% add Gaussian noise
+y = y + noise_magnitude * randn(size(y));
+
+% % plot the spectra
+% figure
+% plot(f(:, 1)/1e3, y)
+% xlabel('frequency (kHz)')
+% ylabel('magnitude')
+% title('noisy spectra')
+
+%% Compute low-dimensional representation
+
+U = UMAP();
+y_new = U.fit_transform(y');
+
[…]

### 2021-05-23 code/wav2spect.m

@@ -1,0 +1,17 @@
+function [s, f] = wav2spect(audio_file)
+    % Reads an audio file (e.g., a .wav file)
+    % and returns a spectogram
+    % in terms of magnitudes, s, and frequencies, f, in Hz.
+
+    % read the audio file
+    [audio, fs] = audioread(audio_file);
+
+    % compute the short-time Fourier transform
+    [s, f] = spectrogram(audio, [], [], [], fs);
+
+    % average out temporal information
+    s = mean(abs(s), 2);
+
+    return
+end
+    

### 2021-05-23 code/zhangpassivegamma.m

@@ -1,0 +1,18 @@
+function s_hat = zhangpassivegamma(Phi,y,h)
+
+m = size(Phi,1);
+n = size(Phi,2);
+
+a = (1/m)*(Phi'*y);
+
+[val idx] = sort(abs(a),'descend');
+gamma = val(h+1);
+
+if norm(a,inf) <= gamma
+    s_hat = zeros(n,1);
+else
+    s_hat = (1/norm(P(a,gamma),2))*P(a,gamma);
+end
+
+return
+%eof

### 2021-06-01 paper/NIHGrant.tex
minor edits

@@
 
-To reconstruct cognitive representations of tinnitus from a binary classification task.
-Participants will classify white noise stimuli as sounding like their tinnitus or not.
-Reverse correlation will be used to infer an unbiased estimate of each participant's
-cognitive representation of their tinnitus percept.
+To reconstruct perceptual representations of tinnitus using a novel reverse correlation procedure.
+Participants with tinnitus will be presented with richly varying stimuli in the context of a yes-no behavioral response paradigm.
+Perceptual representations can be estimated by regressing observed responses against the stimuli over many trials.
+Reconstructed representations will be compared to conventional estimates of tinnitus from the same participants.
+Expected outcome: reconstructed representations of tinnitus will more detailed and less biased than any those obtained through conventional methods.
 
@@
 
-To enhance the efficiency of reverse correlation using compressive sensing,
-which requires significantly fewer samples to achieve convergent accuracy.
-The reverse correlation and compressive sensing framework will be released
-as an open-source software implementation for use by the research community.
-Our pilot data demonstrates that compressive sensing affords a 90\% decrease
-in the number of trials for equivalent resultant latent representation.
+To enhance the efficiency of the reverse correlation procedure using compressive sensing, which substantially reduces the number of trials required to accurately reconstruct perceptual representations.
+We will use compressive sensing to more efficiently and more accurately reconstruct cognitive representations using data obtained in Aim \#1.
+Expected outcome: compressive sensing is expected to improve efficiency of the reverse correlation procedure by up to 90\%.
+% The reverse correlation and compressive sensing framework will be released
+% as an open-source software implementation for use by the research community.
+% Our pilot data demonstrates that compressive sensing affords a 90\% decrease
+% in the number of trials for equivalent resultant latent representation.
 
@@
 
-To characterize cognitive representations of tinnitus between participants and over time.
-Dimensionality reduction algorithms will reveal latent similarities between
-tinnitus representations which will be subtyped using a data-driven approach.
+To characterize variability in perceptual representations of tinnitus between participants and over time.
+We will use unsupervised machine learning techniques to reveal latent similarities between tinnitus representations, and subsequently cluster those into distinct categories.
+Expected outcome: Unsupervised machine learning will identify distinct categories of tinnitus, which will allow us to further improve the effiency and accuracy of uncovering tinnitus representations through improved stimulus generation and representation classification.
+
+% Dimensionality reduction algorithms will reveal latent similarities between
+% tinnitus representations which will be subtyped using a data-driven approach.
 
@@
 in which the subject rates whether a presented stimulus is part of their tinnitus percept or not \cite{norenaPsychoacousticCharacterizationTinnitus2002}.
-While this method is able to capture more features of cognitive representations of tinnitus,
-it is time-consuming and limited by the aural skills of the subject \cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}.
-Both these approaches involve the subject comparing an external stimulus to their cognitive representation of the tinnitus percept,
+While these methods capture more features of cognitive representations of tinnitus,
+they are time-consuming and limited by the aural skills of the subject \cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}.
+Both AFC and likeness measures involve the subject comparing an external stimulus to their cognitive representation of the tinnitus percept,
 however AFC tasks introduce biases by artificially limiting the stimulus space and likeness measures are time-consuming.
@@
 	\includegraphics[width=0.8\textwidth]{Figures/Figures_tinnitus_6.png}
-	\caption{Examples of tinnitus spectrograms from the American Tinnitus Association website.
+	\caption{Examples of tinnitus spectrograms from the American Tinnitus Association website \cite{Symptoms2015}.
 	These spectrograms are heterogeneous as well as high-dimensional; the signals contain many frequency bands and vary over time.}
@@
 
-Reverse correlation, in addition to its prominence as an important tool relative to lower-level
-neural mechanisms, has been increasingly used for inferring higher-level cognitive representations,
+Reverse correlation has been increasingly used for inferring higher-level cognitive representations as well,
 including psychophysical kernels that drive the top-down processes of perception
@@
 recognition \cite{gosselinSuperstitiousPerceptionsReveal2003,liuSeeingJesusToast2014}.
-One speech study has also estimated steady-state representations of vowels the /a/
+One speech study has also estimated steady-state representations of vowels /a/
 and /i/ using a closely-related paradigm to the one proposed here (Fig 2B; \cite{brimijoinInternalRepresentationVowel2013}). Our
@@
 Incomplete characterizations of cognitive representations impoverish our scientific understanding of tinnitus,
-weak causal explanations for its etiology, and hinder progress towards effective treatments.
+weaken causal explanations for its etiology, and hinder progress towards effective treatments.
 Reverse correlation shows promise to provide a more complete characterization of cognitive representations of tinnitus
@@
 
-\begin{description}
-	\item[A.3. Rigor of the Prior Research]{}
-\end{description}
+% \begin{description}
+% 	\item[A.3. Rigor of the Prior Research]{}
+% \end{description}
 
@@
 using dimensionality-reduction and density-based clustering.
+We will use data regarding the space of tinnitus Representations
+to iteratively improve our stimulus generation and representation classification algorithms.
 In \emph{Aim \#1}, we will develop and run an experimental paradigm
@@
 answering the question, ``Does this sound like your tinnitus?''
+Instead of using limited, preconstructed stimuli, we will randomly sample from a distribution.
 Reverse correlation frees us from the methodological constraint of imposing strong \emph{a priori}
@@
 providing direct insight into commonalities and variability of tinnitus experience in and between subjects.
+Furthermore, we will use information about the distribution of representations
+to iteratively improve our stimulus generation and data-driven subtype classification processes.
 
@@
 
-One approach is to use forced-choice selection tasks.
-In this experimental paradigm,
+Two common approaches are alternate forced choice tasks with constructed stimuli
+and likeness measures.
+In the former experimental paradigm,
 the experimenter presents participants with multiple samples of auditory stimuli that vary in well-characterized
@@
 
+A third, more recent approach to uncovering cognitive representations is to employ neuroimaging
+(\eg fMRI) to identify neural activation patterns indicative of tinnitus.
+In investigations of functional connectivity in tinnitus patients,
+resting-state fMRI measures were found to be replicable and reliable,
+though no explicit representations have been proposed
+\cite{husainReplicabilityNeuralBehavioral2019}.
+This approach is also
+limited, in that it can only uncover representations that have a definite, localized seat in the brain.
+Cognitive representations, by contrast, are commonly understood to be constructs that need not have
+such a localized neural seat by definition, and which can best be revealed through analyzing behavior.
+
 The highly-constrained nature of stimuli used in the forced selection approach necessarily results
@@
 therefore may not systematically explore the entire space of perceptually-meaningful variables.
-
-A third, more recent approach to uncovering cognitive representations is to employ neuroimaging
-(\eg fMRI) to identify neural activation patterns indicative of tinnitus.
-In investigations of functional connectivity in tinnitus patients,
-resting-state fMRI measures were found to be replicable and reliable,
-though no explicit representations have been proposed
-\cite{husainReplicabilityNeuralBehavioral2019}.
-This approach is also
-limited, in that it can only uncover representations that have a definite, localized seat in the brain.
-Cognitive representations, by contrast, are commonly understood to be constructs that need not have
-such a localized neural seat by definition, and which can best be revealed through analyzing behavior.
 
@@
 into the auditory domain.
-Reverse correlation allows us (1) to uncover more complex, potentially higher-dimensional representations
+Reverse correlation allows us (\emph{a}) to uncover more complex, potentially higher-dimensional representations
 than would be possible using more focused, constrained stimuli,
-(2) to recover directly the nature of the representations themselves rather than the relation
+(\emph{b} to recover directly the nature of the representations themselves rather than the relation
 between the tinnitus percept and a masking sound,
-and (3) to recover cognitive representations of the tinnitus percept directly rather than a neural correlate.
+and (\emph{c}) to recover cognitive representations of the tinnitus percept directly rather than a neural correlate.
 In short, reverse correlation will be able to provide deeper understanding of cognitive representations of tinnitus percepts
@@
 where bandlimited random stimuli, or stimuli with partial superimposed templates,
-are presented \cite{smithMeasuringInternalRepresentations2012} (\hl{CITE}).
+are presented \cite{smithMeasuringInternalRepresentations2012}.
 The basic approach will be to use inverse Fourier transforms to generate 0.5-s noise stimuli
-including frequencies from 0.1 to 22 kHz.
+including frequencies from 0.1 to 22 kHz \cite{brimijoinInternalRepresentationVowel2013}.
 We will impose minimal constraints on the stimuli generation process,
 in order to selectively generate stimuli approaching the heterogeneous samples of tinnitus percepts
-provided by the American Tinnitus Association on their website.
+provided by the American Tinnitus Association on their website \cite{Symptoms2015}.
 
@@
 selecting whether the presented stimulus sounds similar to their tinnitus percept or not.
+They will be told that the stimuli are representations of tinnitus from other patients.
 Each signal will be presented to subjects over headphones
-at a comfortable listening level ($\approx 75$ dB SPL).
+at an audible level ($\approx 75$ dB SPL) after which
+the subject will select either ``yes'' or ``no'' via keyboard presses.
+The next trial will begin after a 500-ms pause.
 Subjects will be asked to perform the task in hour-long blocks with a rest period in-between.
@@
 	which is compared to a latent internal representation.
-	Reverse correlation is used to reconstruct the latent internal representation
-	from many trials.
+	Reverse correlation is used to reconstruct an estimate of the latent internal representation
+	over many trials.
 	Simulation results are shown, demonstrating proof-of-concept
@@
 for improving the efficiency of reverse correlation.
-Fpr example, using a template time-frequency representation, $x$,
+For example, using a template time-frequency representation, $x$,
 as a proxy for the latent representation of interest,
@@
 	and in (\emph{D-E}) compressive sensing is used.
-	The number of samples $n$ is displayed along with the correlation coefficient $r^2$
+	The number of samples, $n$, is displayed along with the correlation coefficient, $r^2$,
 	between the estimated reconstruction and the original signal,
@@
 but these categories are limited by the fuzziness of linguistic categories and the musical ability of the tinnitus patients.
-One tinnitus patient we interviewed, who has a degree in music performance,
+Tinnitus subtypes are used to better explain and quantify the condition,
+however qualitative subtypes are ill-defined.
+While one tinnitus patient we interviewed, who has a degree in music performance,
 was able to identify her tinnitus as sounding like a particular note played on the crotales,
-a niche percussion instrument.
-For most tinnitus patients who lack the depth of vocabulary to explain their tinnitus percept that precisely,
-linguistic description of tinnitus can be vague and overlapping.
-For instance, two of the aforementioned categories are ``high tension wire'' and ``transformer noise,''
-which may mean different things to different people and are difficult to disambiguate.
-Therefore, we propose to perform a quantitative analysis of the recovered high-dimensional tinnitus percepts
-to reveal data-driven latent subtypes of tinnitus.
-
-We will perform a quantitative analysis based on latent variable analysis methods.
+a niche percussion instrument,
+most tinnitus patients lack the depth of vocabulary to explain their tinnitus percept that precisely.
+Accordingly, linguistic description of tinnitus can be vague and overlapping.
+For instance, two of the subtypes in \cite{vajsakovicPrinciplesMethodsPsychoacoustic2021} are ``high tension wire'' and ``transformer noise.''
+Is ``high tension wire'' meant in the colloquial sense of high-voltage power lines,
+or does it mean the reverberation of a tightly-pulled string?
+If the latter, then how is the sound of a high-voltage power line
+disambiguated from the sound of a distribution transformer,
+which is
+mounted on a utility pole and connected directly to the high-voltage wires?
+Instead of linguistic categories, we propose to use latent variable analysis
+to reveal data-driven subtypes of tinnitus.
+
+We will perform a quantitative analysis of tinnitus representations based on latent variable analysis methods
+to reveal underlying similarities between representations.
 Latent variable methods relate observed variation (\eg in tinnitus representations)
 to latent variables that capture the observed variation (\eg major variation types across tinnitus percepts).
-We will use principle component analysis (PCA), t-stochastic neighbor embedding (t-SNE; \cite{vandermaatenBarnesHutSNE2013}),
-and uniform manifold approximation and projection (UMAP; \cite{mcinnesUMAPUniformManifold2020}).
+We will use principle component analysis (PCA) and uniform manifold approximation and projection (UMAP; \cite{mcinnesUMAPUniformManifold2020}).
 Applying these dimensionality-reduction algorithms to a collection of representations
@@
 We will characterize these subtypes, identifying their properties and assigning them descriptive names.
-In the case of PCA and UMAP, new data can be mapped into the lower-dimensional manifold,
+New data can be mapped into the lower-dimensional manifold,
 allowing representations from new subjects to be classified into these subtypes.
@@
 	\caption{Tinnitus representations with different spectral characteristics cluster in a lower dimensional manifold.
-	Tinnitus representation waveforms were generated using examples from the American Tinnitus Association website with added Gaussian noise.
-	(\emph{a}) shows the frequency spectra for representative waveforms. In (\emph{b}), the waveforms
+	Tinnitus representation waveforms were generated
+	using examples from the American Tinnitus Association website with added Gaussian noise
+	\cite{Symptoms2015}.
+	(\emph{a}) shows the frequency spectra for representative waveforms. (\emph{b}) The waveforms
 	are dimensonally-reduced using UMAP from 8,193 dimensions to 2.
-	The waveforms cluster in this lower dimensional, revealing latent similarities.}
+	The waveforms cluster in this lower dimensional space, revealing latent similarities.}
 	\label{fig:dimredexample}
@@
 In Aim \#1, we generate stimuli by randomly sampling Fourier coefficients from a flat distribution to generate a spectrum.
-We enforce minimal constraints on the stimuli (\eg that the frequency content is audible).
+We enforce only minimal constraints on the stimuli (\eg that the frequency content is audible).
 This has the benefit of reducing bias in the reconstructed representations,

### 2021-06-01 code/pipeline.m

@@ -44,7 +44,7 @@ f = [f{:}];
 
 n_data_points_per_cluster = 20;
 n_data_points = n_data_points_per_cluster * length(data_files);
-noise_magnitude = 1;
+noise_magnitude = 20;
 
 % replicate the canonical representations
 % x = repmat(f, 1, n_data_points);
@@ -68,11 +68,11 @@ y = y + noise_magnitude * randn(size(y));
 
 U = UMAP();
 y_new = U.fit_transform(y');
+y_new_pca = pca(y, 'NumComponents', 2);
 
 c = colormaps.linspecer(length(data_files));
 
-
-%% No Color, with Alpha
+%% No Color, with Alpha, PCA
 % plot some sample spectra
 % and the reduced representation
 fig1 = figure('outerposition',[3 3 1000 1000],'PaperUnits','points','PaperSize',[1000 1000]);
@@ -88,92 +88,58 @@ for ii = 1:length(data_files)
 end
 axis square
 xlabel(ax(1), 'frequency (kHz')
-ylabel(ax(1), 'magnitude')
+ylabel(ax(1), 'power (dB)')
 % set(ax(1), 'YScale', 'log')
-axlib.label(ax(1), 'a')
+axlib.label(ax(1), 'a', 'FontSize', 40)
 
 % plotting the reduced representation
 ax(2) = subplot(1, 2, 2);
+title('PCA projection')
 hold on
-gscatter(ax(2), y_new(:, 1), y_new(:, 2), labels(:), c);
-legend(data_names)
+gscatter(ax(2), y_new_pca(:, 1), y_new_pca(:, 2), labels(:), c);
+legend(data_names, 'Location', 'best')
 axis square
-xlabel('dim 1 (a.u.)')
-ylabel('dim 2 (a.u.)')
+xlabel('dimension 1')
+ylabel('dimension 2')
 axlib.equalize(ax(2),'x','y')
-axlib.label(ax(2), 'b')
+axlib.label(ax(2), 'b', 'FontSize', 40)
 
 figlib.pretty()
 figlib.tight()
 
 axlib.separate(ax(2))
 
-%% Color, no Alpha
+%% No Color, with Alpha, UMAP
 % plot some sample spectra
 % and the reduced representation
-fig2 = figure('outerposition',[3 3 1000 1000],'PaperUnits','points','PaperSize',[1000 1000]);
[…]

### 2021-06-01 paper/NIHGrant.tex
minor edits

@@
 
-To reconstruct cognitive representations from subject responses,
-we will generate a classification spectrogram by taking the difference
-between a spectrogram generated from the positive labels (the ``yes'' responses)
-and a spectrogram generated from the negative labels (the ``no'' responses)
+We will reconstruct cognitive representations of tinnitus from the data
+by taking the least-squares fit to the behavioral data
 (\autoref{fig:experiment}).
-Such reconstructed representations are the best least-squares fit to the behavioral data
+This is equivalent to interpreting the cognitive representation
+as a ``classification spectrogram''
+generated by subtracting the average of the negative trials from the average of the positive trials
 \cite{gosselinSuperstitiousPerceptionsReveal2003}.
-We theorize that the classification spectrogram is used as a template vector
+We theorize that in the underlying transductive cognitive process,
+that the classification spectrogram is used as a template vector
 against which stimuli are compared in a linear matching model of response generation.
+While we acknowledge that this reconstruction approach is inefficient,
+requiring many samples to acquire a coherent reconstruction,
+it is well-studied in the literature
+and will serve as a baseline against which our efficient reconstruction
+algorithm in Aim \#2 will be compared.
 

### 2021-06-10 paper/NIHGrant.tex
Add section on subject recruitment, start fiddling with reconstructing spectrograms

@@
 
-\paragraph{Experimental procedure}
+\paragraph{Subject Recruitment}
 
 Subjects will be recruited from the clinical population by \hl{our clinical collaborator}
-and will be assessed by the Tinnitus Severity Scale.
+and will be assessed by the Tinnitus Severity Scale,
+which measures the negative impact tinnitus has on a subject's quality of life.
 We will not screen for unilateral or bilateral tinnitus but will only include subjects
@@
 
+\paragraph{Experimental procedure}
+
 During the experiment, subjects will be asked to perform an computerized alternate forced-choice task,
 selecting whether the presented stimulus sounds similar to their tinnitus percept or not.
-They will be told that the stimuli are representations of tinnitus from other patients.
+They will be told that the stimuli are tinnitus-like sounds corrupted by noise
+and that not all will sound like their tinnitus percept.
 Each signal will be presented to subjects over headphones
@@
 The next trial will begin after a 500-ms pause.
-Subjects will be asked to perform the task in hour-long blocks with a rest period in-between.
-Subjects can perform the task for one or more blocks at their choice,
+Subjects will be asked to perform the task in 80-trial blocks with a rest period in-between.
+We will ask subjects to perform 20 blocks at minimum, which should take about a half an hour.
+Subjects can perform the task for more blocks at their choice,
 and will be compensated for their participation.
@@
 we can generate new stimuli informed by the representations the model has learned.
-One limitation of VAEs is that sampling from the latent vector
+One limitation of VAEs is that sampling from the latent distribution
 tends to produce new data points that appear noisy.

### 2021-06-10 code/script_tinnitus_2.m

@@ -1,0 +1,327 @@
+% Inspired by 
+% o By S.Gibson, School of Physical Sciences, University of Kent. 
+% o 1st May, 2013.
+% o version 1.0
+% o NOTES: If the max number of iterations exceeds 25, error sometimes
+%   occurs in l1eq_pd function call.
+%
+% www.mathworks.com/matlabcentral/fileexchange/41792-simple-compressed-sensing-example
+
+%%%%%%%%%%%%%%%%%%%
+
+% FIDDLE WITH:
+% noisyness of subject selection process (below)
+% cs samples - parameter m (below)
+% biht parameter - sparsity (biht code) - lower (<64) is better
+% basis type (1d vs 2d) - rougly the same, preference for 2D
+
+%%%%%%%%%%%%%%%%%%%
+% Setup
+
+l = 10000;
+
+A = imread('Screeching.png');
+A = rgb2gray(A);
+A = imresize(A,1024/size(A,1)); % 0.3
+A = imresize(A,[min(size(A)) min(size(A))]); % 0.3
+A = double(A)./256;
+
+% Convert image to spectrum
+A = mean(A,2);
+A = 20.*log10(mean(A,2));
+A = flipud(A);
+A(1:5) = -4;
+
+n = size(A, 1);
+m = 1250; % 2.5% of recommended 20k trials
+
+%%%%%%%%%%%%%%%%%%%
+% Real Basis
+
+% ii = 32;
+% b = dct(A);
+% bm = zeros(n,1);
+% [val idx] = sort(abs(b(:)),'descend');
+% bm(abs(b)>val(ii)) = b(abs(b)>val(ii));
+
+% AA = idct(bm);
+% figure
+% plot(A,'k');
+% hold all
+% plot(AA,'r')
+
+% A = AA;
+
+%%%%%%%%%%%%%%%%%%%
+% Subject Selection Process
+
+AA = repmat(A',l,1);
+X = round(rand(l,n));
+
+% % Ideal selection
+% e = sum((X-AA).^2,2);
+% y = double(e>=prctile(e,49.5));
+% y(y==0) = -1;
+
+% Ideal Selection
+e = X*A;
+y = double(e>=prctile(e,50));
+y(y==0) = -1;
+
[…]

### 2021-06-15 paper/NIHGrant.tex
Refactor script and add clarification edits to Aim #3

@@
 Tinnitus is the perception of ringing, buzzing, or hissing in the ears, which can range from mild and transient to debilitating.
-In the U.S. alone, it affects 45 million people per year, 30\% of which report their tinnitus to be moderate to severe.
-A primary form of treatment habituation therapy that retrains a patient’s nervous system by habituating it to external sounds that mimic the perceptual experience of the tinnitus sound.
-Habituation therapies require accurate estimates of patients’ tinnitus experience in order to promote patient outcomes.
-There is a pressing need for new approaches to uncovering individuals’ perceptual experience of tinnitus,
-because current estimation methods rely on strongly reductionist assumptions concerning the nature of tinnitus sounds, 
-and produce results that are correspondingly biased and incomplete.
-Reverse correlation holds promise in this regard,
-as a primary method used to characterize neural tuning that is known to allow for unconstrained and unbiased estimation of latent neural representations
-(\eg neural receptive fields) \cite{ringachReverseCorrelationNeurophysiology2004, nishimotoReceptiveFieldProperties2006},
-as well as higher-level cognitive representations, including psychophysical kernels that drive the top-down processes of perception 
-(\eg face or phoneme recognition) \cite{gosselinSuperstitiousPerceptionsReveal2003,smithMeasuringInternalRepresentations2012,neriReceptivePerceptiveFields2006,ahumadaStimulusFeaturesSignal1971},
-and even abstract psychological categories (\eg “male” vs. “female” faces)
-\cite{brinkmanVisualisingMentalRepresentations2017,manginiMakingIneffableExplicit2004,ponsotCrackingSocialCode2018},
-all on the basis of fairly simple stimulus-response data \cite{ljungMeasureLackFit1978,marmarelisWhiteNoiseMethodSystem1978}.
-Despite its wide acceptance in other areas of inquiry, reverse correlation has not been brought to bear with respect to uncovering tinnitus experience.
-
-Our \textbf{long-term goal} is to directly uncover and more completely characterize the perceptual experience of tinnitus using the demonstrated capabilities of the reverse correlation approach.
-Our guiding hypothesis is that reverse correlation will produce estimates of tinnitus percepts that are substantially more rich, individualized and unbiased than currently possible using existing approaches.
+In the U.S.
+alone, it affects 45 million people per year, 30\% of which report their tinnitus to be moderate to severe.
+A primary form of treatment is habituation therapy, that retrains a patient's nervous system by habituating its response to sounds that mimic the perceptual experience of the tinnitus sound.
+Habituation therapies require accurate estimates of patients' tinnitus experience in order to promote patient outcomes.
+There is a pressing need for new approaches to uncovering individuals' perceptual experience of tinnitus, because current estimation methods rely on strongly reductionist assumptions concerning the nature of tinnitus sounds, and produce results that are correspondingly biased and incomplete.
+Reverse correlation holds promise in this regard, as a primary method used to characterize neural tuning that is known to allow for unconstrained and unbiased estimation of latent neural representations (e.g., neural receptive fields) [29, 33], as well as higher-level cognitive representations, including psychophysical kernels that drive the top-down processes of perception (e.g., face or phoneme recognition) [1, 10, 28, 34], and even abstract psychological categories (e.g., male vs.
+female faces) [6, 22, 32], all on the basis of fairly simple stimulus-response data [20, 23].
+Despite its wide acceptance in characterizing neural and cognitive representations, reverse correlation has not been brought to bear with respect to uncovering tinnitus experience.
+
+Our long-term goal is to directly uncover and more completely characterize the perceptual experience of tinnitus using the demonstrated capabilities of the reverse correlation approach.
+Our guiding hypothesis is that reverse correlation will produce estimates of tinnitus percepts that are substantially more rich, individualized and unbiased than those currently possible using existing approaches.
 The rationale is that high quality characterization of tinnitus percepts can promote detailed assessment of tinnitus, helping to explain individual variability in tinnitus experience, and ultimately informing individualized treatment through enhanced habituation therapies.
-The proposed work will simultaneously improve the efficiency of the reverse correlation method itself, further enhancing its potential for adoption in clinical settings.
-We will test our central hypothesis and attain our objective via the following specific aims:
-
-\begin{description}
-	\item[Aim \#1: Uncover and reconstruct cognitive representations of tinnitus]{} 
-\end{description}
+The proposed work will furthermore improve the efficiency of the reverse correlation method itself, further enhancing its potential for adoption in clinical settings.
+We will test our guiding hypothesis and attain our objective via the following specific aims:
+
+\subsection*{Aim \#1: Uncover and reconstruct cognitive representations of tinnitus}
 
@@
 Reconstructed representations will be compared to conventional estimates of tinnitus from the same participants.
-Expected outcome: reconstructed representations of tinnitus will more detailed and less biased than any those obtained through conventional methods.
-
-\begin{description}
-	\item[Aim \#2: Develop efficient reconstruction algorithm for cognitive representations using compressive sensing]{} 
-\end{description}
+Expected outcome: reconstructed representations of tinnitus will be more detailed and less biased than any those obtained through conventional methods.
+\subsection*{Aim \#2: Develop efficient reconstruction algorithm for cognitive representations using compressive sensing}
 
@@
 Expected outcome: compressive sensing is expected to improve efficiency of the reverse correlation procedure by up to 90\%.
-% The reverse correlation and compressive sensing framework will be released
-% as an open-source software implementation for use by the research community.
-% Our pilot data demonstrates that compressive sensing affords a 90\% decrease
-% in the number of trials for equivalent resultant latent representation.
-
-\begin{description}
-	\item[Aim \#3: Characterize and interpret cognitive representations of tinnitus]{} 
-\end{description}
+
+\subsection*{Aim \#3: Characterize and categorize cognitive representations of tinnitus}
 
@@
 We will use unsupervised machine learning techniques to reveal latent similarities between tinnitus representations, and subsequently cluster those into distinct categories.
-Expected outcome: Unsupervised machine learning will identify distinct categories of tinnitus, which will allow us to further improve the effiency and accuracy of uncovering tinnitus representations through improved stimulus generation and representation classification.
-
-% Dimensionality reduction algorithms will reveal latent similarities between
-% tinnitus representations which will be subtyped using a data-driven approach.
-
-% Our compressive sensing framework will allow for rapid data acquisition from participants.
-% We will characterize cognitive representations of tinnitus between participants and over time.
-% What is the space of tinnitus cognitive representations?
-% Are there subtypes or clusters on a lower dimensional manifold?
-% We will employ dimensionality reduction and clustering algorithms to represent and visualize the data,
-% providing direct insight into commonalities and variability of tinnitus experience in and between subjects.
+Expected outcome: Unsupervised machine learning will identify distinct categories of tinnitus, which will allow us to further improve the efficiency and accuracy of uncovering tinnitus representations through improved stimulus generation and representation classification.
+\\
+
+Our expected outcomes are (a) a substantially more detailed understanding of tinnitus experience and its variation across patients and (b) an novel, simple and efficient method for characterizing tinnitus experience in new patients.
+This will have a positive impact on individualized assessment of tinnitus and habituation therapies, and ultimately holds potential for improving health outcomes for tinnitus patients.
 
@@
 
-\subsection*{C. Aim \#1: Uncover and reconstruct cognitive representations of tinnitus}
+\subsection*{C.1. Aim \#1: Uncover and reconstruct cognitive representations of tinnitus}
 
@@
 
-\subsubsection*{C.1. Method}
+\subsubsection*{Method}
 
@@
 
+Classification of tinnitus into subtypes allows clinicians
+and researchers to better understand the nature of the condition
+by performing statistical comparisons between discrete, meaningful patient categories.
 Surveys of tinnitus patients have identified sixteen qualitative subtypes of tinnitus
 \cite{vajsakovicPrinciplesMethodsPsychoacoustic2021,meikleTinnitusArchiveArchive2004,stoufferCharacterizationTinnitusTinnitus1990},
-but these categories are limited by the fuzziness of linguistic categories and the musical ability of the tinnitus patients.
+but the utility of these categories Is limited by the fuzziness of linguistic categories and the musical vocabulary of the tinnitus patients.
 Tinnitus subtypes are used to better explain and quantify the condition,
@@
 to reveal data-driven subtypes of tinnitus.
+This will result in a new data-driven framework for categorizing and communicating
+similarities and differences between tinnitus experiences.
 
@@
 	VAEs assume that the data, $x$, are generated by a directed graphical model, $p_\theta(x|z)$,
-	and that the encoder is learning an approximation $q_\phi(z|x)$, where $\phi$ and $\theta$
+	called the decoder,
+	and that the encoder, which maps from the input to the latent space, is learning an approximation $q_\phi(z|x)$. $\phi$ and $\theta$
 	denote the parameters of encoder and decoder respectively.
 	The latent representation, $z$, is interpreted as originating from a multivariate Gaussian distribution.
-	By sampling from the latent distribution, new data can be generated. Figure from \cite{IntroductionAutoencoders2020}.}
+	By sampling from the latent distribution and passing it through the decoder, new data can be generated. Figure from \cite{IntroductionAutoencoders2020}.}
 	\label{fig:vae}
@@
 while the subject performs the task.
-When convergent accuracy is reached, the task will automatically conclude.
-By this process, both patient and clinician time is optimized, while still providing high-fidelity quantitative medical data
+The algorithm monitors goodness-of-fit into the subtype space by posterior probability
+and concludes the task when convergence is reached.
+Through this process, both patient and clinician time is used efficiently, while still providing high-fidelity quantitative medical data
 for use in diagnosis and treatment.
@@
 computed during different temporally-separated experiment sessions.
+
+\section*{D. Involvement of Undergraduate Students and Other Trainees}
+
+The proposed projects will engage undergraduate students and other trainees extensively throughout the study period.
+In 2018, Worcester Polytechnic Institute (WPI) was ranked by the Wall Street Journal as \#1 in Universities that best blend research and teaching.
+WPI has several mechanisms that facilitate integrating students into research, and I have a longstanding personal interest and history of doing so.
+Additional details about the numbers of students who will participate in aspects of this research, and their specific roles, are found in the Personnel Justification.
+Briefly, students will contribute to the proposed research through three mechanisms: 
+(1) class projects, (2) as individual researchers in my lab, and (3) through Major Qualifying Projects (MQPs).
+I will personally oversee undergraduate student involvement, along with my Doctoral student Alec Hoyland.
+
+\paragraph{Class Projects}
+Students studying biomedical engineering must complete a rigorous data analysis (BME2211) course in their sophomore year.
+As part of that course, students complete a term-long project involving the collection of novel data sets and application of statistical modeling techniques to those data.
+All aims described here provide an ideal opportunity to engage students in the application of key methods in the proposed project.
+Students from this class will pilot the yes-no response protocols using existing code, and subsequently apply reverse correlation to the acquired data.
+Approximately 125 students per year take BME 2211.
+
+\paragraph{Individual Researchers}
+Each year my laboratory hosts 3-6 undergraduate student researchers who contribute to ongoing projects in the lab.
+These students typically start by volunteering 5-10 hours/week.
+However, many of them complete independent study projects and work (paid) for me over the summer, both of which require a high level of commitment and interest.
+Students will work on several aspects of the proposed project.
+Each will be given a specific experimental or technical question to answer that represents a subset of one of the Aims.
+For example, in Aim 2, students could be tasked to examine the effect of algorithmic parameters on compressive sensing reconstruction efficiency, in the interest of finding ideal parameter settings for reconstructing tinnitus representations on our collected data.
+Another pair might be tasked with determining the number of distinct tinnitus subtypes implied by the distribution of data.
+
+Our department hosts an NSF-sponsored Research Experiences for Undergraduates (REU) program, which includes support for a female or underrepresented minority student from another University.
+One REU student per year will work on a project related to this research.
+The REU program includes structured mentoring (pairing undergraduate with graduate students, completion of a mentoring agreement, mentor training, etc.) and professional development activities.
+All summer undergraduate students hosted by my laboratory will be able to participate in these REU-affiliated programs, whether they are formally part of the REU or not.
+
+\paragraph{Major Qualifying Projects (MQPs)}
+WPI is a nationally recognized leader in project-based learning at the undergraduate level.
+Our curriculum is built around open-ended, team-based projects that must be completed by every student as a graduation requirement.
+During the senior year, students must complete their MQP, a project that is equivalent to 9 semester credit-hours.
+MQPs are performed in teams of 3-5 students.
+I typically mentor multidisciplinary teams and students pursuing double majors in biomedical engineering and computer science.
+Each year as part of my regular teaching load, I mentor 4-12 MQP students (1-2 teams), meeting weekly for the entire academic year.
+Over the past 2 years at WPI, I have mentored 4 MQP teams (>15 students).
+During the award period, I expect to mentor two MQP teams each year that pursue projects that directly contribute to the Aims of this study or address questions related to the study goal.
+
+\paragraph{Other Mechanisms of Student Engagement}
+In addition to these formal mechanisms to engage students in research, students will have an opportunity for clinical exposure through our collaboration with Massachusetts Eye and Ear Infirmary.
+
+MEEI is accessible from the WPI campus via commuter rail.
+Our collaborative investigator commonly interacts with tinnitus patients, and patients with auditory impairments of many different types.
+Students who participate in projects with Dr.
+Troy will each spend time at MEEI, and will be encouraged to attend seminar talks at MEEI.
+We believe this exposure to both the engineering and clinical aspects of tinnitus issues will provide students with a rich educational experience that will encourage them to pursue research in the future.
 

### 2021-06-15 code/aim3.m

@@ -1,0 +1,136 @@
+%% Aim #3 Proof-of-Concept
+% The goal here is to get a new reconstruction
+% clustered into existing clusters
+% using the minimum number of trials.
+% So we have two questions...
+% (1) how to use the minimum number of trials, and 
+% (2) how to know when to stop.
+% In this script, we will ignore the second question
+% and instead focus on seeing how classification accuracy
+% changes as a function of number of trials.
+
+
+
+data_dir = '/home/alec/data/sounds/';
+data_files = {
+    'ATA_Tinnitus_Buzzing_Tone_1sec.wav',
+    'ATA_Tinnitus_Electric_Tone_1sec.wav',
+    'ATA_Tinnitus_Roaring_Tone_1sec.wav',
+    'ATA_Tinnitus_Static_Tone_1sec.wav',
+    'ATA_Tinnitus_Tea_Kettle_Tone_1sec.wav'
+};
+data_names = {
+    'buzzing',
+    'electric',
+    'roaring',
+    'static',
+    'tea kettle'
+};
+
+%% Compute gold-standard spectra
+
+s = cell(5, 1);
+f = cell(5, 1);
+for ii = 1:length(data_files)
+    [s{ii}, f{ii}] = wav2spect([data_dir, data_files{ii}]);
+end
+s = [s{:}];
+f = [f{:}];
+
+%% Generate fake data
+
+n_data_points_per_cluster = 20;
+n_data_points = n_data_points_per_cluster * length(data_files);
+noise_magnitude = 20;
+
+% replicate the canonical representations
+% x = repmat(f, 1, n_data_points);
+labels = repmat(1:length(data_files), n_data_points_per_cluster, 1)';
+y = repmat(s, 1, n_data_points_per_cluster);
+
+% convert to dB
+y = 10 * log10(y);
+
+% add Gaussian noise
+y = y + noise_magnitude * randn(size(y));
+
+%% Compute low-dimensional representation
+
+U = UMAP();
+y_new = U.fit_transform(y');
+y_new_pca = pca(y, 'NumComponents', 2);
+
+%% Signal reconstruction as a function of number of samples
+
+% n_samples = [100, 1e3, 1e4, 1e5];
+n_samples = round(logspace(1, 5));
+
+% select the first one for testing
+signal = s(:, 1);
+
+% outputs
+reconstructions = zeros(length(signal), length(n_samples));
+
[…]

### 2021-06-15 code/cs.m

@@ -1,0 +1,25 @@
+function x = cs(responses, Phi)
+    
+    n_samples = length(responses);
+    len_signal = size(Phi, 2);
+
+    Theta = zeros(n_samples, len_signal);
+    for ii = 1:len_signal
+        ek = zeros(1, len_signal);
+        ek(ii) = 1;
+        Psi = idct(ek)';
+        Theta(:, ii) = Phi * Psi;
+    end
+
+    Gamma = 32;
+    s = zhangpassivegamma(Theta, responses, Gamma);
+
+    x = zeros(len_signal, 1);
+    for ii = 1:len_signal
+        ek = zeros(1, len_signal);
+        ek(ii) = 1;
+        Psi = idct(ek)';
+        x = x + Psi * s(ii);
+    end
+
+end

### 2021-06-15 code/gs.m

@@ -1,0 +1,4 @@
+function x = gs(responses, Phi)
+    len_signal = size(Phi, 2);
+    x = (1 / len_signal) * Phi' * responses;
+end

### 2021-06-15 code/pipeline.m

@@ -25,8 +25,8 @@ plot_alpha = 0.03;
 
 %% Compute gold-standard spectra
 
-s = {};
-f = {};
+s = cell(5, 1);
+f = cell(5, 1);
 for ii = 1:length(data_files)
     [s{ii}, f{ii}] = wav2spect([data_dir, data_files{ii}]);
 end

### 2021-06-15 code/script_tinnitus_2.m

@@ -1,327 +1,0 @@
-% Inspired by 
-% o By S.Gibson, School of Physical Sciences, University of Kent. 
-% o 1st May, 2013.
-% o version 1.0
-% o NOTES: If the max number of iterations exceeds 25, error sometimes
-%   occurs in l1eq_pd function call.
-%
-% www.mathworks.com/matlabcentral/fileexchange/41792-simple-compressed-sensing-example
-
-%%%%%%%%%%%%%%%%%%%
-
-% FIDDLE WITH:
-% noisyness of subject selection process (below)
-% cs samples - parameter m (below)
-% biht parameter - sparsity (biht code) - lower (<64) is better
-% basis type (1d vs 2d) - rougly the same, preference for 2D
-
-%%%%%%%%%%%%%%%%%%%
-% Setup
-
-l = 10000;
-
-A = imread('Screeching.png');
-A = rgb2gray(A);
-A = imresize(A,1024/size(A,1)); % 0.3
-A = imresize(A,[min(size(A)) min(size(A))]); % 0.3
-A = double(A)./256;
-
-% Convert image to spectrum
-A = mean(A,2);
-A = 20.*log10(mean(A,2));
-A = flipud(A);
-A(1:5) = -4;
-
-n = size(A, 1);
-m = 1250; % 2.5% of recommended 20k trials
-
-%%%%%%%%%%%%%%%%%%%
-% Real Basis
-
-% ii = 32;
-% b = dct(A);
-% bm = zeros(n,1);
-% [val idx] = sort(abs(b(:)),'descend');
-% bm(abs(b)>val(ii)) = b(abs(b)>val(ii));
-
-% AA = idct(bm);
-% figure
-% plot(A,'k');
-% hold all
-% plot(AA,'r')
-
-% A = AA;
-
-%%%%%%%%%%%%%%%%%%%
-% Subject Selection Process
-
-AA = repmat(A',l,1);
-X = round(rand(l,n));
-
-% % Ideal selection
-% e = sum((X-AA).^2,2);
-% y = double(e>=prctile(e,49.5));
-% y(y==0) = -1;
-
-% Ideal Selection
-e = X*A;
-y = double(e>=prctile(e,50));
-y(y==0) = -1;
-
[…]

### 2021-06-15 code/subject_selection_process.m

@@ -1,0 +1,15 @@
+% Model of a subject performing the task.
+% Takes in a signal (the stimuli)
+% and returns an n_samples x 1 vector of 
+% -1 for "no"
+% and 1 for "yes".
+
+function [y, X] = subject_selection_process(signal, n_samples)
+
+    X = round(rand(n_samples, length(signal)));
+
+    % ideal selection
+    e = X * signal(:);
+    y = double(e >= prctile(e, 50));
+    y(y == 0) = -1;
+end

### 2021-06-15 code/wav2spect.m

@@ -1,6 +1,6 @@
 function [s, f] = wav2spect(audio_file)
     % Reads an audio file (e.g., a .wav file)
-    % and returns a spectogram
+    % and returns a spectrum
     % in terms of magnitudes, s, and frequencies, f, in Hz.
 
     % read the audio file

### 2022-05-16 code/utils/parse_config.m
Add stimuli_save_type as config field

@@ -42,12 +42,21 @@ function config = parse_config(config_file, verbose)
         ['Unknown stimuli type: ' config.stimuli_type, '. Allowed values are: ', stimuli_string(1:end-2)], '.');
 
     % data_dir
-    if ~isfield('data_dir', config) || isempty(config.data_dir)
+    if ~isfield(config, 'data_dir') || isempty(config.data_dir)
         project_dir = pathlib.strip(mfilename('fullpath'), 3);
         data_dir = pathlib.join(project_dir, 'code', 'experiment', 'Data');
         corelib.verb(verbose, 'parse_config', ['data_dir is empty, filling with: ', data_dir])
         config.data_dir = data_dir;
     end
+
+    % stimuli_save_type
+    if ~isfield(config, 'stimuli_save_type') || isempty(config.stimuli_save_type)
+        config.stimuli_save_type = 'waveform';
+        corelib.verb(verbose, 'parse_config', 'stimuli_save_type is empty, filling with: waveform.')
+    end
+    assert(any(strcmp(config.stimuli_save_type, {'bins', 'waveform', 'spectrum'})), ...
+        ['Unknown stimuli save type: ', config.stimuli_save_type, '. Allowed values are: [bins, waveform, spectrum].'])
+
 
 end % function
 

### 2022-05-16 code/utils/save_stimuli.m

@@ -1,0 +1,14 @@
+function save_stimuli(options)
+    %
+    %   save_stimuli(options)
+    %
+    %
+    %
+    %
+
+    arguments
+        options
+    end
+
+
+end % function

### 2022-05-16 code/experiment/Protocol.m
Replace 'stimuli' with 'stimuli_object'

@@ -46,8 +46,8 @@ function Protocol(options)
     end
 
     % Instantiate the stimulus generation object
-    stimuli = eval([config.stimuli_type, 'StimulusGeneration()']);
-    stimuli = stimuli.from_config(config);
+    stimuli_object = eval([config.stimuli_type, 'StimulusGeneration()']);
+    stimuli_object = stimuli_object.from_config(config);
     
     % Compute the total trials done
     total_trials_done = 0;
@@ -92,8 +92,8 @@ function Protocol(options)
     %% Generate stimuli
 
     % Generate a block of stimuli
-    % [stimuli_matrix, Fs, nfft] = stimuli.custom_generate_stimuli_matrix();
-    [stimuli_matrix, Fs, nfft] = stimuli.generate_stimuli_matrix();
+    % [stimuli_matrix, Fs, nfft] = stimuli_object.custom_generate_stimuli_matrix();
+    [stimuli_matrix, Fs, nfft] = stimuli_object.generate_stimuli_matrix();
 
     % Write the stimuli to file
     writematrix(stimuli_matrix, filename_stimuli);
@@ -186,7 +186,7 @@ function Protocol(options)
             fid_responses = fopen(filename_responses, 'w');
 
             % Generate stimuli for next block
-            [stimuli_matrix, Fs, nfft] = stimuli.generate_stimuli_matrix();
+            [stimuli_matrix, Fs, nfft] = stimuli_object.generate_stimuli_matrix();
 
             % Save stimuli to file
             writematrix(stimuli_matrix, filename_stimuli)

### 2022-05-16 code/experiment/Protocol.m
Protocol reads from stimuli_save_type field of config files

@@ -93,10 +93,19 @@ function Protocol(options)
 
     % Generate a block of stimuli
     % [stimuli_matrix, Fs, nfft] = stimuli_object.custom_generate_stimuli_matrix();
-    [stimuli_matrix, Fs, nfft] = stimuli_object.generate_stimuli_matrix();
+    [stimuli_matrix, Fs, spect_matrix, binned_repr_matrix] = stimuli_object.generate_stimuli_matrix();
 
     % Write the stimuli to file
-    writematrix(stimuli_matrix, filename_stimuli);
+    switch config.stimuli_save_type
+    case 'waveform'
+        writematrix(stimuli_matrix, filename_stimuli);
+    case 'spectrum'
+        writematrix(spect_matrix, filename_stimuli);
+    case 'bins'
+        write_matrix(binned_repr_matrix, filename_stimuli);
+    otherwise
+        error(['Stimuli save type: ', config.stimuli_save_type, ' not recognized.'])
+    end
 
     %% Intro Screen & Start
 
@@ -186,10 +195,19 @@ function Protocol(options)
             fid_responses = fopen(filename_responses, 'w');
 
             % Generate stimuli for next block
-            [stimuli_matrix, Fs, nfft] = stimuli_object.generate_stimuli_matrix();
+            [stimuli_matrix, Fs, spect_matrix, binned_repr_matrix] = stimuli_object.generate_stimuli_matrix();
 
             % Save stimuli to file
-            writematrix(stimuli_matrix, filename_stimuli)
+            switch config.stimuli_save_type
+            case 'waveform'
+                writematrix(stimuli_matrix, filename_stimuli);
+            case 'spectrum'
+                writematrix(spect_matrix, filename_stimuli);
+            case 'bins'
+                write_matrix(binned_repr_matrix, filename_stimuli);
+            otherwise
+                error(['Stimuli save type: ', config.stimuli_save_type, ' not recognized.'])
+            end
             fprintf(['# of trials completed: ', num2str(total_trials_done) '\n'])
 
         else % continue with block

### 2022-05-16 code/utils/read_stimuli.m

@@ -1,0 +1,1 @@
+% TODO #18

### 2022-05-16 code/utils/save_stimuli.m

@@ -1,14 +1,0 @@
-function save_stimuli(options)
-    %
-    %   save_stimuli(options)
-    %
-    %
-    %
-    %
-
-    arguments
-        options
-    end
-
-
-end % function

### 2022-05-16 code/stimulus_generation/@AbstractStimulusGenerationMethod/AbstractStimulusGenerationMethod.m
TODO

@@ -43,7 +43,7 @@ classdef (Abstract) AbstractStimulusGenerationMethod
 
         function [stimuli_matrix, Fs, spect_matrix, binned_repr_matrix] = generate_stimuli_matrix(self)
             % Generate matrix of stimuli.
-            % TODO: documentation for this
+            % TODO: #19 documentation for this
 
             if any(strcmp('n_bins', properties(self)))
                 % generate first stimulus

### 2022-06-19 code/experiment/Protocol_2AFC.m
Copy over Protocol

@@ -29,7 +29,7 @@ function Protocol_2AFC(options)
     mkdir(config.data_dir);
 
     %% Setup
-
+    
     % Useful variables
     project_dir = pathlib.strip(mfilename('fullpath'), 2);
     
@@ -44,14 +44,17 @@ function Protocol_2AFC(options)
         % Default to 'custom' stimulus generation
         config.stimuli_type = 'GaussianPrior';
     end
-
+    
+    % Generate the experiment ID
+    expID = get_experiment_ID(config);
+    
     % Instantiate the stimulus generation object
     stimuli_object = eval([config.stimuli_type, 'StimulusGeneration()']);
     stimuli_object = stimuli_object.from_config(config);
     
     % Compute the total trials done
     total_trials_done = 0;
-    d = dir(pathlib.join(config.data_dir, [config.subjectID '_responses*.csv']));
+    d = dir(pathlib.join(config.data_dir, [expID '_responses*.csv']));
 
     for ii = 1:length(d)
         responses = readmatrix(pathlib.join(d(ii).folder, d(ii).name));
@@ -61,9 +64,9 @@ function Protocol_2AFC(options)
 
     % Create files needed for saving the data
     uuid = char(java.util.UUID.randomUUID);
-    filename_responses = pathlib.join(config.data_dir, [config.subjectID, '_', 'responses', '_', uuid, '.csv']);
-    filename_stimuli = pathlib.join(config.data_dir, [config.subjectID, '_', 'stimuli', '_', uuid, '.csv']);
-    filename_meta = pathlib.join(config.data_dir, [config.subjectID, '_', 'meta', '_', uuid, '.csv']);
+    filename_responses = pathlib.join(config.data_dir, [expID, '_', 'responses', '_', uuid, '.csv']);
+    filename_stimuli = pathlib.join(config.data_dir, [expID, '_', 'stimuli', '_', uuid, '.csv']);
+    filename_meta = pathlib.join(config.data_dir, [expID, '_', 'meta', '_', uuid, '.csv']);
 
     fid_responses = fopen(filename_responses, 'w');
 
@@ -121,7 +124,7 @@ function Protocol_2AFC(options)
 
     counter = 0;
     while (1)
-        counter = counter + 2;
+        counter = counter + 1;
 
         % Reminder Screen
         imshow(Screen2);
@@ -133,22 +136,10 @@ function Protocol_2AFC(options)
         end
 
 
-        % Present First Stimulus
[…]

### 2022-06-19 code/experiment/Protocol.m
2AFC

@@ -14,7 +14,7 @@
 function Protocol(options)
 
     arguments
-        options.config char = []
+        options.config_file char = []
     end
 
     this_datetime = datetime();
@@ -22,7 +22,7 @@ function Protocol(options)
     % Is a config file provided?
     %   If so, read it.
     %   If not, open a GUI dialog window to find it.
-    config = parse_config(options.config);
+    config = parse_config(options.config_file);
     config.n_trials = config.n_trials_per_block;
 
     % Try to create the data directory if it doesn't exist
@@ -165,7 +165,7 @@ function Protocol(options)
 
         % Write the meta file
         meta = {expID, uuid, this_datetime, total_trials_done};
-        meta_labels = {'subjectID', 'uuid', 'datetime', 'total_trials_done'};
+        meta_labels = {'expID', 'uuid', 'datetime', 'total_trials_done'};
         writetable(cell2table(meta, 'VariableNames', meta_labels), filename_meta);
             
         % Decide How To Continue

### 2022-06-19 code/experiment/Protocol_2AFC.m

@@ -14,7 +14,7 @@
 function Protocol_2AFC(options)
 
     arguments
-        options.config char = []
+        options.config_file char = []
     end
 
     this_datetime = datetime();
@@ -22,7 +22,7 @@ function Protocol_2AFC(options)
     % Is a config file provided?
     %   If so, read it.
     %   If not, open a GUI dialog window to find it.
-    config = parse_config(options.config);
+    config = parse_config(options.config_file);
     config.n_trials = config.n_trials_per_block;
 
     % Try to create the data directory if it doesn't exist
@@ -65,9 +65,13 @@ function Protocol_2AFC(options)
     % Create files needed for saving the data
     uuid = char(java.util.UUID.randomUUID);
     filename_responses = pathlib.join(config.data_dir, [expID, '_', 'responses', '_', uuid, '.csv']);
-    filename_stimuli = pathlib.join(config.data_dir, [expID, '_', 'stimuli', '_', uuid, '.csv']);
     filename_meta = pathlib.join(config.data_dir, [expID, '_', 'meta', '_', uuid, '.csv']);
-
+    
+    % Stimuli file for stimuli batch #1
+    filename_stimuli_1 = pathlib.join(config.data_dir, [expID, '_', 'stimuli_1', '_', uuid, '.csv']);
+    % Stimuli file for stimuli batch #2
+    filename_stimuli_2 = pathlib.join(config.data_dir, [expID, '_', 'stimuli_2', '_', uuid, '.csv']);
+    
     fid_responses = fopen(filename_responses, 'w');
 
     % Is this an A-X experiment protocol?
@@ -91,21 +95,25 @@ function Protocol_2AFC(options)
     Screen2 = imread(pathlib.join(project_dir, 'experiment', 'fixationscreen', 'Slide2B.png'));
     Screen3 = imread(pathlib.join(project_dir, 'experiment', 'fixationscreen', 'Slide3B.png'));
     Screen4 = imread(pathlib.join(project_dir, 'experiment', 'fixationscreen', 'Slide4.png'));
-
+    
     %% Generate stimuli
 
     % Generate a block of stimuli
-    % [stimuli_matrix, Fs, nfft] = stimuli_object.custom_generate_stimuli_matrix();
-    [stimuli_matrix, Fs, spect_matrix, binned_repr_matrix] = stimuli_object.generate_stimuli_matrix();
+    % Each corresponds to the first (left) and second (right) stimuli.
[…]

### 2022-06-19 code/experiment/Protocol.m
Use hashing for file naming

@@ -17,7 +17,8 @@ function Protocol(options)
         options.config_file char = []
     end
 
-    this_datetime = datetime();
+    this_datetime = datetime('now', 'Timezone', 'local');
+    posix_time = num2str(floor(posixtime(this_datetime)));
 
     % Is a config file provided?
     %   If so, read it.
@@ -62,14 +63,6 @@ function Protocol(options)
     end
     fprintf(['# of trials completed: ', num2str(total_trials_done) '\n'])
 
-    % Create files needed for saving the data
-    uuid = char(java.util.UUID.randomUUID);
-    filename_responses = pathlib.join(config.data_dir, [expID, '_', 'responses', '_', uuid, '.csv']);
-    filename_stimuli = pathlib.join(config.data_dir, [expID, '_', 'stimuli', '_', uuid, '.csv']);
-    filename_meta = pathlib.join(config.data_dir, [expID, '_', 'meta', '_', uuid, '.csv']);
-
-    fid_responses = fopen(filename_responses, 'w');
-
     % Is this an A-X experiment protocol?
     %   If it's an A-X experiment protocol,
     %   then we should play a target sound before each stimulus
@@ -91,24 +84,10 @@ function Protocol(options)
     Screen2 = imread(pathlib.join(project_dir, 'experiment', 'fixationscreen', 'Slide2B.png'));
     Screen3 = imread(pathlib.join(project_dir, 'experiment', 'fixationscreen', 'Slide3B.png'));
     Screen4 = imread(pathlib.join(project_dir, 'experiment', 'fixationscreen', 'Slide4.png'));
-
-    %% Generate stimuli
-
-    % Generate a block of stimuli
-    % [stimuli_matrix, Fs, nfft] = stimuli_object.custom_generate_stimuli_matrix();
-    [stimuli_matrix, Fs, spect_matrix, binned_repr_matrix] = stimuli_object.generate_stimuli_matrix();
-
-    % Write the stimuli to file
-    switch config.stimuli_save_type
-    case 'waveform'
-        writematrix(stimuli_matrix, filename_stimuli);
-    case 'spectrum'
-        writematrix(spect_matrix, filename_stimuli);
-    case 'bins'
-        writematrix(binned_repr_matrix, filename_stimuli);
-    otherwise
-        error(['Stimuli save type: ', config.stimuli_save_type, ' not recognized.'])
-    end
+    
+    %% Generate initial files and stimuli
[…]

### 2022-06-19 code/experiment/Protocol_2AFC.m

@@ -11,13 +11,14 @@
 %   Protocol()
 %   Protocol('config', 'path2config')
 
-function Protocol_2AFC(options)
+function Protocol(options)
 
     arguments
         options.config_file char = []
     end
 
-    this_datetime = datetime();
+    this_datetime = datetime('now', 'Timezone', 'local');
+    posix_time = num2str(floor(posixtime(this_datetime)));
 
     % Is a config file provided?
     %   If so, read it.
@@ -62,18 +63,6 @@ function Protocol_2AFC(options)
     end
     fprintf(['# of trials completed: ', num2str(total_trials_done) '\n'])
 
-    % Create files needed for saving the data
-    uuid = char(java.util.UUID.randomUUID);
-    filename_responses = pathlib.join(config.data_dir, [expID, '_', 'responses', '_', uuid, '.csv']);
-    filename_meta = pathlib.join(config.data_dir, [expID, '_', 'meta', '_', uuid, '.csv']);
-    
-    % Stimuli file for stimuli batch #1
-    filename_stimuli_1 = pathlib.join(config.data_dir, [expID, '_', 'stimuli_1', '_', uuid, '.csv']);
-    % Stimuli file for stimuli batch #2
-    filename_stimuli_2 = pathlib.join(config.data_dir, [expID, '_', 'stimuli_2', '_', uuid, '.csv']);
-    
-    fid_responses = fopen(filename_responses, 'w');
-
     % Is this an A-X experiment protocol?
     %   If it's an A-X experiment protocol,
     %   then we should play a target sound before each stimulus
@@ -96,27 +85,9 @@ function Protocol_2AFC(options)
     Screen3 = imread(pathlib.join(project_dir, 'experiment', 'fixationscreen', 'Slide3B.png'));
     Screen4 = imread(pathlib.join(project_dir, 'experiment', 'fixationscreen', 'Slide4.png'));
     
-    %% Generate stimuli
-
-    % Generate a block of stimuli
-    % Each corresponds to the first (left) and second (right) stimuli.
-    [stimuli_matrix_1, ~, spect_matrix_1, binned_repr_matrix_1] = stimuli_object.generate_stimuli_matrix();
-    [stimuli_matrix_2, Fs, spect_matrix_2, binned_repr_matrix_2] = stimuli_object.generate_stimuli_matrix();
-
-    % Write the stimuli to file
-    switch config.stimuli_save_type
-    case 'waveform'
[…]

### 2022-06-19 code/experiment/Protocol_2AFC.m
Update 2AFC protocol to use hashing

@@ -11,7 +11,7 @@
 %   Protocol()
 %   Protocol('config', 'path2config')
 
-function Protocol(options)
+function Protocol_2AFC(options)
 
     arguments
         options.config_file char = []
@@ -86,7 +86,7 @@ function Protocol(options)
     Screen4 = imread(pathlib.join(project_dir, 'experiment', 'fixationscreen', 'Slide4.png'));
     
     %% Generate initial files and stimuli
-    [stimuli_matrix, Fs, filename_responses, ~, filename_meta, this_hash] = create_files_and_stimuli(config, stimuli_object, posix_time);
+    [stimuli_matrix_1, stimuli_matrix_2, Fs, filename_responses, ~, ~, filename_meta_1, filename_meta_2, this_hash_1, this_hash_2] = create_files_and_stimuli_2AFC(config, stimuli_object, posix_time);
     fid_responses = fopen(filename_responses, 'w');
 
     %% Intro Screen & Start
@@ -108,16 +108,8 @@ function Protocol(options)
         % Reminder Screen
         imshow(Screen2);
 
-        % Present Target (if A-X protocol)
-        if ~isempty(target_sound)
-            soundsc(target_sound, target_fs)
-            pause(length(target_sound) / target_fs + 0.3) % ACL added (5MAY2022) to add 300ms pause between target and stimulus
-        end
-
-
-        % Present Stimulus
-        soundsc(stimuli_matrix(:, counter), Fs)
-        pause(length(stimuli_matrix(:, counter)) / Fs)
+        %% Play the stimuli
+        play_stimuli(stimuli_matrix_1, stimuli_matrix_2, Fs, counter, target_sound, target_fs, 0.3)
             
         % Obtain Response
         k = waitforbuttonpress;
@@ -142,10 +134,14 @@ function Protocol(options)
         % Update the number of trials done in this block
         total_trials_done = total_trials_done + 1;
 
-        % Write the meta file
-        meta = {expID, this_hash, this_datetime, total_trials_done};
+        % Write the meta files
+        meta = {expID, this_hash_1, this_datetime, total_trials_done};
         meta_labels = {'expID', 'hash', 'datetime', 'total_trials_done'};
-        writetable(cell2table(meta, 'VariableNames', meta_labels), filename_meta);
[…]

### 2022-06-27 supplemental/OJEMB Supplementary Material.tex
Add supplemental info template

%% Supplementary Materials IEEE OJEMB

\documentclass[journal]{IEEEtran}
\usepackage[usenames]{color}
\usepackage{epsfig}
\usepackage{graphics}
\usepackage{caption}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{cite}
\usepackage{array}
\usepackage{pslatex} 
\usepackage{url}
\usepackage{lineno}
\usepackage{graphicx}  % Written by David Carlisle and Sebastian Rahtz
\usepackage{setspace}
\usepackage{tikz}
\usepackage{hhline}
\usepackage{mathtools}
\usepackage{caption}
\usepackage[letterpaper]{geometry}
\geometry{verbose,tmargin=0.7in,bmargin=0.7in,lmargin=0.65in,rmargin=0.65in}
\setlength{\headheight}{17pt}
\setlength{\headsep}{5pt}
%\captionsetup{labelfont={up},font=small}
\captionsetup[figure]{name={Fig.},labelsep=period,font=small}
 \captionsetup[table]{name={TABLE},labelsep=period,font=small}
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

\usepackage{lipsum}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
% Axel Sommerfeldt. This package may be useful when used in conjunction with 
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/pkg/endfloat
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

\newcommand{\flogo}{\includegraphics[height=18pt]{embLogo.eps}}

%\lhead{\textsc{\flogo}}

% The paper headers
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{\textsc{\flogo}}
\rhead{\textcolor{violet}{\Large\textbf{Supplementary Materials}}}
\fancyfoot[C]{\thepage}
\renewcommand{\footrulewidth}{0.4pt}% default is 0pt

\begin{document}

\twocolumn[
\begin{@twocolumnfalse}
\thispagestyle{fancy}   
\vspace*{0.5cm}
\textbf{\LARGE{Supplementary Materials}}\\
\\
\medskip\Large{Title of the Manuscript}\\
\normalsize{ First A. Author,~\IEEEmembership{Fellow, IEEE,}
	Second B. Author,and Third C. Author*, Jr.,~\IEEEmembership{Member,~IEEE}}\\
	\vspace*{0.5cm}
\end{@twocolumnfalse}
]

% make the title area

\IEEEPARstart{T}{he}  Supplementary Materials should either be organized in sections as per the main manuscript body (using up to 4,000 words) or it should be used to provide readers with a set of up to 10 additional display items (i.e. figures and tables).
Figures and tables should be prepared using the same format and guidelines as per the main body of the manuscript. References should be included using the same format utilized in the main body of the manuscript.

% that's all folks
\end{document}

### 2022-06-28 supplemental/OJEMB Supplementary Material.tex
Add to supplemental info

@@
 \usepackage{lipsum}
+
+\usepackage{soul}
+\newcommand{\etal}{\textit{et al}., }
+\newcommand{\ie}{\textit{i}.\textit{e}., }
+\newcommand{\eg}{\textit{e}.\textit{g}.\ }
+\newcommand{\cf}{\textit{cf}.\ }
+\usepackage{hyperref}
 
@@
 %
-%\usepackage{amsmath}
+\usepackage{amsmath}
 % A popular package from the American Mathematical Society that provides
@@
 %
-%\usepackage{algorithmic}
+\usepackage{algorithmic}
 % algorithmic.sty was written by Peter Williams and Rogerio Brito.
@@
 %
-%\usepackage{array}
+\usepackage{array}
 % Frank Mittelbach's and David Carlisle's array.sty patches and improves
@@
 %
-%\usepackage{url}
+\usepackage{url}
 % url.sty was written by Donald Arseneau. It provides better support for
@@
 \\
-\medskip\Large{Title of the Manuscript}\\
-\normalsize{ First A. Author,~\IEEEmembership{Fellow, IEEE,}
-	Second B. Author,and Third C. Author*, Jr.,~\IEEEmembership{Member,~IEEE}}\\
+\medskip\Large{Compressed Sensing for Characterization of Tinnitus}\\
+\normalsize{ Alec Hoyland,
+	Nelson Barnett, Benjamin W. Roop, Adam C. Lammert}\\
 	\vspace*{0.5cm}
@@
 
-\IEEEPARstart{T}{he}  Supplementary Materials should either be organized in sections as per the main manuscript body (using up to 4,000 words) or it should be used to provide readers with a set of up to 10 additional display items (i.e.
-figures and tables).
-Figures and tables should be prepared using the same format and guidelines as per the main body of the manuscript.
-References should be included using the same format utilized in the main body of the manuscript.
+\IEEEPARstart{T}his document contains a description of additional experiments to find a performant
+stimulus generation method and a discussion of sparsity in tinnitus signals.
+The code for all experiments is freely available at \url{https://github.com/alec-hoyland/tinnitus-project}
+and the data are available upon request.
+
+\section{Stimulus Generation}
+
+In the context of this paper, a stimulus generation method
+is a process that generates a random waveform that is:
+
+\begin{enumerate}
+  \item auditorally-distinguishable
+  \item statistically uncorrelated, and
+  \item similar to tinnitus percepts.
+\end{enumerate}
+
+Additionally, compressed sensing requires that the matrix of stimuli
+should satisfy the restricted isometry property,
+which many random matrices do with high probability (\eg Gaussian random matrices)
+\cite{candesRestrictedIsometryProperty2008,candesIntroductionCompressiveSampling2008}.
+
+\subsection{Auditorally-Distinguishable Stimuli}
+
+We used mel-frequency binning to ensure that our stimuli were auditorally-distinguishable.
+The mel scale is a perceptual scale of pitches judged by listeners to be equal in distance
+from one to another (Fig. \ref{fig:hz2mel}) \cite{hamiltonTopographySpeechrelatedAcoustic2020}.
+
+The formula
+
+\begin{equation}
+  m = 2595 \log_10 \bigg( 1 + \frac{f}{700} \big)
+\end{equation}
+
+converts $f$ Hz to $m$ mels.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{gfx/hz2mel.eps}
+	\caption{The relationship between Hz and mels is logarithmic.}
+	\label{fig:hz2mel}
+\end{figure}
+
+\bibliographystyle{IEEEtran}
+\bibliography{IEEEabrv,../paper/mybib}
 

### 2022-06-28 supplemental/scripts/make_figures.m

@@ -1,0 +1,44 @@
+%% Mel 2 Hz
+
+hz = 100:100:13e3;
+fig1 = new_figure();
+
+plot(hz * 1e-3, hz2mels(hz));
+xlabel('frequency (kHz)')
+ylabel('mels')
+
+axis square
+
+figlib.pretty('FontSize', 36);
+figlib.tight();
+
+%% Example Stimulus
+
+config = parse_config("../code/experiment/configs/config_template.yaml");
+stimgen = UniformPriorStimulusGeneration();
+stimgen = stimgen.from_config(config);
+[stim, Fs, spect, binned_repr, frequency_vector] = stimgen.generate_stimulus();
+
+fig2 = new_figure();
+
+for ii = 3:-1:1
+    ax(ii) = subplot(3, 1, ii);
+end
+
+plot(ax(1), (1:length(stim)) / Fs, convert2db(stim));
+xlabel(ax(1), 'time (s)')
+ylabel('amplitude (dB)')
+xlim(ax(1), [0, 0.5])
+
+plot(ax(2), 1e-3 * frequency_vector, spect)
+xlabel(ax(2), 'frequency (kHz)')
+ylabel(ax(2), 'amplitude (dB)')
+xlim(ax(2), 'manual')
+
+stem(ax(3), 1:100, binned_repr)
+xlabel(ax(3), 'bin number')
+ylabel(ax(3), 'amplitude (dB)')
+ylim(ax(3), [-25, 5])
+
+figlib.pretty('FontSize', 36, 'PlotBuffer', 0.2)
+figlib.label('FontSize', 36)

### 2022-06-28 code/utils/adjust_volume.m
adjust_volume small changes
Increased adjustable max and added a check in protocol so it only occurs during A-X experiments

@@ -12,7 +12,7 @@ function scalar = adjust_volume(target_sound, target_fs, stimuli, Fs, scalar)
     end
     
     % Allowable range within which to scale target audio
-    sld_max = 2;
+    sld_max = 3;
     sld_min = 0.1;
 
     %% GUI

### 2022-06-30 code/scripts/pilot_reconstructions.m
Changes re: Alec's comments
Of note, removed preprocessing from pilot_reconstructions.m, added documentation, arguments, and slight improvements to config2table.m

@@ -65,7 +65,7 @@ for ii = 1:length(this_dir)
 end
 
 T = config2table(this_dir);
-T.config_filename = config_filenames'; 
+T.config_filename = config_filenames(:); 
 
 
 %% Compute the reconstructions
@@ -97,20 +97,13 @@ for ii = 1:height(T)%progress(1:height(T), 'Title', 'Computing reconstructions',
     for qq = 1:length(trial_fractions)
         corelib.verb(true, 'INFO: pilot_reconstructions', ['trial fractions: ', num2str(trial_fractions(qq))])
         % Compute the reconstructions
-        if strcmp(T.subject_ID(ii,:), 'AL')
-            preprocessing = {'bins', 'bit flip'};
-        else
-            preprocessing = {};
-        end
         corelib.verb(true, 'INFO: pilot_reconstructions', 'computing CS reconstruction')
         [reconstructions_cs{ii, qq}, responses, stimuli_matrix] = get_reconstruction('config', config, ...
-                                    'preprocessing', preprocessing, ...
                                     'method', 'cs', ...
                                     'fraction', trial_fractions(qq), ...
                                     'verbose', true);
         corelib.verb(true, 'INFO: pilot_reconstructions', 'computing linear reconstruction')
         reconstructions_lr{ii, qq} = get_reconstruction('config', config, ...
-                                    'preprocessing', preprocessing, ...
                                     'method', 'linear', ...
                                     'fraction', trial_fractions(qq), ...
                                     'verbose', true);

### 2022-06-30 code/utils/config2table.m

@@ -1,39 +1,56 @@
-%%% Collect and present the desired fields for data table
+function data_table = config2table(curr_dir)
+    
+    % Take information from directory containing config files and return
+    % a table with all relevant information for each config.
+    %
+    % Arguments: 
+    %
+    %   curr_dir: struct
+    %   Directory information containing config file name, path, and other
+    %   returns from dir() function.
+    %
+    % Outputs: 
+    %
+    %   data_table: table
 
-function data_table = config2table(dir)
-
-    config_file = dir(1);
+    arguments
+        curr_dir (:,1)
+    end
+    
+    config_file = curr_dir(1);
     config = parse_config(pathlib.join(config_file.folder, config_file.name));
     
     data_table = struct2table(config);
-
     data_table.ID = 1;
-
-    if length(dir) > 1
-        for ii = 2:length(dir)
-            config_file = dir(ii);
+    
+    % Create and outer join each new data table, keeping column names the same
+    if length(curr_dir) > 1
+        for ii = 2:length(curr_dir)
+            config_file = curr_dir(ii);
             config = parse_config(pathlib.join(config_file.folder, config_file.name));
-
+    
             new_data_table = struct2table(config);
             new_data_table.ID = ii;
             data_table = outerjoin(data_table, new_data_table, 'MergeKeys', true);
         end
     end
-
+    
     %% Remove unnecessary info from table / clean fields
     
+    % Extract tone name from target .wav filepath
     if ~isempty(data_table.target_audio_filepath)
         audPath_cell = mat2cell(data_table.target_audio_filepath, ...
-            [1 1], length(data_table.target_audio_filepath));
+            repelem(1,size(data_table.target_audio_filepath,1)), ...
+            repelem(size(data_table.target_audio_filepath,2),1));
         data_table.target_audio = cellfun(@(x) extractBetween(x,'Tinnitus_','_Tone'), audPath_cell);
     end
-
+    
     remove_fields = {'n_trials_per_block', 'n_blocks', ...
         'min_freq', 'max_freq', 'duration', 'n_bins', ...
-        'target_audio_filepath', 'bin_target_signal', ... 
+        'target_audio_filepath', 'bin_target_signal', ...
         'data_dir', 'stimuli_save_type'};
-
+    
     data_table = removevars(data_table,remove_fields);
 
-end
+end % function
 

### 2022-07-06 supplemental/OJEMB Supplementary Material.tex
Add new figure
Add to supplemental info

@@
 \begin{equation}
-  m = 2595 \log_10 \bigg( 1 + \frac{f}{700} \big)
+  m = 2595 \log_10 \bigg( 1 + \frac{f}{700} \bigg)
 \end{equation}
@@
 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{gfx/example_stimulus.eps}
+	\caption{Example stimulus. \textbf{(a)} shows the waveform of the stimulus,
+  \textbf{(b)} the frequency spectrum from which the waveform was generated,
+  and \textbf{(c)} the $100$-dimensional bin representation.}
+	\label{fig:examplestimulus}
+\end{figure}
+
+Furthermore, to reduce the system complexity by more than 80x,
+we implement tonotopic binning, where the frequency scale is binned
+along $100$ equally mel-spaced bins (Fig. \ref{fig:examplestimulus}).
+
+\section{Hyperparameter Sweep}
+
+To determine a suitable stimulus generation method,
+we performed a hyperparameter sweep over hyperparameters
+of nine different stimulus generation methods.
+We used an \textit{in-silico} model of the experiment,
+matching against an American Tinnitus Association tinnitus example,
+as in the human experiment.
+
+The methods are as follows:
+
+\begin{enumerate}
+  \item \textit{Bernoulli}: A binned method in which each tonotopic bin
+  has a probability $p$ of being set to $0$ dB otherwise it is set to $-20$ dB.
+  \item \textit{Brimijoin}: A binned method inspired by \cite{brimijoinInternalRepresentationVowel2013}.
+  Each bin is assigned an amplitude value chosen from a uniform distribution of discrete values
+  on the interval $[-20, 0]$. We used $6$ steps, which is consistent with the original paper.
+  \item \textit{Gaussian Noise No Bins}: The amplitude of each frequency was determined by
+  Gaussian noise with known mean and variance, which are hyperparameters $\mu$ and $\sigma$.
+  \item \textit{Gaussian Noise}: A binned method where the bin amplitudes were
+  determined by a Gaussian random variable with known mean and variance, \eg $\mathcal{N}(\mu, \sigma)$.
+  \item \textit{Gaussian Prior}: A binned method where the number of filled bins
+  was set by $\mathrm{round}(\mathcal{N}(\mu, \sigma))$,
+  and that many bins were filled randomly at $0$ dB (unfilled bins were set to $-20$ dB).
+  \item \textit{Power Distribution}: A binned method where the amplitude of each bin
+  is drawn from a distribution matching the histogram of amplitudes
+  of the American Tinnitus Association tinnitus examples from their website.
+  \item \textit{Uniform Noise No Bins}: The amplitude associated with each frequency
+  is determined by a uniform random variable on the interval $[-20, 0]$ dB.
+  \item \textit{Uniform Noise}: The amplitude associated with each tonotopic bin
+  is determined by a uniform random variable on the interval $[-20, 0]$ dB.
+  \item \textit{Uniform Prior}: The number of filled bins is determined by drawing an integer
+  from the discrete interval $[x_1, x_2] \in \mathbb{Z}^+$. Then, that many bins are set to $0$ dB,
+  and all other bins are set to $-20$ dB. $x_1$ and $x_2$ are hyperparameters.
+\end{enumerate}
+
+9 methods and 8 hyperparameters were varied in the hyperparameter sweep grid search.
+Methods were evaluated \textit{in-silico} using the model:
+
+\begin{equation}
+  y = \mathrm{sgn}(\Psi * \bar{x})
+\end{equation}
+
+where $y \in \mathbb{R}^n$ is the binary response vector,
+$\Psi \in \mathbb{R}^{n \times d}$ is the stimulus matrix,
+and $\bar{x} \in \mathbb{R}^d$ is the true target signal (the spectrum of the ATA tinnitus example).
+
+Each stimulus generation method, with different hyperparameters,
+was evaluated for target signals: buzzing, electric, roaring, screeching, static, and tea kettle.
+
+\begin{table}[ht]
+	\begin{center}	
+		\small
+		\resizebox{1\columnwidth}{!}{
+			\begin{tabular}{ m{0.35\columnwidth} m{0.65\columnwidth} }	
+				\multicolumn{2}{c}{\textsc{Units for Magnetic Properties}} \\
+				\hhline{===}
+				{Symbol} & {Quantity} \\
+				\hhline{===}
+
+			\end{tabular}
+		}
+	\end{center}
+\end{table}
+
+% n_bins: [10 30 100 200 300]
+% bin_prob: [0.1000 0.3000 0.5000 0.8000]
+% amplitude_mean: -35
+% amplitude_var: [5 10 20]
+% n_bins_filled_mean: [1 3 10 20 30]
+% n_bins_filled_var: [0.0100 1 3 10]
+% min_bins: [1 3 10 20 30]
+% max_bins: [10 20 30 50]
+
 \bibliographystyle{IEEEtran}

### 2022-07-06 code/scripts/hyperparameter_sweep_custom.m

@@ -251,6 +251,8 @@ for ii = 1:length(n_bins)
     write_stimuli(data_dir, stimulus_generation_names{9}, stimuli, false, VERBOSE, {'distribution', 'distribution_filepath'}, {'bins'});
 end
 
+return
+
 if RUN
 
     %% Reconstruction across the Bin Representation

### 2022-07-06 supplemental/OJEMB Supplementary Material.tex
Add to supplemental info

@@
   \item \textit{Bernoulli}: A binned method in which each tonotopic bin
-  has a probability $p$ of being set to $0$ dB otherwise it is set to $-20$ dB.
+  has a probability $bin \_ prob$ of being set to $0$ dB otherwise it is set to $-20$ dB.
   \item \textit{Brimijoin}: A binned method inspired by \cite{brimijoinInternalRepresentationVowel2013}.
@@
   \item \textit{Gaussian Noise No Bins}: The amplitude of each frequency was determined by
-  Gaussian noise with known mean and variance, which are hyperparameters $\mu$ and $\sigma$.
+  Gaussian noise with known mean and variance, which are hyperparameters $amplitude \_ mean$ and $amplitude \_ var$.
   \item \textit{Gaussian Noise}: A binned method where the bin amplitudes were
-  determined by a Gaussian random variable with known mean and variance, \eg $\mathcal{N}(\mu, \sigma)$.
+  determined by a Gaussian random variable with known mean and variance, \eg $\mathcal{N}(amplitude \_ mean$ and $amplitude \_ var)$.
   \item \textit{Gaussian Prior}: A binned method where the number of filled bins
-  was set by $\mathrm{round}(\mathcal{N}(\mu, \sigma))$,
+  was set by $\mathrm{round}(\mathcal{N}(n \_ bins \_ filled \_ mean, n \_ bins \_ filled \_ var))$,
   and that many bins were filled randomly at $0$ dB (unfilled bins were set to $-20$ dB).
@@
   \item \textit{Uniform Prior}: The number of filled bins is determined by drawing an integer
-  from the discrete interval $[x_1, x_2] \in \mathbb{Z}^+$. Then, that many bins are set to $0$ dB,
-  and all other bins are set to $-20$ dB. $x_1$ and $x_2$ are hyperparameters.
+  from the discrete interval $[min \_ bins, max \_ bins] \in \mathbb{Z}^+$. Then, that many bins are set to $0$ dB,
+  and all other bins are set to $-20$ dB. $min \_ bins$ and $max \_ bins$ are hyperparameters.
 \end{enumerate}
 
-9 methods and 8 hyperparameters were varied in the hyperparameter sweep grid search.
+9 methods and 8 hyperparameters were varied in the hyperparameter sweep grid search (Table \ref{tbl:hyperparameters}).
 Methods were evaluated \textit{in-silico} using the model:
@@
 		\resizebox{1\columnwidth}{!}{
-			\begin{tabular}{ m{0.35\columnwidth} m{0.65\columnwidth} }	
-				\multicolumn{2}{c}{\textsc{Units for Magnetic Properties}} \\
+			\begin{tabular}{ m{0.35\columnwidth} m{0.5\columnwidth} b{0.15\columnwidth}}	
+				\multicolumn{3}{c}{\textsc{Hyperparameters}} \\
 				\hhline{===}
-				{Symbol} & {Quantity} \\
+				{Name} & {Values} & Unit \\ 
+				\hline
+				n\textunderscore bins & 10, 30, 100, 200, 300 & n.d. \\
+				bin\textunderscore prob & 0.1, 0.3, 0.5, 0.8 & n.d. \\
+                amplitude\textunderscore mean & -35 & dB \\
+                amplitude\textunderscore var & 5, 10, 20 & $\sqrt{\mathrm{dB}}$ \\
+                n\textunderscore bins\textunderscore filled \textunderscore mean & 1, 3, 10, 20, 30 & n.d. \\
+                n\textunderscore bins\textunderscore filled\textunderscore var & 0.01, 1, 3, 10 & n.d. \\
+                min\textunderscore bins & 1, 3, 10, 20, 30 & n.d. \\
+                max\textunderscore bins & 10, 20, 30, 50 & n.d. \\
 				\hhline{===}
-
 			\end{tabular}
@@
 	\end{center}
+%\normalsize
+	\caption{Hyperparameter values tested in the parameter sweep. Not all methods use all hyperparameters,
+    and some combinations of hyperparameters are invalid (\eg when $min\_ bins > max \_ bins$).
+    n.d. means ``non-dimensional'' and refers to a unitless number.
+    }
+	\label{tbl:hyperparameters}
 \end{table}
+
+Reconstructions were computed using linear regression and compressed sensing
+and reconstruction accuracy was measured using Pearson's $r^2$ vs. the target signal.
 

### 2022-07-09 supplemental/OJEMB Supplementary Material.tex
Add to supplementary info

@@
 
+\usepackage{siunitx}
+\sisetup{parse-numbers = false}
+
 \newcommand{\flogo}{\includegraphics[height=18pt]{embLogo.eps}}
@@
 To determine a suitable stimulus generation method,
-we performed a hyperparameter sweep over hyperparameters
-of nine different stimulus generation methods.
+we performed a hyperparameter sweep over
+nine different stimulus generation methods.
 We used an \textit{in-silico} model of the experiment,
-matching against an American Tinnitus Association tinnitus example,
+with an artificial subject, but matched against American Tinnitus Association (ATA) tinnitus examples,
 as in the human experiment.
@@
 \begin{equation}
-  y = \mathrm{sgn}(\Psi * \bar{x})
+  y = \mathrm{sgn}(\Psi \bar{x})
 \end{equation}
@@
 Reconstructions were computed using linear regression and compressed sensing
+(\cf the main paper)
 and reconstruction accuracy was measured using Pearson's $r^2$ vs. the target signal.
 
-% n_bins: [10 30 100 200 300]
-% bin_prob: [0.1000 0.3000 0.5000 0.8000]
-% amplitude_mean: -35
-% amplitude_var: [5 10 20]
-% n_bins_filled_mean: [1 3 10 20 30]
-% n_bins_filled_var: [0.0100 1 3 10]
-% min_bins: [1 3 10 20 30]
-% max_bins: [10 20 30 50]
+Fine-tuning of parameters proceeded iteratively,
+bearing in mind both the performance of the stimulus generation methods
+in the \textit{in-silico} experiment as well as computational efficiency,
+qualitative distinguishability of stimuli from each other by a human listener,
+and viability of compressed sensing as an efficiency enhancement.
+This process resulted in $n \_ bins$ being fixed to $100$ and
+the number of trials in the \textit{in-silico} experiment being set to $1000$.
+
+\begin{table}[ht]
+	\begin{center}	
+		\small
+		\resizebox{1\columnwidth}{!}{
+			\begin{tabular}{l S[table-format=12.2] S[table-format=12.2] S[table-format=12.2] S[table-format=6.2] S[table-format=6.2] S[table-format=6.2] S[table-format=6.2]}	
+				\multicolumn{7}{c}{\textsc{Hyperparameter Sweep Results}} \\
+				\hhline{=======}
+				Stimulus Type & n \_ bins \_ filled \_ mean & n \_ bins \_ filled \_ var & min \_ bins & max \_ bins & CS \_ r^2 & LR \_ r^2 \\ 
+				\hline
+				Gaussian Prior    & 20 & 1 & & & 0.83 & 0.86 \\
+        Uniform Prior     & & & 30 & 30 & 0.82 & 0.86 \\
+        Uniform Prior     & & & 20 & 20 & 0.82 & 0.86 \\
+        Gaussian Prior    & 20 & 1 & & & 0.82 & 0.86 \\
+        Gaussian Prior    & 12 & 0.01 & & & 0.81 & 0.83 \\
+				\hhline{=======}
+			\end{tabular}
+		}
+	\end{center}
+%\normalsize
+	\caption{Top-5 stimulus generation methods by $r^2$ score averaged over
+  buzzing, electric, roaring, screeching, and static tinnitus examples,
+  with $n \_ bins = 100$ and $n \_ trials = 1000$.
+  }
+	\label{tbl:hparam_results}
+\end{table}
+
+%       stimuli_type       n_bins_filled_mean    n_bins_filled_var    min_bins    max_bins    mean_r2_cs    mean_r2_linear
+%     _________________    __________________    _________________    ________    ________    __________    ______________
+
+%     {'GaussianPrior'}            20                  0.01             NaN         NaN          0.83            0.86     
+%     {'UniformPrior' }           NaN                   NaN              30          30          0.82            0.86     
+%     {'UniformPrior' }           NaN                   NaN              20          20          0.82            0.86     
+%     {'GaussianPrior'}            20                     1             NaN         NaN          0.81            0.86     
+%     {'GaussianPrior'}            10                  0.01             NaN         NaN          0.81            0.83     
+%     {'GaussianPrior'}            30                     1             NaN         NaN           0.8            0.84     
+%     {'UniformPrior' }           NaN                   NaN              10          10           0.8            0.83     
+%     {'GaussianPrior'}            10                     1             NaN         NaN          0.79            0.83     
+%     {'UniformPrior' }           NaN                   NaN              20          30          0.79            0.79     
+%     {'GaussianPrior'}            30                  0.01             NaN         NaN          0.79            0.86
+
+Table \ref{tbl:hparam_results} shows the top 5 best-performing methods
+in the \textit{in-silico} experiment.
+Gaussian Prior and Uniform Prior outperform all other methods,
+with 10-30\% of bins being filled.
+The variance of the number of filled bins for top-performing methods
+is extremely low.
+Due to rounding to the nearest integer, a Gaussian Prior method with very low variance
+converges to a Uniform Prior method with equal min and max bin parameters.
+In the main paper, we used the Uniform Prior method with 30 filled bins ($min \_ bins = max \_ bins = 30$).
+
+\section{Sparsity of ATA Tinnitus Examples}
+
+A necessary condition for compressed sensing to produce reconstructions results
+beyond the Shannon-Nyquist limit is that the signal to be reconstructed is sparse in some basis
+\cite{taghoutiCompressedSensing2020}.
+A signal is considered to be at least $k$ sparse when it has at most $k$ nonzero elements.
+A signal is considered $k$-sparse under some basis, when a basis-transformed version
+of that signal is $k$-sparse.
+Here we show that the 8,193-dimensional ATA example tinnitus spectra are sparse under
+the discrete cosine basis.
+The signal representation in the basis is produced by computing its discrete cosine transform (DCT).
+We computed the DCT of each ATA example spectrum
+and set all but the top 32 DCT-frequencies to zero
+before taking the inverse transform back to the Fourier domain.
+Figure \ref{fig:target_signal_sparsity_1}
+shows that while some high-frequency information was lost,
+that the 32-sparse signal preserves the salient information of the signal.
+The tonotopic bin representation is also sparse under the discrete cosine basis
+(Fig. \ref{fig:target_signal_sparsity_2}).
+The sparsity value $k=32$ was chosen by examining the decay of the sorted power spectrum
+of the tinnitus Fourier spectra in the discrete cosine basis (Fig. \ref{fig:target_signal_sparsity_3}).
+We see that the power of the signal rapidly decays after only a few DCT-frequencies.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{gfx/target_signal_sparsity_1.eps}
+	\caption{Tinnitus signals are approximately sparse.
+    Each subfigure plots the true spectrum of an ATA tinnitus example
+    in blue (8,193 nonzero dimensions) and a 32-sparse (32 non-zero dimensions)
+    approximation in green.
+    The sparse signal is a low-pass filtered version of the original signal
+    that retains the salient dynamics.
+    \textbf{(a)} through \textbf{(f)} correspond to
+    buzzing, electric, roaring, static, tea kettle, and screeching ATA examples
+    respectively.}
+	\label{fig:target_signal_sparsity_1}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{gfx/target_signal_sparsity_2.eps}
+	\caption{Tonotopic bin representations of tinnitus signals are approximately sparse
+    in the DCT basis.
+    Each subfigure plots the tonotopic bin representation of an ATA tinnitus spectrum
+    in blue (100 nonzero dimensions) and the bin representation of a 10-sparse
+    approximation in red (10 nonzero dimensions).
+    The sparse signal is a low-pass filtered version of the original signal
+    that retains the salient dynamics.
+    \textbf{(a)} through \textbf{(f)} correspond to
+    buzzing, electric, roaring, static, tea kettle, and screeching ATA examples
+    respectively.}
+	\label{fig:target_signal_sparsity_2}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{gfx/target_signal_sparsity_3.eps}
+	\caption{DCT-transformed tinnitus spectra have high power in a few frequencies
+  and low power elsewhere. \textbf{a} shows the power spectrum of DCT-transformed
+  ATA tinnitus example Fourier spectra. \textbf{b} shows the highest 40 DCT frequencies
+  in ranked order, illustrating a sharp decay to zero, indicating sparsity
+  of tinnitus spectra in the DCT basis.}
+	\label{fig:target_signal_sparsity_3}
+\end{figure}
 

### 2022-07-09 code/scripts/hyperparameter_sweep_custom.m

@@ -7,7 +7,7 @@
 %% Preamble
 
 % Script-level parameters
-RUN         = false;
+RUN         = true;
 VERBOSE     = true;
 
 % Set random number seed
@@ -251,7 +251,7 @@ for ii = 1:length(n_bins)
     write_stimuli(data_dir, stimulus_generation_names{9}, stimuli, false, VERBOSE, {'distribution', 'distribution_filepath'}, {'bins'});
 end
 
-return
+% return
 
 if RUN
 

### 2022-07-09 code/scripts/target_signal_sparsity.m

@@ -1,7 +1,9 @@
-%% Quantify the sparisty of the target signals (ATA tinnitus examples)
+%% Quantify the sparsity of the target signals (ATA tinnitus examples)
 %% in the DCT basis.
 
 %% Preamble
+
+font_size = 36;
 
 % Project Directory (i.e., tinnitus-project/)
 project_dir = pathlib.strip(mfilename('fullpath'), 3);
@@ -34,14 +36,9 @@ f = [f{:}];
 
 % Get bin-space representation
 
-options = struct;
-options.min_freq  = 100;
-options.max_freq  = 22e3;
-options.duration  = size(target_signal, 1) / options.max_freq;
-options.n_trials  = 2e3;
-stimgen = GaussianPriorStimulusGeneration();
-stimgen = stimgen.from_config(options);
-
+config = parse_config(pathlib.join(project_dir, 'code', 'experiment', 'configs', 'config_template.yaml'));
+stimgen = UniformPriorStimulusGeneration();
+stimgen = stimgen.from_config(config);
 target_signal_binrep = stimgen.spect2binnedrepr(target_signal);
 
 % Convert signals to decibels
@@ -72,29 +69,43 @@ for ii = 1:size(ts_br_dct_compressed, 2)
 end
 
 % Compare compressed representation to full representation
+
 fig1 = new_figure();
+
 for ii = 1:length(data_names)
-    ax = subplot(length(data_names), 1, ii);
-    plot(ax, 1e-3 * stimgen.get_freq(), idct(ts_dct(:, ii)));
+    ax = subplot(length(data_names), 2, ii);
+    plot(ax, 1e-3 * f, idct(ts_dct(:, ii)));
     hold on
-    plot(ax, 1e-3 * stimgen.get_freq(), idct(ts_dct_compressed(:, ii)));
-    ylabel('amplitude')
-    xlabel('frequency (kHz)')
-    title(data_names{ii})
+    plot(ax, 1e-3 * f, idct(ts_dct_compressed(:, ii)));
+    % title(data_names{ii})
+    ylabel(ax, 'amplitude (dB)', 'FontSize', font_size)
[…]

### 2022-07-09 code/utils/buffer_x_axis.m

@@ -1,0 +1,6 @@
+function xlims = buffer_x_axis(vec, buffer)
+    diff_scale = max(vec) - min(vec);
+    this_min = min(vec) - buffer * diff_scale;
+    this_max = max(vec) + buffer * diff_scale;
+    xlims = [this_min, this_max];
+end

### 2022-07-09 code/utils/new_publication_figure.m

@@ -1,0 +1,11 @@
+function fig = new_publication_figure(options)
+
+    arguments
+        options.fontsize = 8
+        options.width = 8
+        options.height = 10
+        options.units = 'centimeters'
+    end
+
+    fig = figure('Units', options.units, 'Position', [0, 0, options.width, options.height]);
+end

### 2022-07-09 code/scripts/pilot_reconstructions.m
minor changes

@@ -3,7 +3,7 @@
 % number of bins and that the reconstructions
 % should be done over the bin representation.
 
-DATA_DIR = '/home/alec/code/tinnitus-project/code/experiment/Data/data_pilot';
+DATA_DIR = '/home/alec/code/tinnitus-project/code/experiment/Data/data-paper';
 PROJECT_DIR = pathlib.strip(mfilename('fullpath'), 3);
 
 %% Compute the bin representations of the target signals
@@ -51,7 +51,7 @@ config_ids = cell(length(this_dir), 1);
 config = parse_config(pathlib.join(this_dir(1).folder, this_dir(1).name));
 stimgen = eval([config.stimuli_type, 'StimulusGeneration()']);
 stimgen = stimgen.from_config(config);
-stimgen.duration = size(target_signal, 1) / stimgen.max_freq;
+stimgen.duration = 2 * size(target_signal, 1) / stimgen.Fs;
 binned_target_signal = stimgen.spect2binnedrepr(target_signal);
 
 %% Convert subject IDs into a data table
@@ -59,7 +59,7 @@ binned_target_signal = stimgen.spect2binnedrepr(target_signal);
 for ii = 1:length(this_dir)
     config_file = this_dir(ii);
     config = parse_config(pathlib.join(config_file.folder, config_file.name));
-    config_ids{ii} = config.subjectID;
+    config_ids{ii} = config.experiment_name;
 end
 
 T = collect_parameters(config_ids);

### 2022-07-09 code/utils/cellstr4tables.m
Fix bug where character vectors are used instead of cell arrays

@@ -1,0 +1,17 @@
+function T = cellstr4tables(T)
+    % Converts all character vector columns (variables)
+    % of a table into cell arrays of character vectors.
+    % This is a workaround because `varfun` is bad, actually.
+
+    arguments
+        T table
+    end
+
+    d = T(1, vartype("char"));
+    vars = d.Properties.VariableNames;
+
+    for ii = 1:length(vars)
+        T.(vars{ii}) = cellstr(T.(vars{ii}));
+    end
+
+end % function

### 2022-07-09 code/utils/config2table.m

@@ -20,7 +20,7 @@ function data_table = config2table(curr_dir)
     config_file = curr_dir(1);
     config = parse_config(pathlib.join(config_file.folder, config_file.name));
     
-    data_table = struct2table(config);
+    data_table = cellstr4tables(struct2table(config));
     data_table.ID = 1;
     
     % Create and outer join each new data table, keeping column names the same
@@ -29,7 +29,7 @@ function data_table = config2table(curr_dir)
             config_file = curr_dir(ii);
             config = parse_config(pathlib.join(config_file.folder, config_file.name));
     
-            new_data_table = struct2table(config);
+            new_data_table = cellstr4tables(struct2table(config));
             new_data_table.ID = ii;
             data_table = outerjoin(data_table, new_data_table, 'MergeKeys', true);
         end

### 2022-07-09 code/utils/get_reconstruction.m
Add 'data_dir' option to get_reconstruction

@@ -19,6 +19,7 @@ function [x, responses_output, stimuli_matrix_output] = get_reconstruction(optio
         options.method = 'cs'
         options.verbose (1,1) logical = true
         options.fraction (1,1) {mustBeReal, mustBeNonnegative} = 1.0
+        options.data_dir (1,:) char = ''
     end
 
     % If no config file path is provided,
@@ -36,7 +37,7 @@ function [x, responses_output, stimuli_matrix_output] = get_reconstruction(optio
     end
 
     % collect the data from files
-    [responses, stimuli_matrix] = collect_data('config', config, 'verbose', options.verbose);
+    [responses, stimuli_matrix] = collect_data('config', config, 'verbose', options.verbose, 'data_dir', options.data_dir);
 
     % bin preprocessing
     if strcmp(config.stimuli_save_type, 'bins') || any(contains(options.preprocessing, 'bins'))

### 2022-07-09 code/scripts/pilot_reconstructions.m
Use the data directory from the script rather than from the config file

@@ -101,12 +101,14 @@ for ii = 1:height(T)%progress(1:height(T), 'Title', 'Computing reconstructions',
         [reconstructions_cs{ii, qq}, responses, stimuli_matrix] = get_reconstruction('config', config, ...
                                     'method', 'cs', ...
                                     'fraction', trial_fractions(qq), ...
-                                    'verbose', true);
+                                    'verbose', true, ...
+                                    'data_dir', DATA_DIR);
         corelib.verb(true, 'INFO: pilot_reconstructions', 'computing linear reconstruction')
         reconstructions_lr{ii, qq} = get_reconstruction('config', config, ...
                                     'method', 'linear', ...
                                     'fraction', trial_fractions(qq), ...
-                                    'verbose', true);
+                                    'verbose', true, ...
+                                    'data_dir', DATA_DIR);
         
                                     
         % Compute the r^2 values

### 2022-07-10 code/scripts/pilot_reconstructions.m
Start work on Results, minor fixes

@@ -5,6 +5,7 @@
 
 DATA_DIR = '/home/alec/code/tinnitus-project/code/experiment/Data/data-paper';
 PROJECT_DIR = pathlib.strip(mfilename('fullpath'), 3);
+PUBLISH = true;
 
 %% Compute the bin representations of the target signals
 
@@ -162,42 +163,97 @@ end
 %% Visualization
 
 T.reconstructions_cs_1 = reconstructions_cs(:, end);
+T.reconstructions_lr_1 = reconstructions_lr(:, end);
 T.reconstructions_rand = reconstructions_rand;
 T.reconstructions_synth = reconstructions_synth;
 
 % Plotting the bin-representation of the target signal vs. the reconstructions
 
 fig1 = new_figure();
-cmap = colormaps.linspecer(length(unique(T.subject_ID)) + 2);
+cmap = colormaps.linspecer(2 * length(unique(T.subject_ID)) + 2);
+alpha = 0.25;
 
-subplot_labels = T.target_audio';
+subplot_labels = unique(T.target_audio)';
 
-for ii = 2:-1:1
+for ii = length(subplot_labels):-1:1
     ax(ii) = subplot(2, 1, ii, 'Parent', fig1);
     hold on
 end
 
-for qq = 1:length(subplot_labels)
+for ii = 1:length(subplot_labels)
+    ylabel(ax(ii), 'norm. bin ampl. (a.u.)')
 
-    % True signal
-    plot(ax(qq), normalize(binned_target_signal(:, strcmp(data_names, subplot_labels{qq}))), '-ok');
-    ylabel(ax(qq), 'norm. bin ampl. (a.u.)')
-    
-    % Reconstructions
-    T2 = T(strcmp(T.target_audio, subplot_labels{qq}), :);
-    for ii = 1:height(T2)
-        plot(ax(qq), normalize(T2.reconstructions_cs_1{ii}), '-o', 'Color', cmap(ii, :))
+    % Target signal (ground truth)
+    p = plot(ax(ii), normalize(binned_target_signal(:, strcmp(data_names, subplot_labels{ii}))), '-ok');
+    % p.Color(4) = alpha;
+
+    % Reconstructions from subjects
+    T2 = T(strcmp(T.target_audio, subplot_labels{ii}), :);
+    legend_labels = cell(2 * height(T2), 1);
+    for qq = 1:height(T2)
+        if PUBLISH
[…]

### 2022-07-12 supplemental/supplemental.tex

--- 2022-07-09 supplemental/OJEMB Supplementary Material.tex
@@
 \sisetup{parse-numbers = false}
+\usepackage{placeins}
 
@@
 
-\IEEEPARstart{T}his document contains a description of additional experiments to find a performant
+\IEEEPARstart{T}HIS document contains a description of additional experiments to find a performant
 stimulus generation method and a discussion of sparsity in tinnitus signals.
@@
 
-\subsection{Auditorally-Distinguishable Stimuli}
-
 We used mel-frequency binning to ensure that our stimuli were auditorally-distinguishable.
@@
 from one to another (Fig. \ref{fig:hz2mel}) \cite{hamiltonTopographySpeechrelatedAcoustic2020}.
+Figure \ref{fig:examplestimulus} shows an example generated stimulus.
 
@@
 \begin{equation}
-  m = 2595 \log_10 \bigg( 1 + \frac{f}{700} \bigg)
+  m = 2595 \log_{10} \bigg( 1 + \frac{f}{700} \bigg)
 \end{equation}
@@
 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{gfx/binned_vs_unbinned_spect.eps}
+	\caption{Binned spectra capture the salient characteristics of unbinned spectra.
+  \textbf{(a)} shows the spectrum for the ``buzzing'' ATA tinnitus example
+  (black) and its binned version (red). \textbf{(b)} shows the same for the ``buzzing'' example.}
+	\label{fig:binned_vs_unbinned_spect}
+\end{figure}
+
 Furthermore, to reduce the system complexity by more than 80x,
 we implement tonotopic binning, where the frequency scale is binned
-along $100$ equally mel-spaced bins (Fig. \ref{fig:examplestimulus}).
+along $100$ equally mel-spaced bins (Fig. \ref{fig:binned_vs_unbinned_spect}).
+This has the effect of smoothing some peaks of the spectra
+as well as reducing the dimensionally by a factor of 80x.
+Despite the dimensionality reduction, less than 10\% of information is lost.
 
@@
 and $\bar{x} \in \mathbb{R}^d$ is the true target signal (the spectrum of the ATA tinnitus example).
+
+\subsection{Hyperparameter Sweep Results}
 
@@
 
+\subsection{Human vs. Synthetic Performance}
+
+For the hyperparameter sweep, we relied heavily on a synthetic model subject
+who made the yes/no decisions.
+This model relies on an idealized process,
+in which the \textit{in-silico} subject compares
+the incoming stimuli to an internal representation in a purely linear process.
+The \textit{in-silico} subject is internally consistent over trials,
+something which subjects have self-reported as not necessarily being true.
+In the \textsc{Conclusion} of the paper, we discuss some of the reasons,
+namely, that the yes/no decision threshold may not be fixed for a human subject,
+but instead varies as the subject drifts and overcorrects during the trial.
+Figure \ref{fig:r2_vs_trials} shows
+reconstruction accuracy measured by Pearson $r^2$ as a function of the
+number of trials.
+Synthetic performance increases monotonically as a function of the number of trials,
+but human performance drops consistently after 1,600 trials.
+We hypothesis that decision drift and subject fatigue are the main causes.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{gfx/r2_vs_trials.eps}
+	\caption{Performance for human subjects on the task is non-monotonic,
+  contrasting with theoretical and synthetic results.
+  \textbf{(a)} shows synthetic and human subject reconstruction accuracy
+  as measured by Pearson's $r^2$ as a function of number of trials
+  for the ``buzzing'' condition. \textbf{(b)} shows results for the ``roaring'' condition.}
+	\label{fig:r2_vs_trials}
+\end{figure}
+
 \section{Sparsity of ATA Tinnitus Examples}
@@
 
+\FloatBarrier
+
 \bibliographystyle{IEEEtran}

### 2022-07-12 code/comment2docs.py
Documentation second pass
Rearranging docs files, fixing 'see all' in comment2docs.py, creating files necessary for mkdocs, updating 'see all' sections in comments within code files, adding temp logos.

@@ -2,6 +2,9 @@
 # Generates documentation based on the comments within each file. 
 # Intended to be used in conjunction with build_docs.py
 
+import os
+from glob import glob
+
 def comment2docs(filename, file, out_file, first, a = -1):
 
     lines = tuple(open(file, 'r'))
@@ -16,8 +19,7 @@ def comment2docs(filename, file, out_file, first, a = -1):
     if 'abstract' in filename.lower():
 
         # Get line number and name of all functions within abstract class
-        lines_stripped = tuple(map(str.strip,lines))
-        fns = [(ind, line) for ind, line in enumerate(lines_stripped) if line.find('function') == 0]
+        fns = [(ind, line.strip()) for ind, line in enumerate(lines) if line.strip().find('function') == 0]
 
         # Find exact function name
         for i in range(0, len(fns)):
@@ -108,14 +110,37 @@ def comment2docs(filename, file, out_file, first, a = -1):
                 # pre-formatted link, just write it
                 out_file.write('    ' + thisline)
 
-            elif format_link:
-                # ok, this is a class method
+            elif '.' in thisline and format_link:
+                # This is a class method
                 words = thisline.split('.')
                 link_class = words[0]
                 link_method = words[1]
 
                 out_file.write('    * [' + thisline.strip() + '](../' +
                             link_class + '/#' + link_method.strip().lower() + ')\n')
+
+            elif format_link:
+                # This is a reference to a standalone function or script
+
+                # Find file being referred to. Not using 'in' to avoid finding multiple files.
+                ref = [item for item in glob('./*/*.m') if thisline.strip() == os.path.basename(item)[:-2]]
+
+                if not ref:
+                    print(f"[WARN]: 'See also' not formatted properly in {filename}.")
+                    continue
+
+                elif os.path.dirname(ref[0]) == os.path.dirname(file):
+                    out_file.write(f'    * [{thisline.strip()}]' + 
+                                f'(./#{thisline.strip().lower()})\n')
+
+                elif 'stimulus_generation' in file:
+                    out_file.write(f'    * [{thisline.strip()}]' + 
+                                f'(../.{os.path.dirname(ref[0])}/#{thisline.strip().lower()})\n')
+
+                else:
+                    out_file.write(f'    * [{thisline.strip()}]' + 
+                                f'(.{os.path.dirname(ref[0])}/#{thisline.strip().lower()})\n')
+
             else:
                 out_file.write(thisline)
 

### 2022-07-12 code/utils/binnedrepr2spect.m

@@ -22,9 +22,7 @@
 %       representing the stimulus spectra
 % 
 % See Also:
-% * [spect2binnedrepr](./spect2binnedrepr)
-% * [spect2bin](./spect2bin)
-% * [bin2spect](./bin2spect)
+% spect2binnedrepr
 
 function T = binnedrepr2spect(binned_repr, B, n_bins)
 

### 2022-07-12 code/utils/collect_parameters.m

@@ -19,9 +19,9 @@
 %   data_table = collect_parameters(filenames)
 % 
 % See Also: 
-% * [collect_reconstructions](./collect_reconstructions) 
-% * [collect_data](./collect_data)
-% * [config2table](./config2table)
+% collect_reconstructions
+% collect_data
+% config2table
 
 function data_table = collect_parameters(filenames)
 

### 2022-07-12 code/utils/config2table.m

@@ -12,7 +12,7 @@
 %   data_table: table
 % 
 % See also:
-% * [parse_config](./parse_config)
+% parse_config
 
 function data_table = config2table(curr_dir)
 

### 2022-07-12 code/utils/create_files_and_stimuli.m

@@ -4,7 +4,7 @@
 % Write the stimuli into the stimuli file.
 % 
 % See also:
-% * [Protocol](../experiment/Protocol)
+% Protocol
 
 function [stimuli_matrix, Fs, filename_responses, filename_stimuli, filename_meta, file_hash] = create_files_and_stimuli(config, stimuli_object, hash_prefix)
 

### 2022-07-12 code/utils/get_experiment_ID.m

@@ -19,8 +19,8 @@
 %   expID: character vector
 % 
 % See Also: 
-% * [prop2str](./prop2str)
-% * [parse_config](./parse_config)
+% prop2str
+% parse_config
 
 function expID = get_experiment_ID(config, ignore_fields, property_separator)
 

### 2022-07-12 code/utils/get_reconstruction.m

@@ -7,9 +7,9 @@
 % Compute the reconstruction, given the response vector and the stimuli matrix with a preprocessing step and a method chosen from {'cs', 'cs_nb', 'linear'}
 % 
 % See Also: 
-% * [collect_reconstructions](./collect_reconstructions) 
-% * [collect_data](./collect_data)
-% * [config2table](./config2table)
+% collect_reconstructions
+% collect_data
+% config2table
 
 function [x, responses_output, stimuli_matrix_output] = get_reconstruction(options)
 

### 2022-07-12 code/utils/prop2str.m

@@ -28,7 +28,7 @@
 %   stringified_properties = prop2str(obj, [], '&&')
 % 
 % See Also: 
-% * [collect_parameters](./collect_parameters)
+% collect_parameters
 
 function [stringified_properties] = prop2str(obj, properties_to_skip, property_separator)
 

### 2022-07-12 code/utils/str2prop.m

@@ -1,30 +1,32 @@
+% ### str2prop
+% Converts a string of properties and values
+% into a struct or cell array.
+% TODO: more documentation, use property_separator
+% 
+% Arguments:
+% 
+%   prop_string: character vector
+%       String containing property : value pairs
+% 
+%   properties_to_skip: character vector or cell array
+%       Properties to not incude in the output character vector
+% 
+%   property_separator: character vector
+%       What separator to use between parameter statements.
+% 
+% Returns:
+% 
+%   obj: struct or cell array
+% 
+% 
+% Example:
+% 
+%   obj = str2prop(prop_string, [], '&&')
+% 
+% See Also: 
+% collect_parameters
+
 function obj = str2prop(prop_string, properties_to_skip, property_separator, output_type)
-    % Converts a string of properties and values
-    % into a struct or cell array.
-    % TODO: more documentation, use property_separator
-    % 
-    % Arguments:
-    % 
-    %   prop_string: character vector
-    %       String containing property : value pairs
-    % 
-    %   properties_to_skip: character vector or cell array
-    %       Properties to not incude in the output character vector
-    % 
-    %   property_separator: character vector
-    %       What separator to use between parameter statements.
-    % 
-    % Returns:
-    % 
-    %   obj: struct or cell array
-    % 
-    % 
-    % Example:
-    % 
-    %   obj = str2prop(prop_string, [], '&&')
-    % 
-    % See Also: collect_parameters, str2prop
-    % 
 
     arguments
         prop_string {mustBeText}

### 2022-07-12 code/comment2docs.py
Doc 2nd pass fix
Fixing small bug in comment2docs.py where 'see also' reference matched abstract method.

@@ -13,6 +13,7 @@ def comment2docs(filename, file, out_file, first, a = -1):
     lastcomment = -1
     z_range_min = 0
     abstract = False
+    prev_comment = True
     fn_names = []
 
     # Abstract classes need to be handled differently because of multiple functions within the file.
@@ -31,12 +32,17 @@ def comment2docs(filename, file, out_file, first, a = -1):
         # Identify beginning of documentation. 
         # If function name is not in comment, no docs will be written.
         for i in range(a + 1, len(lines)):
+            
+            # Prevent 'see also' section matching value in fn_names and assigning 'a'.
+            if lines[i].lstrip() and lines[i].lstrip()[0] != '%':
+                prev_comment = False
+
             thisline = lines[i].replace('#', '')
             thisline = thisline.replace(' ', '')
             thisline = thisline.replace('%', '')
             thisline = thisline.strip()
 
-            if thisline.lower() in fn_names:
+            if thisline.lower() in fn_names and not prev_comment:
                 abstract = True
                 a = i
                 break

### 2022-07-16 code/scripts/pilot_reconstructions.m
Rescale spectra

@@ -170,7 +170,9 @@ T.reconstructions_synth = reconstructions_synth;
 if PUBLISH
     for ii = 1:height(T)
         this_filepath = pathlib.join(DATA_DIR, [T.experiment_name{ii}, '.wav']);
-        this_spectrum = stimgen.binnedrepr2spect(T.reconstructions_cs_1{ii});
+        this_binrep = rescale(T.reconstructions_cs_1{ii}, -20, 0);
+        this_spectrum = stimgen.binnedrepr2spect(this_binrep);
+        this_spectrum(f(:,1) > 13e3) = -20;
         this_waveform = stimgen.synthesize_audio(this_spectrum, stimgen.get_nfft());
         audiowrite(this_filepath, this_waveform, stimgen.Fs);
     end

### 2022-07-26 code/utils/munge.m
Add munge function

@@ -1,0 +1,20 @@
+function munge(config_file)
+    
+    config = parse_config(config_file);
+    config_hash = get_hash(config);
+    hash_prefix = [config_hash '_' num2str(floor(posixtime(datetime('now', 'TimeZone', 'local'))))];
+    
+    files = dir("*.csv");
+    
+    for ii = 1:length(files)
+        this_filename = strrep(files(ii).name, 'pilot&&subject=AL&&stimuli_type=uniformprior&&target_audio=roar_', '');
+        this_filename = strrep(this_filename, 'meta_', ['meta_', hash_prefix, '_']);
+        this_filename = strrep(this_filename, 'stimuli_', ['stimuli_', hash_prefix, '_']);
+        this_filename = strrep(this_filename, 'responses_', ['responses_', hash_prefix, '_']);
+        this_filename(end-31:end) = [];
+        this_filename = [this_filename, '.csv'];
+        movefile(files(ii).name, this_filename)
+        disp(this_filename)
+    end
+
+end % function

### 2022-07-26 code/scripts/pilot_reconstructions.m
Fix ordering

@@ -68,6 +68,7 @@ for ii = 1:length(this_dir)
 end
 
 T = config2table(this_dir);
+T = sortrows(T, 'ID');
 T.config_filename = config_filenames(:); 
 
 

### 2022-12-10 code/scripts/pilot_reconstructions.m
135 box and whisker plot of r values (#150)
* Add r values

* Add class definition

* Add template code

* Finish function

* Add rand bootstrapping

@@ -7,7 +7,7 @@
 %% Preamble
 % Change the DATA_DIR and PUBLISH flags as you need to.
 
-DATA_DIR = ['~/Downloads/data-paper-8-bins'];
+DATA_DIR = '/home/alec/code/tinnitus-project/code/experiment/Data/data-paper';
 PROJECT_DIR = pathlib.strip(mfilename('fullpath'), 3);
 BOOTSTRAP = 1000; % Set to 0 or false if not using.
 PUBLISH = false;

### 2022-12-10 code/stimulus_generation/@BrimijoinGaussianSmoothedStimulusGeneration/BrimijoinGaussianSmoothedStimulusGeneration.m

@@ -1,0 +1,8 @@
+classdef BrimijoinGaussianSmoothedStimulusGeneration < AbstractBinnedStimulusGenerationMethod
+    % TODO: write some documentation
+
+    properties
+        amplitude_values (1, :) {mustBeReal} = linspace(-20, 0, 6)
+    end
+
+end % classdef

### 2022-12-10 code/utils/bootstrap_reconstruction_synth.m

@@ -1,0 +1,79 @@
+% Runs the synthetic subject selection process N times
+% and reconstructs each time.
+function [r] = bootstrap_reconstruction_synth(options)
+    
+    arguments
+        options.config_file (1,:) = ''
+        options.config = []
+        options.method = 'linear' % or 'cs'
+        options.verbose (1,1) logical = true
+        options.gamma (1,1) {mustBeReal, mustBeNonnegative, mustBeInteger} = 0
+        options.N (1,1) {mustBeReal, mustBeNonnegative, mustBeInteger} = 100
+        options.strategy (1,:) {mustBeText} = 'synth' % or 'rand'
+    end
+
+    % If no config file path is provided,
+    % open a UI to load the config
+    if isempty(options.config) && isempty(options.config_file)
+        [file, abs_path] = uigetfile();
+        config = parse_config(pathlib.join(abs_path, file), options.legacy, options.verbose);
+        corelib.verb(options.verbose, 'INFO: get_reconstruction', ['config file [', file, '] loaded from GUI'])
+    elseif isempty(options.config)
+        config = parse_config(options.config_file, options.legacy, options.verbose);
+        corelib.verb(options.verbose, 'INFO: get_reconstruction', ['config object loaded from provided file [', char(options.config_file), ']'])
+    else
+        config = options.config;
+        corelib.verb(options.verbose, 'INFO: get_reconstruction', 'config object provided')
+    end
+    
+    % Set the gamma parameter if not set
+    if options.gamma == 0
+        options.gamma = get_gamma_from_config(options.config, options.verbose);
+    else
+        % Gamma set by user
+        corelib.verb(options.verbose, 'INFO: get_reconstruction', ['gamma parameter set to ', num2str(options.gamma), ', as specified by the user.']);
+    end
+
+    assert(any(strcmp(options.strategy, {'synth', 'rand'})), 'options.strategy must be synth or rand')
+    corelib.verb(options.verbose, 'INFO: bootstrap_reconstruction_synth', ['strategy is ', options.strategy])
+    assert(any(strcmp(options.method, {'cs', 'linear'})), 'options.method must be cs or linear')
+    corelib.verb(options.verbose, 'INFO: bootstrap_reconstruction_synth', ['method is ', options.method])
+
+    % Create the stimulus generation object
+    stimgen = eval([char(config.stimuli_type), 'StimulusGeneration()']);
+    stimgen = stimgen.from_config(config);
+
[…]

### 2022-12-10 code/utils/plot_violin.m

@@ -1,0 +1,53 @@
+function plot_violin(T, options)
+
+    arguments
+        T table
+        options.figure = []
+        options.cs = true
+        options.lr = false
+        options.colormap = @colormaps.linspecer
+        options.baseline = false
+        options.synthetic = false
+        options.publish = false
+    end
+
+    if isempty(options.figure)
+        options.figure = new_figure();
+    end
+
+    % Set current figure
+    figure(options.figure);
+
+    % Colormap for plotting
+    cmap = options.colormap();
+
+    % How many different target signals are there?
+    subplot_labels = unique(T.target_signal_name);
+    assert(~isempty(subplot_labels), 'couldn''t find any data to plot')
+ 
+    % Generate one subplot for each unique target signal
+    for ii = length(subplot_labels):-1:1
+        ax(ii) = subplot(length(subplot_labels), 1, ii, 'Parent', options.figure);
+        hold on
+    end
+
+    for ii = 1:length(subplot_labels)
+        filtered_table = T(strcmp(T.target_signal_name), subplot_labels{ii});
+
+        ydata = [filtered_table.r_lr_bins_1; ...
+                filtered_table.r_cs_bins_1; ...
+                r_rand_lr; ...
+                r_rand_cs; ...
+                r_synth_lr; ...
+                r_synth_cs];
+        
+        xdata = [repmat({'Subj. LR'}, length(filtered_table.r_lr_bins_1), 1); ...
+                repmat({'Subj. CS'}, length(filtered_table.r_cs_bins_1), 1); ...
+                repmat({'Rand LR'}, length(r_rand_lr), 1), ...
+                repmat({'Rand CS'}, length(r_rand_cs), 1), ...
+                repmat({'Synth LR'}, length(r_synth_lr), 1), ...
+                repmat({'Synth CS'}, length(r_synth_cs), 1)];
+
+        violinplot(ax(ii), ydata, xdata);
+        
+    end

### 2022-12-10 code/utils/plot_violin.m
minor fixes

@@ -3,16 +3,21 @@ function plot_violin(T, options)
     arguments
         T table
         options.figure = []
-        options.cs = true
-        options.lr = false
+        options.cs = false
+        options.lr = true
         options.colormap = @colormaps.linspecer
         options.baseline = false
         options.synthetic = false
         options.publish = false
+        options.data_dir = '/home/alec/code/tinnitus-project/code/experiment/Data/data-paper'
     end
 
     if isempty(options.figure)
         options.figure = new_figure();
+    end
+
+    if options.cs
+        error('not currently supported')
     end
 
     % Set current figure
@@ -26,28 +31,65 @@ function plot_violin(T, options)
     assert(~isempty(subplot_labels), 'couldn''t find any data to plot')
  
     % Generate one subplot for each unique target signal
-    for ii = length(subplot_labels):-1:1
-        ax(ii) = subplot(length(subplot_labels), 1, ii, 'Parent', options.figure);
-        hold on
-    end
+    m = length(subplot_labels) + 1;
+    n = 3;
 
-    for ii = 1:length(subplot_labels)
-        filtered_table = T(strcmp(T.target_signal_name), subplot_labels{ii});
+    % Plot the 1 to m-1 subplots
+    categories = {'subject', 'synthetic', 'random'};
+    counter = 0;
+    data_container = cell(length(subplot_labels), 1);
+    for ii = 1:(m-1)
+        % Get the config filepath
+        subset = T(strcmp(T.target_signal_name, subplot_labels{ii}) & contains(T.config_filename, 'AH'), :);
+        config_filename = char(subset(1, :).config_filename);
+        % Get the data to plot
+        data_to_plot = cell(3, 1);
+        data_to_plot{1} = table2array(T(strcmp(T.target_signal_name, subplot_labels{ii}), "r_lr_bins_1"));
+        data_to_plot{2} = bootstrap_reconstruction_synth(...
+            'config_file', pathlib.join(options.data_dir, config_filename), ...
+            'method', 'linear', ...
+            'strategy', 'synth', ...
+            'N', 100);
+        data_to_plot{3} = bootstrap_reconstruction_synth(...
+            'config_file', pathlib.join(options.data_dir, config_filename), ...
+            'method', 'linear', ...
+            'strategy', 'rand', ...
+            'N', 100);
 
[…]

### 2022-12-10 code/utils/bootstrap_reconstruction_synth.m
135 box and whisker plot of r values (#151)
* Add r values

* Add class definition

* Add template code

* Finish function

* Add rand bootstrapping

* minor fixes

@@ -10,6 +10,8 @@ function [r] = bootstrap_reconstruction_synth(options)
         options.gamma (1,1) {mustBeReal, mustBeNonnegative, mustBeInteger} = 0
         options.N (1,1) {mustBeReal, mustBeNonnegative, mustBeInteger} = 100
         options.strategy (1,:) {mustBeText} = 'synth' % or 'rand'
+        options.legacy = false
+        options.parallel = true
     end
 
     % If no config file path is provided,
@@ -28,7 +30,7 @@ function [r] = bootstrap_reconstruction_synth(options)
     
     % Set the gamma parameter if not set
     if options.gamma == 0
-        options.gamma = get_gamma_from_config(options.config, options.verbose);
+        options.gamma = get_gamma_from_config(config, options.verbose);
     else
         % Gamma set by user
         corelib.verb(options.verbose, 'INFO: get_reconstruction', ['gamma parameter set to ', num2str(options.gamma), ', as specified by the user.']);
@@ -50,30 +52,54 @@ function [r] = bootstrap_reconstruction_synth(options)
 
     % Run the synthetic subject selection process N times
     r = zeros(options.N, 1);
-    for ii = 1:options.N
-        if strcmp(options.strategy, 'synth')
-            [responses, ~, stimuli_binned_repr] = stimgen.subject_selection_process(target_signal);
-        elseif strcmp(options.strategy, 'rand')
-            responses = sign(rand(options.N, 1) - 0.5);
-            [~, ~, ~, stimuli_binned_repr] = stimgen.generate_stimuli_matrix();
-        else
-            error('not implemented')
+    if options.parallel
+        parfor ii = 1:options.N
+            if strcmp(options.strategy, 'synth')
+                [responses, ~, stimuli_binned_repr] = stimgen.subject_selection_process(target_signal);
+            elseif strcmp(options.strategy, 'rand')
+                responses = sign(rand(options.N, 1) - 0.5);
+                [~, ~, ~, stimuli_binned_repr] = stimgen.generate_stimuli_matrix();
+            else
+                error('not implemented')
+            end
+
+            % Compute the reconstruction
+            if strcmp(options.method, 'cs')
+                x = cs(responses, stimuli_binned_repr', options.gamma, 'verbose', true);
+            elseif strcmp(options.method, 'linear')
+                x = gs(responses, stimuli_binned_repr');
+            else
+                error('not implemented')
+            end
+
+            % Get the correlation for the reconstruction
[…]

### 2022-12-10 code/utils/plot_violin.m

@@ -3,18 +3,34 @@ function plot_violin(T, options)
     arguments
         T table
         options.figure = []
+<<<<<<< HEAD
+        options.cs = false
+        options.lr = true
+=======
         options.cs = true
         options.lr = false
+>>>>>>> main
         options.colormap = @colormaps.linspecer
         options.baseline = false
         options.synthetic = false
         options.publish = false
+<<<<<<< HEAD
+        options.data_dir = '/home/alec/code/tinnitus-project/code/experiment/Data/data-paper'
+=======
+>>>>>>> main
     end
 
     if isempty(options.figure)
         options.figure = new_figure();
     end
 
+<<<<<<< HEAD
+    if options.cs
+        error('not currently supported')
+    end
+
+=======
+>>>>>>> main
     % Set current figure
     figure(options.figure);
 
@@ -26,6 +42,70 @@ function plot_violin(T, options)
     assert(~isempty(subplot_labels), 'couldn''t find any data to plot')
  
     % Generate one subplot for each unique target signal
+<<<<<<< HEAD
+    m = length(subplot_labels) + 1;
+    n = 3;
+
+    % Plot the 1 to m-1 subplots
+    categories = {'subject', 'synthetic', 'random'};
+    counter = 0;
+    data_container = cell(length(subplot_labels), 1);
+    for ii = 1:(m-1)
+        % Get the config filepath
+        subset = T(strcmp(T.target_signal_name, subplot_labels{ii}) & contains(T.config_filename, 'AH'), :);
+        config_filename = char(subset(1, :).config_filename);
+        % Get the data to plot
+        data_to_plot = cell(3, 1);
+        data_to_plot{1} = table2array(T(strcmp(T.target_signal_name, subplot_labels{ii}), "r_lr_bins_1"));
+        data_to_plot{2} = bootstrap_reconstruction_synth(...
+            'config_file', pathlib.join(options.data_dir, config_filename), ...
+            'method', 'linear', ...
+            'strategy', 'synth', ...
+            'N', 100);
+        data_to_plot{3} = bootstrap_reconstruction_synth(...
+            'config_file', pathlib.join(options.data_dir, config_filename), ...
+            'method', 'linear', ...
+            'strategy', 'rand', ...
+            'N', 100);
+
+        for qq = 1:n
+            counter = counter + 1;
[…]

### 2022-12-10 code/utils/plot_violin.m
Merge from main

@@ -3,34 +3,23 @@ function plot_violin(T, options)
     arguments
         T table
         options.figure = []
-<<<<<<< HEAD
         options.cs = false
         options.lr = true
-=======
-        options.cs = true
-        options.lr = false
->>>>>>> main
         options.colormap = @colormaps.linspecer
         options.baseline = false
         options.synthetic = false
         options.publish = false
-<<<<<<< HEAD
         options.data_dir = '/home/alec/code/tinnitus-project/code/experiment/Data/data-paper'
-=======
->>>>>>> main
     end
 
     if isempty(options.figure)
         options.figure = new_figure();
     end
 
-<<<<<<< HEAD
     if options.cs
         error('not currently supported')
     end
 
-=======
->>>>>>> main
     % Set current figure
     figure(options.figure);
 
@@ -42,7 +31,6 @@ function plot_violin(T, options)
     assert(~isempty(subplot_labels), 'couldn''t find any data to plot')
  
     % Generate one subplot for each unique target signal
-<<<<<<< HEAD
     m = length(subplot_labels) + 1;
     n = 3;
 
@@ -105,30 +93,3 @@ function plot_violin(T, options)
 
 
 end % function
-=======
-    for ii = length(subplot_labels):-1:1
-        ax(ii) = subplot(length(subplot_labels), 1, ii, 'Parent', options.figure);
-        hold on
-    end
-
-    for ii = 1:length(subplot_labels)
-        filtered_table = T(strcmp(T.target_signal_name), subplot_labels{ii});
-
-        ydata = [filtered_table.r_lr_bins_1; ...
-                filtered_table.r_cs_bins_1; ...
-                r_rand_lr; ...
-                r_rand_cs; ...
-                r_synth_lr; ...
-                r_synth_cs];
-        
-        xdata = [repmat({'Subj. LR'}, length(filtered_table.r_lr_bins_1), 1); ...
-                repmat({'Subj. CS'}, length(filtered_table.r_cs_bins_1), 1); ...
-                repmat({'Rand LR'}, length(r_rand_lr), 1), ...
-                repmat({'Rand CS'}, length(r_rand_cs), 1), ...
-                repmat({'Synth LR'}, length(r_synth_lr), 1), ...
-                repmat({'Synth CS'}, length(r_synth_cs), 1)];
-
-        violinplot(ax(ii), ydata, xdata);
-        
-    end
->>>>>>> main

### 2022-12-10 code/utils/plot_violin.m
wip

@@ -1,15 +1,15 @@
-function plot_violin(T, options)
+function ax = plot_violin(T, options)
 
     arguments
         T table
         options.figure = []
         options.cs = false
         options.lr = true
-        options.colormap = @colormaps.linspecer
-        options.baseline = false
-        options.synthetic = false
+        % options.colormap = @colormaps.linspecer
         options.publish = false
         options.data_dir = '/home/alec/code/tinnitus-project/code/experiment/Data/data-paper'
+        options.N = 100
+        options.parallel = true
     end
 
     if isempty(options.figure)
@@ -23,8 +23,8 @@ function plot_violin(T, options)
     % Set current figure
     figure(options.figure);
 
-    % Colormap for plotting
-    cmap = options.colormap();
+    % % Colormap for plotting
+    % cmap = options.colormap();
 
     % How many different target signals are there?
     subplot_labels = unique(T.target_signal_name);
@@ -49,12 +49,14 @@ function plot_violin(T, options)
             'config_file', pathlib.join(options.data_dir, config_filename), ...
             'method', 'linear', ...
             'strategy', 'synth', ...
-            'N', 100);
+            'N', options.N, ...
+            'parallel', options.parallel);
         data_to_plot{3} = bootstrap_reconstruction_synth(...
             'config_file', pathlib.join(options.data_dir, config_filename), ...
             'method', 'linear', ...
             'strategy', 'rand', ...
-            'N', 100);
+            'N', options.N, ...
+            'parallel', false);
 
         for qq = 1:n
             counter = counter + 1;
@@ -87,9 +89,5 @@ function plot_violin(T, options)
 
         title(ax(m, qq), 'combined');
     end
-    figlib.pretty('FontSize', 18, 'PlotBuffer', 0.2);
-    axlib.equalize(ax(:), 'x', 'y');
-    figlib.label();
-
 
 end % function

### 2022-12-10 paper/make_figures.m

@@ -1,0 +1,23 @@
+%% Make figures for the main paper
+
+% Set rng seed
+rng(112358, 'twister');
+
+%% Collect and analyze the data
+
+% Run the collection and analysis script (run the following line)
+% pilot_reconstructions
+
+% Table with only data to show in the paper
+
+T2 = T(T.n_bins == 8, :);
+summary(T2);
+
+%% Violin plots with buzzing and roaring 
+
+ax = plot_violin(T2, 'lr', true, 'publish', true, 'N', 1000);
+
+figlib.pretty('FontSize', 18, 'PlotBuffer', 0.2);
+axlib.equalize(ax(:), 'x', 'y');
+figlib.label();
+

### 2022-12-11 code/utils/plot_violin.m
wip

@@ -3,10 +3,6 @@ function ax = plot_violin(T, options)
     arguments
         T table
         options.figure = []
-        options.cs = false
-        options.lr = true
-        % options.colormap = @colormaps.linspecer
-        options.publish = false
         options.data_dir = '/home/alec/code/tinnitus-project/code/experiment/Data/data-paper'
         options.N = 100
         options.parallel = true
@@ -14,10 +10,6 @@ function ax = plot_violin(T, options)
 
     if isempty(options.figure)
         options.figure = new_figure();
-    end
-
-    if options.cs
-        error('not currently supported')
     end
 
     % Set current figure
@@ -33,6 +25,8 @@ function ax = plot_violin(T, options)
     % Generate one subplot for each unique target signal
     m = length(subplot_labels) + 1;
     n = 3;
+
+    ax = figlib.tightSubplots(m, n, 'ShareX', false, 'ShareY', false);
 
     % Plot the 1 to m-1 subplots
     categories = {'subject', 'synthetic', 'random'};
@@ -60,14 +54,15 @@ function ax = plot_violin(T, options)
 
         for qq = 1:n
             counter = counter + 1;
-            ax(ii, qq) = subplot(m, n, counter);
+            % ax(ii, qq) = subplot(m, n, counter);
+            axes(ax(sub2ind([m, n], qq, ii)));
             violinplot(data_to_plot{qq}, categories(qq), 'ViolinAlpha', 0.3, 'ShowBox', true);
             
             if qq == 1
-                ylabel(ax(ii, qq), 'Pearson''s r');
+                ylabel(ax(sub2ind([m, n], qq, ii)), 'Pearson''s r');
             end
 
-            title(ax(ii, qq), subplot_labels{ii});
+            % title(ax(sub2ind([m, n], qq, ii)), subplot_labels{ii});
             
         end
         
@@ -76,7 +71,8 @@ function ax = plot_violin(T, options)
     
     for qq = 1:n
         counter = counter + 1;
-        ax(m, qq) = subplot(m, n, counter);
+        % ax(m, qq) = subplot(m, n, counter);
+        axes(ax(sub2ind([m, n], qq, m)));
         data_to_plot = [];
         for ii = 1:length(data_container)
             data_to_plot = [data_to_plot; data_container{ii}{qq}];
@@ -84,10 +80,10 @@ function ax = plot_violin(T, options)
[…]

### 2022-12-11 paper/make_figures.m

@@ -15,9 +15,10 @@ summary(T2);
 
 %% Violin plots with buzzing and roaring 
 
-ax = plot_violin(T2, 'lr', true, 'publish', true, 'N', 1000);
+ax = plot_violin(T2, 'N', 10, 'parallel', false);
 
-figlib.pretty('FontSize', 18, 'PlotBuffer', 0.2);
+figlib.pretty('FontSize', 36, 'PlotBuffer', 0.2, 'AxisBox', 'off', 'YMinorTicks', 'on');
 axlib.equalize(ax(:), 'x', 'y');
-figlib.label();
+% figlib.tight();
+figlib.label('XOffset', 0.01, 'YOffset', -0.03, 'FontSize', 36);
 

### 2022-12-11 code/utils/plot_violin.m
Submit first draft

@@ -1,4 +1,4 @@
-function ax = plot_violin(T, options)
+function [ax, data_container] = plot_violin(T, options)
 
     arguments
         T table
@@ -26,7 +26,10 @@ function ax = plot_violin(T, options)
     m = length(subplot_labels) + 1;
     n = 3;
 
-    ax = figlib.tightSubplots(m, n, 'ShareX', false, 'ShareY', false);
+    % ax = figlib.tightSubplots(m, n, 'ShareX', false, 'ShareY', false, 'padding', 0.05);
+    for ii = (m*n):-1:1
+        ax(ii) = subplot(m, n, ii);
+    end
 
     % Plot the 1 to m-1 subplots
     categories = {'subject', 'synthetic', 'random'};
@@ -56,7 +59,7 @@ function ax = plot_violin(T, options)
             counter = counter + 1;
             % ax(ii, qq) = subplot(m, n, counter);
             axes(ax(sub2ind([m, n], qq, ii)));
-            violinplot(data_to_plot{qq}, categories(qq), 'ViolinAlpha', 0.3, 'ShowBox', true);
+            violinplot(data_to_plot{qq}, {''}, 'ViolinAlpha', 0.3, 'ShowBox', true);
             
             if qq == 1
                 ylabel(ax(sub2ind([m, n], qq, ii)), 'Pearson''s r');

### 2022-12-11 paper/make_figures.m

@@ -15,10 +15,23 @@ summary(T2);
 
 %% Violin plots with buzzing and roaring 
 
-ax = plot_violin(T2, 'N', 10, 'parallel', false);
+[ax, data_container] = plot_violin(T2, 'N', 1000, 'parallel', false);
 
 figlib.pretty('FontSize', 36, 'PlotBuffer', 0.2, 'AxisBox', 'off', 'YMinorTicks', 'on');
 axlib.equalize(ax(:), 'x', 'y');
 % figlib.tight();
-figlib.label('XOffset', 0.01, 'YOffset', -0.03, 'FontSize', 36);
+figlib.label('XOffset', -0.01, 'YOffset', 0.03, 'FontSize', 36);
 
+%% Bar with error for bootstrapped r-values
+
+fig2 = new_figure();
+T2 = sortrows(T2, ["subject_ID", "r_bootstrap_lr_mean_1"]);
+errs = [table2array(T2(strcmp(T2.target_signal_name, 'buzzing'), "r_bootstrap_lr_std_1")), ...
+        table2array(T2(strcmp(T2.target_signal_name, 'roaring'), "r_bootstrap_lr_std_1"))];
+vals = [table2array(T2(strcmp(T2.target_signal_name, 'buzzing'), "r_bootstrap_lr_mean_1")), ...
+        table2array(T2(strcmp(T2.target_signal_name, 'roaring'), "r_bootstrap_lr_mean_1"))];
+plotlib.barwitherr(errs, vals);
+xlabel('subject #')
+ylabel('Pearson''s r')
+legend({'buzzing', 'roaring'})
+figlib.pretty('FontSize', 36, 'PlotBuffer', 0.1, 'AxisBox', 'off', 'YMinorTicks', 'on');

### 2022-12-14 code/utils/fisher_transform.m
Add fisher transform

@@ -1,0 +1,3 @@
+function y = fisher_transform(x)
+    y = (1/2) * log((1 + x) / (1 - x));
+end

### 2022-12-14 paper/make_figures.m
Add fig 3

@@ -1,5 +1,7 @@
 %% Make figures for the main paper
 
+DATA_DIR = '/home/alec/code/tinnitus-project/code/experiment/Data/data-paper';
+
 % Set rng seed
 rng(112358, 'twister');
 
@@ -15,23 +17,66 @@ summary(T2);
 
 %% Violin plots with buzzing and roaring 
 
-[ax, data_container] = plot_violin(T2, 'N', 1000, 'parallel', false);
+% [ax, data_container] = plot_violin(T2, 'N', 1000, 'parallel', false);
+
+% figlib.pretty('FontSize', 36, 'PlotBuffer', 0.2, 'AxisBox', 'off', 'YMinorTicks', 'on');
+% axlib.equalize(ax(:), 'x', 'y');
+% % figlib.tight();
+% figlib.label('XOffset', -0.01, 'YOffset', 0.03, 'FontSize', 36);
+
+%% Bar with error for bootstrapped r-values
+
+config = parse_config(pathlib.join(DATA_DIR, T2.config_filename{1}));
+stimgen = eval([char(config.stimuli_type), 'StimulusGeneration()']);
+stimgen = stimgen.from_config(config);
+
+fig2 = new_figure();
+
+for ii = 2:-1:1
+    ax(ii) = subplot(2, 1, ii);
+    hold on;
+end
+
+T3 = sortrows(T2, "r_lr_bins_1", 'descend');
+n_traces = 3;
+
+% buzzing
+plot(ax(1), 1e-3 * f(:, 1), normalize(target_signal(:, strcmp(data_names, 'buzzing'))), 'k')
+data_to_plot = [T3(strcmp(T3.target_signal_name, 'buzzing'), :).reconstructions_lr_1{:}]';
+cmap = colormaps.linspecer(n_traces);
+for ii = 1:n_traces
+    plt = plot(ax(1), 1e-3 * f(:, 1), normalize(stimgen.binnedrepr2spect(data_to_plot(:, ii))), 'Color', cmap(ii, :));
+    plt.Color(4) = 0.8;
+end
+
+% roaring
+plot(ax(2), 1e-3 * f(:, 1), normalize(target_signal(:, strcmp(data_names, 'roaring'))), 'k')
+
+data_to_plot = [T3(strcmp(T3.target_signal_name, 'roaring'), :).reconstructions_lr_1{:}]';
[…]

### 2022-12-14 paper/scripts/get_stats.m
Add scripts

@@ -1,0 +1,2 @@
+%% Compute stats used in the main paper
+

### 2022-12-14 code/utils/fisher_transform.m
Add stats

@@ -1,3 +1,3 @@
 function y = fisher_transform(x)
-    y = (1/2) * log((1 + x) / (1 - x));
+    y = (1/2) * log((1 + x) ./ (1 - x));
 end

### 2022-12-14 paper/scripts/get_stats.m

@@ -1,2 +1,32 @@
 %% Compute stats used in the main paper
 
+T2 = T(T.n_bins == 8, :);
+
+%% Stats for buzzing
+
+T3 = T2(strcmp(T2.target_signal_name, 'buzzing'), :);
+r_values = fisher_transform(T3.r_lr_bins_1);
+
+[H, P, CI, stats] = ttest(r_values, [], 'tail', 'right');
+disp('One-tailed t-test for buzzing on Fisher-transformed r-values:')
+disp(['p = ', num2str(P)])
+disp(stats)
+
+%% Stats for roaring
+
+T3 = T2(strcmp(T2.target_signal_name, 'roaring'), :);
+r_values = fisher_transform(T3.r_lr_bins_1);
+
+[H, P, CI, stats] = ttest(r_values, [], 'tail', 'right');
+disp('One-tailed t-test for roaring on Fisher-transformed r-values:')
+disp(['p = ', num2str(P)])
+disp(stats)
+
+%% Stats for combined
+
+r_values = fisher_transform(T2.r_lr_bins_1);
+
+[H, P, CI, stats] = ttest(r_values, [], 'tail', 'right');
+disp('One-tailed t-test for combined on Fisher-transformed r-values:')
+disp(['p = ', num2str(P)])
+disp(stats)

### 2022-12-14 code/utils/bootstrap_reconstruction_synth.m
DRAFT 149 paper rewrite (#152)
* Merge from main

* wip

* wip

* Submit first draft

* Fixes based on Adam's comments

* minor fixes

* Add new Fig 1

* Add fisher transform

* Add fig 3

* Add scripts

* Add stats

@@ -41,15 +41,24 @@ function [r] = bootstrap_reconstruction_synth(options)
     assert(any(strcmp(options.method, {'cs', 'linear'})), 'options.method must be cs or linear')
     corelib.verb(options.verbose, 'INFO: bootstrap_reconstruction_synth', ['method is ', options.method])
 
+    if options.verbose
+        corelib.verb(options.verbose, 'INFO: boostrap_reconstruction_synth', 'options are:')
+        disp(options);
+    end
+
     % Create the stimulus generation object
     stimgen = eval([char(config.stimuli_type), 'StimulusGeneration()']);
     stimgen = stimgen.from_config(config);
+
+    % Set the number of trials to be total number of trials,
+    % instead of the number of trials in a single block
+    stimgen.n_trials = config.total_trials;
 
     % Load and preprocess the target signal
     [target_signal, ~] = wav2spect(config.target_signal_filepath);
     target_signal = 10 * log10(target_signal);
     binned_target_signal = stimgen.spect2binnedrepr(target_signal);
-
+    
     % Run the synthetic subject selection process N times
     r = zeros(options.N, 1);
     if options.parallel
@@ -80,7 +89,7 @@ function [r] = bootstrap_reconstruction_synth(options)
             if strcmp(options.strategy, 'synth')
                 [responses, ~, stimuli_binned_repr] = stimgen.subject_selection_process(target_signal);
             elseif strcmp(options.strategy, 'rand')
-                responses = sign(rand(options.N, 1) - 0.5);
+                responses = sign(rand(stimgen.n_trials, 1) - 0.5);
                 [~, ~, ~, stimuli_binned_repr] = stimgen.generate_stimuli_matrix();
             else
                 error('not implemented')

### 2022-12-14 code/utils/plot_violin.m

@@ -1,50 +1,35 @@
-function plot_violin(T, options)
+function [ax, data_container] = plot_violin(T, options)
 
     arguments
         T table
         options.figure = []
-<<<<<<< HEAD
-        options.cs = false
-        options.lr = true
-=======
-        options.cs = true
-        options.lr = false
->>>>>>> main
-        options.colormap = @colormaps.linspecer
-        options.baseline = false
-        options.synthetic = false
-        options.publish = false
-<<<<<<< HEAD
         options.data_dir = '/home/alec/code/tinnitus-project/code/experiment/Data/data-paper'
-=======
->>>>>>> main
+        options.N = 100
+        options.parallel = true
     end
 
     if isempty(options.figure)
         options.figure = new_figure();
     end
 
-<<<<<<< HEAD
-    if options.cs
-        error('not currently supported')
-    end
-
-=======
->>>>>>> main
     % Set current figure
     figure(options.figure);
 
-    % Colormap for plotting
-    cmap = options.colormap();
+    % % Colormap for plotting
+    % cmap = options.colormap();
 
     % How many different target signals are there?
     subplot_labels = unique(T.target_signal_name);
     assert(~isempty(subplot_labels), 'couldn''t find any data to plot')
  
     % Generate one subplot for each unique target signal
-<<<<<<< HEAD
     m = length(subplot_labels) + 1;
     n = 3;
+
+    % ax = figlib.tightSubplots(m, n, 'ShareX', false, 'ShareY', false, 'padding', 0.05);
+    for ii = (m*n):-1:1
+        ax(ii) = subplot(m, n, ii);
+    end
 
     % Plot the 1 to m-1 subplots
     categories = {'subject', 'synthetic', 'random'};
@@ -61,23 +46,26 @@ function plot_violin(T, options)
             'config_file', pathlib.join(options.data_dir, config_filename), ...
             'method', 'linear', ...
             'strategy', 'synth', ...
-            'N', 100);
+            'N', options.N, ...
+            'parallel', options.parallel);
         data_to_plot{3} = bootstrap_reconstruction_synth(...
             'config_file', pathlib.join(options.data_dir, config_filename), ...
             'method', 'linear', ...
             'strategy', 'rand', ...
-            'N', 100);
[…]

### 2022-12-14 paper/scripts/make_figures.m

@@ -1,0 +1,82 @@
+%% Make figures for the main paper
+
+DATA_DIR = '/home/alec/code/tinnitus-project/code/experiment/Data/data-paper';
+
+% Set rng seed
+rng(112358, 'twister');
+
+%% Collect and analyze the data
+
+% Run the collection and analysis script (run the following line)
+% pilot_reconstructions
+
+% Table with only data to show in the paper
+
+T2 = T(T.n_bins == 8, :);
+summary(T2);
+
+%% Violin plots with buzzing and roaring 
+
+% [ax, data_container] = plot_violin(T2, 'N', 1000, 'parallel', false);
+
+% figlib.pretty('FontSize', 36, 'PlotBuffer', 0.2, 'AxisBox', 'off', 'YMinorTicks', 'on');
+% axlib.equalize(ax(:), 'x', 'y');
+% % figlib.tight();
+% figlib.label('XOffset', -0.01, 'YOffset', 0.03, 'FontSize', 36);
+
+%% Bar with error for bootstrapped r-values
+
+config = parse_config(pathlib.join(DATA_DIR, T2.config_filename{1}));
+stimgen = eval([char(config.stimuli_type), 'StimulusGeneration()']);
+stimgen = stimgen.from_config(config);
+
+fig2 = new_figure();
+
+for ii = 2:-1:1
+    ax(ii) = subplot(2, 1, ii);
+    hold on;
+end
+
+T3 = sortrows(T2, "r_lr_bins_1", 'descend');
+n_traces = 3;
+
+% buzzing
+plot(ax(1), 1e-3 * f(:, 1), normalize(target_signal(:, strcmp(data_names, 'buzzing'))), 'k')
+data_to_plot = [T3(strcmp(T3.target_signal_name, 'buzzing'), :).reconstructions_lr_1{:}]';
+cmap = colormaps.linspecer(n_traces);
+for ii = 1:n_traces
+    plt = plot(ax(1), 1e-3 * f(:, 1), normalize(stimgen.binnedrepr2spect(data_to_plot(:, ii))), 'Color', cmap(ii, :));
+    plt.Color(4) = 0.8;
+end
+
+% roaring
+plot(ax(2), 1e-3 * f(:, 1), normalize(target_signal(:, strcmp(data_names, 'roaring'))), 'k')
+
[…]

### 2022-12-14 code/stimulus_generation/@BrimijoinGaussianSmoothedStimulusGeneration/generate_stimulus.m
145 write stimgen method with smoothed amplitudes (#157)
* Add class definition

* Add template code

* Finish generate_stimulus() function

@@ -39,9 +39,9 @@
 % AbstractBinnedStimulusGenerationMethod.get_freq_bins
 % AbstractStimulusGenerationMethod.generate_stimuli_matrix
 
-function [stim, Fs, spect, binned_repr, frequency_vector, bin_starts, bin_stops] = generate_stimulus(self)
+function [stim, Fs, spect, binned_repr, frequency_vector] = generate_stimulus(self)
 
-    [binnum, Fs, nfft, frequency_vector] = self.get_freq_bins();
+    [~, Fs, nfft, frequency_vector, bin_starts, bin_stops] = self.get_freq_bins();
     spect = self.get_empty_spectrum();
     binned_repr = zeros(self.n_bins, 1);
 
@@ -49,16 +49,18 @@ function [stim, Fs, spect, binned_repr, frequency_vector, bin_starts, bin_stops]
         this_amplitude_value = self.amplitude_values(randi(length(self.amplitude_values)));
         binned_repr(ii) = this_amplitude_value;
 
-        %% Find the two parameters of the gaussian (mu and sigma)
         % mu: the center of the bin
+        mu = ((bin_starts(ii) + bin_stops(ii)) / 2);
         % sigma: half the width of the bin
+        sigma = ((bin_stops(ii) - bin_starts(ii)) / 2);
 
-        %% Create a normal distribution with the correct number of points
-        % (same size as spect)
-        % with parameters mu and sigma.
-        % Normalize and add it to the spectrum.
+        % Create a normal distribution with the correct number of points
+        normal = normpdf(frequency_vector, mu, sigma);
+        % Rescale spectrum
+        normal = this_amplitude_value * normal ./ max(normal);
 
-        %% Rescale spectrum
+        % Adda to the spectrum
+        spect = spect + normal;
     end
 
     % Synthesize Audio

### 2022-12-14 code/utils/plot_violin.m

@@ -1,11 +1,24 @@
+<<<<<<< HEAD
+function plot_violin(T, options)
+=======
 function [ax, data_container] = plot_violin(T, options)
+>>>>>>> main
 
     arguments
         T table
         options.figure = []
+<<<<<<< HEAD
+        options.cs = true
+        options.lr = false
+        options.colormap = @colormaps.linspecer
+        options.baseline = false
+        options.synthetic = false
+        options.publish = false
+=======
         options.data_dir = '/home/alec/code/tinnitus-project/code/experiment/Data/data-paper'
         options.N = 100
         options.parallel = true
+>>>>>>> main
     end
 
     if isempty(options.figure)
@@ -15,14 +28,46 @@ function [ax, data_container] = plot_violin(T, options)
     % Set current figure
     figure(options.figure);
 
+<<<<<<< HEAD
+    % Colormap for plotting
+    cmap = options.colormap();
+=======
     % % Colormap for plotting
     % cmap = options.colormap();
+>>>>>>> main
 
     % How many different target signals are there?
     subplot_labels = unique(T.target_signal_name);
     assert(~isempty(subplot_labels), 'couldn''t find any data to plot')
  
     % Generate one subplot for each unique target signal
+<<<<<<< HEAD
+    for ii = length(subplot_labels):-1:1
+        ax(ii) = subplot(length(subplot_labels), 1, ii, 'Parent', options.figure);
+        hold on
+    end
+
+    for ii = 1:length(subplot_labels)
+        filtered_table = T(strcmp(T.target_signal_name), subplot_labels{ii});
+
+        ydata = [filtered_table.r_lr_bins_1; ...
+                filtered_table.r_cs_bins_1; ...
+                r_rand_lr; ...
+                r_rand_cs; ...
+                r_synth_lr; ...
+                r_synth_cs];
+        
+        xdata = [repmat({'Subj. LR'}, length(filtered_table.r_lr_bins_1), 1); ...
+                repmat({'Subj. CS'}, length(filtered_table.r_cs_bins_1), 1); ...
+                repmat({'Rand LR'}, length(r_rand_lr), 1), ...
+                repmat({'Rand CS'}, length(r_rand_cs), 1), ...
+                repmat({'Synth LR'}, length(r_synth_lr), 1), ...
+                repmat({'Synth CS'}, length(r_synth_cs), 1)];
+
+        violinplot(ax(ii), ydata, xdata);
+        
[…]

### 2022-12-16 code/stimulus_generation/@BrimijoinGaussianSmoothedStimulusGeneration/generate_stimulus.m
Updated gaussian stimulus and parse_config

@@ -62,6 +62,9 @@ function [stim, Fs, spect, binned_repr, frequency_vector] = generate_stimulus(se
         % Adda to the spectrum
         spect = spect + normal;
     end
+    
+    spect = (spect-min(spect))/(max(spect)-min(spect));
+    spect = 20*(spect-1);
 
     % Synthesize Audio
     stim = self.synthesize_audio(spect, nfft);

### 2022-12-16 code/utils/parse_config.m

@@ -60,7 +60,7 @@ function varargout = parse_config(config_file,legacy, verbose)
     %% Perform specific parsing of config options
     stimuli_types = {'Bernoulli', 'Brimijoin', 'GaussianNoise', 'GaussianNoiseNoBins', ...
                     'GaussianPrior', 'UniformNoise', 'UniformNoiseNoBins', 'UniformPrior', ...
-                    'PowerDistribution', 'UniformPriorWeightedSampling'};
+                    'PowerDistribution', 'UniformPriorWeightedSampling', 'BrimijoinGaussianSmoothed'};
     stimuli_string = [stimuli_types(:), repmat({', '}, length(stimuli_types), 1)]';
     stimuli_string = [stimuli_string{:}];
     assert(any(strcmp(config.stimuli_type, stimuli_types)), ...

### 2022-12-16 paper/scripts/make_figures.m
Fixes based on Adam's comments

@@ -24,49 +24,172 @@ summary(T2);
 % % figlib.tight();
 % figlib.label('XOffset', -0.01, 'YOffset', 0.03, 'FontSize', 36);
 
-%% Bar with error for bootstrapped r-values
+%% Reconstructions
 
-config = parse_config(pathlib.join(DATA_DIR, T2.config_filename{1}));
+% How many exemplars to plot
+n_traces = 3;
+
+% Colors
+cmap = colormaps.linspecer(n_traces);
+
+% Sort the dataset by r-value
+T3 = sortrows(T2, ["r_lr_bins_1", "subject_ID"]);
+T3_buzzing = T3(strcmp(T3.target_signal_name, 'buzzing'), :);
+T3_roaring = T3(strcmp(T3.target_signal_name, 'roaring'), :);
+
+% Create a stimgen object for binning and unbinning
+config = parse_config(pathlib.join(DATA_DIR, T3.config_filename{1}));
 stimgen = eval([char(config.stimuli_type), 'StimulusGeneration()']);
 stimgen = stimgen.from_config(config);
 
+% target_signal is the non-binned spectra of the target signals
+% this_binned_target_signal is the binned representation of the target signals
+this_binned_target_signal = stimgen.spect2binnedrepr(target_signal);
+
+% my_normalize = @(x) normalize(x, 'zscore', 'std');
+% This normalization scheme normalizes the vectors to a length of 1
+% since we cannot capture magnitude information in the reconstruction.
+% Do we need to center the vectors afterwards?
+% my_normalize = @(x) normalize(normalize(x, 'norm'), 'center');
+my_normalize = @(x) normalize(x, 'norm');
+
+
+% Generate a figure and axes
 fig2 = new_figure();
 
-for ii = 2:-1:1
-    ax(ii) = subplot(2, 1, ii);
-    hold on;
+counter = 0;
+for ii = 1:2
+    for qq = 1:2
+        counter = counter + 1;
+        ax(ii, qq) = subplot(2, 2, counter);
+        hold on;
+    end
 end
 
-T3 = sortrows(T2, "r_lr_bins_1", 'descend');
-n_traces = 3;
-
[…]

### 2022-12-17 paper/scripts/make_figures.m
Bug fix to plot best reconstructions

@@ -1,6 +1,6 @@
 %% Make figures for the main paper
 
-DATA_DIR = '/home/alec/code/tinnitus-project/code/experiment/Data/data-paper';
+% DATA_DIR = '/home/alec/code/tinnitus-project/code/experiment/Data/data-paper';
 
 % Set rng seed
 rng(112358, 'twister');
@@ -33,7 +33,7 @@ n_traces = 3;
 cmap = colormaps.linspecer(n_traces);
 
 % Sort the dataset by r-value
-T3 = sortrows(T2, ["r_lr_bins_1", "subject_ID"]);
+T3 = sortrows(T2, ["r_lr_bins_1", "subject_ID"], "descend");
 T3_buzzing = T3(strcmp(T3.target_signal_name, 'buzzing'), :);
 T3_roaring = T3(strcmp(T3.target_signal_name, 'roaring'), :);
 

### 2022-12-17 paper/scripts/make_figures.m
Fix figure

@@ -50,8 +50,8 @@ this_binned_target_signal = stimgen.spect2binnedrepr(target_signal);
 % This normalization scheme normalizes the vectors to a length of 1
 % since we cannot capture magnitude information in the reconstruction.
 % Do we need to center the vectors afterwards?
-% my_normalize = @(x) normalize(normalize(x, 'norm'), 'center');
-my_normalize = @(x) normalize(x, 'norm');
+my_normalize = @(x) normalize(normalize(x, 'norm'), 'center');
+% my_normalize = @(x) normalize(x, 'norm');
 
 
 % Generate a figure and axes
@@ -79,7 +79,7 @@ for ii = 1:n_traces
 end
 xlabel(ax(1, 1), 'bins');
 ylabel(ax(1, 1), 'amplitude (a.u.)');
-title(ax(1, 1), 'buzzing, binned')
+% title(ax(1, 1), 'buzzing, binned')
 legend(ax(1, 1), {'ground truth', 'subject #1', 'subject #2', 'subject #3'})
 
 %% Roaring, binned representation
@@ -94,7 +94,7 @@ for ii = 1:n_traces
     p.Color(4) = 0.8;
 end
 xlabel(ax(1, 2), 'bins');
-title('roaring, binned')
+% title('roaring, binned')
 legend(ax(1, 2), {'ground truth', 'subject #1', 'subject #2', 'subject #3'})
 
 %% Buzzing, full spectra
@@ -119,7 +119,7 @@ for ii = 1:n_traces
 end
 xlabel(ax(2, 1), 'frequency (kHz)')
 ylabel(ax(2, 1), 'amplitude (a.u.)');
-title(ax(2, 1), 'buzzing, spectra')
+% title(ax(2, 1), 'buzzing, spectra')
 legend(ax(2, 1), {'ground truth', 'bin-transformed g.t.' 'subject #1', 'subject #2', 'subject #3'})
 
 
@@ -143,7 +143,7 @@ for ii = 1:n_traces
 end
 xlabel(ax(2, 2), 'frequency (kHz)')
 ylabel(ax(2, 2), 'amplitude (a.u.)');
-title(ax(2, 2), 'roaring, spectra')
+% title(ax(2, 2), 'roaring, spectra')
 legend(ax(2, 2), {'ground truth', 'bin-transformed g.t.' 'subject #1', 'subject #2', 'subject #3'})
 
 

### 2022-12-17 code/utils/parse_config.m
Add BrimijoinGaussianSmoothed

@@ -60,7 +60,8 @@ function varargout = parse_config(config_file,legacy, verbose)
     %% Perform specific parsing of config options
     stimuli_types = {'Bernoulli', 'Brimijoin', 'GaussianNoise', 'GaussianNoiseNoBins', ...
                     'GaussianPrior', 'UniformNoise', 'UniformNoiseNoBins', 'UniformPrior', ...
-                    'PowerDistribution', 'UniformPriorWeightedSampling', 'BrimijoinGaussianSmoothed'};
+                    'PowerDistribution', 'UniformPriorWeightedSampling', 'BrimijoinGaussianSmoothed', ...
+		    'BrimijoinGaussianSmoothed'};
     stimuli_string = [stimuli_types(:), repmat({', '}, length(stimuli_types), 1)]';
     stimuli_string = [stimuli_string{:}];
     assert(any(strcmp(config.stimuli_type, stimuli_types)), ...

### 2022-12-21 code/utils/plot_violin.m
make new figures

@@ -1,110 +1,95 @@
-<<<<<<< HEAD
-function plot_violin(T, options)
-=======
 function [ax, data_container] = plot_violin(T, options)
->>>>>>> main
 
     arguments
         T table
         options.figure = []
-<<<<<<< HEAD
-        options.cs = true
-        options.lr = false
-        options.colormap = @colormaps.linspecer
-        options.baseline = false
-        options.synthetic = false
-        options.publish = false
-=======
         options.data_dir = '/home/alec/code/tinnitus-project/code/experiment/Data/data-paper'
         options.N = 100
         options.parallel = true
->>>>>>> main
+        options.data_container = {}
     end
 
     if isempty(options.figure)
         options.figure = new_figure();
     end
 
+    
     % Set current figure
     figure(options.figure);
-
-<<<<<<< HEAD
-    % Colormap for plotting
-    cmap = options.colormap();
-=======
+    
     % % Colormap for plotting
     % cmap = options.colormap();
->>>>>>> main
-
+    
     % How many different target signals are there?
     subplot_labels = unique(T.target_signal_name);
     assert(~isempty(subplot_labels), 'couldn''t find any data to plot')
- 
+    
+    % Whether to rerun the synthetic experiments or not
+    if isempty(options.data_container)
+        generate_results = true;
+        data_container = cell(length(subplot_labels), 1);
+    else
+        generate_results = false;
+        data_container = options.data_container;
+    end
+
     % Generate one subplot for each unique target signal
-<<<<<<< HEAD
-    for ii = length(subplot_labels):-1:1
-        ax(ii) = subplot(length(subplot_labels), 1, ii, 'Parent', options.figure);
-        hold on
-    end
-
-    for ii = 1:length(subplot_labels)
-        filtered_table = T(strcmp(T.target_signal_name), subplot_labels{ii});
-
-        ydata = [filtered_table.r_lr_bins_1; ...
-                filtered_table.r_cs_bins_1; ...
-                r_rand_lr; ...
-                r_rand_cs; ...
-                r_synth_lr; ...
-                r_synth_cs];
-        
-        xdata = [repmat({'Subj. LR'}, length(filtered_table.r_lr_bins_1), 1); ...
[…]

### 2022-12-21 paper/scripts/make_figures.m

@@ -17,12 +17,19 @@ summary(T2);
 
 %% Violin plots with buzzing and roaring 
 
-% [ax, data_container] = plot_violin(T2, 'N', 1000, 'parallel', false);
+if ~exist('data_container', 'var')
+    load('data_container.mat', 'data_container');
+end
+[ax, data_container] = plot_violin(T2, 'N', 1000, 'parallel', false, 'data_container', data_container);
 
-% figlib.pretty('FontSize', 36, 'PlotBuffer', 0.2, 'AxisBox', 'off', 'YMinorTicks', 'on');
-% axlib.equalize(ax(:), 'x', 'y');
-% % figlib.tight();
-% figlib.label('XOffset', -0.01, 'YOffset', 0.03, 'FontSize', 36);
+figlib.pretty('FontSize', 48, 'PlotBuffer', 0.2, 'AxisBox', 'off', 'YMinorTicks', 'on');
+axlib.equalize(ax(:), 'x', 'y');
+% figlib.tight();
+% figlib.label('XOffset', 0.15, 'YOffset', -0.25, 'FontSize', 48);
+for ii = 1:length(ax)
+    axes(ax(ii));
+    box off
+end
 
 %% Reconstructions
 
@@ -46,13 +53,7 @@ stimgen = stimgen.from_config(config);
 % this_binned_target_signal is the binned representation of the target signals
 this_binned_target_signal = stimgen.spect2binnedrepr(target_signal);
 
-% my_normalize = @(x) normalize(x, 'zscore', 'std');
-% This normalization scheme normalizes the vectors to a length of 1
-% since we cannot capture magnitude information in the reconstruction.
-% Do we need to center the vectors afterwards?
-my_normalize = @(x) normalize(normalize(x, 'norm'), 'center');
-% my_normalize = @(x) normalize(x, 'norm');
-
+my_normalize = @(x) normalize(x, 'zscore', 'std');
 
 % Generate a figure and axes
 fig2 = new_figure();
@@ -78,9 +79,9 @@ for ii = 1:n_traces
     p.Color(4) = 0.8;
 end
 xlabel(ax(1, 1), 'bins');
-ylabel(ax(1, 1), 'amplitude (a.u.)');
[…]

### 2022-12-21 code/utils/+subaxis/subaxis.m
162 remake figures 2 and 3 (#168)
* rebuild

* make new figures

@@ -1,0 +1,89 @@
+function h=subaxis(varargin)
+%SUBAXIS Create axes in tiled positions. (just like subplot)
+%   Usage:
+%      h=subaxis(rows,cols,cellno[,settings])
+%      h=subaxis(rows,cols,cellx,celly[,settings])
+%      h=subaxis(rows,cols,cellx,celly,spanx,spany[,settings])
+%
+% SETTINGS: Spacing,SpacingHoriz,SpacingVert
+%           Padding,PaddingRight,PaddingLeft,PaddingTop,PaddingBottom
+%           Margin,MarginRight,MarginLeft,MarginTop,MarginBottom
+%           Holdaxis
+%
+%           all units are relative (i.e. from 0 to 1)
+%
+%           Abbreviations of parameters can be used.. (Eg MR instead of MarginRight)
+%           (holdaxis means that it wont delete any axes below.)
+%
+%
+% Example:
+%
+%   >> subaxis(2,1,1,'SpacingVert',0,'MR',0); 
+%   >> imagesc(magic(3))
+%   >> subaxis(2,'p',.02);
+%   >> imagesc(magic(4))
+%
+% 2001-2014 / Aslak Grinsted  (Feel free to modify this code.)
+f=gcf;
+UserDataArgsOK=0;
+Args=get(f,'UserData');
+if isstruct(Args) 
+    UserDataArgsOK=isfield(Args,'SpacingHorizontal')&isfield(Args,'Holdaxis')&isfield(Args,'rows')&isfield(Args,'cols');
+end
+OKToStoreArgs=isempty(Args)|UserDataArgsOK;
+if isempty(Args)&&(~UserDataArgsOK)
+    Args=struct('Holdaxis',0, ...
+        'SpacingVertical',0.05,'SpacingHorizontal',0.05, ...
+        'PaddingLeft',0,'PaddingRight',0,'PaddingTop',0,'PaddingBottom',0, ...
+        'MarginLeft',.1,'MarginRight',.1,'MarginTop',.1,'MarginBottom',.1, ...
+        'rows',[],'cols',[]); 
+end
+Args=subaxis.parseArgs(varargin,Args,{'Holdaxis'},{'Spacing' {'sh','sv'}; 'Padding' {'pl','pr','pt','pb'}; 'Margin' {'ml','mr','mt','mb'}});
+if (length(Args.NumericArguments)>2)
+    Args.rows=Args.NumericArguments{1};
[…]

### 2022-12-22 code/utils/plot_violin.m
Fix figures

@@ -51,6 +51,7 @@ function [ax, data_container] = plot_violin(T, options)
     % Plot the 1 to m-1 subplots
     % categories = {'subject', 'synthetic', 'random'};
     categories = {{'Random'; 'Subject'}, {'Human'; 'Subject'}, {'Ideal'; 'Subject'}};
+    order = [3, 1, 2]; %[1, 2, 3];
     counter = 0;
 
     for ii = 1:(m-1)
@@ -82,7 +83,7 @@ function [ax, data_container] = plot_violin(T, options)
             counter = counter + 1;
             % ax(ii, qq) = subplot(m, n, counter);
             axes(ax(sub2ind([m, n], qq, ii)));
-            violinplot(data_to_plot{qq}, {''}, 'ViolinAlpha', 0.3, 'ShowBox', true);
+            violinplot(data_to_plot{order(qq)}, {''}, 'ViolinAlpha', 0.3, 'ShowBox', true);
             hold on
             p = plot(xlim, [1, 1], '--k');
             p.Color(4) = 0.3;
@@ -108,7 +109,7 @@ function [ax, data_container] = plot_violin(T, options)
         axes(ax(sub2ind([m, n], qq, m)));
         data_to_plot = [];
         for ii = 1:length(data_container)
-            data_to_plot = [data_to_plot; data_container{ii}{qq}];
+            data_to_plot = [data_to_plot; data_container{ii}{order(qq)}];
         end
         violinplot(data_to_plot, {''}, 'ViolinAlpha', 0.3, 'ShowBox', true);
         hold on

### 2022-12-22 paper/scripts/make_figures.m

@@ -78,9 +78,10 @@ for ii = 1:n_traces
     p = plot(ax(1, 1), my_normalize(this_reconstruction), 'Color', cmap(ii, :));
     p.Color(4) = 0.8;
 end
-xlabel(ax(1, 1), 'bins');
+xlabel(ax(1, 1), 'Bin #');
 ylabel(ax(1, 1), {'Standardized'; 'Amplitude'});
 title(ax(1, 1), 'Buzzing')
+xticklabels(ax(1, 1), 1:size(this_binned_target_signal, 1));
 % legend(ax(1, 1), {'ground truth', 'subject #1', 'subject #2', 'subject #3'})
 
 %% Roaring, binned representation
@@ -96,6 +97,7 @@ for ii = 1:n_traces
 end
 xlabel(ax(1, 2), 'Bin #');
 title('Roaring')
+xticklabels(ax(1, 2), 1:size(this_binned_target_signal, 1));
 % legend(ax(1, 2), {'ground truth', 'subject #1', 'subject #2', 'subject #3'})
 
 %% Buzzing, full spectra
@@ -115,6 +117,7 @@ plot(ax(2, 1), 1e-3 * f(indices_to_plot, 1), my_normalize(unbinned_buzzing(indic
 for ii = 1:n_traces
     this_reconstruction = T3_buzzing.reconstructions_lr_1{ii};
     unbinned_this_reconstruction = stimgen.binnedrepr2spect(this_reconstruction);
+    unbinned_this_reconstruction(unbinned_this_reconstruction == 0) = NaN;
     p = plot(ax(2, 1), 1e-3 * f(indices_to_plot, 1), my_normalize(unbinned_this_reconstruction(indices_to_plot)), 'Color', cmap(ii, :));
     p.Color(4) = 0.8;
 end
@@ -140,6 +143,7 @@ plot(ax(2, 2), 1e-3 * f(indices_to_plot, 1), my_normalize(unbinned_roaring(indic
 for ii = 1:n_traces
     this_reconstruction = T3_roaring.reconstructions_lr_1{ii};
     unbinned_this_reconstruction = stimgen.binnedrepr2spect(this_reconstruction);
+    unbinned_this_reconstruction(unbinned_this_reconstruction == 0) = NaN;
     p = plot(ax(2, 2), 1e-3 * f(indices_to_plot, 1), my_normalize(unbinned_this_reconstruction(indices_to_plot)), 'Color', cmap(ii, :));
     p.Color(4) = 0.8;
 end

### 2023-01-05 paper/short/main_wc1255.tex
Cleanup

%% bare_jrnl.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[journal]{IEEEtran}
\usepackage[usenames]{color}
\usepackage{epsfig}
\usepackage{graphics}
\usepackage{caption}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{cite}
\usepackage{array}
\usepackage{pslatex} 
\usepackage{url}
\usepackage{lineno}
\usepackage{graphicx}  % Written by David Carlisle and Sebastian Rahtz
\usepackage{setspace}
\usepackage{tikz}
\usepackage{hhline}
\usepackage{mathtools}
\usepackage{caption}
\usepackage[letterpaper]{geometry}
\geometry{verbose,tmargin=0.7in,bmargin=0.7in,lmargin=0.65in,rmargin=0.65in}
\setlength{\headheight}{17pt}
\setlength{\headsep}{5pt}
 \newcommand{\flogo}{\includegraphics[height=18pt]{Logo.jpg}
 }
%\captionsetup{labelfont={up},font=small}
\captionsetup[figure]{name={Fig.},labelsep=period,font=small}
 \captionsetup[table]{name={TABLE},labelsep=period,font=small}
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". \eg, [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage{graphicx}
  % declare the path(s) where your graphic files are
  \graphicspath{{gfx}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  \DeclareGraphicsExtensions{.pdf,.jpeg,.png,.eps}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (\eg, "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
% Axel Sommerfeldt. This package may be useful when used in conjunction with 
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/pkg/endfloat
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% *** Custom ***
% \usepackage[utf8]{inputenc}
% \usepackage[backend=biber, style=ieee]{biblatex}
% \addbibresource{mybib.bib}
% \usepackage{csquotes}
\usepackage{soul}
\newcommand{\etal}{\textit{et al}.,\ }
\newcommand{\ie}{\textit{i}.\textit{e}.,\ }
\newcommand{\eg}{\textit{e}.\textit{g}.,\ }
\newcommand{\cf}{\textit{cf}.\ }
\usepackage{hyperref}
\usepackage{siunitx}
\sisetup{parse-numbers = false}

% correct bad hyphenation here
\hyphenation{com-press-ive sens-ing cor-rel-a-tion}
\pagenumbering{gobble}

% The paper headers
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
% \lhead{\flogo}
% \fancyhead[L,RO]{\hl{PAPER ID NUMBER}}
\rhead{\textcolor{violet}{\Large\textbf{Technology Letter         }} \thepage}
\pagestyle{fancyplain}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{\textcolor{violet}{Reverse Correlation Uncovers More Complete Tinnitus Spectra \vspace{0.25cm}}}

%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Alec Hoyland, Nelson V. Barnett, Benjamin W. Roop, Danae Alexandrou, Myah Caplan, Jacob Mills, Benjamin Parrell, Divya A. Chari, and Adam C. Lammert\textsuperscript{\textdagger{}}%
\thanks{This work was supported in part by the University of Massachusetts
Center for Clinical and Translation Science.}%
\thanks{A. Hoyland is with the Department of Biomedical Engineering (BME)
at Worcester Polytechnic Institute (WPI), Worcester, MA and with Clarifai, Inc., Wilmington, DE.
N.V. Barnett, M. Caplan, J. Mills and A.C. Lammert are also with BME at WPI.
B.W. Roop is formerly of the Neuroscience Program at WPI, now with  MIT Lincoln Laboratory, Lexington, MA.
D. Alexandrou is with the Stritch School of Medicine at Loyola University Chicago, Chicago, IL.
B. Parrell is with the Department of Communication Sciences and Disorders and the Waisman Center at University of Wisconsin, Madison, WI. D.A. Chari is with the
University of Massachusetts Chan Medical School, Worcester, MA
and the Massachusetts Eye and Ear Infirmary,
Boston, MA.
The authors declare no competing interests.}%
\thanks{\textsuperscript{\textdagger{}} Corresponding Author}}%

% note the % following the last \IEEEmembership and also \thanks - 
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
% 
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!
%
% a space would be appended to the last name and could cause every name on that
% line to be shifted left slightly. This is one of those "LaTeX things". For
% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
% "AB" then you have to do: "\textbf{A}\textbf{B}"
% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.

% The paper headers
%\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle\thispagestyle{fancy}

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
% TC:ignore
\begin{abstract}
  \textit{Goal:} This study validates a reverse correlation method for characterizing the sounds experienced by tinnitus patients with potential for characterizing a wider range of sounds than currently possible.
  \textit{Methods:} Ten normal-hearing subjects assessed the subjective similarity of random auditory stimuli and target tinnitus-like sounds (“buzzing” and “roaring”).
  Reconstructions of the targets were obtained by regressing subject responses on the stimuli, and were compared for accuracy to the frequency spectra of the targets using Pearson's $r$.
  \textit{Results:} Reconstruction accuracy was significantly higher than chance across subjects: buzzing ($M=0.53$, $SD=0.27$): $t(9)=5.766$, $p<0.001$; roaring ($M=0.57$, $SD=0.30$): $t(9)=5.76$, $p<0.001$.
  \textit{Conclusion:} Reverse correlation can accurately reconstruct non-tonal tinnitus-like sounds in normal-hearing subjects,
  indicating its potential for characterizing the sounds experienced by patients with non-tonal tinnitus.
% The purpose of this document is to illustrate how one should prepare manuscripts for submission to the IEEE Open Journal of Engineering in Medicine and Biology (OJEMB). Please notice that this is the template for TECHNOLOGY LETTERS. These are short manuscripts with primary focus on the development of new devices, methods, and technologies. The material must be organized in a main manuscript body and a section entitled Supplementary Materials. The main manuscript body should be limited to 1,000 words and the material should be organized in the following sections (in the order shown here): Introduction, Materials and Methods, Results, Discussion, Conclusions. Authors can include in the main manuscript body up to 3 display items (i.e. figures and tables). In addition, the main manuscript body should include an abstract and up to 20 references. The references are not considered in the 1,000-word count. The abstract should be organized in subsections as shown here (i.e., Goal, Methods, Results, Conclusions). An impact statement should be included. The impact statement should be a short paragraph of no more than 30 words. Additional material should be included in the Supplementary Materials section of the manuscript. The Supplementary Materials section should either be organized in sections as per the main manuscript body (using up to 4,000 words) or it should be used to provide readers with a set of up to 10 additional display items (i.e. figures and tables). \textit{Methods}: Use this document as a template if you are using Latex. Otherwise, use this document as an instruction set. \textit{Results}: Paper titles should be written in uppercase and lowercase letters as shown above. Do not cite references in the abstract. Do not delete the blank line immediately above the abstract; it sets the footnote at the bottom of this column. The abstract should not exceed 150 words. \textit{Conclusions}: Preparing carefully your manuscript will lead to enhanced readability.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
    reverse correlation, tinnitus, behavioral assay
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
\ifCLASSOPTIONpeerreview
\begin{center} \bfseries EDICS Category: 3-BBND \end{center}
\fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

%TC:ignore
\begin{minipage}[t]{0.9\columnwidth}
  \textbf{\textit{Impact Statement}\textemdash{}Characterization of tinnitus can inform tinnitus treatment by allowing for individualized sound therapies, leading to better outcomes for patients suffering from the cognitive and psychological effects of tinnitus.}\\
\\
\end{minipage}
%TC:endignore

\section{Introduction}
% INTRO PARAGRAPH 1/3
\IEEEPARstart{T}{INNITUS}\textemdash{}the perception of sound
in the absence of any corresponding external stimulus\textemdash{}affects up to 50 million people in the U.S. \cite{bhattPrevalenceSeverityExposures2016,nationalinstituteondeafnessandothercommunicationdisordersQuickStatisticsHearing},
a third of whom experience functional cognitive impairment and substantial reduction in quality of life
\cite{ahmedImpactTinnitusPerception2017,nondahlImpactTinnitusQuality2007,tegg-quinnImpactTinnitusCognition2016}.
Clinical guidelines for tinnitus management frequently involve targeted exposure to tinnitus-like external sounds, either as a form of habituation therapy (termed \textit{sound therapy}), or in the context of Cognitive Behavioral Therapy \cite{tunkelClinicalPracticeGuideline2014}.
Critically, sound therapy is shown to improve with knowledge of the patient's internal tinnitus experience \cite{davisNeuromonicsTinnitusTreatment2007,landgrebeMethodologicalAspectsClinical2012,nickelOutcomeResearchMusic2005,okamotoListeningTailormadeNotched2010,schaetteAcousticStimulationTreatments2010,steinInhibitioninducedPlasticityTinnitus2015,tassCounteractingTinnitusAcoustic2012,wangStateArtSound2020}.
However, existing strategies for characterizing tinnitus sounds, such as Pitch Matching (PM) methods, are best suited for patients who experience sounds resembling pure tones (\eg ringing).
This group may represent only between 20-50\% of all tinnitus patients \cite{turnerjrAuditoryDysfunctionTinnitus1990,henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017}, with others experiencing non-tonal (\eg buzzing, roaring) tinnitus sounds.
There is a pressing need for more robust tinnitus characterization methods \cite{henryTinnitusEpidemiologicPerspective2020,henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002,robertsResidualInhibitionFunctions2006}.

% INTRO PARAGRAPH 2/3
Tinnitus sounds are presumed to be both complex and heterogeneous
\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021,henryTinnitusEpidemiologicPerspective2020,meikleTinnitusArchiveArchive2004},
although little has been firmly established about the specific characteristics.
Therefore, we base our approach on \textit{reverse correlation} (RC),
an established behavioral method
\cite{ahumadaStimulusFeaturesSignal1971,gosselinSuperstitiousPerceptionsReveal2003,brimijoinInternalRepresentationVowel2013}
for probing internal representations of visual and auditory percepts that is unconstrained by prior knowledge about the percepts themselves.
RC asks subjects to render subjective judgments (\eg “does this sound like your tinnitus?”)
over random stimuli, 
from which unbiased estimates of the percepts can be produced.
RC is closely related to Wiener theory \cite{wienerNonlinearProblemsRandom1966},
which has also inspired ``white-noise'' approaches to system characterization in physiology
\cite{ringachReverseCorrelationNeurophysiology2004,marmarelisWhiteNoiseMethodSystem1978} and engineering more broadly
\cite{ljungMeasureLackFit1978}.

% INTRO PARAGRAPH 3/3
Here, we validate RC as a method for characterizing all component
frequencies of non-tonal tinnitus sounds
by estimating the full psychoacoustic tinnitus spectrum (PTS).
To that end, we asked normal-hearing participants to complete an augmented RC experiment, comparing random stimuli to a target tinnitus-like sound.
Target sounds were subsequently used as the basis for validating the quality of the estimated PTS.
Our results demonstrate, for the first time, that tinnitus-like sounds with complex spectra can be accurately estimated using RC. 
This discovery may open the door to developing a clinical assay for characterizing the full range of sounds experienced by tinnitus patients.

% document is a Latex  template for Technology Letters to be submitted to IEEE OJEMB \cite{ahumadaStimulusFeaturesSignal1971}. Submissions must have the sections listed in the following exactly in the order shown here: Introduction, Materials and Methods, Results, Discussion, Conclusions. Manuscripts to be submitted to IEEE OJEMB as a Science Letters must use a different template. For both types of manuscript, the authors can opt to add a Supplementary Materials section.

% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)

\section{Materials and Methods }
% To use this template, type over sections of the template or cut and paste from another document. Highlight a section that you want to designate with a certain style, then select the appropriate name on the style menu. The style will adjust your fonts and line spacing. Do not change the font sizes or line spacing to squeeze more text into a limited number of pages. Use italics for emphasis; do not underline. 
% IEEE will do the final formatting of your paper. However, you should format your manuscript for submission to IEEE OJEMB for review and also for preparing for preprint that will be e-published several days after you upload the final version of an accepted manuscript.

Software code used for the experiments and analysis was written in MATLAB and is freely available at \protect\url{https://github.com/alec-hoyland/tinnitus-reconstruction/}.

\subsection{Stimuli}

Stimuli were composed of $b=8$ Mel-spaced frequency bins,
which divide the frequency spectrum between $[100,~13,000]$
Hz into continuous segments of equal amplitude (\ie ``rectangular'' bins).
Reconstruction detail increases with $b$, but $b=8$ bins provides a good approximation to the chosen target sounds (see Fig. \ref{fig:spectra}).

For each stimulus, $[2,7]$ bins were randomly ``filled'' with power $0$ dB. ``Unfilled'' bins were assigned a power of $-100$ dB. 
Assigning random phase, the inverse Fourier transform of the spectrum yields a $500$-ms stimulus waveform.

\subsection{Target Sounds}

Two tinnitus-like target sounds (``buzzing'' and ``roaring'') from online examples maintained by the American Tinnitus Association
\cite{MeasuringTinnitusAmerican2022} were downloaded and truncated to $500$-ms in duration. These sounds were selected for the complexity and complementary nature of their frequency spectra.

\subsection{Experiment}

Trials followed an $A-X$ paradigm (Fig. \ref{fig:experimentdiagram}), where $n=10$ subjects with self-reported normal hearing listened to the same target sound ($A$) followed by a random stimulus ($X$) for each trial.
The task is designed to mimic the process by which a tinnitus patient might compare a random stimulus to their own tinnitus percept.

Subjects were told that some stimuli had the target sound embedded in them, and were instructed to respond ``yes'' to any such stimuli, and ``no'' otherwise.
Subjects performed trials in blocks of $100$, with breaks between blocks.
Subjects completed two ($2$) blocks of trials per given target, $A$.
The $400$ total trials took subjects 10-20 minutes to complete.

\begin{figure}[t]
  \centering
  \includegraphics[width=\linewidth]{experiment_overview.pdf}
  \caption{Diagram of the experimental protocol.
  Subjects listen to a series of random stimuli,
  each preceded by a target sound.
  Subjects compare the stimulus to the target, and respond either ``yes'' or ``no''
  depending on their perceived similarity.
  The recorded stimulus-response pairs are used to form an estimate of the target.}
  \label{fig:experimentdiagram}
\end{figure}

\subsection{Reconstruction}

A subject performing $n$ RC trials with $b$ frequency bins produces a stimulus matrix $\Psi \in \mathbb{R}^{b \times n}$
and a response vector $y \in \{1,-1\}^n$,
where $1$ corresponds to a ``yes'' response and $-1$ to a ``no.'' RC classically assumes the subject response model:

\begin{equation}
  y = sign(\Psi^\mathrm{T} x), 
\end{equation}

where $x \in \mathbb{R}^\mathrm{b}$ represents the subject's internal representation of interest (\eg their tinnitus percept).
This model can be inverted, yielding the following formula:

\begin{equation}
  \hat{x} = \frac{1}{n} \Psi y
  \label{eq:linreg}
\end{equation}

This formula is a restricted form of the Normal equation, under
the assumption that the stimulus dimensions are uncorrelated \cite{gosselinSuperstitiousPerceptionsReveal2003}.
Intuitively, $\hat{x}$ is the sum of all stimuli eliciting a ``yes'' response, after subtracting all stimuli eliciting a ``no.''

\subsection{Validation}

The $A-X$ paradigm allows for direct validation of the reconstructions $\hat{x}_{buzzing}$ and $\hat{x}_{roaring}$ against their corresponding target sounds.
To that end, we represent the power spectra of the target sounds as vectors $s_{buzzing} \in \mathbb{R}^\mathrm{b}$ and $s_{roaring} \in \mathbb{R}^\mathrm{b}$ using the same $b=8$ frequency bins used in stimulus generation.
The power in each bin is set as the mean power level of frequencies within that bin.
Pearson's $r$ between $s_{buzzing}$ and $s_{roaring}$ and their corresponding reconstructions ($\hat{x}_{buzzing}$ and $\hat{x}_{roaring}$) represents reconstruction accuracy.
One-sample t-tests were performed on the mean Fisher-transformed $r$ values across subjects to assess significant differences from zero.

\subsection{Synthetic and Random Subjects}

To establish bounds on human performance,
additional experiments were run \textit{in-silico} with two simulated subjects that
represent participants who always give either \textit{ideal} or \textit{random} responses.
Each experiment ran for $n=200$ trials and was repeated $1000$ times.

The \textit{ideal} subject gives responses following:

\begin{equation}
    y_i =
        \begin{cases}
            1 & \text{if } \Psi_i s \geq Q(0.5; \Psi s) \\
            -1 & \text{otherwise}
        \end{cases}
\end{equation}

% NB NOTE: What is s??
for $i \in 1, ..., n$, where $Q(x, y)$ is the quantile function for $x \in [0, 1]$ of the similarity calculation $\Psi s$, and
$\Psi_i$ is the $i^\mathrm{th}$ column of $\Psi$.
The ideal subject represents one who has precise knowledge of every stimulus and where the reconstruction algorithm mirrors \ref{eq:linreg}.

The \textit{random} subject chooses responses at random:

\begin{equation}
    r_i =
    \begin{cases}
        1 & \text{if  } X > 0.5 \\
        -1 & \text{otherwise}
    \end{cases}
\end{equation}

where $X \in [0, 1]$ is a uniform random variable.

\section{Results}

Figure \ref{fig:reconstructions} shows the distribution of Pearson's $r$ (\ie reconstruction accuracy) from human, ideal, and random subject responses in the buzzing and roaring experimental conditions.
Accuracies from human responses were generally higher than those from random subject responses,
with some accuracies approaching those from ideal subject responses.
Mean accuracy from the random subject responses was $0$ in all conditions,
while mean accuracy from human responses was significantly different from $0$ in all conditions: buzzing: $t(9) = 5.766$, $p < 0.001$; roaring: $t(9) = 5.76$, $p < 0.001$; combined: $t(19) = 7.542$, $p < 0.001$.
The buzzing results vary more than the roaring results. The buzzing ground truth spectrum contains significant high-frequency content,
suggesting that the task may be more difficult for subjects with minor high-frequency hearing loss.
Figure \ref{fig:spectra} plots example reconstructions from human responses with the best reconstruction accuracies overlaid on the target sound spectra,
showing that those reconstructions capture many of the salient features of the target.

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{reconstruction_violin_1.eps}
    \caption{Reconstruction accuracy for human subjects is significantly above baseline,
    but is not optimal. Reconstruction accuracies of random, human, and ideal subjects
    are shown as violin plots with box plots overlaid.
    The median is a white dot, the ordinate of the blue points are the Pearson's $r$ values.}
    \label{fig:reconstructions}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{reconstruction_spectra.eps}
    \caption{Reconstructions of the PTS capture many salient features of tinnitus spectra.
    On each set of axes, the black trace indicates the target,
    while colored traces plot exemplar reconstructions from human subjects' data.
    In the top row, the target and reconstructions are shown as
    standardized power levels within each frequency bin.
    In the bottom row, those standardized power levels are mapped from the $8$-dimensional bin domain
    to a $11025$-dimensional frequency domain.
    The unbinned power spectral density of the targets is also shown in gray.}
    \label{fig:spectra}
\end{figure}

\section{Conclusion}

% Promise
Our results show that RC can accurately reconstruct the frequency spectrum of complex, non-tonal tinnitus-like sounds.
This indicates that RC may also be useful for developing a clinical assay to characterize a wider variety of tinnitus percepts than currently possible.
RC is purely behavioral, requires no specialized equipment, and has marginal setup.
Moreover, subjects in the present study were able to complete the required number of trials within 20 minutes,
indicating that this procedure could be conducted in a single clinical visit.
Future work will focus on validating this approach in patients suffering from tinnitus.

% Limitations & Future Work
Reconstruction accuracies observed here are well below those provided by an ideal subject's responses,
which may be attributed to noisy human response characteristics universally observed in applications of RC.
This may be mitigated by optimizing the experimental protocol, stimulus generation, and reconstruction method.
For example, recent approaches to improving RC reconstruction methods have been shown to boost efficiency, noise robustness and overall accuracy \cite{roopCompressiveSensingApproach2021,comptonStimulusWhiteningImproves2022a},
and may also be applicable in the context of tinnitus.

% A conclusion section is required. Although a conclusion may review the main points of the paper, do not replicate the abstract as the conclusion. A conclusion might elaborate on the major findings and significance of the work or suggest applications and extensions. Do not exceed 300 words for the conclusion section.\\
% \\
% \textsc{Supplementary Materials}
% \par Supplementary materials are encouraged. Please use the Supplementary Materials template. If you have Supplementary Materials, please use this section to direct readers to the Supplementary Materials and give them a brief overview of what they can expect to find in the Supplementary Materials. \\
% \\
% \\
% \textsc{REFERENCES AND FOOTNOTES}

% \subsection{References}

% See the end of this document for formats and examples of common references. For a complete discussion of references and their formats, see “The IEEE Style Manual,” available as a PDF link off the  \underline{\textit{Author Digital Toolbox}} main page.

% \subsection{Footnotes}
% Number footnotes separately in superscripts\footnote{It is recommended that footnotes be avoided (except for the unnumbered footnote with the receipt date on the first page). Instead, try to integrate the footnote information into the text.}.  Place the actual footnote at the bottom of the column in which it is cited; do not put footnotes in the reference list (endnotes). Use letters for table footnotes (see Table I).

% \section{Submitting Your Paper for Review}

% {
% 	\subsection{Uploading the Document}
% 	All submissions must be uploaded via ScholarOne Manuscripts. Include full mailing addresses and e-mail addresses of all authors when uploading a manuscript. In addition, designate one author as the “corresponding author.” This is the author to whom proofs of the paper will be sent. Proofs are sent to the corresponding author only.

% 	\subsection{Review Stage Using ScholarOne$^{\tiny\textregistered}$ Manuscripts}
% 	Contributions to IEEE OJEMB must be submitted electronically on IEEE’s on-line manuscript submission and peer-review system, ScholarOne$^{\tiny\textregistered}$ Manuscripts at \textit{http://mc.manuscriptcentral.com/embs-ieee}. First check if you have an existing account. If there is none, please create a new account. After logging in, go to your Author Center and click “Submit First Draft of a New Manuscript.” 
% 	There are various steps to the submission process; you must complete all steps for a complete submission. At the end of each step you must click “Save and Continue”; just uploading the paper is not sufficient. After the last step, you should see a confirmation that the submission is complete. You should also receive an e-mail confirmation. For inquiries regarding the submission of your paper on ScholarOne Manuscripts, please contact oprs-support@ieee.org or call +1 732 465 5861.

% 	\subsection{Final Stage Using ScholarOne Manuscripts}
% 	Upon acceptance, you will receive an email with specific instructions regarding the submission of your final files.  To avoid any delays in publication, please be sure to follow these instructions.  Final submissions should include source files of your accepted manuscript, high quality graphic files, and a formatted pdf file.  If you have any questions regarding the final submission process, please contact the administrative contact for the journal. 
% }

% \section{Editorial Policy}
% {
% 	Do not publish “preliminary” data or results. The submitting author is responsible for obtaining agreement of all coauthors and any consent required from sponsors before submitting a paper. IEEE OJEMB strongly discourages courtesy authorship. It is the obligation of the authors to cite relevant prior work. IEEE OJEMB expects the main source of references be archival journal articles or books or thesis. Conference proceeding papers should be minimized since many are not undergoing rigorous peer reviews. 
% 	At least two reviews are required for every paper submitted. Indecipherable English is a valid reason for rejection. There is a service available that will help you improve your English for a fee, and the link to that service can be found at \textit{http://www.ieee.org/web/publications/authors/transjnl/ index.html}.

% }

% \section{Publication Principles}
% {
% 	The two types of contents of that are published are; 1) peer-reviewed and 2) archival. IEEE OJEMB publishes scholarly articles of archival value as well as tutorial expositions and critical reviews of classical subjects and topics of current interest. 
% 	Authors should consider the following points:
% 	\begin{enumerate}
% 		\item Technical papers submitted for publication must advance the state of knowledge and must cite relevant prior work. 
% 		\item The length of a submitted paper should be commensurate with the importance, or appropriate to the complexity, of the work. 
% 		\item Authors must convince both peer reviewers and the editors of the scientific and technical merit of a paper; the standards of proof are higher when extraordinary or unexpected results are reported. 
% 		\item Because replication is required for scientific progress, papers submitted for publication must provide sufficient information to allow readers to perform similar experiments or calculations and use the reported results. Although not everything need be disclosed, a paper must contain new, useable, and fully described information. For example, a specimen’s chemical composition need not be reported if the main purpose of a paper is to introduce a new measurement technique. Authors should expect to be challenged by reviewers if the results are not supported by adequate data and critical details.
% 		\item Papers that describe ongoing work or announce the latest technical achievement, which are suitable for presentation at a professional conference, may not be appropriate for publication.
% 	\end{enumerate}

% }

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,mybib}
% \printbibliography

% \begin{thebibliography}{1}
% 	%\textit{Basic Format for Books:}\\
% 	\bibitem{BasicBook} \textbf{Basic Format for Books:} J. K. Author, Title of chapter in the book, in \textit{Title of His Published Book}, xth ed. City of Publisher, Country if not USA: Abbrev. of Publisher, year, ch. x, sec. x, pp. xxx–xxx.

% 	\bibitem{ExampleBook1} \textit{Example Book 1:} G. O. Young, “Synthetic structure of industrial plastics”, in \textit{Plastics},  2nd  ed.,  vol.  3,  J.  Peters,  Ed.  New  York: McGraw-Hill, 1964, pp. 15–64.

% 	\bibitem{ExampleBook1} \textit{Example Book 2:} W.-K. Chen, \textit{Linear Networks and Systems}. Belmont, CA: Wadsworth, 1993, pp. 123–135.\\

% 	\bibitem{BasicPeriodical} \textbf{Basic Format for Periodicals:} J. K. Author, “Name of paper”, \textit{Abbrev. Title of Periodical},  vol. x, no. x, pp. xxx-xxx, Abbrev. Month, year.

% 	\bibitem{ExamplePeriodical1} \textit{Example Periodical 1:} J. U. Duncombe, “Infrared navigation—Part I: An assessment of feasibility”, \textit{IEEE Trans. Electron Devices}, vol. ED-11, no. 1, pp. 34–39, Jan. 1959.

% 	\bibitem{ExamplePeriodical2} \textit{Example Periodical 2:} E. P. Wigner, “Theory of traveling-wave optical laser”, \textit{Phys. Rev.}, vol. 134, pp. A635–A646, Dec. 1965.

% 	\bibitem{ExamplePeriodical3} \textit{Example Periodical 3:} E. H. Miller et al., “A note on reflector arrays”,\textit{ IEEE Trans. Antennas Propagat.}, to be published.\\

% 	\bibitem{BasicHandbook} \textbf{Basic Format for Handbooks:} \textit{Name of Manual/Handbook}, x ed., Abbrev. Name of Co., City of Co., Abbrev. State, year, pp. xxx-xxx.

% 	\bibitem{ExampleHandbook1} \textit{Example Handbook 1:} \textit{Transmission Systems for Communications}, 3rd ed., Western Electric Co., Winston-Salem, NC, 1985, pp. 44–60.

% 	\bibitem{ExampleHandbook2} \textit{Example Handbook 2:} \textit{Motorola Semiconductor Data Manual}, Motorola Semiconductor Products Inc., Phoenix, AZ, 1989.\\

% 	\bibitem{BasicBookOnline} \textbf{Basic Format for Books (when available online):} Author. (year, month day). \textit{Title}. (edition) [Type of medium]. volume (issue). Available: site/path/file

% 	\bibitem{ExampleBookOnline} \textit{Example Book Available Online 1:} J. Jones. (1991, May 10). \textit{Networks}. (2nd ed.) [Online]. Available: http://www.atm.com\\

% 	\bibitem{BasicJournalOnline} \textbf{Basic Format for Journals (when available online):} Author. (year, month). Title. \textit{Journal}. [Type of medium]. volume (issue), pages. Available: site/path/file

% 	\bibitem{ExampleJournalOnline} \textit{Example Journal Available Online 1:} R. J. Vidmar. (1992,  Aug.).  On  the  use  of  atmospheric plasmas as electromagnetic reflectors. \textit{IEEE Trans. Plasma Sci.} [Online]. 21(3), pp. 876–880. Available: http://www.halcyon.com/pub/journals/21ps03-vidmar\\

% 	\bibitem{BasicConferenceOnline} \textbf{Basic Format for Papers Presented at Conferences(when available online):} Author. (year, month). Title. Presented at Conference title. [Type of Medium]. Available: site/path/file

% 	\bibitem{ExampleConferenceOnline} \textit{Example Conference Paper Available Online 1:} PROCESS  Corp.,  MA.  Intranets:  Internet  technologies deployed behind the firewall for corporate productivity. Presented at 
% 	INET96 Annual Meeting. [Online]. Available:  http://home.process.com/Intranets/wp2.htp\\

% 	\bibitem{BasicReportsOnline} \textbf{Basic Format for Reports and Handbooks (when available online):} Author.   (year,   month).   Title. Company . City, State or Country. [Type of Medium]. Available: site/path/file

% 	\bibitem{ExampleReportOnline} \textit{Example Report Available Online 1:}  S.L.Talleen. (1996, Apr.). The Intranet  Architecture:  Managing  information  in  the  new paradigm. Amdahl Corp., CA. [Online]. Available: http://www.amdahl.com/doc/products/bsg/intra/infra/html\\

% 	 \textbf{Basic Format for Computer Programs and Electronic Documents (when available online):} ISO recommends that capitalization follow the accepted practice for the language or script in which the information is given.

% 	\bibitem{ExampleProgramOnline}\textit{Example Program Available Online 1:} A. Harriman. (1993, June). Compendium of genealogical software. \textit{Humanist}. [Online]. Available e-mail: HUMANIST@NYVM.ORG Message: get GENEALOGY REPORT\\

% 	\bibitem{BasicPatentsOnline} \textbf{Basic Format for Patents (when available online):} Name of the invention, by inventor’s name. (year, month day). \textit{Patent Number} [Type of medium]. Available: site/path/file\\

% 	\bibitem{ExamplePatentOnline}\text{Example Patent Available Online 1:} Musical toothbrush with adjustable neck and mirror, by L.M.R. Brooks. (1992, May 19). \textit{Patent D326189} [Online]. Available: NEXIS Library: LEXPAT File: DESIGN

% \end{thebibliography}

% that's all folks
\end{document}

### 2023-01-05 paper/short/main_wc995.tex
Cleanup

--- 2023-01-05 paper/short/main_wc1255.tex
@@
 \cite{ahmedImpactTinnitusPerception2017,nondahlImpactTinnitusQuality2007,tegg-quinnImpactTinnitusCognition2016}.
-Clinical guidelines for tinnitus management frequently involve targeted exposure to tinnitus-like external sounds, either as a form of habituation therapy (termed \textit{sound therapy}), or in the context of Cognitive Behavioral Therapy \cite{tunkelClinicalPracticeGuideline2014}.
+Clinical guidelines for tinnitus management frequently involve targeted exposure to tinnitus-like sounds, either as a form of habituation therapy (termed \textit{sound therapy}), or using Cognitive Behavioral Therapy \cite{tunkelClinicalPracticeGuideline2014}.
 Critically, sound therapy is shown to improve with knowledge of the patient's internal tinnitus experience \cite{davisNeuromonicsTinnitusTreatment2007,landgrebeMethodologicalAspectsClinical2012,nickelOutcomeResearchMusic2005,okamotoListeningTailormadeNotched2010,schaetteAcousticStimulationTreatments2010,steinInhibitioninducedPlasticityTinnitus2015,tassCounteractingTinnitusAcoustic2012,wangStateArtSound2020}.
-However, existing strategies for characterizing tinnitus sounds, such as Pitch Matching (PM) methods, are best suited for patients who experience sounds resembling pure tones (\eg ringing).
-This group may represent only between 20-50\% of all tinnitus patients \cite{turnerjrAuditoryDysfunctionTinnitus1990,henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017}, with others experiencing non-tonal (\eg buzzing, roaring) tinnitus sounds.
-There is a pressing need for more robust tinnitus characterization methods \cite{henryTinnitusEpidemiologicPerspective2020,henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002,robertsResidualInhibitionFunctions2006}.
+However, existing strategies for characterizing tinnitus sounds, such as Pitch Matching (PM) methods, are best suited for patients whose tinnitus resembles pure tones (\eg ringing), which may represent only $20-50\%$ of patients \cite{turnerjrAuditoryDysfunctionTinnitus1990,henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017}.
+There is a pressing need for more robust characterization methods \cite{henryTinnitusEpidemiologicPerspective2020,henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002,robertsResidualInhibitionFunctions2006}.
 
 % INTRO PARAGRAPH 2/3
-Tinnitus sounds are presumed to be both complex and heterogeneous
+Tinnitus sounds are presumed to be complex and heterogeneous
 \cite{vajsakovicPrinciplesMethodsPsychoacoustic2021,henryTinnitusEpidemiologicPerspective2020,meikleTinnitusArchiveArchive2004},
-although little has been firmly established about the specific characteristics.
+although few specifics have been firmly established.
 Therefore, we base our approach on \textit{reverse correlation} (RC),
@@
 \cite{ahumadaStimulusFeaturesSignal1971,gosselinSuperstitiousPerceptionsReveal2003,brimijoinInternalRepresentationVowel2013}
-for probing internal representations of visual and auditory percepts that is unconstrained by prior knowledge about the percepts themselves.
-RC asks subjects to render subjective judgments (\eg “does this sound like your tinnitus?”)
-over random stimuli, 
+for probing internal representations of visual and auditory percepts, unconstrained by prior knowledge.
+RC asks subjects to render subjective judgments over random stimuli, 
 from which unbiased estimates of the percepts can be produced.
 RC is closely related to Wiener theory \cite{wienerNonlinearProblemsRandom1966},
-which has also inspired ``white-noise'' approaches to system characterization in physiology
-\cite{ringachReverseCorrelationNeurophysiology2004,marmarelisWhiteNoiseMethodSystem1978} and engineering more broadly
-\cite{ljungMeasureLackFit1978}.
+which has inspired ``white-noise'' approaches to system characterization in physiology
+\cite{ringachReverseCorrelationNeurophysiology2004,marmarelisWhiteNoiseMethodSystem1978} and engineering \cite{ljungMeasureLackFit1978}.
 
@@
 by estimating the full psychoacoustic tinnitus spectrum (PTS).
-To that end, we asked normal-hearing participants to complete an augmented RC experiment, comparing random stimuli to a target tinnitus-like sound.
-Target sounds were subsequently used as the basis for validating the quality of the estimated PTS.
+To that end, we asked normal-hearing participants to complete an augmented RC experiment, comparing random stimuli to a target sound.
+The estimated PTS were subsequently validated against the targets.
 Our results demonstrate, for the first time, that tinnitus-like sounds with complex spectra can be accurately estimated using RC.
-This discovery may open the door to developing a clinical assay for characterizing the full range of sounds experienced by tinnitus patients.
 
@@
 
-\section{Materials and Methods }
+\section{Materials and Methods}
 % To use this template, type over sections of the template or cut and paste from another document.
@@
 
-Software code used for the experiments and analysis was written in MATLAB and is freely available at \protect\url{https://github.com/alec-hoyland/tinnitus-reconstruction/}.
+% Software for the experiments and analysis was written in MATLAB.\footnote{Code is freely available at \protect\url{https://github.com/alec-hoyland/tinnitus-reconstruction/}}
 
@@
 Hz into continuous segments of equal amplitude (\ie ``rectangular'' bins).
-Reconstruction detail increases with $b$, but $b=8$ bins provides a good approximation to the chosen target sounds (see Fig. \ref{fig:spectra}).
+Reconstruction detail increases with $b$, but $b=8$ provides a good approximation to the chosen target sounds (see Fig. \ref{fig:spectra}).
 
 For each stimulus, $[2,7]$ bins were randomly ``filled'' with power $0$ dB. ``Unfilled'' bins were assigned a power of $-100$ dB. 
-Assigning random phase, the inverse Fourier transform of the spectrum yields a $500$-ms stimulus waveform.
+Assigning random phase, the inverse Fourier transform of the spectrum yields a $500$ ms stimulus waveform.\footnote{Software for the experiments and analysis was written in MATLAB and is freely available at \protect\url{https://github.com/alec-hoyland/tinnitus-reconstruction/}}
 
@@
 
-Two tinnitus-like target sounds (``buzzing'' and ``roaring'') from online examples maintained by the American Tinnitus Association
-\cite{MeasuringTinnitusAmerican2022} were downloaded and truncated to $500$-ms in duration. These sounds were selected for the complexity and complementary nature of their frequency spectra.
+Two spectrally complex and complimentary target sounds (``buzzing'' and ``roaring'') were downloaded from the American Tinnitus Association \cite{MeasuringTinnitusAmerican2022} and truncated to $500$ ms in duration.
 
@@
 
-Trials followed an $A-X$ paradigm (Fig.
-\ref{fig:experimentdiagram}), where $n=10$ subjects with self-reported normal hearing listened to the same target sound ($A$) followed by a random stimulus ($X$) for each trial.
-The task is designed to mimic the process by which a tinnitus patient might compare a random stimulus to their own tinnitus percept.
+10 normal-hearing subjects listened to the same target sound followed by a random stimulus for each trial (Fig. \ref{fig:experimentdiagram}).
+The task is designed to mimic how a tinnitus patient might compare random stimuli to their tinnitus.
 
-Subjects were told that some stimuli had the target sound embedded in them, and were instructed to respond ``yes'' to any such stimuli, and ``no'' otherwise.
-Subjects performed trials in blocks of $100$, with breaks between blocks.
-Subjects completed two ($2$) blocks of trials per given target, $A$.
-The $400$ total trials took subjects 10-20 minutes to complete.
+Subjects were instructed to respond ``yes'' to any stimuli that sounded similar to the target, and ``no'' otherwise.
+Subjects completed $200$ trials for both target sounds within $10-20$ minutes.
 
@@
 
-where $x \in \mathbb{R}^\mathrm{b}$ represents the subject's internal representation of interest (\eg their tinnitus percept).
+where $x \in \mathbb{R}^\mathrm{b}$ is the subject's internal representation of interest (\eg their tinnitus percept).
 This model can be inverted, yielding the following formula:
@@
 
-The $A-X$ paradigm allows for direct validation of the reconstructions $\hat{x}_{buzzing}$ and $\hat{x}_{roaring}$ against their corresponding target sounds.
-To that end, we represent the power spectra of the target sounds as vectors $s_{buzzing} \in \mathbb{R}^\mathrm{b}$ and $s_{roaring} \in \mathbb{R}^\mathrm{b}$ using the same $b=8$ frequency bins used in stimulus generation.
-The power in each bin is set as the mean power level of frequencies within that bin.
-Pearson's $r$ between $s_{buzzing}$ and $s_{roaring}$ and their corresponding reconstructions ($\hat{x}_{buzzing}$ and $\hat{x}_{roaring}$) represents reconstruction accuracy.
-One-sample t-tests were performed on the mean Fisher-transformed $r$ values across subjects to assess significant differences from zero.
+The experimental paradigm allows for direct validation of the reconstructions $\hat{x}_{buzzing}$ and $\hat{x}_{roaring}$.
+We represent the spectra of the target sounds as vectors $s_{buzzing} \in \mathbb{R}^\mathrm{b}$ and $s_{roaring} \in \mathbb{R}^\mathrm{b}$ using the same frequency bins as in stimulus generation with power equal to the mean power of frequencies within that bin.
+Pearson's $r$ between $s_{buzzing}$ and $s_{roaring}$ and their corresponding reconstructions represents reconstruction accuracy.
+One-sample t-tests were performed on the mean Fisher-transformed Pearson's $r$ values across subjects to assess significant differences from zero.
 
-\subsection{Synthetic and Random Subjects}
+\subsection{Synthetic Subjects}
 
 To establish bounds on human performance,
-additional experiments were run \textit{in-silico} with two simulated subjects that
-represent participants who always give either \textit{ideal} or \textit{random} responses.
+additional experiments were run with two simulated subjects who give either \textit{ideal} or \textit{random} responses.
 Each experiment ran for $n=200$ trials and was repeated $1000$ times.
@@
 $\Psi_i$ is the $i^\mathrm{th}$ column of $\Psi$.
-The ideal subject represents one who has precise knowledge of every stimulus and where the reconstruction algorithm mirrors \ref{eq:linreg}.
+The ideal subject has precise knowledge of every stimulus and responds mirroring Eq. \ref{eq:linreg}.
 
-The \textit{random} subject chooses responses at random:
-
-\begin{equation}
-    r_i =
-    \begin{cases}
-        1 & \text{if  } X > 0.5 \\
-        -1 & \text{otherwise}
-    \end{cases}
-\end{equation}
-
-where $X \in [0, 1]$ is a uniform random variable.
+The \textit{random} subject responds with uniformly random probability.
 
@@
 
-Figure \ref{fig:reconstructions} shows the distribution of Pearson's $r$ (\ie reconstruction accuracy) from human, ideal, and random subject responses in the buzzing and roaring experimental conditions.
-Accuracies from human responses were generally higher than those from random subject responses,
-with some accuracies approaching those from ideal subject responses.
-Mean accuracy from the random subject responses was $0$ in all conditions,
-while mean accuracy from human responses was significantly different from $0$ in all conditions: buzzing: $t(9) = 5.766$, $p < 0.001$; roaring: $t(9) = 5.76$, $p < 0.001$; combined: $t(19) = 7.542$, $p < 0.001$.
-The buzzing results vary more than the roaring results. The buzzing ground truth spectrum contains significant high-frequency content,
-suggesting that the task may be more difficult for subjects with minor high-frequency hearing loss.
-Figure \ref{fig:spectra} plots example reconstructions from human responses with the best reconstruction accuracies overlaid on the target sound spectra,
-showing that those reconstructions capture many of the salient features of the target.
+Figure \ref{fig:reconstructions} shows the distribution of Pearson's $r$ for human, ideal, and random subject responses.
+Human accuracies were generally higher than random,
+with some approaching ideal.
+Mean random accuracy was $0$ in all conditions,
+while mean human accuracy was significantly different from $0$ in all conditions: buzzing: $t(9) = 5.766$, $p < 0.001$; roaring: $t(9) = 5.76$, $p < 0.001$; combined: $t(19) = 7.542$, $p < 0.001$.
+Greater variability in buzzing results may stem from the target spectrum containing significant high-frequency content, increasing the difficulty for subjects with minor high-frequency hearing loss.
+Figure \ref{fig:spectra} plots the most accurate human reconstructions over the target sound spectra.
 
@@
     \centering
-    \includegraphics[width=\linewidth]{reconstruction_violin_1.eps}
-    \caption{Reconstruction accuracy for human subjects is significantly above baseline,
-    but is not optimal. Reconstruction accuracies of random, human, and ideal subjects
+    \includegraphics[width=\linewidth]{gfx/reconstruction_violin_cropped.pdf}
+    \caption{Human reconstruction accuracy is significantly above baseline,
+    but is not optimal. Random, human, and ideal reconstruction accuracies
     are shown as violin plots with box plots overlaid.
@@
     \centering
-    \includegraphics[width=\linewidth]{reconstruction_spectra.eps}
+    \includegraphics[width=\linewidth]{gfx/reconstruction_spectra_cropped.pdf}
     \caption{Reconstructions of the PTS capture many salient features of tinnitus spectra.
-    On each set of axes, the black trace indicates the target,
-    while colored traces plot exemplar reconstructions from human subjects' data.
-    In the top row, the target and reconstructions are shown as
-    standardized power levels within each frequency bin.
-    In the bottom row, those standardized power levels are mapped from the $8$-dimensional bin domain
-    to a $11025$-dimensional frequency domain.
-    The unbinned power spectral density of the targets is also shown in gray.}
+    The black trace indicates the target,
+    while colored traces plot exemplar human reconstructions.
+    The top row shows standardized power levels within each frequency bin.
+    The bottom row maps the $8$-dimensional bin domain
+    to a $11025$-dimensional frequency domain with the unbinned power spectral density of the targets shown in gray.}
     \label{fig:spectra}
@@
 
-% Promise
-Our results show that RC can accurately reconstruct the frequency spectrum of complex, non-tonal tinnitus-like sounds.
+Reconstruction accuracies observed here are well below the simulated ideal,
+which may be attributed to noisy responses universally observed in applications of RC.
+This may be mitigated by optimizing the experimental protocol, stimulus generation, and reconstruction method.
+For example, recent approaches to improving RC reconstruction methods can boost efficiency, noise robustness and overall accuracy \cite{roopCompressiveSensingApproach2021,comptonStimulusWhiteningImproves2022a}.
+
+Nevertheless, our results show that RC can accurately reconstruct the frequency spectrum of complex, non-tonal tinnitus-like sounds.
 This indicates that RC may also be useful for developing a clinical assay to characterize a wider variety of tinnitus percepts than currently possible.
-RC is purely behavioral, requires no specialized equipment, and has marginal setup.
-Moreover, subjects in the present study were able to complete the required number of trials within 20 minutes,
+Additionally, subjects completed the required number of trials within 20 minutes,
 indicating that this procedure could be conducted in a single clinical visit.
 Future work will focus on validating this approach in patients suffering from tinnitus.
-
-% Limitations & Future Work
-Reconstruction accuracies observed here are well below those provided by an ideal subject's responses,
-which may be attributed to noisy human response characteristics universally observed in applications of RC.
-This may be mitigated by optimizing the experimental protocol, stimulus generation, and reconstruction method.
-For example, recent approaches to improving RC reconstruction methods have been shown to boost efficiency, noise robustness and overall accuracy \cite{roopCompressiveSensingApproach2021,comptonStimulusWhiteningImproves2022a},
-and may also be applicable in the context of tinnitus.
 

### 2023-01-05 paper/short/main_wc995.tex
Merge changes from ACL

@@
 \begin{abstract}
-  \textit{Goal:} This study validates a reverse correlation method for characterizing the sounds experienced by tinnitus patients with potential for characterizing a wider range of sounds than currently possible.
+  \textit{Goal:} This study validates an approach to characterizing the sounds experienced by tinnitus patients via reverse correlation, with potential for characterizing a wider range of sounds than currently possible.
   \textit{Methods:} Ten normal-hearing subjects assessed the subjective similarity of random auditory stimuli and target tinnitus-like sounds (“buzzing” and “roaring”).
@@
 \begin{minipage}[t]{0.9\columnwidth}
-  \textbf{\textit{Impact Statement}\textemdash{}Characterization of tinnitus can inform tinnitus treatment by allowing for individualized sound therapies, leading to better outcomes for patients suffering from the cognitive and psychological effects of tinnitus.}\\
+  \textbf{\textit{Impact Statement}\textemdash{}Characterization of tinnitus sounds can inform treatment by facilitating individualized sound therapies, leading to better outcomes for patients suffering from the cognitive and psychological effects of tinnitus.}\\
 \\
@@
 \cite{bhattPrevalenceSeverityExposures2016,nationalinstituteondeafnessandothercommunicationdisordersQuickStatisticsHearing},
-a third of whom experience functional cognitive impairment and substantial reduction in quality of life
+a third of whom experience functional cognitive impairment and diminished quality of life
 \cite{ahmedImpactTinnitusPerception2017,nondahlImpactTinnitusQuality2007,tegg-quinnImpactTinnitusCognition2016}.
-Clinical guidelines for tinnitus management frequently involve targeted exposure to tinnitus-like sounds, either as a form of habituation therapy (termed \textit{sound therapy}), or using Cognitive Behavioral Therapy \cite{tunkelClinicalPracticeGuideline2014}.
-Critically, sound therapy is shown to improve with knowledge of the patient's internal tinnitus experience \cite{davisNeuromonicsTinnitusTreatment2007,landgrebeMethodologicalAspectsClinical2012,nickelOutcomeResearchMusic2005,okamotoListeningTailormadeNotched2010,schaetteAcousticStimulationTreatments2010,steinInhibitioninducedPlasticityTinnitus2015,tassCounteractingTinnitusAcoustic2012,wangStateArtSound2020}.
-However, existing strategies for characterizing tinnitus sounds, such as Pitch Matching (PM) methods, are best suited for patients whose tinnitus resembles pure tones (\eg ringing), which may represent only $20-50\%$ of patients \cite{turnerjrAuditoryDysfunctionTinnitus1990,henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017}.
-There is a pressing need for more robust characterization methods \cite{henryTinnitusEpidemiologicPerspective2020,henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002,robertsResidualInhibitionFunctions2006}.
+Clinical guidelines for tinnitus management involve targeted exposure to tinnitus-like sounds, for habituation therapy (termed \textit{sound therapy}), or as part of Cognitive Behavioral Therapy \cite{tunkelClinicalPracticeGuideline2014}.
+Critically, sound therapy outcomes improve when closely informed by the patient's internal tinnitus experience \cite{davisNeuromonicsTinnitusTreatment2007,landgrebeMethodologicalAspectsClinical2012,nickelOutcomeResearchMusic2005,okamotoListeningTailormadeNotched2010,schaetteAcousticStimulationTreatments2010,steinInhibitioninducedPlasticityTinnitus2015,tassCounteractingTinnitusAcoustic2012,wangStateArtSound2020}.
+However, existing strategies for characterizing tinnitus sounds, such as Pitch Matching (PM), are best suited for patients whose tinnitus resembles pure tones (\eg ringing), which may represent only $20-50\%$ of patients \cite{turnerjrAuditoryDysfunctionTinnitus1990,henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017}.
+There is a need for methods to characterize nontonal (\eg buzzing, roaring) tinnitus \cite{henryTinnitusEpidemiologicPerspective2020,henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002,robertsResidualInhibitionFunctions2006}.
 
 % INTRO PARAGRAPH 2/3
-Tinnitus sounds are presumed to be complex and heterogeneous
+Nontonal tinnitus sounds are presumed to be complex and heterogeneous
 \cite{vajsakovicPrinciplesMethodsPsychoacoustic2021,henryTinnitusEpidemiologicPerspective2020,meikleTinnitusArchiveArchive2004},
-although few specifics have been firmly established.
+although few characteristics have been firmly established.
 Therefore, we base our approach on \textit{reverse correlation} (RC),
@@
 \cite{ahumadaStimulusFeaturesSignal1971,gosselinSuperstitiousPerceptionsReveal2003,brimijoinInternalRepresentationVowel2013}
-for probing internal representations of visual and auditory percepts, unconstrained by prior knowledge.
-RC asks subjects to render subjective judgments over random stimuli, 
-from which unbiased estimates of the percepts can be produced.
-RC is closely related to Wiener theory \cite{wienerNonlinearProblemsRandom1966},
+for estimating internal perceptual representations that is unconstrained by prior knowledge about the representations themselves.
+RC asks subjects to render subjective judgments over random stimuli, being closely related to Wiener theory \cite{wienerNonlinearProblemsRandom1966},
 which has inspired ``white-noise'' approaches to system characterization in physiology
@@
 % INTRO PARAGRAPH 3/3
-Here, we validate RC as a method for characterizing all component
-frequencies of non-tonal tinnitus sounds
-by estimating the full psychoacoustic tinnitus spectrum (PTS).
-To that end, we asked normal-hearing participants to complete an augmented RC experiment, comparing random stimuli to a target sound.
-The estimated PTS were subsequently validated against the targets.
+Here, we validate RC as a method for characterizing a more complete psychoacoustic tinnitus spectrum (PTS) for tinnitus sounds.
+To that end, normal-hearing participants completed an augmented RC experiment, comparing random stimuli to a target tinnitus-like sound.
+The estimated PTS was subsequently validated against the targets.
 Our results demonstrate, for the first time, that tinnitus-like sounds with complex spectra can be accurately estimated using RC.
@@
 which divide the frequency spectrum between $[100,~13,000]$
-Hz into continuous segments of equal amplitude (\ie ``rectangular'' bins).
+Hz into contiguous segments of equal amplitude (\ie ``rectangular'' bins).
 Reconstruction detail increases with $b$, but $b=8$ provides a good approximation to the chosen target sounds (see Fig. \ref{fig:spectra}).
 
-For each stimulus, $[2,7]$ bins were randomly ``filled'' with power $0$ dB. ``Unfilled'' bins were assigned a power of $-100$ dB. 
-Assigning random phase, the inverse Fourier transform of the spectrum yields a $500$ ms stimulus waveform.\footnote{Software for the experiments and analysis was written in MATLAB and is freely available at \protect\url{https://github.com/alec-hoyland/tinnitus-reconstruction/}}
+For each stimulus, $[2,7]$ bins were randomly ``filled'' with power $0$ dB. ``Unfilled'' bins were assigned $-100$ dB. All frequencies were assigned random phase.
+Inverse Fourier transform of the constructed spectrum yields a $500$ ms stimulus waveform.\footnote{Software for the experiments and analysis was written in MATLAB and is freely available at \protect\url{https://github.com/alec-hoyland/tinnitus-reconstruction/}}
 
@@
 
-Two spectrally complex and complimentary target sounds (``buzzing'' and ``roaring'') were downloaded from the American Tinnitus Association \cite{MeasuringTinnitusAmerican2022} and truncated to $500$ ms in duration.
+Two spectrally complex and complimentary target sounds (``buzzing'' and ``roaring'') were downloaded from the American Tinnitus Association \cite{MeasuringTinnitusAmerican2022} and truncated to $500$ ms in duration (Fig.
+\ref{fig:spectra}).
 
@@
 
-10 normal-hearing subjects listened to the same target sound followed by a random stimulus for each trial (Fig. \ref{fig:experimentdiagram}).
-The task is designed to mimic how a tinnitus patient might compare random stimuli to their tinnitus.
-
-Subjects were instructed to respond ``yes'' to any stimuli that sounded similar to the target, and ``no'' otherwise.
-Subjects completed $200$ trials for both target sounds within $10-20$ minutes.
+Ten ($n=10$) normal-hearing subjects listened to $A-X$ trials containing a target sound ($A$) followed by a stimulus ($X$).
+$X$ was randomly generated for each trial, while $A$ remained the same within a block of $100$ trials (Fig.
+\ref{fig:experimentdiagram}).
+Subjects completed two (2) blocks per target sound.
+Subjects were told that some stimuli had $A$ embedded in them, and were instructed to respond ``yes'' to such stimuli, otherwise ``no''.
+Subjects listened over earphones at a self-determined comfortable level.
+Procedures were approved by the UMass IRB.
 
@@
 
-A subject performing $n$ RC trials with $b$ frequency bins produces a stimulus matrix $\Psi \in \mathbb{R}^{b \times n}$
+A subject performing $p$ RC trials with $b$ frequency bins produces a stimulus matrix $\Psi \in \mathbb{R}^{p \times b}$
 and a response vector $y \in \{1,-1\}^n$,
@@
   y = sign(\Psi^\mathrm{T} x),
+  \label{eq:subjresp} 
 \end{equation}
 
-where $x \in \mathbb{R}^\mathrm{b}$ is the subject's internal representation of interest (\eg their tinnitus percept).
-This model can be inverted, yielding the following formula:
+where $x \in \mathbb{R}^\mathrm{b}$ is the subject's internal representation of interest (\eg of their tinnitus).
+Inverting this model yields:
 
@@
 \end{equation}
-
-This formula is a restricted form of the Normal equation, under
+which is a restricted form of the Normal equation under
 the assumption that the stimulus dimensions are uncorrelated \cite{gosselinSuperstitiousPerceptionsReveal2003}.
-Intuitively, $\hat{x}$ is the sum of all stimuli eliciting a ``yes'' response, after subtracting all stimuli eliciting a ``no.''
 
@@
 The experimental paradigm allows for direct validation of the reconstructions $\hat{x}_{buzzing}$ and $\hat{x}_{roaring}$.
-We represent the spectra of the target sounds as vectors $s_{buzzing} \in \mathbb{R}^\mathrm{b}$ and $s_{roaring} \in \mathbb{R}^\mathrm{b}$ using the same frequency bins as in stimulus generation with power equal to the mean power of frequencies within that bin.
-Pearson's $r$ between $s_{buzzing}$ and $s_{roaring}$ and their corresponding reconstructions represents reconstruction accuracy.
+We represent the spectra of the target sounds as vectors $s_{buzzing} \in \mathbb{R}^\mathrm{b}$ and $s_{roaring} \in \mathbb{R}^\mathrm{b}$ using the same frequency bins as the stimulus with power equal to the mean power at frequencies within that bin.
+Pearson's $r$ between $s_{buzzing}$ and $s_{roaring}$ and their corresponding reconstructions quantifies reconstruction accuracy.
 One-sample t-tests were performed on the mean Fisher-transformed Pearson's $r$ values across subjects to assess significant differences from zero.
@@
 additional experiments were run with two simulated subjects who give either \textit{ideal} or \textit{random} responses.
-Each experiment ran for $n=200$ trials and was repeated $1000$ times.
+Each experiment ran for $p=200$ trials and was repeated $1000$ times.
 
@@
 
-% NB NOTE: What is s??
-for $i \in 1, ..., n$, where $Q(x, y)$ is the quantile function for $x \in [0, 1]$ of the similarity calculation $\Psi s$, and
+% NB NOTE: What is s?? ACL: it is the target sound vector
+for $i \in 1, ..., p$, where $Q(x, y)$ is the quantile function for $x \in [0, 1]$ of the similarity calculation $\Psi s$, and
 $\Psi_i$ is the $i^\mathrm{th}$ column of $\Psi$.
-The ideal subject has precise knowledge of every stimulus and responds mirroring Eq. \ref{eq:linreg}.
-
-The \textit{random} subject responds with uniformly random probability.
+Thus, the ideal subject has precise knowledge of every stimulus and responds according to Eq.
+\ref{eq:subjresp}.
+The \textit{random} subject responds $y_i \in \{1,-1\}^n$ with uniform random probability, thus ignoring the stimulus entirely.
 
@@
 Human accuracies were generally higher than random,
-with some approaching ideal.
-Mean random accuracy was $0$ in all conditions,
-while mean human accuracy was significantly different from $0$ in all conditions: buzzing: $t(9) = 5.766$, $p < 0.001$; roaring: $t(9) = 5.76$, $p < 0.001$; combined: $t(19) = 7.542$, $p < 0.001$.
-Greater variability in buzzing results may stem from the target spectrum containing significant high-frequency content, increasing the difficulty for subjects with minor high-frequency hearing loss.
+with some approaching \textit{ideal}. 
+Mean human accuracy was significantly different from $0$ (i.e., mean \textit{random} accuracy) in all conditions: buzzing: $t(9) = 5.766$, $p < 0.001$; roaring: $t(9) = 5.76$, $p < 0.001$; combined: $t(19) = 7.542$, $p < 0.001$.
 Figure \ref{fig:spectra} plots the most accurate human reconstructions over the target sound spectra.
@@
 
-Reconstruction accuracies observed here are well below the simulated ideal,
-which may be attributed to noisy responses universally observed in applications of RC.
-This may be mitigated by optimizing the experimental protocol, stimulus generation, and reconstruction method.
+Our results show that RC can accurately reconstruct the PTS of complex, non-tonal, tinnitus-like sounds, capturing the most salient features of the target.
+Reconstruction accuracies observed here are below the simulated ideal, which may be attributed to noisy responses universally observed in applications of RC, and which may be mitigated by further optimizing the experimental protocol, stimulus generation, and reconstruction method.
 For example, recent approaches to improving RC reconstruction methods can boost efficiency, noise robustness and overall accuracy \cite{roopCompressiveSensingApproach2021,comptonStimulusWhiteningImproves2022a}.
-
-Nevertheless, our results show that RC can accurately reconstruct the frequency spectrum of complex, non-tonal tinnitus-like sounds.
-This indicates that RC may also be useful for developing a clinical assay to characterize a wider variety of tinnitus percepts than currently possible.
-Additionally, subjects completed the required number of trials within 20 minutes,
+Subjects completed the required number of trials within 10 minutes,
 indicating that this procedure could be conducted in a single clinical visit.
+RC may therefore be useful as the basis for a clinical assay to characterize a wider variety of tinnitus percepts than currently possible.
 Future work will focus on validating this approach in patients suffering from tinnitus.

### 2023-01-05 paper/short/main_wc995.tex
minor fixes
Wc995 acl (#176)
* Edit paper to under 1000 words, crop gfx

* Cleanup

* Cleanup

* Merge changes from ACL

* minor fixes

* Remove citations

Co-authored-by: Nelson Barnett <nelsonvbarnett@gmail.com>

@@
 \fancyhf{}
-% \lhead{\flogo}
-% \fancyhead[L,RO]{\hl{PAPER ID NUMBER}}
+\lhead{\flogo}
+\fancyhead[L,RO]{\hl{PAPER ID NUMBER}}
 \rhead{\textcolor{violet}{\Large\textbf{Technology Letter         }} \thepage}
@@
 N.V. Barnett, M. Caplan, J. Mills and A.C. Lammert are also with BME at WPI.
-B.W. Roop is formerly of the Neuroscience Program at WPI, now with  MIT Lincoln Laboratory, Lexington, MA.
+B.W. Roop is formerly of the Neuroscience Program at WPI.
 D. Alexandrou is with the Stritch School of Medicine at Loyola University Chicago, Chicago, IL.
@@
 \IEEEPARstart{T}{INNITUS}\textemdash{}the perception of sound
-in the absence of any corresponding external stimulus\textemdash{}affects up to 50 million people in the U.S.
-\cite{bhattPrevalenceSeverityExposures2016,nationalinstituteondeafnessandothercommunicationdisordersQuickStatisticsHearing},
+in the absence of any corresponding external stimulus\textemdash{}affects up to 50 million people in the U.S. \cite{bhattPrevalenceSeverityExposures2016},
 a third of whom experience functional cognitive impairment and diminished quality of life
-\cite{ahmedImpactTinnitusPerception2017,nondahlImpactTinnitusQuality2007,tegg-quinnImpactTinnitusCognition2016}.
+\cite{nondahlImpactTinnitusQuality2007,tegg-quinnImpactTinnitusCognition2016}.
 Clinical guidelines for tinnitus management involve targeted exposure to tinnitus-like sounds, for habituation therapy (termed \textit{sound therapy}), or as part of Cognitive Behavioral Therapy \cite{tunkelClinicalPracticeGuideline2014}.
-Critically, sound therapy outcomes improve when closely informed by the patient's internal tinnitus experience \cite{davisNeuromonicsTinnitusTreatment2007,landgrebeMethodologicalAspectsClinical2012,nickelOutcomeResearchMusic2005,okamotoListeningTailormadeNotched2010,schaetteAcousticStimulationTreatments2010,steinInhibitioninducedPlasticityTinnitus2015,tassCounteractingTinnitusAcoustic2012,wangStateArtSound2020}.
-However, existing strategies for characterizing tinnitus sounds, such as Pitch Matching (PM), are best suited for patients whose tinnitus resembles pure tones (\eg ringing), which may represent only $20-50\%$ of patients \cite{turnerjrAuditoryDysfunctionTinnitus1990,henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017}.
-There is a need for methods to characterize nontonal (\eg buzzing, roaring) tinnitus \cite{henryTinnitusEpidemiologicPerspective2020,henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002,robertsResidualInhibitionFunctions2006}.
+Critically, sound therapy outcomes improve when closely informed by the patient's internal tinnitus experience \cite{okamotoListeningTailormadeNotched2010,schaetteAcousticStimulationTreatments2010,steinInhibitioninducedPlasticityTinnitus2015}.
+However, existing strategies for characterizing tinnitus sounds, such as Pitch Matching (PM), are best suited for patients whose tinnitus resembles pure tones (\eg ringing), which may represent only $20-50\%$ of patients \cite{henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017}.
+There is a need for methods to characterize nontonal (\eg buzzing, roaring) tinnitus \cite{henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002}.
 
@@
 Nontonal tinnitus sounds are presumed to be complex and heterogeneous
-\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021,henryTinnitusEpidemiologicPerspective2020,meikleTinnitusArchiveArchive2004},
+\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021,henryTinnitusEpidemiologicPerspective2020},
 although few characteristics have been firmly established.
@@
 for estimating internal perceptual representations that is unconstrained by prior knowledge about the representations themselves.
-RC asks subjects to render subjective judgments over random stimuli, being closely related to Wiener theory \cite{wienerNonlinearProblemsRandom1966},
+RC asks subjects to render subjective judgments over random stimuli, being closely related to Wiener theory,
 which has inspired ``white-noise'' approaches to system characterization in physiology
@@
   \centering
-  \includegraphics[width=\linewidth]{experiment_overview.pdf}
+  \includegraphics[width=\linewidth]{gfx/experiment_overview.pdf}
   \caption{Diagram of the experimental protocol.
@@
 Reconstruction accuracies observed here are below the simulated ideal, which may be attributed to noisy responses universally observed in applications of RC, and which may be mitigated by further optimizing the experimental protocol, stimulus generation, and reconstruction method.
-For example, recent approaches to improving RC reconstruction methods can boost efficiency, noise robustness and overall accuracy \cite{roopCompressiveSensingApproach2021,comptonStimulusWhiteningImproves2022a}.
+For example, recent approaches to improving RC reconstruction methods can boost efficiency, noise robustness and overall accuracy \cite{comptonStimulusWhiteningImproves2022a}.
 Subjects completed the required number of trials within 10 minutes,

### 2023-01-05 paper/short/main_wc995.tex
Final Review

@@
 N.V. Barnett, M. Caplan, J. Mills and A.C. Lammert are also with BME at WPI.
-B.W. Roop is formerly of the Neuroscience Program at WPI.
+B.W. Roop is of the Neuroscience Program at WPI.
 D. Alexandrou is with the Stritch School of Medicine at Loyola University Chicago, Chicago, IL.
@@
 Nontonal tinnitus sounds are presumed to be complex and heterogeneous
-\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021,henryTinnitusEpidemiologicPerspective2020},
+\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021},
 although few characteristics have been firmly established.
@@
 \ref{eq:subjresp}.
-The \textit{random} subject responds $y_i \in \{1,-1\}^n$ with uniform random probability, thus ignoring the stimulus entirely.
+The \textit{random} subject responds $y_i \in \{1,-1\}$ with uniform random probability, thus ignoring the stimulus entirely.
 

### 2023-01-06 paper/short/main_wc995.tex
Finished

@@
 \cite{nondahlImpactTinnitusQuality2007,tegg-quinnImpactTinnitusCognition2016}.
-Clinical guidelines for tinnitus management involve targeted exposure to tinnitus-like sounds, for habituation therapy (termed \textit{sound therapy}), or as part of Cognitive Behavioral Therapy \cite{tunkelClinicalPracticeGuideline2014}.
+Clinical guidelines for tinnitus management involve targeted exposure to tinnitus-like sounds
+in a habituation therapy term \textit{sound therapy},
+or as part of cognitive behavioral therapy \cite{tunkelClinicalPracticeGuideline2014}.
 Critically, sound therapy outcomes improve when closely informed by the patient's internal tinnitus experience \cite{okamotoListeningTailormadeNotched2010,schaetteAcousticStimulationTreatments2010,steinInhibitioninducedPlasticityTinnitus2015}.
-However, existing strategies for characterizing tinnitus sounds, such as Pitch Matching (PM), are best suited for patients whose tinnitus resembles pure tones (\eg ringing), which may represent only $20-50\%$ of patients \cite{henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017}.
+However, existing strategies for characterizing tinnitus sounds, such as \textit{pitch matching} (PM),
+are best suited for patients whose tinnitus resembles pure tones (\eg ringing), which may represent only $20-50\%$ of patients \cite{henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017}.
 There is a need for methods to characterize nontonal (\eg buzzing, roaring) tinnitus \cite{henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002}.
@@
 for estimating internal perceptual representations that is unconstrained by prior knowledge about the representations themselves.
-RC asks subjects to render subjective judgments over random stimuli, being closely related to Wiener theory,
+RC asks participants to render subjective judgments over random stimuli,
+and reconstructs the latent signal as a linear combination of stimuli.
+RC is closely related to Wiener theory,
 which has inspired ``white-noise'' approaches to system characterization in physiology
@@
 
-Stimuli were composed of $b=8$ Mel-spaced frequency bins,
-which divide the frequency spectrum between $[100,~13,000]$
+The frequency space of the stimuli was partitioned into $b=8$ Mel-spaced frequency bins,
+which divide the frequency space between $[100,~13,000]$
 Hz into contiguous segments of equal amplitude (\ie ``rectangular'' bins).
-Reconstruction detail increases with $b$, but $b=8$ provides a good approximation to the chosen target sounds (see Fig. \ref{fig:spectra}).
+Reconstruction detail increases with $b$,
+but $b=8$ provides a good approximation to the chosen target sounds (\cf Fig. \ref{fig:spectra}).
 
@@
 
-Two spectrally complex and complimentary target sounds (``buzzing'' and ``roaring'') were downloaded from the American Tinnitus Association \cite{MeasuringTinnitusAmerican2022} and truncated to $500$ ms in duration (Fig.
+Two spectrally complex and complementary target sounds (``buzzing'' and ``roaring'') were downloaded from the American Tinnitus Association \cite{MeasuringTinnitusAmerican2022} and truncated to $500$ ms in duration (Fig.
 \ref{fig:spectra}).
@@
 \ref{fig:experimentdiagram}).
-Subjects completed two (2) blocks per target sound.
-Subjects were told that some stimuli had $A$ embedded in them, and were instructed to respond ``yes'' to such stimuli, otherwise ``no''.
+Subjects completed two (2) blocks per target sound ($p=200$ total trials per subject).
+Subjects were told that some stimuli had $A$ embedded in them, and were instructed to respond ``yes'' to such stimuli, otherwise ``no.''
 Subjects listened over earphones at a self-determined comfortable level.
@@
 
-A subject performing $p$ RC trials with $b$ frequency bins produces a stimulus matrix $\Psi \in \mathbb{R}^{p \times b}$
-and a response vector $y \in \{1,-1\}^n$,
-where $1$ corresponds to a ``yes'' response and $-1$ to a ``no.'' RC classically assumes the subject response model:
+A subject performing $p$ RC trials with $b$ frequency bins produces a stimulus matrix $\Psi \in \mathbb{R}^{p \times b}$ and a response vector $y \in \{1,-1\}^p$, where $1$ corresponds to a ``yes'' response and $-1$ to a ``no.'' RC classically assumes the subject response model:
 
 \begin{equation}
-  y = sign(\Psi^\mathrm{T} x),
+  y = sign(\Psi x),
   \label{eq:subjresp} 
@@
 
-where $x \in \mathbb{R}^\mathrm{b}$ is the subject's internal representation of interest (\eg of their tinnitus).
+where $x \in \mathbb{R}^\mathrm{b}$ is the subject's internal representation of interest (\ie of their tinnitus).
 Inverting this model yields:
@@
 \begin{equation}
-  \hat{x} = \frac{1}{n} \Psi y
+  \hat{x} = \frac{1}{n} \Psi^\mathrm{T} y
   \label{eq:linreg}
@@
         \end{cases}
+    \label{eq:idealsubject}
 \end{equation}
@@
 Thus, the ideal subject has precise knowledge of every stimulus and responds according to Eq.
-\ref{eq:subjresp}.
+\ref{eq:idealsubject}.
 The \textit{random} subject responds $y_i \in \{1,-1\}$ with uniform random probability, thus ignoring the stimulus entirely.
@@
 Subjects completed the required number of trials within 10 minutes,
-indicating that this procedure could be conducted in a single clinical visit.
+indicating that this procedure can be conducted in a single clinical visit.
 RC may therefore be useful as the basis for a clinical assay to characterize a wider variety of tinnitus percepts than currently possible.

### 2023-03-24 paper/short/main_wc995.tex
Edits from reviews

@@
 Reconstructions of the targets were obtained by regressing subject responses on the stimuli, and were compared for accuracy to the frequency spectra of the targets using Pearson's $r$.
-  \textit{Results:} Reconstruction accuracy was significantly higher than chance across subjects: buzzing ($M=0.53$, $SD=0.27$): $t(9)=5.766$, $p<0.001$; roaring ($M=0.57$, $SD=0.30$): $t(9)=5.76$, $p<0.001$.
+  \textit{Results:} Reconstruction accuracy was significantly higher than chance across subjects: buzzing: $0.52 \pm 0.27$ (mean $\pm$ s.d.), $t(9) = 5.766$, $p < 0.001$;
+  roaring: $0.62 \pm 0.23$, $t(9) = 5.76$, $p < 0.001$;
+  combined: $0.57 \pm 0.25$, $t(19) = 7.542$, $p < 0.001$.
   \textit{Conclusion:} Reverse correlation can accurately reconstruct non-tonal tinnitus-like sounds in normal-hearing subjects,
@@
 However, existing strategies for characterizing tinnitus sounds, such as \textit{pitch matching} (PM),
-are best suited for patients whose tinnitus resembles pure tones (\eg ringing), which may represent only $20-50\%$ of patients \cite{henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017}.
+are best suited for patients whose tinnitus resembles pure tones (\eg ringing), which may represent about $50\%$ of patients \cite{henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017,vajsakovicPrinciplesMethodsPsychoacoustic2021}.
 There is a need for methods to characterize nontonal (\eg buzzing, roaring) tinnitus \cite{henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002}.
@@
 which has inspired ``white-noise'' approaches to system characterization in physiology
-\cite{ringachReverseCorrelationNeurophysiology2004,marmarelisWhiteNoiseMethodSystem1978} and engineering \cite{ljungMeasureLackFit1978}.
+\cite{ringachReverseCorrelationNeurophysiology2004,marmarelisWhiteNoiseMethodSystem1978} and engineering \cite{ljungSystemIdentificationTheory1998}.
 
@@
 
-Ten ($n=10$) normal-hearing subjects listened to $A-X$ trials containing a target sound ($A$) followed by a stimulus ($X$).
+Ten ($n=10$) normal-hearing subjects listened to \textit{A-X} trials containing a target sound ($A$) followed by a stimulus ($X$).
 $X$ was randomly generated for each trial, while $A$ remained the same within a block of $100$ trials (Fig.
@@
 Subjects were told that some stimuli had $A$ embedded in them, and were instructed to respond ``yes'' to such stimuli, otherwise ``no.''
-Subjects listened over earphones at a self-determined comfortable level.
+Subjects listened over earphones at a self-determined comfortable level, which they adjusted themselves while listening to sample stimuli.
+Presentation level (in dB sound pressure level (SPL)) was not recorded.
 Procedures were approved by the UMass IRB.
@@
 Figure \ref{fig:reconstructions} shows the distribution of Pearson's $r$ for human, ideal, and random subject responses.
-Human accuracies were generally higher than random,
-with some approaching \textit{ideal}. 
-Mean human accuracy was significantly different from $0$ (i.e., mean \textit{random} accuracy) in all conditions: buzzing: $t(9) = 5.766$, $p < 0.001$; roaring: $t(9) = 5.76$, $p < 0.001$; combined: $t(19) = 7.542$, $p < 0.001$.
+Human accuracy is statistically significantly higher than random chance and for some subjects, approaches the ideal case.
+% Mean human accuracy was significantly different from $0$ (i.e., mean \textit{random} accuracy) in all conditions: buzzing: $t(9) = 5.766$, $p < 0.001$; roaring: $t(9) = 5.76$, $p < 0.001$; combined: $t(19) = 7.542$, $p < 0.001$.
+Accuracy from the random subject was $0.00 \pm 0.44$ (mean $\pm$ st.dev.) for buzzing and $0.00 \pm 0.39$ for roaring,
+while mean accuracy from human responses was significantly different from $0$ in all conditions:
+buzzing: $0.52 \pm 0.27$, $t(9) = 5.766$, $p < 0.001$;
+roaring: $0.62 \pm 0.23$, $t(9) = 5.76$, $p < 0.001$;
+combined: $0.57 \pm 0.25$, $t(19) = 7.542$, $p < 0.001$.
+From Figure \ref{fig:reconstructions},
+it appears that the distribution of buzzing results differs from that of the roaring results,
+however the difference between buzzing and roaring is not statistically significant
+(two-way ANOVA across subjects ($F(13) = 2.94$, $p > 0.05$) and target signals ($F(1) = 2.44$, $p > 0.05$)).
 Figure \ref{fig:spectra} plots the most accurate human reconstructions over the target sound spectra.
@@
 
-Our results show that RC can accurately reconstruct the PTS of complex, non-tonal, tinnitus-like sounds, capturing the most salient features of the target.
+Our results show that RC can accurately reconstruct the frequency spectrum of certain relevant non-tonal tinnitus sounds.
 Reconstruction accuracies observed here are below the simulated ideal, which may be attributed to noisy responses universally observed in applications of RC, and which may be mitigated by further optimizing the experimental protocol, stimulus generation, and reconstruction method.
@@
 RC may therefore be useful as the basis for a clinical assay to characterize a wider variety of tinnitus percepts than currently possible.
-Future work will focus on validating this approach in patients suffering from tinnitus.
+Future work will focus on validating this approach with larger sample sizes, with more target signals,
+stricter sound pressure level (SPL) control.
 

### 2023-03-24 paper/short/main_wc995.tex
Update paper

@@
 Clinical guidelines for tinnitus management involve targeted exposure to tinnitus-like sounds
-in a habituation therapy term \textit{sound therapy},
+in a habituation therapy termed \textit{sound therapy},
 or as part of cognitive behavioral therapy \cite{tunkelClinicalPracticeGuideline2014}.
-Critically, sound therapy outcomes improve when closely informed by the patient's internal tinnitus experience \cite{okamotoListeningTailormadeNotched2010,schaetteAcousticStimulationTreatments2010,steinInhibitioninducedPlasticityTinnitus2015}.
+Critically, sound therapy outcomes improve when closely informed by the patient's internal tinnitus experience \cite{okamotoListeningTailormadeNotched2010,schaetteAcousticStimulationTreatments2010,steinInhibitioninducedPlasticityTinnitus2015,schoisswohlAmplitudeModulatedNoise2019}.
 However, existing strategies for characterizing tinnitus sounds, such as \textit{pitch matching} (PM),
-are best suited for patients whose tinnitus resembles pure tones (\eg ringing), which may represent about $50\%$ of patients \cite{henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017,vajsakovicPrinciplesMethodsPsychoacoustic2021}.
-There is a need for methods to characterize nontonal (\eg buzzing, roaring) tinnitus \cite{henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002}.
+are best suited for patients whose tinnitus resembles pure tones (\eg ringing), which may represent about 50-80\% of patients \cite{neffComparingThreeEstablished2019,henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017,vajsakovicPrinciplesMethodsPsychoacoustic2021}.
+There is a need for methods to characterize the remaining 20-50\% of nontonal (\eg buzzing, roaring) tinnitus \cite{henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002}.
 
@@
 
-Two spectrally complex and complementary target sounds (``buzzing'' and ``roaring'') were downloaded from the American Tinnitus Association \cite{MeasuringTinnitusAmerican2022} and truncated to $500$ ms in duration (Fig.
+Two spectrally complex and complementary target sounds (``buzzing'' and ``roaring'') were downloaded from the American Tinnitus Association \cite{MeasuringTinnitusAmerican2022} and truncated to $500$ ms in duration (power-spectral densities are displayed in the botton subplots of Fig.
 \ref{fig:spectra}).
@@
 Subjects listened over earphones at a self-determined comfortable level, which they adjusted themselves while listening to sample stimuli.
-Presentation level (in dB sound pressure level (SPL)) was not recorded.
+Presentation level (in dB SPL) was not recorded.
 Procedures were approved by the UMass IRB.

### 2023-03-27 paper/scripts/get_stats.m
201 response to reviewers (#205)
* Add a few words about bigger studies to come

* Update paper

* Edits from reviews

* Update paper

* Update paper

@@ -1,6 +1,7 @@
 %% Compute stats used in the main paper
 
 T2 = T(T.n_bins == 8, :);
+groupsummary(T2, "target_signal_name", ["mean", "std"], ["r_lr_bins_1", "r_synth", "r_rand"])
 
 %% Stats for buzzing
 

### 2023-03-27 paper/short/main_wc995.tex
201 response to reviewers (#205)
* Add a few words about bigger studies to come

* Update paper

* Edits from reviews

* Update paper

* Update paper
Edits from Adam

@@
 % INTRO PARAGRAPH 1/3
-\IEEEPARstart{T}{INNITUS}\textemdash{}the perception of sound
-in the absence of any corresponding external stimulus\textemdash{}affects up to 50 million people in the U.S. \cite{bhattPrevalenceSeverityExposures2016},
-a third of whom experience functional cognitive impairment and diminished quality of life
-\cite{nondahlImpactTinnitusQuality2007,tegg-quinnImpactTinnitusCognition2016}.
-Clinical guidelines for tinnitus management involve targeted exposure to tinnitus-like sounds
-in a habituation therapy termed \textit{sound therapy},
-or as part of cognitive behavioral therapy \cite{tunkelClinicalPracticeGuideline2014}.
-Critically, sound therapy outcomes improve when closely informed by the patient's internal tinnitus experience \cite{okamotoListeningTailormadeNotched2010,schaetteAcousticStimulationTreatments2010,steinInhibitioninducedPlasticityTinnitus2015,schoisswohlAmplitudeModulatedNoise2019}.
-However, existing strategies for characterizing tinnitus sounds, such as \textit{pitch matching} (PM),
-are best suited for patients whose tinnitus resembles pure tones (\eg ringing), which may represent about 50-80\% of patients \cite{neffComparingThreeEstablished2019,henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017,vajsakovicPrinciplesMethodsPsychoacoustic2021}.
-There is a need for methods to characterize the remaining 20-50\% of nontonal (\eg buzzing, roaring) tinnitus \cite{henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002}.
+\IEEEPARstart{T}{INNITUS}\textemdash{}the perception of sound in the absence of any corresponding external stimulus\textemdash{}affects up to 50 million people in the U.S.
+\cite{bhattPrevalenceSeverityExposures2016}, a third of whom experience functional cognitive impairment and diminished quality of life \cite{nondahlImpactTinnitusQuality2007,tegg-quinnImpactTinnitusCognition2016}.
+Clinical guidelines for tinnitus management involve targeted exposure to external sounds as part of \textit{sound therapy} or \textit{cognitive behavioral therapy} \cite{tunkelClinicalPracticeGuideline2014}.
+Critically, patient outcomes improve when the employed external sounds are closely informed by the patient's internal tinnitus experience \cite{okamotoListeningTailormadeNotched2010,schaetteAcousticStimulationTreatments2010,steinInhibitioninducedPlasticityTinnitus2015,schoisswohlAmplitudeModulatedNoise2019}.
+However, existing strategies for characterizing tinnitus sounds, such as \textit{pitch matching} (PM), are best suited for patients whose tinnitus resembles pure tones (\eg ringing) \cite{neffComparingThreeEstablished2019,henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017,vajsakovicPrinciplesMethodsPsychoacoustic2021}.
+There is a need for methods to characterize tinnitus sounds in the estimated 20-50\% of patients with nontonal (\eg buzzing, roaring) tinnitus \cite{henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002}.
 
 % INTRO PARAGRAPH 2/3
-Nontonal tinnitus sounds are presumed to be complex and heterogeneous
-\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021},
-although few characteristics have been firmly established.
-Therefore, we base our approach on \textit{reverse correlation} (RC),
-an established behavioral method
-\cite{ahumadaStimulusFeaturesSignal1971,gosselinSuperstitiousPerceptionsReveal2003,brimijoinInternalRepresentationVowel2013}
-for estimating internal perceptual representations that is unconstrained by prior knowledge about the representations themselves.
-RC asks participants to render subjective judgments over random stimuli,
-and reconstructs the latent signal as a linear combination of stimuli.
-RC is closely related to Wiener theory,
-which has inspired ``white-noise'' approaches to system characterization in physiology
-\cite{ringachReverseCorrelationNeurophysiology2004,marmarelisWhiteNoiseMethodSystem1978} and engineering \cite{ljungSystemIdentificationTheory1998}.
+Nontonal tinnitus sounds are presumed to be complex and heterogeneous \cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}, although few characteristics have been firmly established.
+Therefore, we base our approach on \textit{reverse correlation} (RC), an established behavioral method \cite{ahumadaStimulusFeaturesSignal1971,gosselinSuperstitiousPerceptionsReveal2003,brimijoinInternalRepresentationVowel2013} for estimating internal perceptual representations that is unconstrained by prior knowledge about the representations themselves.
+RC asks participants to render subjective judgments over ambiguous stimuli, and reconstructs the latent representation by regressing subject responses onto the stimuli.
+RC is closely related to Wiener theory, which has inspired ``white-noise'' approaches to system characterization in physiology \cite{ringachReverseCorrelationNeurophysiology2004,marmarelisWhiteNoiseMethodSystem1978} and engineering \cite{ljungSystemIdentificationTheory1998}.
 
@@
 % document is a Latex  template for Technology Letters to be submitted to IEEE OJEMB \cite{ahumadaStimulusFeaturesSignal1971}.
-Submissions must have the sections listed in the following exactly in the order shown here: Introduction, Materials and Methods, Results, Discussion, Conclusions.
-Manuscripts to be submitted to IEEE OJEMB as a Science Letters must use a different template.
-For both types of manuscript, the authors can opt to add a Supplementary Materials section.
+% Submissions must have the sections listed in the following exactly in the order shown here: Introduction, Materials and Methods, Results, Discussion, Conclusions.
+% Manuscripts to be submitted to IEEE OJEMB as a Science Letters must use a different template.
+% For both types of manuscript, the authors can opt to add a Supplementary Materials section.
 
@@
 % To use this template, type over sections of the template or cut and paste from another document.
-Highlight a section that you want to designate with a certain style, then select the appropriate name on the style menu.
-The style will adjust your fonts and line spacing.
-Do not change the font sizes or line spacing to squeeze more text into a limited number of pages.
-Use italics for emphasis; do not underline.
-% IEEE will do the final formatting of your paper.
-However, you should format your manuscript for submission to IEEE OJEMB for review and also for preparing for preprint that will be e-published several days after you upload the final version of an accepted manuscript.
+% Highlight a section that you want to designate with a certain style, then select the appropriate name on the style menu.
+% The style will adjust your fonts and line spacing.
+% Do not change the font sizes or line spacing to squeeze more text into a limited number of pages.
+% Use italics for emphasis; do not underline.
+
+% % IEEE will do the final formatting of your paper.
+% However, you should format your manuscript for submission to IEEE OJEMB for review and also for preparing for preprint that will be e-published several days after you upload the final version of an accepted manuscript.
 
@@
 Reconstruction detail increases with $b$,
-but $b=8$ provides a good approximation to the chosen target sounds (\cf Fig. \ref{fig:spectra}).
+but $b=8$ provides a good approximation to the chosen target sounds (\cf Fig.
+\ref{fig:spectra}).
 
-For each stimulus, $[2,7]$ bins were randomly ``filled'' with power $0$ dB. ``Unfilled'' bins were assigned $-100$ dB. All frequencies were assigned random phase.
+For each stimulus, $[2,7]$ bins were randomly ``filled'' with power $0$ dB.
+``Unfilled'' bins were assigned $-100$ dB.
+All frequencies were assigned random phase.
 Inverse Fourier transform of the constructed spectrum yields a $500$ ms stimulus waveform.\footnote{Software for the experiments and analysis was written in MATLAB and is freely available at \protect\url{https://github.com/alec-hoyland/tinnitus-reconstruction/}}
@@
     \caption{Human reconstruction accuracy is significantly above baseline,
-    but is not optimal. Random, human, and ideal reconstruction accuracies
+    but is not optimal.
+    Random, human, and ideal reconstruction accuracies
     are shown as violin plots with box plots overlaid.
@@
 
-Our results show that RC can accurately reconstruct the frequency spectrum of certain relevant non-tonal tinnitus sounds.
-Reconstruction accuracies observed here are below the simulated ideal, which may be attributed to noisy responses universally observed in applications of RC, and which may be mitigated by further optimizing the experimental protocol, stimulus generation, and reconstruction method.
+Our results show that RC can accurately reconstruct the frequency spectrum of tinnitus-like sounds relevant to non-tonal tinnitus,
+and therefore represent a proof of concept for using RC to characterize non-tonal tinnitus.
+Subjects completed the required number of trials within ten minutes,
+indicating that this procedure could be conducted within a single clinical visit.
+RC may therefore be useful as the basis for a clinical assay to characterize a wider variety of tinnitus percepts than currently possible.
+Reconstruction accuracies observed here are below the simulated ideal, which may be attributed to noisy responses universally observed in applications of RC,
+and which may be mitigated by further optimizing the experimental protocol, stimulus generation, and reconstruction method.
 For example, recent approaches to improving RC reconstruction methods can boost efficiency, noise robustness and overall accuracy \cite{comptonStimulusWhiteningImproves2022a}.
-Subjects completed the required number of trials within 10 minutes,
-indicating that this procedure can be conducted in a single clinical visit.
-RC may therefore be useful as the basis for a clinical assay to characterize a wider variety of tinnitus percepts than currently possible.
-Future work will focus on validating this approach with larger sample sizes, with more target signals,
-stricter sound pressure level (SPL) control.
+Future work will focus on more comprehensive validation of this approach, using larger sample sizes, more target sounds, and stricter control of sound presentation level.
 

### 2023-03-27 paper/short/main_wc995.tex
Edits from lab meeting

@@
 % INTRO PARAGRAPH 3/3
-Here, we validate RC as a method for characterizing a more complete psychoacoustic tinnitus spectrum (PTS) for tinnitus sounds.
-To that end, normal-hearing participants completed an augmented RC experiment, comparing random stimuli to a target tinnitus-like sound.
-The estimated PTS was subsequently validated against the targets.
+Here, we validate RC as a method for characterizing individuals' internal representations of tinnitus
+more completely.
+To that end, normal-hearing participants completed an augmented RC experiment, comparing random stimuli to a target tinnitus-like sound,
+yielding frequency spectrum estimates of their tinnitus representation.
+The estimated spectra were subsequently validated against the target tinnitus sounds.
 Our results demonstrate, for the first time, that tinnitus-like sounds with complex spectra can be accurately estimated using RC.
@@
 Subjects listened over earphones at a self-determined comfortable level, which they adjusted themselves while listening to sample stimuli.
-Presentation level (in dB SPL) was not recorded.
+Presentation level was not recorded.
 Procedures were approved by the UMass IRB.
@@
     \includegraphics[width=\linewidth]{gfx/reconstruction_spectra_cropped.pdf}
-    \caption{Reconstructions of the PTS capture many salient features of tinnitus spectra.
+    \caption{Reconstructions of the tinnitus spectra capture many salient features of the target sounds.
     The black trace indicates the target,

### 2023-03-29 paper/short/main_wc995.tex
Update paper

@@
 Subjects were told that some stimuli had $A$ embedded in them, and were instructed to respond ``yes'' to such stimuli, otherwise ``no.''
-Subjects listened over earphones at a self-determined comfortable level, which they adjusted themselves while listening to sample stimuli.
-Presentation level was not recorded.
+Subjects listened over earphones at a self-determined comfortable level.
+Presentation level was not recorded in this study.
 Procedures were approved by the UMass IRB.
@@
   \centering
-  \includegraphics[width=\linewidth]{gfx/experiment_overview.pdf}
+  \includegraphics[width=\linewidth]{gfx/fig1.pdf}
   \caption{Diagram of the experimental protocol.

### 2023-03-29 paper/main_preprint.tex
Reorganize papers

--- 2023-01-05 paper/short/main_wc1255.tex
@@
   % declare the path(s) where your graphic files are
-  \graphicspath{{gfx}}
+  \graphicspath{{gfx_preprint}}
   % and their extensions so you won't have to specify these with
@@
 
+% \author{Alec Hoyland, %,~\IEEEmembership{Fellow, IEEE,}
+%         Samantha Peznola, and Adam C. Lammert% <-this % stops a space
+% \thanks{Paper submitted on DATE.
+% 	This work was supported in part by the University of Massachusetts
+% 	Center for Clinical and Translational Science Pilot Project Program 2022,
+% 	grant number GRANT_NUMBER.
+% 	Alec Hoyland is a graduate student in the Department of Biomedical Engineering
+% 	at Worcester Polytechnic Institute (WPI), Worcester, MA, USA;
+% 	Samantha Peznola is a Research Assistant at WPI;
+% 	and Dr. Adam C. Lammert is Assistant Professor of Biomedical Engineering at WPI.
+% }}
+% \author{Alec Hoyland, Nelson Barnett, Benjamin W. Roop, and Adam C. Lammert\textsuperscript{\textdagger{}}%
 \author{Alec Hoyland, Nelson V. Barnett, Benjamin W. Roop, Danae Alexandrou, Myah Caplan, Jacob Mills, Benjamin Parrell, Divya A. Chari, and Adam C. Lammert\textsuperscript{\textdagger{}}%
@@
 B.W. Roop is formerly of the Neuroscience Program at WPI, now with  MIT Lincoln Laboratory, Lexington, MA.
-D. Alexandrou is with the Stritch School of Medicine at Loyola University Chicago, Chicago, IL.
+D. Alexandrou is with the Stritch School of Medicine at Loyola University Chicago, IL.
 B. Parrell is with the Department of Communication Sciences and Disorders and the Waisman Center at University of Wisconsin, Madison, WI. D.A. Chari is with the
@@
 \thanks{\textsuperscript{\textdagger{}} Corresponding Author}}%
+% NB NOTE: This is mentioned at the top of Materials and Methods. Should be just one or the other. 
+% I like the footnote better, but the footnote could be moved to MM section. 
+% \thanks{Code is freely available at \protect\url{https://github.com/alec-hoyland/tinnitus-project/}.
+% Data are available upon request.}}
 
@@
 % in the abstract or keywords.
-% TC:ignore
 \begin{abstract}
-  \textit{Goal:} This study validates a reverse correlation method for characterizing the sounds experienced by tinnitus patients with potential for characterizing a wider range of sounds than currently possible.
-  \textit{Methods:} Ten normal-hearing subjects assessed the subjective similarity of random auditory stimuli and target tinnitus-like sounds (“buzzing” and “roaring”).
+  \textit{Goal:} This study validates a method for characterizing the sounds experienced by tinnitus patients with potential for characterizing a wider range of sounds than currently possible.
+  The approach is based on reverse correlation, an established behavioral method widely used in psychophysics for unconstrained characterization of internal perceptual representations.
+  \textit{Methods:} Ten normal-hearing subjects participated in a reverse correlation experiment, where they assessed the subjective similarity of random auditory stimuli and target tinnitus-like sounds (“buzzing” and “roaring”).
   Reconstructions of the targets were obtained by regressing subject responses on the stimuli, and were compared for accuracy to the frequency spectra of the targets using Pearson's $r$.
-  \textit{Results:} Reconstruction accuracy was significantly higher than chance across subjects: buzzing ($M=0.53$, $SD=0.27$): $t(9)=5.766$, $p<0.001$; roaring ($M=0.57$, $SD=0.30$): $t(9)=5.76$, $p<0.001$.
+  \textit{Results:} Reconstruction accuracy was significantly higher than chance across subjects: buzzing: $0.52 \pm 0.27$ (mean $\pm$ s.d.), $t(9) = 5.766$, $p < 0.001$;
+  roaring: $0.62 \pm 0.23$, $t(9) = 5.76$, $p < 0.001$;
+  combined: $0.57 \pm 0.25$, $t(19) = 7.542$, $p < 0.001$.
   \textit{Conclusion:} Reverse correlation can accurately reconstruct non-tonal tinnitus-like sounds in normal-hearing subjects,
@@
 
-%TC:ignore
 \begin{minipage}[t]{0.9\columnwidth}
@@
 \end{minipage}
-%TC:endignore
 
@@
 % INTRO PARAGRAPH 1/3
-\IEEEPARstart{T}{INNITUS}\textemdash{}the perception of sound
-in the absence of any corresponding external stimulus\textemdash{}affects up to 50 million people in the U.S.
-\cite{bhattPrevalenceSeverityExposures2016,nationalinstituteondeafnessandothercommunicationdisordersQuickStatisticsHearing},
+\IEEEPARstart{T}{INNITUS}\textemdash{}the perception of sound (\eg ringing, buzzing)
+in the absence of any corresponding external stimulus\textemdash{}affects over 25 million people in the U.S., with some estimates ranging up to 50 million \cite{bhattPrevalenceSeverityExposures2016,nationalinstituteondeafnessandothercommunicationdisordersQuickStatisticsHearing},
 a third of whom experience functional cognitive impairment and substantial reduction in quality of life
 \cite{ahmedImpactTinnitusPerception2017,nondahlImpactTinnitusQuality2007,tegg-quinnImpactTinnitusCognition2016}.
-Clinical guidelines for tinnitus management frequently involve targeted exposure to tinnitus-like external sounds, either as a form of habituation therapy (termed \textit{sound therapy}), or in the context of Cognitive Behavioral Therapy \cite{tunkelClinicalPracticeGuideline2014}.
-Critically, sound therapy is shown to improve with knowledge of the patient's internal tinnitus experience \cite{davisNeuromonicsTinnitusTreatment2007,landgrebeMethodologicalAspectsClinical2012,nickelOutcomeResearchMusic2005,okamotoListeningTailormadeNotched2010,schaetteAcousticStimulationTreatments2010,steinInhibitioninducedPlasticityTinnitus2015,tassCounteractingTinnitusAcoustic2012,wangStateArtSound2020}.
-However, existing strategies for characterizing tinnitus sounds, such as Pitch Matching (PM) methods, are best suited for patients who experience sounds resembling pure tones (\eg ringing).
-This group may represent only between 20-50\% of all tinnitus patients \cite{turnerjrAuditoryDysfunctionTinnitus1990,henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017}, with others experiencing non-tonal (\eg buzzing, roaring) tinnitus sounds.
-There is a pressing need for more robust tinnitus characterization methods \cite{henryTinnitusEpidemiologicPerspective2020,henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002,robertsResidualInhibitionFunctions2006}.
+Primary treatment options for tinnitus are currently limited by a lack of methods for accurately characterizing the full breadth of internal sounds experienced by patients.
+Clinical guidelines for tinnitus management frequently involve targeted exposure to tinnitus-like external sounds, either as a form of habituation therapy (termed \textit{sound therapy}), or in the context of Cognitive Behavioral Therapy, where patients are encouraged to perceive their tinnitus as a neutral stimulus \cite{tunkelClinicalPracticeGuideline2014}.
+Critically, treatment outcomes have been repeatedly shown to improve when the external sounds used in sound therapy are closely informed by the internal tinnitus experience of the patient
+\cite{davisNeuromonicsTinnitusTreatment2007,landgrebeMethodologicalAspectsClinical2012,nickelOutcomeResearchMusic2005,okamotoListeningTailormadeNotched2010,schaetteAcousticStimulationTreatments2010,steinInhibitioninducedPlasticityTinnitus2015,tassCounteractingTinnitusAcoustic2012,wangStateArtSound2020,neffComparingThreeEstablished2019,schoisswohlAmplitudeModulatedNoise2019}.
+However, existing strategies for characterizing the tinnitus sounds, such as Pitch Matching (PM) methods, are best suited for patients with tonal tinnitus, who experience sounds resembling pure tones (\eg ringing).
+% However, existing methods for characterizing the tinnitus sounds\textemdash{}Pitch Matching (PM) methods\textemdash{}are best suited for patients with tonal tinnitus, who experience sounds resembling pure tones (\eg ringing).
+This group may represent between 50-80\% of all tinnitus patients \cite{turnerjrAuditoryDysfunctionTinnitus1990,henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017,vajsakovicPrinciplesMethodsPsychoacoustic2021}, with the other 20-50\% experiencing nontonal (\eg buzzing, roaring) tinnitus sounds.
+There is a pressing need for characterization methods targeting tinnitus patients who are not served by current procedures
+\cite{henryTinnitusEpidemiologicPerspective2020,henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002,robertsResidualInhibitionFunctions2006}.
 
@@
 although little has been firmly established about the specific characteristics.
-Therefore, we base our approach on \textit{reverse correlation} (RC),
+Therefore, we base our approach on the demonstrated capabilities of \textit{reverse correlation} (RC),
 an established behavioral method
@@
 RC asks subjects to render subjective judgments (\eg “does this sound like your tinnitus?”)
-over random stimuli, 
-from which unbiased estimates of the percepts can be produced.
+over random stimuli that have no direct relation to the percepts of interest,
+from which correspondingly unbiased estimates of those objects can be produced.
 RC is closely related to Wiener theory \cite{wienerNonlinearProblemsRandom1966},
-which has also inspired ``white-noise'' approaches to system characterization in physiology
+which has also inspired so-called white-noise approaches to system characterization in physiology
 \cite{ringachReverseCorrelationNeurophysiology2004,marmarelisWhiteNoiseMethodSystem1978} and engineering more broadly
-\cite{ljungMeasureLackFit1978}.
+\cite{ljungSystemIdentificationTheory1998}.
 
@@
 by estimating the full psychoacoustic tinnitus spectrum (PTS).
-To that end, we asked normal-hearing participants to complete an augmented RC experiment, comparing random stimuli to a target tinnitus-like sound.
+To that end, we asked normal-hearing participants to complete an augmented RC experiment where they had to compare random stimuli to a target tinnitus-like sound.
 Target sounds were subsequently used as the basis for validating the quality of the estimated PTS.
 Our results demonstrate, for the first time, that tinnitus-like sounds with complex spectra can be accurately estimated using RC. 
-This discovery may open the door to developing a clinical assay for characterizing the full range of sounds experienced by tinnitus patients.
+This discovery may open the door to developing a clinical assay based on RC for characterizing the full range of sounds experienced by tinnitus patients.
 
@@
 
-Software code used for the experiments and analysis was written in MATLAB and is freely available at \protect\url{https://github.com/alec-hoyland/tinnitus-reconstruction/}.
+Software code used for the experiments and analysis was written in MATLAB (Mathworks, Inc., Natick, Massachusetts)
+and is freely available at \protect\url{https://github.com/alec-hoyland/tinnitus-project/}.
+% The code depends on \cite{bechtoldViolinPlotsMatlab2022,kochYaml2022,gorur-shandilyaSrinivasGsMtools2022}.
 
+% ACL, DONE
 \subsection{Stimuli}
@@
 Hz into continuous segments of equal amplitude (\ie ``rectangular'' bins).
-Reconstruction detail increases with $b$, but $b=8$ bins provides a good approximation to the chosen target sounds (see Fig. \ref{fig:spectra}).
+While $b=8$ bins were found to provide a good approximation to the target sounds used here (see Fig. \ref{fig:spectra}),
+more bins results in finer spectral details in the reconstruction as well as increased computational complexity.
 
-For each stimulus, $[2,7]$ bins were randomly ``filled'' with power $0$ dB. ``Unfilled'' bins were assigned a power of $-100$ dB. 
-Assigning random phase, the inverse Fourier transform of the spectrum yields a $500$-ms stimulus waveform.
+To generate a stimulus, we randomly select $[2,7]$ bins with uniform probability to be ``filled'' with power $0$ dB,
+while ``unfilled'' bins were assigned a power of $-100$ dB. 
+Assigning random phase, we then take the inverse Fourier transform of the spectrum to yield a $500$-ms stimulus waveform.
 
+% ACL, DONE
 \subsection{Target Sounds}
 
-Two tinnitus-like target sounds (``buzzing'' and ``roaring'') from online examples maintained by the American Tinnitus Association
-\cite{MeasuringTinnitusAmerican2022} were downloaded and truncated to $500$-ms in duration. These sounds were selected for the complexity and complementary nature of their frequency spectra.
+Tinnitus-like target sounds were drawn from online examples maintained by the American Tinnitus Association
+\cite{MeasuringTinnitusAmerican2022}.
+The two examples selected for this study corresponded to those described as ``buzzing'' and ``roaring.''
+These sounds were selected for the complexity and complementary nature of their frequency spectra.
+These examples were downloaded and truncated to $500$-ms in duration.
 
+% ACL, DONE
 \subsection{Experiment}
 
-Trials followed an $A-X$ paradigm (Fig.
-\ref{fig:experimentdiagram}), where $n=10$ subjects with self-reported normal hearing listened to the same target sound ($A$) followed by a random stimulus ($X$) for each trial.
-The task is designed to mimic the process by which a tinnitus patient might compare a random stimulus to their own tinnitus percept.
+We recruited $n=10$ subjects with self-reported normal hearing to participate in the experiment.
+All procedures were approved by the UMass IRB.
+Subjects listened over earphones, and manually adjusted the loudness of presented sounds to a self-determined comfortable level.
+Presentation level was not recorded.
+Trials followed an $A-X$ presentation paradigm (Fig. \ref{fig:experimentdiagram}),
+where subjects listened to a target sound ($A$) followed by a stimulus ($X$).
+$A$ remained the same for every trial within a given experimental condition,
+while $X$ was randomly generated for each trial.
+The task is designed to mimic the process by which a tinnitus patient might compare a random stimulus to their own tinnitus percept in the context of a RC experiment.
 
-Subjects were told that some stimuli had the target sound embedded in them, and were instructed to respond ``yes'' to any such stimuli, and ``no'' otherwise.
+Subjects were told that some stimuli had the target sound embedded in them, and were instructed to respond ``yes'' to any such stimuli, and to respond ``no'' otherwise.
 Subjects performed trials in blocks of $100$, with breaks between blocks.
-Subjects completed two ($2$) blocks of trials per given target, $A$.
-The $400$ total trials took subjects 10-20 minutes to complete.
+% NB QUESTION: Is the (2) necessary? If they don't require it, I'd remove it. 
+Subjects completed two ($2$) blocks of trials per experimental condition (\ie for a given target, $A$).
+The $400$ total trials took subjects about 10-20 minutes to complete.
 
@@
   depending on their perceived similarity.
-  The recorded stimulus-response pairs are used to form an estimate of the target.}
+  The recorded stimulus-response pairs are used to form an estimate of the target
+  using a restricted regression procedure.}
   \label{fig:experimentdiagram}
@@
 
+% ACL, DONE
 \subsection{Reconstruction}
@@
 where $x \in \mathbb{R}^\mathrm{b}$ represents the subject's internal representation of interest (\eg their tinnitus percept).
-This model can be inverted, yielding the following formula:
+This model can be inverted, yielding the following commonly-used formula for reconstructing internal representations in RC experiments:
 
@@
 
-This formula is a restricted form of the Normal equation, under
+This formula is a restricted form of the Normal equation\textemdash{}the least-squares solution to a linear regression problem\textemdash{}under
 the assumption that the stimulus dimensions are uncorrelated \cite{gosselinSuperstitiousPerceptionsReveal2003}.
-Intuitively, $\hat{x}$ is the sum of all stimuli eliciting a ``yes'' response, after subtracting all stimuli eliciting a ``no.''
+Intuitively, this implies that the reconstruction, $\hat{x}$, is the sum of all stimuli eliciting a ``yes'' response, after subtracting the sum of all stimuli eliciting a ``no.''
 
+% ACL, DONE
 \subsection{Validation}
 
-The $A-X$ paradigm allows for direct validation of the reconstructions $\hat{x}_{buzzing}$ and $\hat{x}_{roaring}$ against their corresponding target sounds.
+By adopting the $A-X$ paradigm for the present experiments,
+we have the opportunity to directly validate the reconstructions
+$\hat{x}_{buzzing}$ and $\hat{x}_{roaring}$ against their corresponding target sounds.
 To that end, we represent the power spectra of the target sounds as vectors $s_{buzzing} \in \mathbb{R}^\mathrm{b}$ and $s_{roaring} \in \mathbb{R}^\mathrm{b}$ using the same $b=8$ frequency bins used in stimulus generation.
-The power in each bin is set as the mean power level of frequencies within that bin.
-Pearson's $r$ between $s_{buzzing}$ and $s_{roaring}$ and their corresponding reconstructions ($\hat{x}_{buzzing}$ and $\hat{x}_{roaring}$) represents reconstruction accuracy.
+The power in each bin is taken to be the mean power level for frequencies contained within that bin.
+The vectors $s_{buzzing}$ and $s_{roaring}$ can then be directly compared to their corresponding reconstructions
+$\hat{x}_{buzzing}$ and $\hat{x}_{roaring}$ using Pearson's $r$, representing a measure of reconstruction accuracy.
 One-sample t-tests were performed on the mean Fisher-transformed $r$ values across subjects to assess significant differences from zero.
 
+% ACL, DONE
 \subsection{Synthetic and Random Subjects}
 
-To establish bounds on human performance,
-additional experiments were run \textit{in-silico} with two simulated subjects that
-represent participants who always give either \textit{ideal} or \textit{random} responses.
+For the purposes of establishing upper and lower bounds on human performance in this experiment,
+additional experiments were run \textit{in-silico} with two simulated subjects,
+representing a participant who always gives \textit{ideal} responses and one who always gives \textit{random} responses.
 Each experiment ran for $n=200$ trials and was repeated $1000$ times.
@@
 
-% NB NOTE: What is s??
 for $i \in 1, ..., n$, where $Q(x, y)$ is the quantile function for $x \in [0, 1]$ of the similarity calculation $\Psi s$, and
 $\Psi_i$ is the $i^\mathrm{th}$ column of $\Psi$.
-The ideal subject represents one who has precise knowledge of every stimulus and where the reconstruction algorithm mirrors \ref{eq:linreg}.
+The ideal subject represents an \textit{upper bound} on task performance,
+where the subject has precise knowledge of every stimulus and where the reconstruction algorithm mirrors the subject response model assumed by RC.
 
@@
 where $X \in [0, 1]$ is a uniform random variable.
+The random subject represents a \textit{lower bound} on task performance,
+where the subject ignores any knowledge of the stimulus, or indeed their own internal representation.
 
+% ACL, DONE
 \section{Results}
@@
 with some accuracies approaching those from ideal subject responses.
-Mean accuracy from the random subject responses was $0$ in all conditions,
-while mean accuracy from human responses was significantly different from $0$ in all conditions: buzzing: $t(9) = 5.766$, $p < 0.001$; roaring: $t(9) = 5.76$, $p < 0.001$; combined: $t(19) = 7.542$, $p < 0.001$.
-The buzzing results vary more than the roaring results. The buzzing ground truth spectrum contains significant high-frequency content,
-suggesting that the task may be more difficult for subjects with minor high-frequency hearing loss.
-Figure \ref{fig:spectra} plots example reconstructions from human responses with the best reconstruction accuracies overlaid on the target sound spectra,
+Accuracy from the random subject was $0.00 \pm 0.44$ (mean $\pm$ st.dev.) for buzzing and $0.00 \pm 0.39$ for roaring,
+while mean accuracy from human responses was significantly different from $0$ in all conditions:
+buzzing: $0.52 \pm 0.27$, $t(9) = 5.766$, $p < 0.001$;
+roaring: $0.62 \pm 0.23$, $t(9) = 5.76$, $p < 0.001$;
+combined: $0.57 \pm 0.25$, $t(19) = 7.542$, $p < 0.001$.
+From Figure \ref{fig:reconstructions},
+it appears that the distribution of buzzing results differs from that of the roaring results,
+however the difference between buzzing and roaring is not statistically significant
+(two-way ANOVA across subjects ($F(13) = 2.94$, $p > 0.05$) and target signals ($F(1) = 2.44$, $p > 0.05$)).
+The buzzing ground truth spectrum contains significant high-frequency content,
+suggesting that the task may vary in difficulty for subjects with different audiograms (\ie for subjects with minor high-frequency hearing loss).
+Figure \ref{fig:spectra} shows example reconstructions from the best human responses (as quantified by reconstruction accuracy) overlaid on the target sound spectra,
 showing that those reconstructions capture many of the salient features of the target.
@@
     are shown as violin plots with box plots overlaid.
-    The median is a white dot, the ordinate of the blue points are the Pearson's $r$ values.}
+    The median is a white dot, the ordinate of the blue points are the Pearson's $r$ values.
+    The top row shows accuracies for the buzzing target, the middle row shows accuracies
+    for the roaring target signal, and the bottom row shows results for both buzzing and roaring combined.}
     \label{fig:reconstructions}
@@
     \caption{Reconstructions of the PTS capture many salient features of tinnitus spectra.
+    The left-hand column shows reconstructions for the buzzing target,
+    while the right-hand column shows reconstructions for the roaring target.
     On each set of axes, the black trace indicates the target,
@@
     to a $11025$-dimensional frequency domain.
-    The unbinned power spectral density of the targets is also shown in gray.}
+    In the bottom row, the unbinned power spectral densities (ground-truth) of the target signals are shown in gray.}
     \label{fig:spectra}
@@
 
+% ACL, DONE
 \section{Conclusion}
@@
 % Promise
-Our results show that RC can accurately reconstruct the frequency spectrum of complex, non-tonal tinnitus-like sounds.
-This indicates that RC may also be useful for developing a clinical assay to characterize a wider variety of tinnitus percepts than currently possible.
-RC is purely behavioral, requires no specialized equipment, and has marginal setup.
+Our results show that RC can accurately reconstruct the frequency spectrum of certain relevant non-tonal tinnitus sounds.
+This indicates that RC may also be useful for characterizing the sounds experienced by patients with non-tonal forms of tinnitus,
+for whom existing tinnitus characterization methods are ill-suited.
+As such, this study may represent the first step in the development of a clinical assay to characterize a wider variety of tinnitus percepts than currently possible.
+The clinical utility of RC is further reinforced by its practical advantages,
+as an approach that is purely behavioral, requires no specialized equipment, and has a marginal setup time.
 Moreover, subjects in the present study were able to complete the required number of trials within 20 minutes,
-indicating that this procedure could be conducted in a single clinical visit.
-Future work will focus on validating this approach in patients suffering from tinnitus.
+indicating that this procedure is feasible as an assay that could be conducted in a single clinical visit.
+Future work will focus on validating this approach with larger sample sizes, with more target signals,
+stricter sound pressure level (SPL) control,
+and in patients suffering from tinnitus.
 
@@
 Reconstruction accuracies observed here are well below those provided by an ideal subject's responses,
-which may be attributed to noisy human response characteristics universally observed in applications of RC.
-This may be mitigated by optimizing the experimental protocol, stimulus generation, and reconstruction method.
-For example, recent approaches to improving RC reconstruction methods have been shown to boost efficiency, noise robustness and overall accuracy \cite{roopCompressiveSensingApproach2021,comptonStimulusWhiteningImproves2022a},
+which may be attributed to noisy human response characteristics.
+Whereas noisy responses are universally observed in applications of RC,
+this situation may nonetheless be improved by optimizing the experimental protocol, stimulus generation, and reconstruction method,
+none of which are guaranteed optimal in this early-stage validation study.
+For example, recent approaches to improving RC reconstruction methods have been shown to boost the efficiency, noise robustness and overall accuracy of RC
+\cite{roopCompressiveSensingApproach2021,comptonStimulusWhiteningImproves2022a},
 and may also be applicable in the context of tinnitus.
@@
 % \\
+\vspace{18pt}
+\textsc{Acknowledgment}
+\par A. H. thanks Drs. Srinivas Gorur-Shandilya and Mark Zielinski for informative discussions regarding data visualization.
 % \\
@@
 \bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv,mybib}
+\bibliography{IEEEabrv,mybib_preprint}
 % \printbibliography

### 2023-03-29 code/stimulus_generation/@PowerDistributionStimulusGeneration/build_distribution.m
Bug fix

@@ -47,6 +47,7 @@ function [distribution] = build_distribution(self, save_path)
     pxx = abs(Y(1:Fs_file/2 + 1));
     
     power_spectra = zeros(length(pxx), length(filenames));
+    power_spectra(:, 1) = 10*log10(pxx);
 
     for ii = 2:length(filenames)
         [y, Fs_file] = audioread(pathlib.join(sound_dir, filenames{ii}));

### 2023-05-23 code/scripts/patient_reconstructions.m
Set knn flag to false, update k_vals

@@ -233,12 +233,12 @@ T = table(bal_accuracy, accuracy, sensitivity, specificity, yesses, ...
 
 % Prediction settings
 folds = 5;
-knn = true;
+knn = false;
 mean_zero = true;
 from_responses = false;
 gs_ridge = true;
 thresh_vals = linspace(10,90,200);
-k_vals = 1:2:25;
+k_vals = 1:2:15;
 
 % Initialize
 pred_acc_cs = zeros(n,1);

### 2023-05-23 paper/main_ojemb.tex
Fix main_objem.tex --> main_ojemb.tex

--- 2023-03-29 paper/short/main_wc995.tex
@@
   % declare the path(s) where your graphic files are
-  \graphicspath{{gfx}}
+  \graphicspath{{gfx_ojemb}}
   % and their extensions so you won't have to specify these with
@@
   \centering
-  \includegraphics[width=\linewidth]{gfx/fig1.pdf}
+  \includegraphics[width=\linewidth]{gfx_ojemb/fig1.pdf}
   \caption{Diagram of the experimental protocol.
@@
     \centering
-    \includegraphics[width=\linewidth]{gfx/reconstruction_violin_cropped.pdf}
+    \includegraphics[width=\linewidth]{gfx_ojemb/reconstruction_violin_cropped.pdf}
     \caption{Human reconstruction accuracy is significantly above baseline,
@@
     \centering
-    \includegraphics[width=\linewidth]{gfx/reconstruction_spectra_cropped.pdf}
+    \includegraphics[width=\linewidth]{gfx_ojemb/reconstruction_spectra_cropped.pdf}
     \caption{Reconstructions of the tinnitus spectra capture many salient features of the target sounds.
@@
 \bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv,mybib}
+\bibliography{IEEEabrv,mybib_ojemb}
 % \printbibliography

### 2023-05-23 code/utils/cs.m
Documentation touchups and delete empty files

@@ -23,6 +23,7 @@
 %       a flag to print information messages
 % 
 % **OUTPUTS:**
+% 
 %   - x: `m x 1` vector,
 %       representing the compressed sensing reconstruction of the signal.
 

### 2023-05-23 code/utils/disp_fullscreen.m

@@ -2,13 +2,13 @@
 % 
 % Fill full screen figure with new image.
 % 
-% **Arguments:**
+% **ARGUMENTS:**
 % 
 %   - img: image loaded via imread()
 %   - hFig: handle to maximized figure. 
 %       Defaults to current figure handle.
 % 
-% **Outputs:**
+% **OUTPUTS:**
 % 
 %   - hFig now displays an image.
 

### 2023-05-23 code/utils/get_highest_power_of_2.m

@@ -10,11 +10,12 @@
 % ```
 % 
 % **ARGUMENTS:**
+% 
 %   - N: a 1x1 scalar, positive, real integer
 % 
 % **OUTPUTS:**
-%   - n: a 1x1 scalar, positive, real power of 2
 % 
+%   - n: a 1x1 scalar, positive, real power of 2
 
 function n = get_highest_power_of_2(N)
 

### 2023-05-23 code/utils/get_reconstruction.m

@@ -3,6 +3,11 @@
 % Compute reconstructions using data specified
 % by a configuration file.
 % 
+% ```matlab
+% [x, responses_output, stimuli_matrix_output] = get_reconstruction('key', value, ...)
+% x = get_reconstruction('config_file', 'path_to_config', 'preprocessing', {'bit_flip'}, 'method', 'cs', 'verbose', true)
+% ```
+% 
 % **ARGUMENTS:**
 % 
 %   - config_file: string or character array, name-value, default: ``''``
@@ -16,18 +21,14 @@
 %       Currently, the only supported preprocessing step is ``'bit flip'``,
 %       which flips the sign on all responses before computing the reconstruction.
 %   - method: character vector, name-value, default: ``'cs'``
-%       Which reconstruction algorithm to use.
+%       Which reconstruction algorithm to use. 
+%       Options: ``'cs'``, ``'cs_nb'``, ``'linear'`, ``'linear_ridge'``.
 %   - use_n_trials: Positive scalar, name-value, default: `inf`
 %       Indicates how many trials to use of data. `inf` uses all data.
 %   - bootstrap: Positive scalar, name-value, deafult: 0
 %       Number of bootstrap iterations to perform.
 % 
-% ```matlab
-% [x, responses_output, stimuli_matrix_output] = get_reconstruction('key', value, ...)
-% x = get_reconstruction('config_file', 'path_to_config', 'preprocessing', {'bit_flip'}, 'method', 'cs', 'verbose', true)
-% ```
 % 
-% Compute the reconstruction, given the response vector and the stimuli matrix with a preprocessing step and a method chosen from {'cs', 'cs_nb', 'linear'}
 % 
 % See Also: 
 % collect_reconstructions

### 2023-05-23 code/utils/munge_hashes.m

@@ -1,8 +1,12 @@
 % ### munge_hashes
+% 
 % Processes config files, correcting errors.
 % Then, fixes the hashes for saved data files
 % associated with changed config files.
 % 
+% ```matlab
+%   munge_hashes("file_string", "config*.yaml", "verbose", true)
+% ```
 % 
 % **Arguments:**
 % 
@@ -20,11 +24,6 @@
 %   - data_dir: ``string`` or ``character vector``, name-value, default: ``"."``  
 %   Path to the directory where the data files to-be-munged are.
 % 
-% **Example:**
-% 
-% ```matlab
-%   munge_hashes("file_string", "config*.yaml", "verbose", true)
-% ```
 % **See Also:**
 % update_hashes
 

### 2023-05-23 code/utils/parse_config.m

@@ -4,20 +4,20 @@
 % 
 % **ARGUMENTS:**
 % 
-%     config_file: character vector, default: []
+%   - config_file: character vector, default: []
 %         Path to the config file to be used.
 %         If empty, opens a GUI to find the file using a file browser.
 % 
 % **OUTPUTS:**
 % 
-%     varargout: `1 x 2` cell array:
+%   - varargout: `1 x 2` cell array:
 %         varargout{1} = config: `struct`, the parsed config file.
 %         varargout{2} = config_file OR abs_path, `char`,
 %             if path provided, return the path, else return path chosen
 %             from GUI.
 % 
 % See Also: 
-% * yaml.loadFile
+% yaml.loadFile
 
 function varargout = parse_config(config_file,legacy, verbose)
 

### 2023-05-23 code/utils/r_viz.m

@@ -8,6 +8,7 @@
 %   - T: `table` that includes r values of interest
 % 
 % **OUTPUTS:**
+% 
 %   - n figures, where n is the number of subjects included
 %       in the table.
 % 
